### 2015-02-19 ms.tex
Very basic outline

%\documentclass[]{aastex}
\documentclass{emulateapj}
%\documentclass[]{emulateapj}

\bibliographystyle{apj}
\usepackage{subfigure}
\usepackage{url}
\usepackage{hyperref}
\usepackage{datetime}
\usepackage{longtable}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{ulem}
\usepackage{bm}
\usepackage[usenames,dvipsnames]{xcolor}

%\usepackage{pdflscape}

% FIGSET-MACROS-BEGIN
\newcommand{\noprint}[1]{}
\newcommand{\figsetstart}{{\bf Fig. Set} }
\newcommand{\figsetend}{}
\newcommand{\figsetgrpstart}{}
\newcommand{\figsetgrpend}{}
\newcommand{\figsetnum}[1]{{\bf #1.}}
\newcommand{\figsettitle}[1]{ {\bf #1} }
\newcommand{\figsetgrpnum}[1]{\noprint{#1}}
\newcommand{\figsetgrptitle}[1]{\noprint{#1}}
\newcommand{\figsetplot}[1]{\noprint{#1}}
\newcommand{\figsetgrpnote}[1]{\noprint{#1}}
% FIGSET-MACROS-END
\usepackage{color}

\newcommand{\ron}{\color{red}} 
\newcommand{\bon}{\color{blue}} 
\newcommand{\gon}{\color{green}} 
\newcommand{\coff}{\color{black}\,}

\newcommand{\rprs}{{$R_p/R_{\star}$}}

\newcommand{\eg}{{\it e.g.}}
\newcommand{\ie}{{\it i.e.}}
\newcommand{\project}[1]{\textsl{#1}} 
\newcommand{\kep}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\vsini}{{$V \sin i$}}
\newcommand{\teff}{$T_{\rm eff}$}
\newcommand{\kms}{{km\,s$^{-1}$}}
\newcommand{\gcc}{{g\,cm$^{-3}$}}
\newcommand{\rstar}{{$R_\star$}}
\newcommand{\rhostar}{{$\rho_\star$}}
\newcommand{\mearth}{{M$_\oplus$}}
\newcommand{\rearth}{{R$_\oplus$}}
\newcommand{\rsun}{{R$_\odot$}}
\newcommand{\msun}{{M$_\odot$}}
\newcommand{\mjup}{{M$_\textrm{Jup}$}}
\newcommand{\rjup}{{R$_\textrm{Jup}$}}
\newcommand{\LA}{{LHS\,6343\,A}}
\newcommand{\LB}{{LHS\,6343\,B}}
\newcommand{\LC}{{LHS\,6343\,C}}
\newcommand{\LHS}{{LHS\,6343}}

\newcommand{\mstar}{{$M_\star$}}
\newcommand{\logg}{{log(g)}}
\newcommand{\mh}{{[M/H]}~}
\newcommand{\feh}{{[Fe/H]}~}

\newcommand{\is}{importance sampling}
\newcommand{\Is}{Importance sampling}
%\newcommand{\h2ok2}{{$\rm H_2O-K2$}}

\newcommand{\todo}[3]{{\color{#2} \emph{#1} TO DO: #3}}
\newcommand{\btmtodo}[1]{\todo{BEN}{red}{#1}}

\begin{document}
\title{(Working Title) Properties of the \KT\ Campaign 1 Planets, 
False Positive Probabilities, and Confirmation of $N$ Systems. You 
Were Warned it's a Working Title.}

\author{
% The Heavy Lifters
Benjamin T. Montet\altaffilmark{1,2}, 
Daniel Foreman-Mackey\altaffilmark{3},
Timothy D. Morton,
% The Benefactors
John Asher Johnson,
David W. Hogg,
% The Observers, as individuals
Brendan P. Bowler,
Andrew W. Mann,
David W. Latham,
% The observers, as a group
And Whoever DaveL Tells Us to Add as TRES Team Members
}

\email{btm@astro.caltech.edu}

\altaffiltext{1}{Cahill Center for Astronomy and Astrophysics, California Institute of Technology, 1200 E. California Blvd., MC 249-17, Pasadena, CA 91106, USA}
\altaffiltext{2}{Harvard-Smithsonian Center for Astrophysics, 60 Garden
Street, Cambridge, MA 02138, USA}
\altaffiltext{3}{Department of Astronomy, University of Michigan, Ann Arbor, MI 48109, USA}

\date{\today, \currenttime}

\begin{abstract}
\btmtodo{This is where the abstract will go}
\end{abstract}

\keywords{\btmtodo{Keywords}}

\maketitle

\section{Introduction}

\section{Stellar Properties}
\subsection{Photometry}

\subsection{SpeX Spectroscopy}

\section{False Positive Analysis}
\subsection{Adaptive Optics Imaging}

\subsection{Archival Imaging}

\subsection{Known Background Stars}

\subsection{False Positive Rates (and confirmations?)}
This is Tim.

\section{Potentially Interesting Systems}
\subsection{The One Around the M dwarf}

\subsection{Some Multi (possible multi of these}

\subsection{Others? Really bright ones amenable to followup?}

\section{Results and Discussion}

Something about Multis and TTVs.

\acknowledgements
We thank [People] for [things] which improved the quality of this manuscript.

We are grateful to the entire Kepler team, past and present. 
Their tireless efforts were all essential to the tremendous success of the mission and the successes of K2, present and future.

Some of the data presented in this paper were obtained from the Mikulski
Archive for Space Telescopes (MAST). 
STScI is operated by the Association of Universities for Research 
in Astronomy, Inc., under NASA contract NAS5--26555. 
for MAST for non--HST data is provided by the NASA Office of Space 
Science via grant NNX13AC07G and by other grants and contracts. 
This paper includes data collected by the \kep\ mission. 
Funding for the \kep\ mission is provided by the NASA Science 
Mission directorate.

B.T.M. is supported by the National Science Foundation Graduate Research
Fellowship under Grant No. DGE‐1144469. 
J.A.J. is supported by generous grants from the David and Lucile Packard
Foundation and the Alfred P. Sloan Foundation.

{\it Facilities:} \facility{Kepler}

\bibliography{planetspapers}

\end{document}

### 2015-02-23 ms.tex
bib file

@@
+% The rules:
+% I guess same as DFM because he'll complain if we don't use the 
+% character limit.
+% New sentences on each line.
+% Citation format is \citet{AuthornameYY}.
+% References go into papers.bib alphabetically, with ties broken
+% chronologically.
+
 %\documentclass[]{aastex}
@@
 \newcommand{\rjup}{{R$_\textrm{Jup}$}}
-\newcommand{\LA}{{LHS\,6343\,A}}
-\newcommand{\LB}{{LHS\,6343\,B}}
-\newcommand{\LC}{{LHS\,6343\,C}}
-\newcommand{\LHS}{{LHS\,6343}}
 
@@
 \newcommand{\feh}{{[Fe/H]}~}
+\newcommand{\afe}{{[$\alpha$/Fe]}~}
 
@@
 
+With the exception of one star in our sample (EPIC 201912552), we do not have
+spectroscopic data with which to characterize the stellar properties. 
+Instead, we rely on photometry.
+For each system, we query the VizieR database of astronomical catalogues
+\citep{Ochseinbein00}. 
+We record the $B$, $V$, $g'$, $r'$, and $i'$ magnitudes and their
+uncertainties from the AAVSO Photometric all-sky survey (APASS) DR6 
+\btmtodo{Cite: Who?}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
+We also record the $J$, $H$, and $K$ magnitudes and their uncertainties 
+as found in the 2MASS All-Sky Catalog of Point Sources \citep{Cutri03}
+and the four WISE magnitudes and uncertainties from the ALLWise Data
+Release \citep{Cutri13}.
+For all except two of our targets, the $W4$ band is only an upper limit.
+These data are reported in Table \ref{Tab:Photometry}.
+
+\btmtodo{Make this table!}
+
+\subsection{Stellar Models}
+To convert the observed photometric data into physical properties for each
+star, we employ the use of two stellar models. 
+We first download the isochrone grids from the 2012 updated photometric
+systems for the relevant bandpasses from the Dartmouth Stellar Evolution
+Database \citep{Dotter08}. 
+We then interpolate the isochrones onto a grid uniformly spaced in
+stellar mass (from 0.20 to 2.0 \msun), metallicity (from \feh$=-1.5$ to 
+\feh$=+0.5$), age (from 1.0 to 14.0 Gyr), and log distance (from 10 pc to 
+1000 pc). 
+In our interpolation, we assume \afe$=0.0$ and $Y=0.2741$, the solar value.
+We then compare the expected apparent magnitudes to our observed photometry
+to measure the likelihood of each grid point.
+For each parameter, we then marginalize our likelihood over all other 
+parameters in order to estimate the value of the physical properties
+for each star.
+
+Such a scheme enables us to infer the statistical uncertainties on the
+mass, radius, and effective temperature.
+However, we remain ignorant of any systematic uncertainties that may be
+induced by our reliance on the Dartmouth models.
+To this end, we repeat this procedure with the Padova database of stellar
+evolutionary tracks and isochrones \btmtodo{Cite: Who? Claims to be in
+file headers}. 
+Comparing two models will not help us understand any systematic errors
+of the two are biased in the same way, but in general it will allow us
+to calculate a more accurate assessment of our true uncertainties than 
+relying on one model alone.
+
 \subsection{SpeX Spectroscopy}
@@
 
-{\it Facilities:} \facility{Kepler}
+{\it Facilities:} \facility{Kepler}%, \btmtodo{More...}
 
-\bibliography{planetspapers}
+\bibliography{exopapers}
 

### 2015-02-23 ms.tex
Updates from ShareLaTeX
More text.

@@
 
+\btmtodo{Padova parameters, information}
+
+\btmtodo{Show plot}
+
+The Padova models consistently produce radii which are \btmtodo{VALUE\%} 
+larger than those predicted by the Dartmouth models. 
+There is some evidence that the Dartmouth models may underpredict 
+radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
+Montet15}. 
+Given that these stars form the majority of our sample, this discrepancy
+is perhaps not surprising.
+
+\btmtodo{Then we combine them into one set of stellar properties?}
+
 \subsection{SpeX Spectroscopy}

### 2015-02-24 fpp/k2fpp.py
added starmodels example notebook

@@ -1,0 +1,26 @@
+from __future__ import print_function, division
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+import logging
+
+import os,os.path,sys,re
+
+import parse_tables as pt
+
+MAGS = pt.mag_table()
+DARTMOUTH_PARS = pt.dartmouth_table()
+PADOVA_PARS = pt.padova_table()
+PAPER1_TABLE = pt.paper1_table()
+
+def mags(epic_id):
+    """returns dictionary of magnitudes
+    """
+    s = MAGS.ix[epic_id]
+    d = {b:s[b] for b in s.index}
+    del d['name']
+    return d
+
+    

### 2015-02-24 fpp/parse_tables.py

@@ -1,0 +1,64 @@
+from __future__ import print_function, division
+import re,sys,os
+import pandas as pd
+
+def parse_value(entry):
+    """parse latex table entry = number +/- stuff
+    """
+    m = re.search('\$\s*(\d+\.?\d+)_\{-(\d+\.?\d+)\}\^\{\+(\d+\.?\d+)\}\s*\$',entry)
+    if m:
+        return float(m.group(1)), float(m.group(2)), float(m.group(3))
+
+def paper1_table(filename='paper1_tab-cand.tex'):
+    epic_id = []
+    ra = []
+    dec = []
+    period = []
+    epoch = []
+    rprs = []
+    for line in open(filename):
+        if re.search('EPIC', line):
+            continue
+        line = line.split('&')
+        if len(line) < 6:
+            continue
+        epic_id.append(int(line[0]))
+        ra.append(float(line[1]))
+        dec.append(float(line[2]))
+        per, lo, hi = parse_value(line[3])
+        period.append(per)
+        ep, lo, hi = parse_value(line[4])
+        epoch.append(ep)
+        r, lo, hi = parse_value(line[5])
+        rprs.append(r)
+    df = pd.DataFrame({'epic_id':epic_id,
+                         'ra':ra,
+                         'dec':dec,
+                         'period':period,
+                         'epoch':epoch,
+                         'rprs':rprs})
+    df.index = df['epic_id']
+    return df
+
+def padova_table(filename='../padova_params.txt'):
+    df = pd.read_table(filename, delim_whitespace=True, skiprows=1,
+                       names=['epic_id','teff','e_teff',
+                              'radius','e_radius','distance',
+                              'e_distance','mass','e_mass',
+                              'feh','e_feh'])
+    df.index = df['epic_id'].astype(int)
+    return df
+
+def dartmouth_table(filename='../dartmouth_params.txt'):
+    df = pd.read_table(filename, delim_whitespace=True, skiprows=1,
+                       names=['epic_id','teff','e_teff',
+                              'radius','e_radius','distance',
+                              'e_distance','mass','e_mass',
+                              'feh','e_feh'])
+    df.index = df['epic_id'].astype(int)
+    return df
+
+def mag_table(filename='../table_photometry.txt'):
+    df = pd.read_table(filename, delim_whitespace=True)
+    df.index = df['name']
+    return df

### 2015-02-24 ms.tex

--- 2015-02-23 ms.tex
@@
 \newcommand{\vsini}{{$V \sin i$}}
-\newcommand{\teff}{$T_{\rm eff}$}
+\newcommand\teff{\ensuremath{T_\text{eff}}}
 \newcommand{\kms}{{km\,s$^{-1}$}}
@@
 To convert the observed photometric data into physical properties for each
-star, we employ the use of two stellar models. 
+star, we employ the use of stellar models. 
 We first download the isochrone grids from the 2012 updated photometric
@@
 mass, radius, and effective temperature.
-However, we remain ignorant of any systematic uncertainties that may be
-induced by our reliance on the Dartmouth models.
-To this end, we repeat this procedure with the Padova database of stellar
-evolutionary tracks and isochrones \btmtodo{Cite: Who? Claims to be in
-file headers}. 
-Comparing two models will not help us understand any systematic errors
-of the two are biased in the same way, but in general it will allow us
-to calculate a more accurate assessment of our true uncertainties than 
-relying on one model alone.
+However, we are subject to biases induced by systematics in the models themselves.
+There is some evidence that the Dartmouth models may underpredict 
+radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
+Montet15}. 
+Such an effect may be the result of the Dartmouth model reliance on BT-Settl
+atmospheres, which have been shown to predict near-IR colors that are too blue
+\citep{Thompson14}.
+We find that by measuring stellar parameters without any WISE data (that is, using
+only $BVgriJHK$), we largely reproduce the same effective temperatures as when
+the WISE data is included. 
+However, at the low-mass end including the WISE data systematically increases the 
+measured radius and increases \logg, as shown in \btmtodo{Figure}.
+Suggestively, spectroscopic stellar parameters of EPIC 201912552 
+(\textsection\ref{Spexobs}) suggest the derived photometric properties better 
+represent the true physical parameters when the WISE data is included.
+
+\btmtodo{Show plot}
 
 \subsection{SpeX Spectroscopy}
+\label{Spexobs}
+
+\btmtodo{Some of Mann's references aren't in his .bib file. Fix.}
+
+A near-infrared spectrum of EPIC 201912552 was obtained using the updated SpeX 
+(uSpeX) spectrograph \citep{Rayner03} on the NASA Infrared Telescope Facility 
+(IRTF) on January 29 2015 (UT). 
+SpeX observations were taking using the short cross-dispersed mode and the
+0.3$\times15\arcsec$ slit, which provides simultaneous coverage from 0.7 
+to 2.5$\mu$m at $R\simeq2000$. 
+The target was observed at two positions along the slit to subsequently subtract 
+the sky background. Eight spectra were taking following this pattern, which provided 
+a final S/N of $>150$ per resolving element. 
+The spectrum was flat fielded, extracted, wavelength calibrated, and stacked 
+using the \textit{SpeXTool} package \citep{Cushing:2004}. 
+An A0V-type star was observed immediately after 
+the target, which was used to create a telluric correction using the 
+\textit{xtellcor} package \citep{Vacca:2003}.
+
+An optical spectrum was obtained using the SuperNova Integral Field Spectrograph
+\citep[SNIFS,][]{2002SPIE.4836...61A,Lantz:2004} on the University of Hawai'i 
+2.2m telescope on the night of January 30 2015. 
+SNIFS provides simultaneous coverage from 3200\AA--9700\,AA\ at a resolution 
+of $\simeq1000$. Final S/N of the spectrum was $>100$ pre resolving element 
+in the red ($\sim6000$\AA). 
+Details of the SNIFS reduction, including dark, bias, and flat-field corrections,
+cleaning the data of bad pixels and cosmic rays, and extraction of the 
+one-dimensional spectrum are  described in \citet{Bacon:2001} and 
+\citet{Aldering:2006}. 
+Flux calibration was performed using a separate pipeline described in \citet{Mann2015}.
+
+\teff\ was calculated by comparing our optical spectra with the CFIST
+suite\footnote{http://phoenix.ens-lyon.fr/Grids/BT-Settl/CIFIST2011/} of the BT-SETTL
+version of the PHOENIX atmosphere models \citep{Allard:2013}, which gave a temperature
+of 3503 $\pm$ 60\,K. 
+More details of this procedure are given in \citet{2013ApJ...779..188M} and
+\citet{2014MNRAS.443.2561G}. 
+This method was used because it is known to accurately reproduce empirical 
+\teff\ values from long-baseline optical interferometry \citet{Boyajian2012}.
+
+Metallcity was determined using the procedures from \citet{Mann2013a}. 
+\citet{Mann2013a} provide empirical relations between atomic features and M dwarf
+metallicity, calibrated using wide binaries. 
+We adopted the weighted mean of the $H-$ and $K-$band calibrations, 
+which yielded a metallicity of 0.09$\pm$0.09.
+
+We combined the derived \teff\ and [Fe/H] values with the empirical 
+\teff-[Fe/H]-$R_*$ relation from \citet{Mann2015} to compute a radius. 
+Accounting for measurement and calibration errors in [Fe/H] and \teff\ we calculated 
+a radius 0.394$\pm0.038R_\odot$. 
+We use these parameters instead of the derived photometric properties for this target.
 
@@
 \subsection{Known Background Stars}
+
+\subsection{TRES Radial Velocities}
 
@@
 
-\bibliography{exopapers}
+\bibliography{exopapers; mannbib}
 

### 2015-02-25 ms.tex
Mann references

@@
 False Positive Probabilities, and Confirmation of $N$ Systems. You 
-Were Warned it's a Working Title.}
+Were Warned: it's a Working Title.}
 
@@
 The spectrum was flat fielded, extracted, wavelength calibrated, and stacked 
-using the \textit{SpeXTool} package \citep{Cushing:2004}. 
+using the \textit{SpeXTool} package \citep{Cushing04}. 
 An A0V-type star was observed immediately after 
 the target, which was used to create a telluric correction using the 
-\textit{xtellcor} package \citep{Vacca:2003}.
+\textit{xtellcor} package \citep{Vacca03}.
 
 An optical spectrum was obtained using the SuperNova Integral Field Spectrograph
-\citep[SNIFS,][]{2002SPIE.4836...61A,Lantz:2004} on the University of Hawai'i 
+\citep[SNIFS,][]{Aldering02,Lantz04} on the University of Hawai'i 
 2.2m telescope on the night of January 30 2015. 
@@
 cleaning the data of bad pixels and cosmic rays, and extraction of the 
-one-dimensional spectrum are  described in \citet{Bacon:2001} and 
-\citet{Aldering:2006}. 
-Flux calibration was performed using a separate pipeline described in \citet{Mann2015}.
+one-dimensional spectrum are described in \citet{Bacon01} and 
+\citet{Aldering06}. 
+Flux calibration was performed using a separate pipeline described in \citet{Mann15}.
 
@@
 suite\footnote{http://phoenix.ens-lyon.fr/Grids/BT-Settl/CIFIST2011/} of the BT-SETTL
-version of the PHOENIX atmosphere models \citep{Allard:2013}, which gave a temperature
+version of the PHOENIX atmosphere models \citep{Allard13}, which gave a temperature
 of 3503 $\pm$ 60\,K. 
-More details of this procedure are given in \citet{2013ApJ...779..188M} and
-\citet{2014MNRAS.443.2561G}. 
+More details of this procedure are given in \citet{Mann14} and
+\citet{Gaidos14}. 
 This method was used because it is known to accurately reproduce empirical 
-\teff\ values from long-baseline optical interferometry \citet{Boyajian2012}.
+\teff\ values from long-baseline optical interferometry \citet{Boyajian12}.
 
-Metallcity was determined using the procedures from \citet{Mann2013a}. 
-\citet{Mann2013a} provide empirical relations between atomic features and M dwarf
+Metallcity was determined using the procedures from \citet{Mann13a}, in which the
+authors provide empirical relations between atomic features and M dwarf
 metallicity, calibrated using wide binaries. 
@@
 We combined the derived \teff\ and [Fe/H] values with the empirical 
-\teff-[Fe/H]-$R_*$ relation from \citet{Mann2015} to compute a radius. 
+\teff-[Fe/H]-$R_*$ relation from \citet{Mann15} to compute a radius. 
 Accounting for measurement and calibration errors in [Fe/H] and \teff\ we calculated 
@@
 
-\bibliography{exopapers; mannbib}
+\bibliography{exopapers}
 

### 2015-02-26 ms.tex
Started 3.2

@@
 \btmtodo{This is where the abstract will go}
+Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
+hosting a \btmtodo{Radius} planet with $T_{eq} = $\btmtodo{Temp} and an 
+orbital period of 33 days.
 \end{abstract}
@@
 
-\btmtodo{Some of Mann's references aren't in his .bib file. Fix.}
-
 A near-infrared spectrum of EPIC 201912552 was obtained using the updated SpeX 
@@
 
+This is Brendan.
+
+\subsection{Known Background Stars}
+The P3K AO system has a field of view of $3.84 \times 3.84$ arcseconds.
+\btmtodo{Check with Brendan to make sure he used this mode}.
+Each \KT\ pixel is a square of $3.98 \times 3.98$ arcseconds. 
+A background eclipsing binary within a few \KT\ pixels of our target 
+stars could mimic a transit signal while evading detection by P3K.
+Such wide eclipsing binaries should appear in seeing-limited ground-based
+surveys.
+
+To investigate the possibility that such wide companions exist,
+we query the ninth data release of the Sloan Digital Sky Survey 
+\citep[SDSS DR9,][]{Ahn12}. For each target, we return
+all stars within 12\arcsec with $\Delta r < 8$ relative to each object
+of interest.
+
 \subsection{Archival Imaging}
 
-\subsection{Known Background Stars}
+This is Ben.
 
@@
 Science via grant NNX13AC07G and by other grants and contracts.
+
 This paper includes data collected by the \kep\ mission. 
@@
 Mission directorate.
+
+This paper includes data collected by the Sloan Digital Sky Survey.
+Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation,
+the Participating Institutions, the National Science Foundation, and the
+U.S. Department of Energy Office of Science. The SDSS-III web site is
+http://www.sdss3.org/.
+SDSS-III is managed by the Astrophysical Research Consortium for the
+Participating Institutions of the SDSS-III Collaboration including the
+University of Arizona, the Brazilian Participation Group, Brookhaven
+National Laboratory, Carnegie Mellon University, University of Florida,
+the French Participation Group, the German Participation Group, Harvard
+University, the Instituto de Astrofisica de Canarias, the Michigan
+State/Notre Dame/JINA Participation Group, Johns Hopkins University,
+Lawrence Berkeley National Laboratory, Max Planck Institute for
+Astrophysics, Max Planck Institute for Extraterrestrial Physics, New
+Mexico State University, New York University, Ohio State University,
+Pennsylvania State University, University of Portsmouth, Princeton
+University, the Spanish Participation Group, University of Tokyo,
+University of Utah, Vanderbilt University, University of Virginia,
+University of Washington, and Yale University.
 

### 2015-02-26 ms.tex
text tweaks

@@
 
+\newcommand{\paperip}{\citep{Foreman-Mackey15}}
+\newcommand{\paperit}{\citet{Foreman-Mackey15}}
+
 \newcommand{\is}{importance sampling}
@@
 \btmtodo{This is where the abstract will go}
-Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
+Of the 36 planet candidates presented in \paperit{} we confirm 
+\btmtodo{Nconfirm} as planets and \btmtodo{NFP} as false positives
+at the \btmtodo{confidence} level. Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
 hosting a \btmtodo{Radius} planet with $T_{eq} = $\btmtodo{Temp} and an 
@@
 
+\section{Planet Properties}
+
+This is Dan?
+
 \section{False Positive Analysis}

### 2015-02-26 ms.tex
SDSS data...

@@
 David W. Hogg,
-% The Observers, as individuals
+% The Observers, as PIs 
+% (ranked by integration time x collecting area)
 Brendan P. Bowler,
+David W. Latham,
 Andrew W. Mann,
-David W. Latham,
 % The observers, as a group
@@
 we query the ninth data release of the Sloan Digital Sky Survey 
-\citep[SDSS DR9,][]{Ahn12}. For each target, we return
+\citep[SDSS DR9,][]{Ahn12}. 
+For each target, we return
 all stars within 12\arcsec with $\Delta r < 8$ relative to each object
 of interest.
+Of the 31 stars in our sample, four have such a companion.
+Unlike the original \kep\ field, the field for \KT\ Campaign 1 is 
+well out of the galactic plane, so the rate of giant, distanct background
+stars is significantly lower.
+We include a list of these potential contaminants as Table 
+\ref{Table:BGstars}.
+
+%Table:BGstars
+% Primary    RA Dec Separation DeltaR         MaxDepth
+% 201295312  &  &   &          & 7.10 \pm 0.10 & 0.75
+% 201465501  &  &   &          & 7.90 \pm 0.25 & 0.36
+% 201546283  &  &   &          & 5.87 \pm 0.06 & 2.31
+% 201779067  &  &   &          & 4.21 \pm 0.03 & 10.56
+
+In Table \ref{Table:BGstars}, the ``maximum depth'' column represents
+the maximum observed ``transit'' depth if the transit were actually caused
+by a total eclipse of the hypothetical background binary system, inducing
+a 50\% flux decrement in the background star's apparent brightness...
 

### 2015-02-26 ms.tex
SDSS background object text, TRES skeleton

@@
 \newcommand{\btmtodo}[1]{\todo{BEN}{red}{#1}}
+\newcommand{\anytodo}[1]{\todo{ANYONE}{NavyBlue}{#1}}
 
@@
 by a total eclipse of the hypothetical background binary system, inducing
-a 50\% flux decrement in the background star's apparent brightness...
+a 50\% flux decrement in the background star's apparent brightness.
+
+For EPIC 201465501 and 201779067, the observed transit depth is 
+larger than each of these values, so we reject the possibility that
+these events could be the eclipses of the background binaries detected
+here.
+
+For EPIC 201546283, the observed transit depth is nearly identical to 
+the maximum false positive depth. 
+The photometry for this potential contaminant is consistent with that
+of an M3V star; for this object to cause the observed eclipse it must
+be a total eclipse of two M3V stars. 
+However, in that case, the observed event would be exactly V-shaped,
+with second and third contact occurring simultaneously. 
+Since the transit is not V-shaped, it must be the result of
+a relatively small body passing in front of a relatively large body. 
+Therefore, it cannot be caused by this observed background dwarf star.
+
+For EPIC 201295312, the transit depth is significantly shallower than
+the maximum false positive depth, so we cannot immediately
+reject the hypothesis that the transit is actually a false positive 
+induced by a background eclipsing binary. \anytodo{Can we place limits
+on this possibility from the lack of a centroid shift?}
+
+SDSS is 95\% complete at $r=22.2$ and the telescope has a point
+spread function of $1\farcs4$. In all cases except the four above, we 
+treat the SDSS data as providing a contrast curve at wide separations
+down to a limiting magnitude of $r=22.2$.
 
@@
 \subsection{TRES Radial Velocities}
+
+We observed EPIC 201912552 on (all UT) February 04 2015, February 24 2015,
+and February \btmtodo{XX} 2015 with the Tillinghast Reflector Echelle
+Spectrograph (TRES) on the 1.5 m Tillinghast Reflector at the Fred L.
+Whipple Observatory. 
+The spectra were taken with a resolving power of $R=44,000$ and 
+integration times ranging from 2800 to 3600 seconds, resulting in 
+signal-to-noise ratios between 17 and 29 per resolution element.
+
+\anytodo{This will be text from DaveL and/or Allyson Bieryla.}
+
+The observed radial velocities are included in Table \ref{Tab:RVs}.
+
+\btmtodo{RVs table}
+
+%57057.83314
+%57077.75616
 
@@
 
-Something about Multis and TTVs.
+Something about Multis and TTVs will go in here.
+
+\anytodo{We should have a figure of many subplots, of phase-folded
+transits for all the confirmed planets. 
+To ease Dan's mind, we will say that they are the product of 
+some fidicual transit model and are only presented here for illustrative
+purposes.}
 

### 2015-02-27 fpp/k2fpp.py
reorganize; downloaded samples, cannot load them

@@ -1,26 +1,0 @@
-from __future__ import print_function, division
-
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-
-import logging
-
-import os,os.path,sys,re
-
-import parse_tables as pt
-
-MAGS = pt.mag_table()
-DARTMOUTH_PARS = pt.dartmouth_table()
-PADOVA_PARS = pt.padova_table()
-PAPER1_TABLE = pt.paper1_table()
-
-def mags(epic_id):
-    """returns dictionary of magnitudes
-    """
-    s = MAGS.ix[epic_id]
-    d = {b:s[b] for b in s.index}
-    del d['name']
-    return d
-
-    

### 2015-02-27 fpp/k2fpp/photometry.py

@@ -1,0 +1,12 @@
+from __future__ import print_function, division
+
+from .tables import MAGS
+
+def mags(epic_id):
+    """returns dictionary of magnitudes
+    """
+    s = MAGS.ix[epic_id]
+    d = {b:s[b] for b in s.index}
+    del d['name']
+    return d
+

### 2015-02-27 fpp/k2fpp/starmodels.py

@@ -1,0 +1,13 @@
+from __future__ import print_function, division
+
+import numpy as np
+import pandas as pd
+
+from isochrones.starmodel import StarModel
+from isochrones.dartmouth import Dartmouth_Isochrone
+
+DARTMOUTH = Dartmouth_Isochrone()
+
+from k2fpp import mags
+
+def starmodel

### 2015-02-27 fpp/k2fpp/transitsignal.py

@@ -1,0 +1,34 @@
+from __future__ import print_function, division
+
+import numpy as np
+import pandas as pd
+import os, os.path, shutil
+
+import logging
+
+from vespa.transitsignal import TransitSignal_FromSamples
+
+from .tables import PAPER1_TABLE
+
+URLBASE = 'http://bbq.dfm.io/~dfm/research/ketu/trap/'
+SAMPLEDIR = 'samples'
+if not os.path.exists(SAMPLEDIR):
+    os.makedirs(SAMPLEDIR)
+
+def get_samples(epic_id):
+    url = URLBASE + '{:.0f}.h5'.format(epic_id)
+    filename = os.path.join(SAMPLEDIR, '{:.0f}.h5'.format(epic_id))
+
+    try:
+        samples = pd.read_hdf(filename, 'samples')
+    except:
+        logging.error(filename)
+        raise
+        raise RuntimeError('You need to download file.')
+
+    return samples
+
+class TransitSignal(TransitSignal_FromSamples):
+    def __init__(self, epic_id):
+        samples = get_samples(epic_id)
+        

### 2015-02-27 fpp/parse_tables.py

@@ -1,64 +1,0 @@
-from __future__ import print_function, division
-import re,sys,os
-import pandas as pd
-
-def parse_value(entry):
-    """parse latex table entry = number +/- stuff
-    """
-    m = re.search('\$\s*(\d+\.?\d+)_\{-(\d+\.?\d+)\}\^\{\+(\d+\.?\d+)\}\s*\$',entry)
-    if m:
-        return float(m.group(1)), float(m.group(2)), float(m.group(3))
-
-def paper1_table(filename='paper1_tab-cand.tex'):
-    epic_id = []
-    ra = []
-    dec = []
-    period = []
-    epoch = []
-    rprs = []
-    for line in open(filename):
-        if re.search('EPIC', line):
-            continue
-        line = line.split('&')
-        if len(line) < 6:
-            continue
-        epic_id.append(int(line[0]))
-        ra.append(float(line[1]))
-        dec.append(float(line[2]))
-        per, lo, hi = parse_value(line[3])
-        period.append(per)
-        ep, lo, hi = parse_value(line[4])
-        epoch.append(ep)
-        r, lo, hi = parse_value(line[5])
-        rprs.append(r)
-    df = pd.DataFrame({'epic_id':epic_id,
-                         'ra':ra,
-                         'dec':dec,
-                         'period':period,
-                         'epoch':epoch,
-                         'rprs':rprs})
-    df.index = df['epic_id']
-    return df
-
-def padova_table(filename='../padova_params.txt'):
-    df = pd.read_table(filename, delim_whitespace=True, skiprows=1,
-                       names=['epic_id','teff','e_teff',
-                              'radius','e_radius','distance',
-                              'e_distance','mass','e_mass',
-                              'feh','e_feh'])
-    df.index = df['epic_id'].astype(int)
-    return df
-
-def dartmouth_table(filename='../dartmouth_params.txt'):
-    df = pd.read_table(filename, delim_whitespace=True, skiprows=1,
-                       names=['epic_id','teff','e_teff',
-                              'radius','e_radius','distance',
-                              'e_distance','mass','e_mass',
-                              'feh','e_feh'])
-    df.index = df['epic_id'].astype(int)
-    return df
-
-def mag_table(filename='../table_photometry.txt'):
-    df = pd.read_table(filename, delim_whitespace=True)
-    df.index = df['name']
-    return df

### 2015-02-27 fpp/starmodels.py

@@ -1,13 +1,0 @@
-from __future__ import print_function, division
-
-import numpy as np
-import pandas as pd
-
-from isochrones.starmodel import StarModel
-from isochrones.dartmouth import Dartmouth_Isochrone
-
-DARTMOUTH = Dartmouth_Isochrone()
-
-from k2fpp import mags
-
-def starmodel

### 2015-02-27 ms.tex
notes

@@
 
-This is Dan?
+This is Dan.
+
+(Include comment here about how the planet parameters assume no dilution. 
+Except for the two that we have AO detected binaries for, probably?
+Brendan should have us flux ratios by the end of the day.
+In those cases, I suppose we need to include planet properties in both cases
+in which the transit is around either the more or less massive star.)
 
@@
 
-\subsection{Others? Really bright ones amenable to followup?}
+\subsection{Systems Orbiting Bright Stars}
 

### 2015-02-27 ms.tex
Archival imaging words, but not data or figures.

@@
 
-This is Ben.
+For the stars with AO nondetections, there is still the
+possibility that a background binary could be positioned
+directly behind the target star, evading detection.
+The probability is small, given the $0\farcs1$ diffraction limit
+of P200 at $2\mu$m, but nonzero.
+We can rule out the possibility of such chance alignments with 
+archival imaging data.
+
+\btmtodo{Method}
+
+\btmtodo{Plots showing POSS observations.}
+
+For these targets, we can extend our contrast curves to zero 
+present-day orbital separation and rule out the possibility that
+these transit events are caused by background eclipsing binaries.
+By combining present-day seeing-limited photometric survey data, 
+adaptive optics imaging, and archival photometry, the only stellar companions 
+we would not detect would be those that are gravitationally bound to the target 
+star and positioned in their orbits so that their projected separation is
+smaller than the diffraction limit of the P200 telescope.
+Such an alignment would require the orbital inclination of the binary to be 
+nearly $90^\circ$ and the phase $\varpi + \theta \approx \pi/2$ or $3\pi/2$.
+While we cannot fully rule out this possibility, such an alignment is unlikely
+to occur, and highly unlikely to cause enough dilution to call the planetary
+nature of these signals into question.
 

### 2015-02-27 fpp/k2fpp/photometry.py
added starmodels and some other stuff

@@ -2,7 +2,7 @@ from __future__ import print_function, division
 
 from .tables import MAGS
 
-def mags(epic_id):
+def all_mags(epic_id):
     """returns dictionary of magnitudes
     """
     s = MAGS.ix[epic_id]

### 2015-02-27 fpp/k2fpp/starmodels.py

@@ -1,13 +1,47 @@
 from __future__ import print_function, division
 
+import re
 import numpy as np
 import pandas as pd
 
 from isochrones.starmodel import StarModel
 from isochrones.dartmouth import Dartmouth_Isochrone
 
+from .photometry import all_mags
+
 DARTMOUTH = Dartmouth_Isochrone()
 
-from k2fpp import mags
+STARMODEL_DIR = 'starmodels'
 
-def starmodel
+class EPIC_StarModel(StarModel):
+    def __init__(self, epic_id, exclude_bands=['B','V','g','r','i','W4'],
+                 maxAV=0.1, refit=False, **kwargs):
+
+        self.epic_id = epic_id
+
+        filename = os.path.join(STARMODEL_DIR,'{}.h5'.format(epic_id))
+        if os.path.exists(filename) and not refit:
+            self = StarModel.load_hdf(filename)
+            self.epic_id = epic_id #hack-y
+        else:
+            mags = all_mags(epic_id)
+            kws = {}
+            for k,v in mags.items():
+                if re.search('err',k):
+                    continue
+                if k not in exclude_bands:
+                    kws[k] = (v, mags['{}err'.format(k)])
+
+            super(type(self),self).__init__(DARTMOUTH, maxAV=maxAV,
+                                            **kws)
+
+    def save_hdf(self,filename=None, path=''):
+        if filename is None:
+            filename = os.path.join(STARMODEL_DIR,
+                                    '{}.h5'.format(self.epic_id))
+        StarModel.save_hdf(self, filename, path=path)
+
+    @classmethod
+    def load_hdf(cls, filename, path=''):
+        return StarModel.load_hdf(filename, path=path)
+

### 2015-02-27 fpp/k2fpp/transitsignal.py

@@ -2,6 +2,7 @@ from __future__ import print_function, division
 
 import numpy as np
 import pandas as pd
+import h5py
 import os, os.path, shutil
 
 import logging
@@ -11,7 +12,7 @@ from vespa.transitsignal import TransitSignal_FromSamples
 from .tables import PAPER1_TABLE
 
 URLBASE = 'http://bbq.dfm.io/~dfm/research/ketu/trap/'
-SAMPLEDIR = 'samples'
+SAMPLEDIR = 'trap_samples'
 if not os.path.exists(SAMPLEDIR):
     os.makedirs(SAMPLEDIR)
 
@@ -20,15 +21,35 @@ def get_samples(epic_id):
     filename = os.path.join(SAMPLEDIR, '{:.0f}.h5'.format(epic_id))
 
     try:
-        samples = pd.read_hdf(filename, 'samples')
+        f = h5py.File(filename, 'r')
+        samples = f['samples'][...]
+        cols = ["T", "delta", "T_tau", "period", "t0"]
+        if samples.shape[1] > 5:
+            df = []
+            for i in range(0, samples.shape[1], 5):
+                df.append(pd.DataFrame.from_items(zip(cols, 
+                                                      samples[:, i:i+5].T)))
+        else:
+            df = pd.DataFrame.from_items(zip(cols, samples[:, :5].T))
     except:
         logging.error(filename)
         raise
         raise RuntimeError('You need to download file.')
 
-    return samples
+    return df
 
-class TransitSignal(TransitSignal_FromSamples):
-    def __init__(self, epic_id):
+class K2_TransitSignal(TransitSignal_FromSamples):
+    def __init__(self, epic_id, i=None):
         samples = get_samples(epic_id)
         
+        if(samples.shape[1]>5):
+            #integer nunmber must be passed
+            samples = samples[i]
+            period = PAPER1_TABLE.ix[epic_id, 'period'][i]
+        else:
+            period = PAPER1_TABLE.ix[epic_id, 'period']
+
+        super(type(self),self).__init__(period, 
+                                        samples['T'],
+                                        samples['delta'],
+                                        samples['T_tau'])

### 2015-02-27 ms.tex
EPIC 201912552 section. I now have this EPIC memorized. Time for PuppyButtonFace.

@@
 \newcommand{\rprs}{{$R_p/R_{\star}$}}
+\newcommand{\ars}{{$a/R_{\star}$}}
 
@@
 \section{Potentially Interesting Systems}
-\subsection{The One Around the M dwarf}
+\subsection{A Mini-Neptune with Earthlike Insolation}
 
-\subsection{Some Multi (possible multi of these}
+Of particular interest is EPIC 201912552.
+
+By combining archival and modern seeing-limited data with adaptive optics 
+imaging, we can exclude the possibility these transit events are caused by 
+a background eclipsing binary.
+The apparent transits must be caused by an object co-moving with EPIC 201912552;
+radial velocities eliminate the possibility the companion is nonplanetary.
+Therefore, we confirm the planetary nature of this system.
+
+This star is an M2.8 dwarf at a distance of \btmtodo{Distance: around 30 pc}.
+Of our planet candidate hosts, only EPIC 201367065 \citep[originally
+discovered by][]{Crossfield15} is brighter in $K$-band.
+This star is only 0.1 magnitudes fainter in $K$ than GJ\,1214 
+\citep{Charbonneau09}.
+Due to the relative brightness of the host star, this target is likely
+to become a prime target for atmospheric characterization studies
+and is ideal as a target for future space-based missions such as JWST.
+
+Unlike GJ\,1214b, EPIC 201912552b is not highly irradiated. 
+Instead, it is at an reduced semimajor axis \ars$ = 82.1 \pm 8.6$.
+Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 275 \pm 15$
+K, meaning its bulk insolation is similar to that of the Earth's.
+Although the planet is likely too large to be rocky \citep{Rogers14}, 
+its atmosphere is likely to be the focus of many future observations, providing
+a cool analogue to the highly irradiated planets of a similar size found by 
+\kep.
+
+\subsection{EPIC 201465501?}
+Is this a subsection? It's a star with a mass of ~0.2 Msun and a cnadidate with
+a period of 18 days. I suppose it depends on the FPP.
+
+\subsection{An Instrumental False Positive}
+
+EPIC 201555883 was originally listed in \paperit\ as a planet candidate.
+
+\subsection{Multiple Planet Systems}
 

### 2015-02-27 ms.tex
more text

@@
 EPIC 201555883 was originally listed in \paperit\ as a planet candidate.
+After submission of that work, this object of interest was identified as 
+having a transit ephemeris consistent with that of EPIC 201569483, 
+which we identify as a likely eclipsing binary due to the observed transit
+depth \anytodo{Right? Right?}. 
+We conclude the observed transit signal from EPIC 201555883 is likely the result 
+of an instrumental artifact.
+
+Cite \citet{Coughlin14} and \citet{Batalha13} in here.
 
@@
 \acknowledgements
-We thank [People] for [things] which improved the quality of this manuscript.
+We thank [Eric Agol (UW) and Other People] for [things] which improved the quality of this manuscript.
 

### 2015-03-02 fpp/all_starmodels.py
tried fitting starmodels; some worked some did not

@@ -1,0 +1,14 @@
+#!/usr/bin/env python
+from __future__ import print_function, division
+
+from k2fpp.tables import MAGS
+from k2fpp.starmodels import get_starmodel
+
+import logging
+
+for epic_id in MAGS.index:
+    try:
+        mod = get_starmodel(epic_id)
+    except:
+        logging.error('Fit for {} broke.'.format(epic_id))
+

### 2015-03-02 fpp/k2fpp/starmodels.py

@@ -1,8 +1,10 @@
 from __future__ import print_function, division
 
-import re
+import re, os, os.path
 import numpy as np
 import pandas as pd
+
+import logging
 
 from isochrones.starmodel import StarModel
 from isochrones.dartmouth import Dartmouth_Isochrone
@@ -19,21 +21,22 @@ class EPIC_StarModel(StarModel):
 
         self.epic_id = epic_id
 
-        filename = os.path.join(STARMODEL_DIR,'{}.h5'.format(epic_id))
-        if os.path.exists(filename) and not refit:
-            self = StarModel.load_hdf(filename)
-            self.epic_id = epic_id #hack-y
-        else:
-            mags = all_mags(epic_id)
-            kws = {}
-            for k,v in mags.items():
-                if re.search('err',k):
-                    continue
-                if k not in exclude_bands:
-                    kws[k] = (v, mags['{}err'.format(k)])
+        mags = all_mags(epic_id)
+        kws = {}
+        for k,v in mags.items():
+            if re.search('err',k):
+                continue
+            if k not in exclude_bands:
+                kws[k] = (v, mags['{}err'.format(k)])
+                
+        super(type(self),self).__init__(DARTMOUTH, maxAV=maxAV,
+                                        **kws)
 
-            super(type(self),self).__init__(DARTMOUTH, maxAV=maxAV,
-                                            **kws)
+    def fit_mcmc(self, **kwargs):
+        super(type(self),self).fit_mcmc(**kwargs)
+        filename = os.path.join(STARMODEL_DIR,
+                                '{}.h5'.format(self.epic_id))
+        self.save_hdf(filename)
 
     def save_hdf(self,filename=None, path=''):
         if filename is None:
@@ -45,3 +48,12 @@ class EPIC_StarModel(StarModel):
     def load_hdf(cls, filename, path=''):
         return StarModel.load_hdf(filename, path=path)
 
+def get_starmodel(epic_id, **kwargs):
+    filename = os.path.join(STARMODEL_DIR,'{}.h5'.format(epic_id))
+    try:
+        return StarModel.load_hdf(filename)
+    except:
+        model = EPIC_StarModel(epic_id, **kwargs)
+        logging.info('Fitting {} starmodel...'.format(epic_id))
+        model.fit_mcmc()
+        return model

### 2015-03-02 ms.tex
testing pdflscape
Apparently revtex4.1 doesn't play well with pdflscape...

@@
 \usepackage{longtable}
+%\usepackage{lscape}
 \usepackage{natbib}
@@
 \begin{document}
+
 \title{(Working Title) Properties of the \KT\ Campaign 1 Planets, 
@@
 For all except two of our targets, the $W4$ band is only an upper limit.
-These data are reported in Table \ref{Tab:Photometry}.
+These data are reported in Table 1.
 
@@
 We use these parameters instead of the derived photometric properties for this target.
+
+The full list of stellar parameters adopted in this paper is included in
+Table 2.
+% For some reason I can't get it to identify the table \ref here. 
+% If anyone can figure it out, be my guest!
 
@@
 Whipple Observatory. 
+These dates were chosen to be near the times of largest RV variations, 
+corresponding to phases of \btmtodo{PHASES} relative to the time
+of transit.
 The spectra were taken with a resolving power of $R=44,000$ and 
@@
 
-\anytodo{This will be text from DaveL and/or Allyson Bieryla.}
+The spectra were extracted as described in \citet{Buchhave10}. 
+The relative RVs were derived by cross-correlating the spectra against the
+strongest observed spectrum (in this case, the first) over the wavelength
+range 4700 - 6800 Angstroms. 
+We selected 19 echelle orders in the analysis, being careful to reject
+orders with telluric absorption lines, fringing in the far red and those
+with very low SNR in the blue.
+
+The two observed spectra have RVs that differ by $47.1 \pm xx.x$ m s$^{-1}$.
+A deviation at this magnitude can only be explained by the presence of 
+a planetary system and instrumental noise, eliminating the possibility the
+transiting planet is actually a false positive.
 
@@
 
+\include{table_photometry}
+
+\include{table_stellarprops}
+
 \end{document}

### 2015-03-03 ms.tex
First half of intro

@@
 
-\title{(Working Title) Properties of the \KT\ Campaign 1 Planets, 
-False Positive Probabilities, and Confirmation of $N$ Systems. You 
-Were Warned: it's a Working Title.}
+\title{(Working Title) Stellar and Planetary Properties of \KT\ Campaign 1
+Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving 
+Earth-like Insolation?)}
 
@@
 David W. Hogg,
-% The Observers, as PIs 
+% The Observers
 % (ranked by integration time x collecting area)
@@
 David W. Latham,
+Allyson Bieryla,
 Andrew W. Mann,
-% The observers, as a group
-And Whoever DaveL Tells Us to Add as TRES Team Members
+And Any TRES Team Members We Should Add
 }
@@
 \begin{abstract}
-\btmtodo{This is where the abstract will go}
-Of the 36 planet candidates presented in \paperit{} we confirm 
+Recently, \paperit{} presented a list of 36 planet candidates orbiting
+31 stars in \KT\ Campaign 1. 
+In this paper, we present stellar and planetary properties for all systems.
+We combine archival imaging, ground-based seeing limited survey data, and
+adaptive optics imaging with a detailed transit analysis scheme to confirm 
 \btmtodo{Nconfirm} as planets and \btmtodo{NFP} as false positives
-at the \btmtodo{confidence} level. Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
+at the \btmtodo{confidence} level.
+Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
 hosting a \btmtodo{Radius} planet with $T_{eq} = $\btmtodo{Temp} and an 
 orbital period of 33 days.
+\anytodo{Anything we should add?}
 \end{abstract}
@@
 \section{Introduction}
+The \kep\ telescope \citep{Borucki10} has led to a revolution in stellar and planetary 
+astrophysics, with 7305 ``objects of interest'' and 4173 ``planet candidates''
+discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, Mullaly15}.
+The demise of two reaction wheels on the spacecraft led to a repurposing 
+of the spacecraft into the \KT\ mission, in which the telescope points at
+fields near the ecliptic plane for $\sim 75$ days at a time \citep{Howell14}.
+In this observing strategy, two axes of motion of the spacecraft are 
+controlled by the two remaining reaction wheels, while the roll of the 
+spacecraft is balanced with solar radiation pressure and quasiperiodic 
+thruster firing.
+The result of this observing strategy is that the targets appear to drift
+at the rate of $\sim 1\arcsec$ s$^{-1}$, with rapid corrections that occur
+approximately once every six hours.
+Over the full duration of each campaign, the targets appear to remain at 
+approximately the same location on the detector.
+Both the slow drift and the corrections are observable by eye, and by viewing the
+motions of each star \citep{Barentsen15} it is apparent that \KT\ is working as 
+advertised.
+Therefore, apertures can be defined around each star and aperture photometry can be
+defined in the usual way.
+
+\KT\ light curves produced with aperture photometry contain substantial pointing-induced
+photometric variations caused by the star's apparent motion over a poorly-defined flat 
+field. 
+Worse yet, these variations occur on timescales similar to transit signals, potentially
+masking the observational signature of a planet passing between \kep\ and the host star.
+
+There has been considerable effort to recover these signals.
+\citet{Vanderburg14} extract aperture photometry and decorrelate with image centroid
+position, ``correcting'' the data to ``remove'' the effects of the spacecraft motion.
+These data were used to confirm the first planet discovered in \KT\ \citep{Vanderburg15}.
+A similar technique was employed by \citet{Armstrong15a} to identify potential eclipsing
+binary systems and to identify a transiting system very near a 3:2 period commensurability
+\citep{Armstrong15b}.
+\citet{Aigrain15} and \citet{Crossfield15} use a Gaussian Process model for the measured
+flux, with pointing measurements as the inputs, and then “detrend” the data with that model.
+The latter of these detected the first multi-planet system in \KT\ data.
+
+What is common to all of these methods are that removal of systematics is considered a 
+step to be undertaken before the search for planets. 
+Under this strategy, it is implicitly assumed that the systematics are removed perfectly,
+while retaining all of the astrophysical signal. 
+Of course, it is impossible to perfectly separate the astrophysical and instrumental 
+signal, and such a technique is prone to either over-fitting, in which some of the 
+astrophysical signal is also removed, or under-fitting, in which some instrumental noise
+remains.
+A better strategy is to simultaneously fit both the signal and the noise, as is commonly
+done in cosmology and, increasingly, in radial velocity searches for planetary systems
+\citep[e.g.][]{Ferreira00, Boisse11, Haywood14, Grunblatt15}.
+
+\paperit{} apply an altern
 

### 2015-03-03 ms.tex
Intro done!

@@
 \newcommand{\KT}{\project{K2}}
+\newcommand{\Ci}{Campaign~1}
 \newcommand{\vsini}{{$V \sin i$}}
@@
 
-\title{(Working Title) Stellar and Planetary Properties of \KT\ Campaign 1
+\title{(Working Title) Stellar and Planetary Properties of \KT\ \Ci\
 Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving 
@@
 Recently, \paperit{} presented a list of 36 planet candidates orbiting
-31 stars in \KT\ Campaign 1. 
+31 stars in \KT\ \Ci. 
 In this paper, we present stellar and planetary properties for all systems.
@@
 discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, Mullaly15}.
+The fidelity of this sample is high, so most of these planet candidates are truly planets
+\citep{Morton11b, Fressin13}.
 The demise of two reaction wheels on the spacecraft led to a repurposing 
@@
 
-\paperit{} apply an altern
+\paperit{} simultaneously fit both the systematics and potential planetary transit signals
+in a search for transiting planets. 
+The authors of that paper assume that the dominant trends in the observed stellar light
+curves are caused by spacecraft motion and are shared among many stars. \anytodo{Among,
+right? Not between?}
+They then run PCA on all stars to measure the dominant modes, modeling each star as a 
+linear combination of 150 of these ``eigen light curves'' and a transit signal.
+This method enables fitting without over-fitting, and also permits marginalization over
+uncertainties induced by the noise model.
+Therefore, any uncertainties in the systematics can be propogated into uncertainties in
+detected planet parameters, instead of assuming the systematics are understood perfectly.
+Using this technique, \paperit{} detect 36 planet candidates orbiting 31 stars in \KT\
+\Ci\ data.
+
+In \paperit, only transit properties are provided, not absolute parameters about the
+planet or the star. 
+Additionally, the authors follow the convention of the \kep\ team to include any
+transit event as a candidate system rather than a false positive if a secondary eclipse
+is not detected: there is no enforced upper limit on the allowed planet radius.
+The authors intentionally make no effort to separate astrophysical false positives from
+true transiting planets.
+
+In this paper, we present stellar and planetary parameters for each system.
+Given these parameters and the transit data, as well as archival imaging, ground-based
+seeing limited survey data, and adaptive optics imaging, we are able to confirm 
+\anytodo{Number} of these systems as transiting planets at the \anytodo{Sigma} confidence
+level. We also are able to confirm \anytodo{Number} of these systems as false positives.
+
+This paper is organized as follows. 
+In \textsection2, we develop stellar properties through
+photometric and spectroscopic data.
+In \textsection3, we combine the derived stellar properties with \KT\ data to infer planet
+candidate properties.
+In \textsection4, we combine adaptive optics and radial velocity observations with both
+archival and modern ground-based, seeing limited survey data and an analysis of the
+transit parameters to calculate false positive probabilities.
+In \textsection5, we discuss potentially interesting systems.
+In \textsection6, we summarize and discuss our results.
 
@@
 Of the 31 stars in our sample, four have such a companion.
-Unlike the original \kep\ field, the field for \KT\ Campaign 1 is 
+Unlike the original \kep\ field, the field for \KT\ \Ci\ is 
 well out of the galactic plane, so the rate of giant, distanct background

### 2015-03-04 ms.tex
Some words on multis.

@@
 Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
-hosting a \btmtodo{Radius} planet with $T_{eq} = $\btmtodo{Temp} and an 
+hosting a \anytodo{Radius} planet with $T_{eq} = 275 \pm 15$ K and an 
 orbital period of 33 days.
@@
 as found in the 2MASS All-Sky Catalog of Point Sources \citep{Cutri03}
-and the four WISE magnitudes and uncertainties from the ALLWise Data
+and the $W1-W3$ WISE magnitudes and uncertainties from the ALLWise Data
 Release \citep{Cutri13}.
-For all except two of our targets, the $W4$ band is only an upper limit.
+For all except two of our targets, the $W4$ band is only an upper limit,
+and in the remaining two cases, the photometric uncertainity in $W4$ is at least an 
+order of magnitude larger than those in $W1-W3$, so we neglect $W4$.
 These data are reported in Table 1.
-
-\btmtodo{Make this table!}
 
@@
 
-We observed EPIC 201912552 on (all UT) February 04 2015, February 24 2015,
-and February \btmtodo{XX} 2015 with the Tillinghast Reflector Echelle
+We observed EPIC 201912552 on (all UT) February 04 2015 and February 24 2015 
+with the Tillinghast Reflector Echelle
 Spectrograph (TRES) on the 1.5 m Tillinghast Reflector at the Fred L.
@@
 These dates were chosen to be near the times of largest RV variations, 
-corresponding to phases of \btmtodo{PHASES} relative to the time
+corresponding to phases of 0.72 and 0.32 relative to the time
 of transit.
@@
 
-The two observed spectra have RVs that differ by $47.1 \pm xx.x$ m s$^{-1}$.
+The two observed spectra have RVs that differ by $47.1 \pm 41.9$ m s$^{-1}$.
 A deviation at this magnitude can only be explained by the presence of 
@@
 transiting planet is actually a false positive.
-
-The observed radial velocities are included in Table \ref{Tab:RVs}.
-
-\btmtodo{RVs table}
-
-%57057.83314
-%57077.75616
 
@@
 
-This star is an M2.8 dwarf at a distance of \btmtodo{Distance: around 30 pc}.
+This star is an M2.8 dwarf at a distance of $34\pm4$ pc.
 Of our planet candidate hosts, only EPIC 201367065 \citep[originally
@@
 Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 275 \pm 15$
-K, meaning its bulk insolation is similar to that of the Earth's.
+K, meaning its bulk insolation is $135 \pm 30$ percent that of the Earth's.
 Although the planet is likely too large to be rocky \citep{Rogers14}, 
@@
 \subsection{EPIC 201465501?}
-Is this a subsection? It's a star with a mass of ~0.2 Msun and a cnadidate with
+Is this a subsection? It's a star with a mass of ~0.2 Msun and a candidate with
 a period of 18 days. I suppose it depends on the FPP.
@@
 \subsection{Multiple Planet Systems}
+Five of the systems identified by \paperit\ are candidates to be multiply-transiting
+systems. 
+One of these is EPIC 201367065, a three-planet system originally announced by
+\citet{Crossfield15}. 
+Another of these is EPIC 201505350 \citep{Armstrong15b}, a two-planet system with the
+orbital periods of the two planets near a 3:2 period commensurability.
+The remaining three are all representative of the multiple-planet systems observed by
+\kep \citep{Lissauer11b, Fabrycky14}.
+Two of the systems are near a period commensurability and all three consist of 
+mini-Neptune sized planets.
+Like in the \kep\ field, the false positive rate we measure for the multiple planet sample
+here ($0/10$) is lower than for the single systems \citep{Lissauer12, Rowe14}.
+
+We do not detect any significant transit timing variations
 
@@
 \acknowledgements
-We thank [Eric Agol (UW) and Other People] for [things] which improved the quality of this manuscript.
+We thank Eric Agol (UW), Dan Huber (Sydney) [and Other People] for conversations and
+suggestions which improved the quality of this manuscript.
 
 We are grateful to the entire Kepler team, past and present. 
-Their tireless efforts were all essential to the tremendous success of the mission and the successes of K2, present and future.
+Their tireless efforts were all essential to the tremendous success of the mission and the
+successes of K2, present and future.
 

### 2015-03-04 ms.tex
Section 5 done, modulo one maybe subsection.

@@
 
-Cite \citet{Coughlin14} and \citet{Batalha13} in here.
+Such effects are not uncommon in \kep\ data. 
+\citet{Batalha13} found $\sim 25$ planet candidates to be false positives based on matching
+ephemerides between candidates. 
+In that paper, the authors limited their search to candidates within $20\arcsec$ of other
+objects of interest. 
+\citet{Coughlin14} expanded on this method, identifying 685 KOIs as false positives and 
+outlining four physical reasons why these anomalies may occur.
+While EPIC 201555883 is likely a false positive, it does not appear that it can neatly be
+explained by any one of the effects described by \citet{Coughlin14} alone. 
+This artifact should be carefully studied in the future, as it may help illuminate other 
+potential detector artifacts, both in \kep\ and \KT\ data.
 
@@
 
-We do not detect any significant transit timing variations
+We do not detect any significant transit timing variations (TTVs) in any of these systems from 
+the \KT\ data alone. 
+EPIC 201338508 would be expected to have a TTV period of 117 days, but 
+is likely too far from commensurability to have an observable TTV signal. 
+EPIC 201445392 is expected to have a TTV period of 234 days, so this system may be a candidate
+for additional follow-up to constrain the system masses dynamically. 
+The transiting planets orbiting EPIC 201754305 are near a 5:2 period commensurability. 
+There is no evidence from \kep\ of an abundance of planets near this period ratio, and so this 
+may be coincidence.
+Follow-up observations may be warranted to search for an additional planet in this system 
+forming a resonant chain, similar to those observed around other stars \citep[e.g.][]{Swift13,
+Campante15}.
 
 \subsection{Systems Orbiting Bright Stars}
+
+One of the primary goals of \KT\ is the detection of transiting planets around bright stars that
+can be followed up from the ground or with future space-based observatories such as JWST 
+\citep{Howell14}. 
+Of our sample, two systems orbit stars with $K < 9$: EPIC 201367065 \citep{Crossfield15} and
+EPIC 201912552. 
+An additional four targets orbit stars with $K <10$. 
+These targets are ideal for ground-based followup, and may be useful targets for Spitzer and 
+JWST to probe planetary atmospheres.
 

### 2015-03-04 fpp/all_starmodels.py
lots of stuff

@@ -6,9 +6,20 @@ from k2fpp.starmodels import get_starmodel
 
 import logging
 
-for epic_id in MAGS.index:
+import sys
+
+STARMODEL_DIR = 'starmodels_inflated'
+
+refit = '--refit' in sys.argv
+
+for i,epic_id in enumerate(MAGS.index):
+    print('{} of {}: {}'.format(i+1,len(MAGS),epic_id))
     try:
-        mod = get_starmodel(epic_id)
+        mod = get_starmodel(epic_id, refit=refit)
+        mod.triangle_plots('{}/{}'.format(STARMODEL_DIR,epic_id))
+    except KeyboardInterrupt:
+        raise
     except:
+        raise
         logging.error('Fit for {} broke.'.format(epic_id))
 

### 2015-03-04 fpp/k2fpp/photometry.py

@@ -8,5 +8,11 @@ def all_mags(epic_id):
     s = MAGS.ix[epic_id]
     d = {b:s[b] for b in s.index}
     del d['name']
+
+    if (d['g'] - d['r']) <= 0.8:
+        d['Kepler'] = 0.2*d['g'] + 0.8*d['r']
+    else:
+        d['Kepler'] = 0.1*d['g'] + 0.9*d['r']
+
     return d
 

### 2015-03-04 fpp/k2fpp/starmodels.py

@@ -1,5 +1,6 @@
 from __future__ import print_function, division
 
+import matplotlib.pyplot as plt
 import re, os, os.path
 import numpy as np
 import pandas as pd
@@ -13,30 +14,33 @@ from .photometry import all_mags
 
 DARTMOUTH = Dartmouth_Isochrone()
 
-STARMODEL_DIR = 'starmodels'
+STARMODEL_DIR = 'starmodels_inflated'
 
 class EPIC_StarModel(StarModel):
-    def __init__(self, epic_id, exclude_bands=['B','V','g','r','i','W4'],
-                 maxAV=0.1, refit=False, **kwargs):
+    def __init__(self, epic_id, exclude_bands=['W4'],
+                 maxAV=0.1, max_distance=500, refit=False, inflate_error=3,
+                 **kwargs):
 
         self.epic_id = epic_id
 
         mags = all_mags(epic_id)
         kws = {}
         for k,v in mags.items():
-            if re.search('err',k):
+            if re.search('err',k) or k=='Kepler':
                 continue
             if k not in exclude_bands:
-                kws[k] = (v, mags['{}err'.format(k)])
+                kws[k] = (v, mags['{}err'.format(k)]*inflate_error)
                 
         super(type(self),self).__init__(DARTMOUTH, maxAV=maxAV,
+                                        max_distance=max_distance,
                                         **kws)
 
-    def fit_mcmc(self, **kwargs):
+    def fit_mcmc(self, save=True, **kwargs):
         super(type(self),self).fit_mcmc(**kwargs)
         filename = os.path.join(STARMODEL_DIR,
                                 '{}.h5'.format(self.epic_id))
-        self.save_hdf(filename)
+        if save:
+            self.save_hdf(filename)
 
     def save_hdf(self,filename=None, path=''):
         if filename is None:
@@ -48,9 +52,11 @@ class EPIC_StarModel(StarModel):
     def load_hdf(cls, filename, path=''):
         return StarModel.load_hdf(filename, path=path)
 
-def get_starmodel(epic_id, **kwargs):
+def get_starmodel(epic_id, refit=False, **kwargs):
     filename = os.path.join(STARMODEL_DIR,'{}.h5'.format(epic_id))
     try:
+        if refit:
+            raise ValueError
         return StarModel.load_hdf(filename)
     except:
         model = EPIC_StarModel(epic_id, **kwargs)

### 2015-03-04 fpp/k2fpp/transitsignal.py

@@ -42,12 +42,18 @@ class K2_TransitSignal(TransitSignal_FromSamples):
     def __init__(self, epic_id, i=None):
         samples = get_samples(epic_id)
         
-        if(samples.shape[1]>5):
+        if(type(samples)==list):
             #integer nunmber must be passed
-            samples = samples[i]
-            period = PAPER1_TABLE.ix[epic_id, 'period'][i]
+            samples = samples[i-1]
+            period = PAPER1_TABLE.ix[epic_id, 'period'].iloc[i-1]
         else:
             period = PAPER1_TABLE.ix[epic_id, 'period']
+
+        name = '{}'.format(epic_id)
+        if i is None:
+            name += '.1'
+        else:
+            name += '{:.0f}'.format(i)
 
         super(type(self),self).__init__(period, 
                                         samples['T'],

### 2015-03-05 fpp/k2fpp/transitsignal.py
updated fpp table

@@ -59,3 +59,5 @@ class K2_TransitSignal(TransitSignal_FromSamples):
                                         samples['T'],
                                         samples['delta'],
                                         samples['T_tau'])
+        self.name = name
+

### 2015-03-05 ms.tex
not sure how to unrotate pages...

@@
 
-\altaffiltext{1}{Cahill Center for Astronomy and Astrophysics, California Institute of Technology, 1200 E. California Blvd., MC 249-17, Pasadena, CA 91106, USA}
+\altaffiltext{1}{Cahill Center for Astronomy and Astrophysics, California Institute of 
+Technology, 1200 E. California Blvd., MC 249-17, Pasadena, CA 91106, USA}
 \altaffiltext{2}{Harvard-Smithsonian Center for Astrophysics, 60 Garden
 Street, Cambridge, MA 02138, USA}
-\altaffiltext{3}{Department of Astronomy, University of Michigan, Ann Arbor, MI 48109, USA}
+\altaffiltext{3}{Department of Astronomy, University of Michigan, Ann Arbor, MI 
+48109, USA}
 
@@
 astrophysics, with 7305 ``objects of interest'' and 4173 ``planet candidates''
-discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, Mullaly15}.
-The fidelity of this sample is high, so most of these planet candidates are truly planets
+discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, 
+Mullaly15}.
+The fidelity of this sample is high, so most of these planet candidates are truly 
+planets
 \citep{Morton11b, Fressin13}.
@@
 advertised.
-Therefore, apertures can be defined around each star and aperture photometry can be
+Therefore, apertures can be defined around each star and aperture photometry can 
+be
 defined in the usual way.
@@
 Worse yet, these variations occur on timescales similar to transit signals, potentially
-masking the observational signature of a planet passing between \kep\ and the host star.
+masking the observational signature of a planet passing between \kep\ and the host 
+star.
 
 There has been considerable effort to recover these signals.
-\citet{Vanderburg14} extract aperture photometry and decorrelate with image centroid
+\citet{Vanderburg14} extract aperture photometry and decorrelate with image 
+centroid
 position, ``correcting'' the data to ``remove'' the effects of the spacecraft motion.
-These data were used to confirm the first planet discovered in \KT\ \citep{Vanderburg15}.
-A similar technique was employed by \citet{Armstrong15a} to identify potential eclipsing
-binary systems and to identify a transiting system very near a 3:2 period commensurability
+These data were used to confirm the first planet discovered in \KT\ 
+\citep{Vanderburg15}.
+A similar technique was employed by \citet{Armstrong15a} to identify potential 
+eclipsing
+binary systems and to identify a transiting system very near a 3:2 period 
+commensurability
 \citep{Armstrong15b}.
-\citet{Aigrain15} and \citet{Crossfield15} use a Gaussian Process model for the measured
-flux, with pointing measurements as the inputs, and then “detrend” the data with that model.
+\citet{Aigrain15} and \citet{Crossfield15} use a Gaussian Process model for the 
+measured
+flux, with pointing measurements as the inputs, and then “detrend” the data 
+with that model.
 The latter of these detected the first multi-planet system in \KT\ data.
@@
 They then run PCA on all stars to measure the dominant modes, modeling each star as a
+
 linear combination of 150 of these ``eigen light curves'' and a transit signal.
-This method enables fitting without over-fitting, and also permits marginalization over
+This method enables fitting without over-fitting, and also permits marginalization 
+over
 uncertainties induced by the noise model.
-Therefore, any uncertainties in the systematics can be propogated into uncertainties in
-detected planet parameters, instead of assuming the systematics are understood perfectly.
+Therefore, any uncertainties in the systematics can be propogated into uncertainties 
+in
+detected planet parameters, instead of assuming the systematics are understood 
+perfectly.
 Using this technique, \paperit{} detect 36 planet candidates orbiting 31 stars in \KT\
@@
 Additionally, the authors follow the convention of the \kep\ team to include any
-transit event as a candidate system rather than a false positive if a secondary eclipse
+transit event as a candidate system rather than a false positive if a secondary 
+eclipse
 is not detected: there is no enforced upper limit on the allowed planet radius.
-The authors intentionally make no effort to separate astrophysical false positives from
+The authors intentionally make no effort to separate astrophysical false positives 
+from
 true transiting planets.
@@
 In this paper, we present stellar and planetary parameters for each system.
+
 Given these parameters and the transit data, as well as archival imaging, ground-based
@@
 photometric and spectroscopic data.
-In \textsection3, we combine the derived stellar properties with \KT\ data to infer planet
+In \textsection3, we combine the derived stellar properties with \KT\ data to infer 
+planet
 candidate properties.
-In \textsection4, we combine adaptive optics and radial velocity observations with both
-archival and modern ground-based, seeing limited survey data and an analysis of the
+In \textsection4, we combine adaptive optics and radial velocity observations with 
+both
+archival and modern ground-based, seeing limited survey data and an analysis of 
+the
 transit parameters to calculate false positive probabilities.
@@
 mass, radius, and effective temperature.
+
 However, we are subject to biases induced by systematics in the models themselves.
@@
 This is Dan. 
+[for logic flow, perhaps this section should follow the FP section?]
 
@@
 \section{False Positive Analysis}
+
+As has been well known from the early days of transit searches, it is 
+possible for an eclipsing binary star to masquerade as a transiting 
+planet if (a) it is a highly grazing eclipse, or (b) the binary system
+comprises only a small fraction of the total light in the photometric
+aperture, resulting in a diluted eclipse depth.
+When possible, such astrophsycial false positive scenarios are traditionally
+ruled out by detailed follow-up observations, such as high-resolution
+imaging or radial-velocity measurements.  
+However, the \kep\ mission, with its thousands of planet candidates
+around mostly faint stars, necessitated a paradigm shift---a move 
+toward probabilistic interpretation of transit signals, rather than 
+comprehensive follow-up of each individual candidate.
+
+\citet{Morton12} described an automated method to calculate the
+probability that a planet candidate might be caused by an
+astrophysical false positive.  
+This method uses population simulations
+of false positive scenarios and true transiting planets to quantify
+the typical shape of each, and combines prior information about the
+populations of field stars and multiple star systems in order to
+determine the probability that the observed signal may be a false
+positive.  
+Similar in spirit to other published methods of probabilistic
+validation, such as Blender \citep{} and PASTIS \citep{}, it
+has the advantage of being computationally less demanding and 
+fully automated, and thus easily applied in batch to a large number of
+candidates.
+
 \subsection{Adaptive Optics Imaging}
@@
 a background eclipsing binary.
-The apparent transits must be caused by an object co-moving with EPIC 201912552;
+The apparent transits must be caused by an object co-moving with EPIC 
+201912552;
 radial velocities eliminate the possibility the companion is nonplanetary.
@@
 One of these is EPIC 201367065, a three-planet system originally announced by
+
 \citet{Crossfield15}.
@@
 orbital periods of the two planets near a 3:2 period commensurability.
-The remaining three are all representative of the multiple-planet systems observed by
+The remaining three are all representative of the multiple-planet systems observed 
+by
 \kep \citep{Lissauer11b, Fabrycky14}.
@@
 mini-Neptune sized planets.
-Like in the \kep\ field, the false positive rate we measure for the multiple planet sample
+Like in the \kep\ field, the false positive rate we measure for the multiple planet 
+sample
 here ($0/10$) is lower than for the single systems \citep{Lissauer12, Rowe14}.
@@
 \acknowledgements
-We thank Eric Agol (UW), Dan Huber (Sydney) [and Other People] for conversations and
+We thank Eric Agol (UW), Dan Huber (Sydney) [and Other People] for 
+conversations and
 suggestions which improved the quality of this manuscript.
@@
 
+\include{table_planets}
+
 \end{document}

### 2015-03-05 ms.tex
Revert "sorry bogus merge conflicts because of bogus hard wrap"
This reverts commit 69d7b2de27ba703d4c284e06966c3a21b757ce23, reversing
changes made to b16f301aa6d5b40adb30b7988176c89e0b8ee798.

@@
 
-\KT\ light curves produced with aperture photometry contain substantial pointing-induced
-photometric variations caused by the star's apparent motion over a poorly-defined flat
+\KT\ light curves produced with aperture photometry contain substantial pointing-
+induced
+photometric variations caused by the star's apparent motion over a poorly-defined 
+flat 
 field. 
@@
 
-What is common to all of these methods are that removal of systematics is considered a
+What is common to all of these methods are that removal of systematics is 
+considered a 
 step to be undertaken before the search for planets. 
-Under this strategy, it is implicitly assumed that the systematics are removed perfectly,
+Under this strategy, it is implicitly assumed that the systematics are removed 
+perfectly,
 while retaining all of the astrophysical signal. 
@@
 signal, and such a technique is prone to either over-fitting, in which some of the 
-astrophysical signal is also removed, or under-fitting, in which some instrumental noise
+astrophysical signal is also removed, or under-fitting, in which some instrumental 
+noise
 remains.
-A better strategy is to simultaneously fit both the signal and the noise, as is commonly
-done in cosmology and, increasingly, in radial velocity searches for planetary systems
+A better strategy is to simultaneously fit both the signal and the noise, as is 
+commonly
+done in cosmology and, increasingly, in radial velocity searches for planetary 
+systems
 \citep[e.g.][]{Ferreira00, Boisse11, Haywood14, Grunblatt15}.
 
-\paperit{} simultaneously fit both the systematics and potential planetary transit signals
+\paperit{} simultaneously fit both the systematics and potential planetary transit 
+signals
 in a search for transiting planets. 
-The authors of that paper assume that the dominant trends in the observed stellar light
-curves are caused by spacecraft motion and are shared among many stars. \anytodo{Among,
+The authors of that paper assume that the dominant trends in the observed stellar 
+light
+curves are caused by spacecraft motion and are shared among many stars. 
+\anytodo{Among,
 right? Not between?}
-They then run PCA on all stars to measure the dominant modes, modeling each star as a
-
+They then run PCA on all stars to measure the dominant modes, modeling each 
+star as a 
 linear combination of 150 of these ``eigen light curves'' and a transit signal.
@@
 In this paper, we present stellar and planetary parameters for each system.
-
-Given these parameters and the transit data, as well as archival imaging, ground-based
+Given these parameters and the transit data, as well as archival imaging, ground-
+based
 seeing limited survey data, and adaptive optics imaging, we are able to confirm 
-\anytodo{Number} of these systems as transiting planets at the \anytodo{Sigma} confidence
-level. We also are able to confirm \anytodo{Number} of these systems as false positives.
+\anytodo{Number} of these systems as transiting planets at the \anytodo{Sigma} 
+confidence
+level. We also are able to confirm \anytodo{Number} of these systems as false 
+positives.
 
@@
 mass, radius, and effective temperature.
-
-However, we are subject to biases induced by systematics in the models themselves.
+However, we are subject to biases induced by systematics in the models 
+themselves.
 There is some evidence that the Dartmouth models may underpredict 
@@
 \citet{Aldering06}. 
-Flux calibration was performed using a separate pipeline described in \citet{Mann15}.
+Flux calibration was performed using a separate pipeline described in 
+\citet{Mann15}.
 
 \teff\ was calculated by comparing our optical spectra with the CFIST
-suite\footnote{http://phoenix.ens-lyon.fr/Grids/BT-Settl/CIFIST2011/} of the BT-SETTL
-version of the PHOENIX atmosphere models \citep{Allard13}, which gave a temperature
+suite\footnote{http://phoenix.ens-lyon.fr/Grids/BT-Settl/CIFIST2011/} of the BT-
+SETTL
+version of the PHOENIX atmosphere models \citep{Allard13}, which gave a 
+temperature
 of 3503 $\pm$ 60\,K. 
@@
 a radius 0.394$\pm0.038R_\odot$. 
-We use these parameters instead of the derived photometric properties for this target.
+We use these parameters instead of the derived photometric properties for this 
+target.
 
@@
 Such effects are not uncommon in \kep\ data. 
-\citet{Batalha13} found $\sim 25$ planet candidates to be false positives based on matching
+\citet{Batalha13} found $\sim 25$ planet candidates to be false positives based on 
+matching
 ephemerides between candidates. 
-In that paper, the authors limited their search to candidates within $20\arcsec$ of other
+In that paper, the authors limited their search to candidates within $20\arcsec$ of 
+other
 objects of interest. 
-\citet{Coughlin14} expanded on this method, identifying 685 KOIs as false positives and
+\citet{Coughlin14} expanded on this method, identifying 685 KOIs as false positives 
+and 
 outlining four physical reasons why these anomalies may occur.
-While EPIC 201555883 is likely a false positive, it does not appear that it can neatly be
+While EPIC 201555883 is likely a false positive, it does not appear that it can neatly 
+be
 explained by any one of the effects described by \citet{Coughlin14} alone. 
@@
 One of these is EPIC 201367065, a three-planet system originally announced by
-
 \citet{Crossfield15}. 
-Another of these is EPIC 201505350 \citep{Armstrong15b}, a two-planet system with the
+Another of these is EPIC 201505350 \citep{Armstrong15b}, a two-planet system 
+with the
 orbital periods of the two planets near a 3:2 period commensurability.
@@
 
-We do not detect any significant transit timing variations (TTVs) in any of these systems from
+We do not detect any significant transit timing variations (TTVs) in any of these 
+systems from 
 the \KT\ data alone. 
@@
 is likely too far from commensurability to have an observable TTV signal. 
-EPIC 201445392 is expected to have a TTV period of 234 days, so this system may be a candidate
+EPIC 201445392 is expected to have a TTV period of 234 days, so this system may 
+be a candidate
 for additional follow-up to constrain the system masses dynamically. 
-The transiting planets orbiting EPIC 201754305 are near a 5:2 period commensurability.
-There is no evidence from \kep\ of an abundance of planets near this period ratio, and so this
+The transiting planets orbiting EPIC 201754305 are near a 5:2 period 
+commensurability. 
+There is no evidence from \kep\ of an abundance of planets near this period ratio, 
+and so this 
 may be coincidence.
-Follow-up observations may be warranted to search for an additional planet in this system
-forming a resonant chain, similar to those observed around other stars \citep[e.g.][]{Swift13,
+Follow-up observations may be warranted to search for an additional planet in this 
+system 
+forming a resonant chain, similar to those observed around other stars \citep[e.g.][]
+{Swift13,
 Campante15}.
@@
 
-One of the primary goals of \KT\ is the detection of transiting planets around bright stars that
-can be followed up from the ground or with future space-based observatories such as JWST
+One of the primary goals of \KT\ is the detection of transiting planets around bright 
+stars that
+can be followed up from the ground or with future space-based observatories such 
+as JWST 
 \citep{Howell14}. 
-Of our sample, two systems orbit stars with $K < 9$: EPIC 201367065 \citep{Crossfield15} and
+Of our sample, two systems orbit stars with $K < 9$: EPIC 201367065 
+\citep{Crossfield15} and
 EPIC 201912552. 
 An additional four targets orbit stars with $K <10$. 
-These targets are ideal for ground-based followup, and may be useful targets for Spitzer and
+These targets are ideal for ground-based followup, and may be useful targets for 
+Spitzer and 
 JWST to probe planetary atmospheres.
@@
 We are grateful to the entire Kepler team, past and present. 
-Their tireless efforts were all essential to the tremendous success of the mission and the
+Their tireless efforts were all essential to the tremendous success of the mission 
+and the
 successes of K2, present and future.
@@
 
-\include{table_planets}
-
 \end{document}

### 2015-03-05 ms.tex
Updates from ShareLaTeX

--- 2015-03-04 ms.tex
@@
 
-Such effects are not uncommon in \kep\ data. 
+False positives induced by the presence of a true astrophysical object with the same 
+transit ephemeris are not uncommon in \kep\ data. 
 \citet{Batalha13} found $\sim 25$ planet candidates to be false positives based on matching
@@
 
-Something about Multis and TTVs will go in here.
+We have presented stellar parameters for all planet candidates systems observed by 
+\paperit, confirming \btmtodo{Nconfirm} of the 36 candidates as bona fide planets and 
+\btmtodo{NFP} as bona fide false positives.
+
+With the exception of one object, all of the stellar parameters are derived from comparing 
+photometric observations to the Dartmouth stellar evolution models. 
+As a result, both the stellar and planet parameters are subject to systematic biases induced
+by discrepancies between the models and reality.
 
@@
 
+D.F.M. and D.W.H. were partially supported by the National Science Foundation 
+(grant IIS-1124794), the National Aeronautics and Space Administration (grant 
+NNX12AI50G), and the Moore–Sloan Data Science Environment at NYU.
+
 {\it Facilities:} \facility{Kepler}%, \btmtodo{More...}

### 2015-03-05 ms.tex
discussion
initial fpp text

--- 2015-03-05 ms.tex
@@
 
+\newcommand{\Nfp}{$X$}
+\newcommand{\Nvalidated}{$Y$}
+\newcommand{\Nlimbo}{$Z$}
+
 \begin{document}
@@
 
-\altaffiltext{1}{Cahill Center for Astronomy and Astrophysics, California Institute of 
-Technology, 1200 E. California Blvd., MC 249-17, Pasadena, CA 91106, USA}
+\altaffiltext{1}{Cahill Center for Astronomy and Astrophysics, California Institute of Technology, 1200 E. California Blvd., MC 249-17, Pasadena, CA 91106, USA}
 \altaffiltext{2}{Harvard-Smithsonian Center for Astrophysics, 60 Garden
 Street, Cambridge, MA 02138, USA}
-\altaffiltext{3}{Department of Astronomy, University of Michigan, Ann Arbor, MI 
-48109, USA}
+\altaffiltext{3}{Department of Astronomy, University of Michigan, Ann Arbor, MI 48109, USA}
 
@@
 astrophysics, with 7305 ``objects of interest'' and 4173 ``planet candidates''
-discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, 
-Mullaly15}.
-The fidelity of this sample is high, so most of these planet candidates are truly 
-planets
+discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, Mullaly15}.
+The fidelity of this sample is high, so most of these planet candidates are truly planets
 \citep{Morton11b, Fressin13}.
@@
 advertised.
-Therefore, apertures can be defined around each star and aperture photometry can 
-be
+Therefore, apertures can be defined around each star and aperture photometry can be
 defined in the usual way.
@@
 Worse yet, these variations occur on timescales similar to transit signals, potentially
-masking the observational signature of a planet passing between \kep\ and the host 
-star.
+masking the observational signature of a planet passing between \kep\ and the host star.
 
 There has been considerable effort to recover these signals.
-\citet{Vanderburg14} extract aperture photometry and decorrelate with image 
-centroid
+\citet{Vanderburg14} extract aperture photometry and decorrelate with image centroid
 position, ``correcting'' the data to ``remove'' the effects of the spacecraft motion.
-These data were used to confirm the first planet discovered in \KT\ 
-\citep{Vanderburg15}.
-A similar technique was employed by \citet{Armstrong15a} to identify potential 
-eclipsing
-binary systems and to identify a transiting system very near a 3:2 period 
-commensurability
+These data were used to confirm the first planet discovered in \KT\ \citep{Vanderburg15}.
+A similar technique was employed by \citet{Armstrong15a} to identify potential eclipsing
+binary systems and to identify a transiting system very near a 3:2 period commensurability
 \citep{Armstrong15b}.
-\citet{Aigrain15} and \citet{Crossfield15} use a Gaussian Process model for the 
-measured
-flux, with pointing measurements as the inputs, and then “detrend” the data 
-with that model.
+\citet{Aigrain15} and \citet{Crossfield15} use a Gaussian Process model for the measured
+flux, with pointing measurements as the inputs, and then “detrend” the data with that model.
 The latter of these detected the first multi-planet system in \KT\ data.
@@
 They then run PCA on all stars to measure the dominant modes, modeling each star as a 
-
 linear combination of 150 of these ``eigen light curves'' and a transit signal.
-This method enables fitting without over-fitting, and also permits marginalization 
-over
+This method enables fitting without over-fitting, and also permits marginalization over
 uncertainties induced by the noise model.
-Therefore, any uncertainties in the systematics can be propogated into uncertainties 
-in
-detected planet parameters, instead of assuming the systematics are understood 
-perfectly.
+Therefore, any uncertainties in the systematics can be propogated into uncertainties in
+detected planet parameters, instead of assuming the systematics are understood perfectly.
 Using this technique, \paperit{} detect 36 planet candidates orbiting 31 stars in \KT\
@@
 Additionally, the authors follow the convention of the \kep\ team to include any
-transit event as a candidate system rather than a false positive if a secondary 
-eclipse
+transit event as a candidate system rather than a false positive if a secondary eclipse
 is not detected: there is no enforced upper limit on the allowed planet radius.
-The authors intentionally make no effort to separate astrophysical false positives 
-from
+The authors intentionally make no effort to separate astrophysical false positives from
 true transiting planets.
@@
 In this paper, we present stellar and planetary parameters for each system.
-
 Given these parameters and the transit data, as well as archival imaging, ground-based
@@
 photometric and spectroscopic data.
-In \textsection3, we combine the derived stellar properties with \KT\ data to infer 
-planet
+In \textsection3, we combine the derived stellar properties with \KT\ data to infer planet
 candidate properties.
-In \textsection4, we combine adaptive optics and radial velocity observations with 
-both
-archival and modern ground-based, seeing limited survey data and an analysis of 
-the
+In \textsection4, we combine adaptive optics and radial velocity observations with both
+archival and modern ground-based, seeing limited survey data and an analysis of the
 transit parameters to calculate false positive probabilities.
@@
 mass, radius, and effective temperature.
-
 However, we are subject to biases induced by systematics in the models themselves.
@@
 This is Dan.
-[for logic flow, perhaps this section should follow the FP section?]
 
@@
 \section{False Positive Analysis}
-
 As has been well known from the early days of transit searches, it is 
@@
 probability that a planet candidate might be caused by an
-astrophysical false positive.  
-This method uses population simulations
+astrophysical false positive.  This method uses population simulations
 of false positive scenarios and true transiting planets to quantify
@@
 determine the probability that the observed signal may be a false
-positive.  
-Similar in spirit to other published methods of probabilistic
-validation, such as Blender \citep{} and PASTIS \citep{}, it
-has the advantage of being computationally less demanding and 
-fully automated, and thus easily applied in batch to a large number of
-candidates.
+positive.  Similar in spirit to other published methods of
+probabilistic validation, such as Blender \citep{} and PASTIS
+\citep{}, it has the advantage of being computationally less demanding
+and fully automated, and thus easily applied in batch to a large
+number of candidates.
+
+In this work, we use
+\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
+a new implementation of the \citet{Morton12} procedure, to calculate
+the false positive probabilities of each of these K2 candidates,
+supplemented in a few cases by high-resolution imaging, where
+available.  Table \ref{table:FPP} summarizes the results of these
+calculations, presenting the relative probability for each candidate
+to be caused by any of three false positive scenarios: an undiluted
+eclipsing binary (EB), a hierarchical triple eclipsing binary (HEB),
+and a chance-aligned background(/foreground) eclipsing binary (BEB).
+We find that \Nfp\ of the presented candidates have false positive
+probabilities (FPPs) $>$80\%; these we consider to be likely false
+positives.  On the other hand, we find that \Nvalidated\ candidates
+have FPP $<$ 1\%; these we consider to be validated planets.  The
+remaining \Nlimbo\ candidates have FPPs neither high enough to discard
+nor low enough to securely validate.
 
@@
 a background eclipsing binary.
-The apparent transits must be caused by an object co-moving with EPIC 
-201912552;
+The apparent transits must be caused by an object co-moving with EPIC 201912552;
 radial velocities eliminate the possibility the companion is nonplanetary.
@@
 One of these is EPIC 201367065, a three-planet system originally announced by
-
 \citet{Crossfield15}. 
@@
 orbital periods of the two planets near a 3:2 period commensurability.
-The remaining three are all representative of the multiple-planet systems observed 
-by
+The remaining three are all representative of the multiple-planet systems observed by
 \kep \citep{Lissauer11b, Fabrycky14}.
@@
 mini-Neptune sized planets.
-Like in the \kep\ field, the false positive rate we measure for the multiple planet 
-sample
+Like in the \kep\ field, the false positive rate we measure for the multiple planet sample
 here ($0/10$) is lower than for the single systems \citep{Lissauer12, Rowe14}.
@@
 \acknowledgements
-We thank Eric Agol (UW), Dan Huber (Sydney) [and Other People] for 
-conversations and
+We thank Eric Agol (UW), Dan Huber (Sydney) [and Other People] for conversations and
 suggestions which improved the quality of this manuscript.

### 2015-03-06 ms.tex
tdm grant added
tdm edits

@@
 
-\newcommand{\Nfp}{$X$}
-\newcommand{\Nvalidated}{$Y$}
-\newcommand{\Nlimbo}{$Z$}
+\newcommand{\Nfp}{4}
+\newcommand{\Nvalidated}{21}
+\newcommand{\Nlimbo}{11}
 
@@
 \title{(Working Title) Stellar and Planetary Properties of \KT\ \Ci\
-Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving 
+Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving 
 Earth-like Insolation?)}
@@
 Daniel Foreman-Mackey\altaffilmark{3},
-Timothy D. Morton,
+Timothy D. Morton\altaffilmark{4},
 % The Benefactors
@@
 \altaffiltext{3}{Department of Astronomy, University of Michigan, Ann Arbor, MI 48109, USA}
+\altaffiltext{4}{Department of Astrophysics, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
 
@@
 adaptive optics imaging with a detailed transit analysis scheme to confirm 
-\btmtodo{Nconfirm} as planets and \btmtodo{NFP} as false positives
-at the \btmtodo{confidence} level.
+\Nvalidated\ as planets and identify \Nfp\ as likely false positives.
 Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
@@
 
-\citet{Morton12} described an automated method to calculate the
+\citet{Morton12} presented an automated method to calculate the
 probability that a planet candidate might be caused by an
-astrophysical false positive.  This method uses population simulations
+astrophysical false positive.  
+This method uses population simulations
 of false positive scenarios and true transiting planets to quantify
-the typical shape of each, and combines prior information about the
-populations of field stars and multiple star systems in order to
-determine the probability that the observed signal may be a false
-positive.  Similar in spirit to other published methods of
+the typical shape of each, comparing to the observed transit shape.
+It then combines this information with observationally motivated prior
+assumtions about the populations of field stars, the properties of 
+multiple star systems, and the occurrence rate of planets as determined
+from \kep\ \citet{Fressin13}, in order to determine the probability that 
+the observed signal may be a false positive.  
+Similar in spirit to other published methods of
 probabilistic validation, such as Blender \citep{} and PASTIS
@@
 a new implementation of the \citet{Morton12} procedure, to calculate
-the false positive probabilities of each of these K2 candidates,
-supplemented in a few cases by high-resolution imaging, where
-available.  Table \ref{table:FPP} summarizes the results of these
+the false positive probabilities of each of these K2 candidates.  
+While we do have follow-up observations of a number of these systems,
+we do the preliminary FPP calculations without taking these into account,
+relying solely on the probabilistic \texttt{vespa} analysis.
+
+Table \ref{table:FPP} summarizes the results of these
 calculations, presenting the relative probability for each candidate
@@
 and a chance-aligned background(/foreground) eclipsing binary (BEB).
+
 We find that \Nfp\ of the presented candidates have false positive
-probabilities (FPPs) $>$80\%; these we consider to be likely false
-positives.  On the other hand, we find that \Nvalidated\ candidates
-have FPP $<$ 1\%; these we consider to be validated planets.  The
-remaining \Nlimbo\ candidates have FPPs neither high enough to discard
+probabilities (FPPs) $>$90\%; these we consider to be likely false
+positives.  
+On the other hand, we find that \Nvalidated\ candidates
+have FPP $<$ 1\%; these we consider to be validated planets.  
+The remaining \Nlimbo\ candidates have FPPs neither high enough to discard
 nor low enough to securely validate.
+
+We emphasize that t
 
@@
 
+T.D.M.~is supported by the National Aeronautics and Space Administration (grant 
+NNX14AE11G).
+
 {\it Facilities:} \facility{Kepler}%, \btmtodo{More...}

### 2015-03-06 ms.tex
more FPP text

@@
 a new implementation of the \citet{Morton12} procedure, to calculate
-the false positive probabilities of each of these K2 candidates.  
-While we do have follow-up observations of a number of these systems,
+false positive probabilities (FPPs) for each of these K2 candidates.  
+While we have obtained follow-up observations of a number of these systems,
 we do the preliminary FPP calculations without taking these into account,
-relying solely on the probabilistic \texttt{vespa} analysis.
+in order to demonstrate the power of \texttt{vespa} analysis
+even in the absence of follow-up observations.  
+The constraints we impose on false positive scenarios in these
+``follow-up free'' calculations are the following:
+\begin{itemize}
+\item A chance-aligned eclipsing binary system must reside within 
+a 4 arcsecond radius of the target star.
+\item The maximum allowed depth of a potential secondary eclipse event,
+determined as the most significantly detected signal at the same 
+period of the planet candidate, once the primary transit is masked out.
+\end{itemize}
 
@@
 
-We find that \Nfp\ of the presented candidates have false positive
-probabilities (FPPs) $>$90\%; these we consider to be likely false
-positives.  
+We find that \Nfp\ of the presented candidates FPP $>$90\%; 
+these we consider to be likely false positives.  
 On the other hand, we find that \Nvalidated\ candidates

### 2015-03-07 ms.tex
fixing and adding some affiliations

@@
 
-\author{
+\newcommand{\caltech}{2}
+\newcommand{\cfa}{3}
+\newcommand{\nyu}{4}
+\newcommand{\princeton}{5}
+\newcommand{\mpia}{6}
+\newcommand{\cds}{7}
+\author{%
 % The Heavy Lifters
-Benjamin T. Montet\altaffilmark{1,2}, 
-Daniel Foreman-Mackey\altaffilmark{3},
-Timothy D. Morton\altaffilmark{4},
+Benjamin~T.~Montet\altaffilmark{1,\caltech,\cfa},
+Daniel~Foreman-Mackey\altaffilmark{\nyu},
+Timothy~D.~Morton\altaffilmark{\princeton},
 % The Benefactors
-John Asher Johnson,
-David W. Hogg,
+John~Asher~Johnson\altaffilmark{\cfa},
+David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
 % The Observers
 % (ranked by integration time x collecting area)
-Brendan P. Bowler,
-David W. Latham,
-Allyson Bieryla,
-Andrew W. Mann,
+Brendan~P.~Bowler,
+David~W.~Latham,
+Allyson~Bieryla,
+Andrew~W.~Mann,
 And Any TRES Team Members We Should Add
@@
 
-\email{btm@astro.caltech.edu}
-
-\altaffiltext{1}{Cahill Center for Astronomy and Astrophysics, California Institute of Technology, 1200 E. California Blvd., MC 249-17, Pasadena, CA 91106, USA}
-\altaffiltext{2}{Harvard-Smithsonian Center for Astrophysics, 60 Garden
-Street, Cambridge, MA 02138, USA}
-\altaffiltext{3}{Department of Astronomy, University of Michigan, Ann Arbor, MI 48109, USA}
-\altaffiltext{4}{Department of Astrophysics, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
+\altaffiltext{1}         {btm@astro.caltech.edu}
+\altaffiltext{\caltech}  {Cahill Center for Astronomy and Astrophysics,
+                          California Institute of Technology, Pasadena, CA,
+                          91125, USA}
+\altaffiltext{\cfa}      {Harvard-Smithsonian Center for Astrophysics,
+                          Cambridge, MA 02138, USA}
+\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
+                          Department of Physics, New York University,
+                          4 Washington Place, New York, NY, 10003, USA}
+\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
+                          Princeton, NJ, 08544, USA}
+\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
+                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
+\altaffiltext{\cds}      {Center for Data Science,
+                          New York University,
+                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
 

### 2015-03-07 ms.tex
small changes in intro

@@
 approximately once every six hours.
-Over the full duration of each campaign, the targets appear to remain at
-approximately the same location on the detector.
-Both the slow drift and the corrections are observable by eye, and by viewing the
-motions of each star \citep{Barentsen15} it is apparent that \KT\ is working as
-advertised.
-Therefore, apertures can be defined around each star and aperture photometry can be
-defined in the usual way.
+Over the full duration of each campaign, the targets appear to remain near the
+same location on the detector but both the slow drift and the corrections are
+observable by eye \citep{Barentsen15}.
 
@@
 There has been considerable effort to recover these signals.
-\citet{Vanderburg14} extract aperture photometry and decorrelate with image centroid
+\citet{Vanderburg14} extract aperture photometry and de-correlate with image centroid
 position, ``correcting'' the data to ``remove'' the effects of the spacecraft motion.
@@
 \citet{Aigrain15} and \citet{Crossfield15} use a Gaussian Process model for the measured
-flux, with pointing measurements as the inputs, and then “detrend” the data with that model.
+flux, with pointing measurements as the inputs, and then ``de-trend'' the data with that model.
 The latter of these detected the first multi-planet system in \KT\ data.
@@
 The authors of that paper assume that the dominant trends in the observed stellar light
-curves are caused by spacecraft motion and are shared among many stars. \anytodo{Among,
-right? Not between?}
+curves are caused by spacecraft motion and are shared by many stars.
 They then run PCA on all stars to measure the dominant modes, modeling each star as a

### 2015-03-09 fpp/write_fpptable.py
added file

@@ -1,0 +1,86 @@
+#!/usr/bin/env python
+
+import re
+import os, os.path, glob
+
+from k2fpp.fpp import max_secondary
+
+def prob_entry(val):
+    val = float(val)
+    if val > 1e-4:
+        return '${:.2g}$'.format(val)
+    else:
+        return '$< 10^{-4}$'
+
+def format_line(line, fpp):
+    fpp = float(fpp)
+    newline = line
+    if fpp < 0.01:
+        newline = ''
+        for v in line.split('&'):
+            m = re.search('(.*)\s+\\\\',v)
+            if m:
+                newline += r' {\bf ' + m.group(1) + '} \\\\\n'
+            else:
+                newline += r' {\bf ' + v + '} &'
+    if fpp > 0.9:
+        newline = ''
+        for v in line.split('&'):
+            m = re.search('(.*)\s+\\\\',v)
+            if m:
+                newline += r' \color{red} ' + m.group(1) + '\color{black} \\\\\n'
+            else:
+                newline += r' \color{red} ' + v + '\color{black} &'
+        
+    return newline
+        
+
+fout = open('../table_fpp.tex','w')
+
+fout.write(r"""
+\clearpage
+%\LongTables
+\begin{deluxetable*}{lcccccc}
+\tablewidth{0pt}
+\tabletypesize{\scriptsize}
+\tablecaption{False Positive Probability Calculation Results}
+\label{Tab:FPP}}
+\tablehead{
+\colhead{EPIC} &
+\colhead{Cand. Num.} &
+\colhead{max($\delta_{\rm sec}$)} &
+\colhead{${\rm Pr}_{\rm EB}$} &
+\colhead{${\rm Pr}_{\rm BEB}$} &
+\colhead{${\rm Pr}_{\rm HEB}$} &
+\colhead{$f_{p}$} &
+\colhead{FPP}
+}
+\startdata
+""")
+
+folders = glob.glob('fppmodels/*')
+for f in folders:
+    resultsfile = f + '/results.txt'
+    for line in open(resultsfile,'r'):
+        line = line.split()
+    beb,eb,heb,pl,fpV,fp,FPP = line
+    m = re.search('(\d+)\.(\d)',f)
+    epic_id = int(m.group(1))
+    i = int(m.group(2))
+    line = '${}$ & ${}$ & '.format(epic_id,i)
+    line += '${:.2f}$ & '.format(max_secondary(epic_id,i)*1e3)
[…]

### 2015-03-09 ms.tex

@@
 \newcommand{\afe}{{[$\alpha$/Fe]}~}
+
+\newcommand{\dd}{{\ensuremath{\,\mathrm{d}}}}
 
@@
 for each star.
+\anytodo{This was done using MCMC right? Did you interpolate the
+\emph{likelihood function} or the \emph{model predictions}?}
 
@@
 However, we are subject to biases induced by systematics in the models themselves.
-There is some evidence that the Dartmouth models may underpredict
+There is some evidence that the Dartmouth models may under-predict
 radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
@@
 
-This is Dan.
+To derive the physical planet parameters conditioned on the measured stellar
+parameters, we used the posterior probability distribution for quantities
+measured using the light curve---from \paperit---and re-weighted them using
+the results of the photometric and spectroscopic analysis.
+In \paperit, the authors generated MCMC samples from the posterior
+probability distribution over all the physical parameters (including stellar
+mass and radius, and the planet radius) using broad, un-informative priors on
+the values that are not constrained by the light curve.
+As described in SOME APPENDIX, these samples can be re-weighted and used to
+evaluate the posterior probability of the physical parameters of the planets
+conditioned on the stellar values.
+This also means that the effects of different measurements of the stellar
+parameters can be easily tested by applying the method described in THAT SAME
+APPENDIX.
+
+The key assumption of this method is that the likelihood function used in
+\paperit\ is correct.
+That model was an exposure-time integrated, limb darkened light curve
+\citep{Mandel02,Kipping10b} marginalized over the parameters of the
+data-driven model of the instrumental systematics described in \paperit.
+
+The results are given in SOME TABLE.
 
@@
 
+\appendix
+\section{Computing physical planet parameters}
+
+In \paperit, the authors generated $K$ samples from the posterior probability
+distribution of the physical parameters of the systems conditioned on the
+light curves using broad, un-informative priors on most of the parameters.
+
+\begin{eqnarray}
+p(w\,|\,x) &=& \frac{p(w)\,p(x\,|\,w)}{p(x)} \\
+&=& \frac{q(w)\,p(x\,|\,w)}{q(x)}\,\frac{p(w)}{q(w)}\,\frac{q(x)}{p(x)} \\
+&=& q(w\,|\,x)\,\frac{p(w)}{q(w)}\,\frac{q(x)}{p(x)}
+\end{eqnarray}
+
+We have $K$ samples
+\begin{eqnarray}
+w^{(k)} &\sim& p(w\,|\,x)
+\end{eqnarray}
+and the point of these samples is to do integrals of the form
+\begin{eqnarray}
+E[f(w)] &=& \int f(w)\,p(w\,|\,x) \dd w \quad.
+\end{eqnarray}
+Now, if we want to update this with a new measurement $p^\prime(w)$,
+
 \bibliography{exopapers}

### 2015-03-09 table_fpp.tex
added fpp table

\clearpage
%\LongTables
\begin{deluxetable*}{lcccccc}
\tablewidth{0pt}
\tabletypesize{\scriptsize}
\tablecaption{False Positive Probability Calculation Results}
\label{Tab:FPP}}
\tablehead{
\colhead{EPIC} &
\colhead{Cand. Num.} &
\colhead{max($\delta_{\rm sec}$)} &
\colhead{${\rm Pr}_{\rm EB}$} &
\colhead{${\rm Pr}_{\rm BEB}$} &
\colhead{${\rm Pr}_{\rm HEB}$} &
\colhead{$f_{p}$} &
\colhead{FPP}
}
\startdata
 {\bf $201208431$ } & {\bf  $1$ } & {\bf  $0.51$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0058$ } & {\bf  $0.00011$ } & {\bf  $0.22$ } & {\bf  $0.0059$} \\
 {\bf $201384232$ } & {\bf  $1$ } & {\bf  $0.44$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00017$ } & {\bf  $0.00023$ } & {\bf  $0.21$ } & {\bf  $0.0004$} \\
 {\bf $201613023$ } & {\bf  $1$ } & {\bf  $0.08$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0016$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.15$ } & {\bf  $0.0016$} \\
 {\bf $201546283$ } & {\bf  $1$ } & {\bf  $0.15$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.16$ } & {\bf  $< 10^{-4}$} \\
$201779067$ & $1$ & $1.97$ & $0.034$ & $0.038$ & $0.3$ & $0.03$ & $0.37$ \\
 \color{red} $201257461$ \color{black} & \color{red}  $1$ \color{black} & \color{red}  $0.59$ \color{black} & \color{red}  $< 10^{-4}$ \color{black} & \color{red}  $0.072$ \color{black} & \color{red}  $0.93$ \color{black} & \color{red}  $0.22$ \color{black} & \color{red}  $1$\color{black} \\
$201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.014$ & $0.0024$ & $0.17$ & $0.016$ \\
$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ \\
$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ \\
$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ \\
 {\bf $201295312$ } & {\bf  $1$ } & {\bf  $0.04$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.008$ } & {\bf  $0.00014$ } & {\bf  $0.15$ } & {\bf  $0.0082$} \\
 {\bf $201855371$ } & {\bf  $1$ } & {\bf  $0.62$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0006$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.20$ } & {\bf  $0.00071$} \\
 {\bf $201555883$ } & {\bf  $1$ } & {\bf  $0.94$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0044$ } & {\bf  $0.0004$ } & {\bf  $0.20$ } & {\bf  $0.0048$} \\
 {\bf $201629650$ } & {\bf  $1$ } & {\bf  $0.43$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.005$ } & {\bf  $0.0012$ } & {\bf  $0.17$ } & {\bf  $0.0062$} \\
 {\bf $201403446$ } & {\bf  $1$ } & {\bf  $0.18$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0069$ } & {\bf  $0.0013$ } & {\bf  $0.13$ } & {\bf  $0.0083$} \\
 \color{red} $201565013$ \color{black} & \color{red}  $1$ \color{black} & \color{red}  $1.69$ \color{black} & \color{red}  $0.0023$ \color{black} & \color{red}  $0.14$ \color{black} & \color{red}  $0.82$ \color{black} & \color{red}  $0.07$ \color{black} & \color{red}  $0.96$\color{black} \\
 {\bf $201912552$ } & {\bf  $1$ } & {\bf  $0.47$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00058$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.22$ } & {\bf  $0.00058$} \\
$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ \\
$201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.15$ & $0.0028$ & $0.14$ & $0.15$ \\
$201569483$ & $1$ & $2.06$ & $0.48$ & $0.00061$ & $0.097$ & $0.01$ & $0.58$ \\
$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$ \\
 \color{red} $201649426$ \color{black} & \color{red}  $1$ \color{black} & \color{red}  $3.10$ \color{black} & \color{red}  $0.81$ \color{black} & \color{red}  $0.0016$ \color{black} & \color{red}  $0.13$ \color{black} & \color{red}  $0.01$ \color{black} & \color{red}  $0.94$\color{black} \\
 {\bf $201577035$ } & {\bf  $1$ } & {\bf  $0.14$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00015$ } & {\bf  $0.20$ } & {\bf  $0.0002$} \\
$201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.03$ & $0.29$ & $0.06$ & $0.32$ \\
$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ \\
 {\bf $201736247$ } & {\bf  $1$ } & {\bf  $0.42$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0015$ } & {\bf  $0.00092$ } & {\bf  $0.22$ } & {\bf  $0.0024$} \\
 {\bf $201338508$ } & {\bf  $2$ } & {\bf  $0.33$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.006$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.17$ } & {\bf  $0.006$} \\
 {\bf $201367065$ } & {\bf  $2$ } & {\bf  $0.67$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00063$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.14$ } & {\bf  $0.00063$} \\
$201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.22$ & $0.048$ & $0.18$ & $0.27$ \\
 {\bf $201505350$ } & {\bf  $2$ } & {\bf  $0.70$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0025$ } & {\bf  $0.00013$ } & {\bf  $0.07$ } & {\bf  $0.0026$} \\
$201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0099$ & $0.00069$ & $0.17$ & $0.011$ \\
$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ \\
 {\bf $201367065$ } & {\bf  $1$ } & {\bf  $0.15$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.01$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.18$ } & {\bf  $0.01$} \\
$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ \\
 \color{red} $201505350$ \color{black} & \color{red}  $1$ \color{black} & \color{red}  $2.69$ \color{black} & \color{red}  $< 10^{-4}$ \color{black} & \color{red}  $0.13$ \color{black} & \color{red}  $0.86$ \color{black} & \color{red}  $0.18$ \color{black} & \color{red}  $0.99$\color{black} \\
$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ \\

\enddata
\tablecomments{blurgh.}
\end{deluxetable*}

### 2015-03-09 table_fpp.tex
table formatting

@@
 $201779067$ & $1$ & $1.97$ & $0.034$ & $0.038$ & $0.3$ & $0.03$ & $0.37$ \\
- \color{red} $201257461$ \color{black} & \color{red}  $1$ \color{black} & \color{red}  $0.59$ \color{black} & \color{red}  $< 10^{-4}$ \color{black} & \color{red}  $0.072$ \color{black} & \color{red}  $0.93$ \color{black} & \color{red}  $0.22$ \color{black} & \color{red}  $1$\color{black} \\
+ \cellcolor{red} $201257461$  & \cellcolor{red}  $1$  & \cellcolor{red}  $0.59$  & \cellcolor{red}  $< 10^{-4}$  & \cellcolor{red}  $0.072$  & \cellcolor{red}  $0.93$  & \cellcolor{red}  $0.22$  & \cellcolor{red}  $1$\\
 $201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.014$ & $0.0024$ & $0.17$ & $0.016$ \\
@@
  {\bf $201403446$ } & {\bf  $1$ } & {\bf  $0.18$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0069$ } & {\bf  $0.0013$ } & {\bf  $0.13$ } & {\bf  $0.0083$} \\
- \color{red} $201565013$ \color{black} & \color{red}  $1$ \color{black} & \color{red}  $1.69$ \color{black} & \color{red}  $0.0023$ \color{black} & \color{red}  $0.14$ \color{black} & \color{red}  $0.82$ \color{black} & \color{red}  $0.07$ \color{black} & \color{red}  $0.96$\color{black} \\
+ \cellcolor{red} $201565013$  & \cellcolor{red}  $1$  & \cellcolor{red}  $1.69$  & \cellcolor{red}  $0.0023$  & \cellcolor{red}  $0.14$  & \cellcolor{red}  $0.82$  & \cellcolor{red}  $0.07$  & \cellcolor{red}  $0.96$\\
  {\bf $201912552$ } & {\bf  $1$ } & {\bf  $0.47$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00058$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.22$ } & {\bf  $0.00058$} \\
@@
 $201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$ \\
- \color{red} $201649426$ \color{black} & \color{red}  $1$ \color{black} & \color{red}  $3.10$ \color{black} & \color{red}  $0.81$ \color{black} & \color{red}  $0.0016$ \color{black} & \color{red}  $0.13$ \color{black} & \color{red}  $0.01$ \color{black} & \color{red}  $0.94$\color{black} \\
+ \cellcolor{red} $201649426$  & \cellcolor{red}  $1$  & \cellcolor{red}  $3.10$  & \cellcolor{red}  $0.81$  & \cellcolor{red}  $0.0016$  & \cellcolor{red}  $0.13$  & \cellcolor{red}  $0.01$  & \cellcolor{red}  $0.94$\\
  {\bf $201577035$ } & {\bf  $1$ } & {\bf  $0.14$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00015$ } & {\bf  $0.20$ } & {\bf  $0.0002$} \\
@@
 $201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ \\
- \color{red} $201505350$ \color{black} & \color{red}  $1$ \color{black} & \color{red}  $2.69$ \color{black} & \color{red}  $< 10^{-4}$ \color{black} & \color{red}  $0.13$ \color{black} & \color{red}  $0.86$ \color{black} & \color{red}  $0.18$ \color{black} & \color{red}  $0.99$\color{black} \\
-$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ \\
+ \cellcolor{red} $201505350$  & \cellcolor{red}  $1$  & \cellcolor{red}  $2.69$  & \cellcolor{red}  $< 10^{-4}$  & \cellcolor{red}  $0.13$  & \cellcolor{red}  $0.86$  & \cellcolor{red}  $0.18$  & \cellcolor{red}  $0.99$\\
+$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$
 

### 2015-03-09 fpp/write_fpptable.py

@@ -28,9 +28,9 @@ def format_line(line, fpp):
         for v in line.split('&'):
             m = re.search('(.*)\s+\\\\',v)
             if m:
-                newline += r' \color{red} ' + m.group(1) + '\color{black} \\\\\n'
+                newline += r' \cellcolor{red} ' + m.group(1) + '\\\\\n'
             else:
-                newline += r' \color{red} ' + v + '\color{black} &'
+                newline += r' \cellcolor{red} ' + v + ' &'
         
     return newline
         
@@ -73,9 +73,12 @@ for f in folders:
         val = float(val)
         line += '{} & '.format(prob_entry(val))
     line += '${:.2f}$ & '.format(float(fp))
-    line += '{} \\\\\n'.format(prob_entry(FPP))
+    line += '{} '.format(prob_entry(FPP))
+    if f != folders[-1]:
+        line += '\\\\'
+    line += '\n'
     fout.write(format_line(line,FPP))
-               
+
 
 fout.write(r"""
 \enddata

### 2015-03-09 ms.tex
blah

@@
 
-Table \ref{table:FPP} summarizes the results of these
+Table \ref{Tab:FPP} summarizes the results of these
 calculations, presenting the relative probability for each candidate
@@
 
+%\include{table_fpp}
+
 \end{document}

### 2015-03-09 fpp/write_fpptable.py
table typo

@@ -44,7 +44,7 @@ fout.write(r"""
 \tablewidth{0pt}
 \tabletypesize{\scriptsize}
 \tablecaption{False Positive Probability Calculation Results}
-\label{Tab:FPP}}
+\label{Tab:FPP}
 \tablehead{
 \colhead{EPIC} &
 \colhead{Cand. Num.} &

### 2015-03-09 table_fpp.tex
blah
table typo
sorting

@@
 %\LongTables
-\begin{deluxetable*}{lcccccc}
+\begin{deluxetable*}{lccccccc}
 \tablewidth{0pt}
@@
 \tablecaption{False Positive Probability Calculation Results}
-\label{Tab:FPP}}
+\label{Tab:FPP}
 \tablehead{
@@
  {\bf $201208431$ } & {\bf  $1$ } & {\bf  $0.51$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0058$ } & {\bf  $0.00011$ } & {\bf  $0.22$ } & {\bf  $0.0059$} \\
+ \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.072$  & \color{red}  $0.93$  & \color{red}  $0.22$  & \color{red}  $1$\\
+ {\bf $201295312$ } & {\bf  $1$ } & {\bf  $0.04$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.008$ } & {\bf  $0.00014$ } & {\bf  $0.15$ } & {\bf  $0.0082$} \\
+$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ \\
+ {\bf $201338508$ } & {\bf  $2$ } & {\bf  $0.33$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.006$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.17$ } & {\bf  $0.006$} \\
+ {\bf $201367065$ } & {\bf  $1$ } & {\bf  $0.15$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.01$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.18$ } & {\bf  $0.01$} \\
+ {\bf $201367065$ } & {\bf  $2$ } & {\bf  $0.67$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00063$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.14$ } & {\bf  $0.00063$} \\
  {\bf $201384232$ } & {\bf  $1$ } & {\bf  $0.44$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00017$ } & {\bf  $0.00023$ } & {\bf  $0.21$ } & {\bf  $0.0004$} \\
+$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ \\
+ {\bf $201403446$ } & {\bf  $1$ } & {\bf  $0.18$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0069$ } & {\bf  $0.0013$ } & {\bf  $0.13$ } & {\bf  $0.0083$} \\
+$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ \\
+$201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.22$ & $0.048$ & $0.18$ & $0.27$ \\
+$201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.15$ & $0.0028$ & $0.14$ & $0.15$ \\
+ \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.13$  & \color{red}  $0.86$  & \color{red}  $0.18$  & \color{red}  $0.99$\\
+ {\bf $201505350$ } & {\bf  $2$ } & {\bf  $0.70$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0025$ } & {\bf  $0.00013$ } & {\bf  $0.07$ } & {\bf  $0.0026$} \\
+ {\bf $201546283$ } & {\bf  $1$ } & {\bf  $0.15$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.16$ } & {\bf  $< 10^{-4}$} \\
+$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ \\
+ {\bf $201555883$ } & {\bf  $1$ } & {\bf  $0.94$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0044$ } & {\bf  $0.0004$ } & {\bf  $0.20$ } & {\bf  $0.0048$} \\
+ \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}  $0.0023$  & \color{red}  $0.14$  & \color{red}  $0.82$  & \color{red}  $0.07$  & \color{red}  $0.96$\\
+$201569483$ & $1$ & $2.06$ & $0.48$ & $0.00061$ & $0.097$ & $0.01$ & $0.58$ \\
+ {\bf $201577035$ } & {\bf  $1$ } & {\bf  $0.14$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00015$ } & {\bf  $0.20$ } & {\bf  $0.0002$} \\
+$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ \\
  {\bf $201613023$ } & {\bf  $1$ } & {\bf  $0.08$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0016$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.15$ } & {\bf  $0.0016$} \\
- {\bf $201546283$ } & {\bf  $1$ } & {\bf  $0.15$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.16$ } & {\bf  $< 10^{-4}$} \\
+$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ \\
+ {\bf $201629650$ } & {\bf  $1$ } & {\bf  $0.43$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.005$ } & {\bf  $0.0012$ } & {\bf  $0.17$ } & {\bf  $0.0062$} \\
+$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ \\
+ \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}  $0.81$  & \color{red}  $0.0016$  & \color{red}  $0.13$  & \color{red}  $0.01$  & \color{red}  $0.94$\\
+$201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.03$ & $0.29$ & $0.06$ & $0.32$ \\
+ {\bf $201736247$ } & {\bf  $1$ } & {\bf  $0.42$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0015$ } & {\bf  $0.00092$ } & {\bf  $0.22$ } & {\bf  $0.0024$} \\
+$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ \\
+$201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0099$ & $0.00069$ & $0.17$ & $0.011$ \\
 $201779067$ & $1$ & $1.97$ & $0.034$ & $0.038$ & $0.3$ & $0.03$ & $0.37$ \\
- \cellcolor{red} $201257461$  & \cellcolor{red}  $1$  & \cellcolor{red}  $0.59$  & \cellcolor{red}  $< 10^{-4}$  & \cellcolor{red}  $0.072$  & \cellcolor{red}  $0.93$  & \cellcolor{red}  $0.22$  & \cellcolor{red}  $1$\\
 $201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.014$ & $0.0024$ & $0.17$ & $0.016$ \\
-$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ \\
-$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ \\
-$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ \\
- {\bf $201295312$ } & {\bf  $1$ } & {\bf  $0.04$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.008$ } & {\bf  $0.00014$ } & {\bf  $0.15$ } & {\bf  $0.0082$} \\
  {\bf $201855371$ } & {\bf  $1$ } & {\bf  $0.62$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0006$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.20$ } & {\bf  $0.00071$} \\
- {\bf $201555883$ } & {\bf  $1$ } & {\bf  $0.94$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0044$ } & {\bf  $0.0004$ } & {\bf  $0.20$ } & {\bf  $0.0048$} \\
- {\bf $201629650$ } & {\bf  $1$ } & {\bf  $0.43$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.005$ } & {\bf  $0.0012$ } & {\bf  $0.17$ } & {\bf  $0.0062$} \\
- {\bf $201403446$ } & {\bf  $1$ } & {\bf  $0.18$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0069$ } & {\bf  $0.0013$ } & {\bf  $0.13$ } & {\bf  $0.0083$} \\
- \cellcolor{red} $201565013$  & \cellcolor{red}  $1$  & \cellcolor{red}  $1.69$  & \cellcolor{red}  $0.0023$  & \cellcolor{red}  $0.14$  & \cellcolor{red}  $0.82$  & \cellcolor{red}  $0.07$  & \cellcolor{red}  $0.96$\\
  {\bf $201912552$ } & {\bf  $1$ } & {\bf  $0.47$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00058$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.22$ } & {\bf  $0.00058$} \\
-$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ \\
-$201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.15$ & $0.0028$ & $0.14$ & $0.15$ \\
-$201569483$ & $1$ & $2.06$ & $0.48$ & $0.00061$ & $0.097$ & $0.01$ & $0.58$ \\
-$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$ \\
- \cellcolor{red} $201649426$  & \cellcolor{red}  $1$  & \cellcolor{red}  $3.10$  & \cellcolor{red}  $0.81$  & \cellcolor{red}  $0.0016$  & \cellcolor{red}  $0.13$  & \cellcolor{red}  $0.01$  & \cellcolor{red}  $0.94$\\
- {\bf $201577035$ } & {\bf  $1$ } & {\bf  $0.14$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00015$ } & {\bf  $0.20$ } & {\bf  $0.0002$} \\
-$201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.03$ & $0.29$ & $0.06$ & $0.32$ \\
-$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ \\
- {\bf $201736247$ } & {\bf  $1$ } & {\bf  $0.42$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0015$ } & {\bf  $0.00092$ } & {\bf  $0.22$ } & {\bf  $0.0024$} \\
- {\bf $201338508$ } & {\bf  $2$ } & {\bf  $0.33$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.006$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.17$ } & {\bf  $0.006$} \\
- {\bf $201367065$ } & {\bf  $2$ } & {\bf  $0.67$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00063$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.14$ } & {\bf  $0.00063$} \\
-$201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.22$ & $0.048$ & $0.18$ & $0.27$ \\
- {\bf $201505350$ } & {\bf  $2$ } & {\bf  $0.70$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0025$ } & {\bf  $0.00013$ } & {\bf  $0.07$ } & {\bf  $0.0026$} \\
-$201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0099$ & $0.00069$ & $0.17$ & $0.011$ \\
-$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ \\
- {\bf $201367065$ } & {\bf  $1$ } & {\bf  $0.15$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.01$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.18$ } & {\bf  $0.01$} \\
-$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ \\
- \cellcolor{red} $201505350$  & \cellcolor{red}  $1$  & \cellcolor{red}  $2.69$  & \cellcolor{red}  $< 10^{-4}$  & \cellcolor{red}  $0.13$  & \cellcolor{red}  $0.86$  & \cellcolor{red}  $0.18$  & \cellcolor{red}  $0.99$\\
-$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$
+$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$
 

### 2015-03-09 fpp/write_fpptable.py

@@ -59,6 +59,7 @@ fout.write(r"""
 """)
 
 folders = glob.glob('fppmodels/*')
+folders.sort()
 for f in folders:
     resultsfile = f + '/results.txt'
     for line in open(resultsfile,'r'):

### 2015-03-09 fpp/write_fpptable.py
fixing bold

@@ -18,11 +18,11 @@ def format_line(line, fpp):
     if fpp < 0.01:
         newline = ''
         for v in line.split('&'):
-            m = re.search('$(.*)$\s+\\\\',v)
+            m = re.search('\$(.*)\$\s+\\\\',v)
             if m:
-                newline += r' {\mathbf ' + m.group(1) + '} \\\\\n'
+                newline += r' ${\mathbf ' + m.group(1) + '}$ \\\\\n'
             else:
-                newline += r' {\mathbf ' + v + '} &'
+                newline += r' ${\mathbf ' + v + '}$ &'
     if fpp > 0.9:
         newline = ''
         for v in line.split('&'):

### 2015-03-09 table_fpp.tex
left-align
blah
fixing bold

@@
 %\LongTables
-\begin{deluxetable*}{lccccccc}
+\begin{deluxetable*}{lcllllll}
 \tablewidth{0pt}
@@
 \startdata
- {\bf $201208431$ } & {\bf  $1$ } & {\bf  $0.51$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0058$ } & {\bf  $0.00011$ } & {\bf  $0.22$ } & {\bf  $0.0059$} \\
- \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.072$  & \color{red}  $0.93$  & \color{red}  $0.22$  & \color{red}  $1$\\
- {\bf $201295312$ } & {\bf  $1$ } & {\bf  $0.04$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.008$ } & {\bf  $0.00014$ } & {\bf  $0.15$ } & {\bf  $0.0082$} \\
-$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ \\
- {\bf $201338508$ } & {\bf  $2$ } & {\bf  $0.33$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.006$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.17$ } & {\bf  $0.006$} \\
- {\bf $201367065$ } & {\bf  $1$ } & {\bf  $0.15$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.01$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.18$ } & {\bf  $0.01$} \\
- {\bf $201367065$ } & {\bf  $2$ } & {\bf  $0.67$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00063$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.14$ } & {\bf  $0.00063$} \\
- {\bf $201384232$ } & {\bf  $1$ } & {\bf  $0.44$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00017$ } & {\bf  $0.00023$ } & {\bf  $0.21$ } & {\bf  $0.0004$} \\
-$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ \\
- {\bf $201403446$ } & {\bf  $1$ } & {\bf  $0.18$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0069$ } & {\bf  $0.0013$ } & {\bf  $0.13$ } & {\bf  $0.0083$} \\
-$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ \\
+ {\mathbf $201208431$ } & {\mathbf  $1$ } & {\mathbf  $0.51$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.0058$ } & {\mathbf  $0.00011$ } & {\mathbf  $0.22$ } & {\mathbf  $0.0059$ \\
+} & \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.072$  & \color{red}  $0.93$  & \color{red}  $0.22$  & \color{red}  $1$\\
+ {\mathbf $201295312$ } & {\mathbf  $1$ } & {\mathbf  $0.04$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.008$ } & {\mathbf  $0.00014$ } & {\mathbf  $0.15$ } & {\mathbf  $0.0082$ \\
+} &$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ \\
+ {\mathbf $201338508$ } & {\mathbf  $2$ } & {\mathbf  $0.33$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.006$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.17$ } & {\mathbf  $0.006$ \\
+} & {\mathbf $201367065$ } & {\mathbf  $1$ } & {\mathbf  $0.15$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.01$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.18$ } & {\mathbf  $0.01$ \\
+} & {\mathbf $201367065$ } & {\mathbf  $2$ } & {\mathbf  $0.67$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.00063$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.14$ } & {\mathbf  $0.00063$ \\
+} & {\mathbf $201384232$ } & {\mathbf  $1$ } & {\mathbf  $0.44$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.00017$ } & {\mathbf  $0.00023$ } & {\mathbf  $0.21$ } & {\mathbf  $0.0004$ \\
+} &$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ \\
+ {\mathbf $201403446$ } & {\mathbf  $1$ } & {\mathbf  $0.18$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.0069$ } & {\mathbf  $0.0013$ } & {\mathbf  $0.13$ } & {\mathbf  $0.0083$ \\
+} &$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ \\
 $201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.22$ & $0.048$ & $0.18$ & $0.27$ \\
@@
  \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.13$  & \color{red}  $0.86$  & \color{red}  $0.18$  & \color{red}  $0.99$\\
- {\bf $201505350$ } & {\bf  $2$ } & {\bf  $0.70$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0025$ } & {\bf  $0.00013$ } & {\bf  $0.07$ } & {\bf  $0.0026$} \\
- {\bf $201546283$ } & {\bf  $1$ } & {\bf  $0.15$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.16$ } & {\bf  $< 10^{-4}$} \\
-$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ \\
- {\bf $201555883$ } & {\bf  $1$ } & {\bf  $0.94$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0044$ } & {\bf  $0.0004$ } & {\bf  $0.20$ } & {\bf  $0.0048$} \\
- \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}  $0.0023$  & \color{red}  $0.14$  & \color{red}  $0.82$  & \color{red}  $0.07$  & \color{red}  $0.96$\\
+ {\mathbf $201505350$ } & {\mathbf  $2$ } & {\mathbf  $0.70$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.0025$ } & {\mathbf  $0.00013$ } & {\mathbf  $0.07$ } & {\mathbf  $0.0026$ \\
+} & {\mathbf $201546283$ } & {\mathbf  $1$ } & {\mathbf  $0.15$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.16$ } & {\mathbf  $< 10^{-4}$ \\
+} &$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ \\
+ {\mathbf $201555883$ } & {\mathbf  $1$ } & {\mathbf  $0.94$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.0044$ } & {\mathbf  $0.0004$ } & {\mathbf  $0.20$ } & {\mathbf  $0.0048$ \\
+} & \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}  $0.0023$  & \color{red}  $0.14$  & \color{red}  $0.82$  & \color{red}  $0.07$  & \color{red}  $0.96$\\
 $201569483$ & $1$ & $2.06$ & $0.48$ & $0.00061$ & $0.097$ & $0.01$ & $0.58$ \\
- {\bf $201577035$ } & {\bf  $1$ } & {\bf  $0.14$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00015$ } & {\bf  $0.20$ } & {\bf  $0.0002$} \\
-$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ \\
- {\bf $201613023$ } & {\bf  $1$ } & {\bf  $0.08$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0016$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.15$ } & {\bf  $0.0016$} \\
-$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ \\
- {\bf $201629650$ } & {\bf  $1$ } & {\bf  $0.43$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.005$ } & {\bf  $0.0012$ } & {\bf  $0.17$ } & {\bf  $0.0062$} \\
-$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ \\
+ {\mathbf $201577035$ } & {\mathbf  $1$ } & {\mathbf  $0.14$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.00015$ } & {\mathbf  $0.20$ } & {\mathbf  $0.0002$ \\
+} &$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ \\
+ {\mathbf $201613023$ } & {\mathbf  $1$ } & {\mathbf  $0.08$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.0016$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.15$ } & {\mathbf  $0.0016$ \\
+} &$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ \\
+ {\mathbf $201629650$ } & {\mathbf  $1$ } & {\mathbf  $0.43$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.005$ } & {\mathbf  $0.0012$ } & {\mathbf  $0.17$ } & {\mathbf  $0.0062$ \\
+} &$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ \\
  \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}  $0.81$  & \color{red}  $0.0016$  & \color{red}  $0.13$  & \color{red}  $0.01$  & \color{red}  $0.94$\\
 $201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.03$ & $0.29$ & $0.06$ & $0.32$ \\
- {\bf $201736247$ } & {\bf  $1$ } & {\bf  $0.42$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0015$ } & {\bf  $0.00092$ } & {\bf  $0.22$ } & {\bf  $0.0024$} \\
-$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ \\
+ {\mathbf $201736247$ } & {\mathbf  $1$ } & {\mathbf  $0.42$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.0015$ } & {\mathbf  $0.00092$ } & {\mathbf  $0.22$ } & {\mathbf  $0.0024$ \\
+} &$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ \\
 $201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0099$ & $0.00069$ & $0.17$ & $0.011$ \\
@@
 $201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.014$ & $0.0024$ & $0.17$ & $0.016$ \\
- {\bf $201855371$ } & {\bf  $1$ } & {\bf  $0.62$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0006$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.20$ } & {\bf  $0.00071$} \\
- {\bf $201912552$ } & {\bf  $1$ } & {\bf  $0.47$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00058$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.22$ } & {\bf  $0.00058$} \\
-$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$
+ {\mathbf $201855371$ } & {\mathbf  $1$ } & {\mathbf  $0.62$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.0006$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.20$ } & {\mathbf  $0.00071$ \\
+} & {\mathbf $201912552$ } & {\mathbf  $1$ } & {\mathbf  $0.47$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.00058$ } & {\mathbf  $< 10^{-4}$ } & {\mathbf  $0.22$ } & {\mathbf  $0.00058$ \\
+} &$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$
 

### 2015-03-09 fpp/write_fpptable.py
bold working?

@@ -22,7 +22,8 @@ def format_line(line, fpp):
             if m:
                 newline += r' ${\mathbf ' + m.group(1) + '}$ \\\\\n'
             else:
-                newline += r' ${\mathbf ' + v + '}$ &'
+                m = re.search('\$(.*)\$',v)
+                newline += r' ${\mathbf ' + m.group(1) + '}$ &'
     if fpp > 0.9:
         newline = ''
         for v in line.split('&'):

### 2015-03-09 fpp/write_fpptable.py
took out formatting

@@ -41,7 +41,7 @@ fout = open('../table_fpp.tex','w')
 fout.write(r"""
 \clearpage
 %\LongTables
-\begin{deluxetable*}{lcllllll}
+\begin{deluxetable*}{lcllllllc}
 \tablewidth{0pt}
 \tabletypesize{\scriptsize}
 \tablecaption{False Positive Probability Calculation Results}
@@ -54,7 +54,8 @@ fout.write(r"""
 \colhead{${\rm Pr}_{\rm BEB}$} &
 \colhead{${\rm Pr}_{\rm HEB}$} &
 \colhead{$f_{p}$} &
-\colhead{FPP}
+\colhead{FPP} &
+\colhead{Disposition}
 }
 \startdata
 """)
@@ -75,11 +76,20 @@ for f in folders:
         val = float(val)
         line += '{} & '.format(prob_entry(val))
     line += '${:.2f}$ & '.format(float(fp))
-    line += '{} '.format(prob_entry(FPP))
+    line += '{} & '.format(prob_entry(FPP))
+    FPP = float(FPP)
+    if FPP < 0.01:
+        disp = 'Validated'
+    elif FPP > 0.9:
+        disp = 'FP'
+    else:
+        disp = 'Candidate'
+    line += '{} '.format(disp)
     if f != folders[-1]:
         line += '\\\\'
     line += '\n'
-    fout.write(format_line(line,FPP))
+    fout.write(line)
+    #fout.write(format_line(line,FPP))
 
 
 fout.write(r"""

### 2015-03-09 table_fpp.tex
ok, bold really working?
put back red for FPs

--- 2015-03-09 table_fpp.tex
@@
 %\LongTables
-\begin{deluxetable*}{lccccccc}
+\begin{deluxetable*}{lcllllllc}
 \tablewidth{0pt}
@@
 \colhead{$f_{p}$} &
-\colhead{FPP}
+\colhead{FPP} &
+\colhead{Disposition}
 }
 \startdata
- {\bf $201208431$ } & {\bf  $1$ } & {\bf  $0.51$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0058$ } & {\bf  $0.00011$ } & {\bf  $0.22$ } & {\bf  $0.0059$} \\
- \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.072$  & \color{red}  $0.93$  & \color{red}  $0.22$  & \color{red}  $1$\\
- {\bf $201295312$ } & {\bf  $1$ } & {\bf  $0.04$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.008$ } & {\bf  $0.00014$ } & {\bf  $0.15$ } & {\bf  $0.0082$} \\
-$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ \\
- {\bf $201338508$ } & {\bf  $2$ } & {\bf  $0.33$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.006$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.17$ } & {\bf  $0.006$} \\
- {\bf $201367065$ } & {\bf  $1$ } & {\bf  $0.15$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.01$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.18$ } & {\bf  $0.01$} \\
- {\bf $201367065$ } & {\bf  $2$ } & {\bf  $0.67$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00063$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.14$ } & {\bf  $0.00063$} \\
- {\bf $201384232$ } & {\bf  $1$ } & {\bf  $0.44$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00017$ } & {\bf  $0.00023$ } & {\bf  $0.21$ } & {\bf  $0.0004$} \\
-$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ \\
- {\bf $201403446$ } & {\bf  $1$ } & {\bf  $0.18$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0069$ } & {\bf  $0.0013$ } & {\bf  $0.13$ } & {\bf  $0.0083$} \\
-$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ \\
-$201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.22$ & $0.048$ & $0.18$ & $0.27$ \\
-$201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.15$ & $0.0028$ & $0.14$ & $0.15$ \\
- \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.13$  & \color{red}  $0.86$  & \color{red}  $0.18$  & \color{red}  $0.99$\\
- {\bf $201505350$ } & {\bf  $2$ } & {\bf  $0.70$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0025$ } & {\bf  $0.00013$ } & {\bf  $0.07$ } & {\bf  $0.0026$} \\
- {\bf $201546283$ } & {\bf  $1$ } & {\bf  $0.15$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.16$ } & {\bf  $< 10^{-4}$} \\
-$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ \\
- {\bf $201555883$ } & {\bf  $1$ } & {\bf  $0.94$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0044$ } & {\bf  $0.0004$ } & {\bf  $0.20$ } & {\bf  $0.0048$} \\
- \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}  $0.0023$  & \color{red}  $0.14$  & \color{red}  $0.82$  & \color{red}  $0.07$  & \color{red}  $0.96$\\
-$201569483$ & $1$ & $2.06$ & $0.48$ & $0.00061$ & $0.097$ & $0.01$ & $0.58$ \\
- {\bf $201577035$ } & {\bf  $1$ } & {\bf  $0.14$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00015$ } & {\bf  $0.20$ } & {\bf  $0.0002$} \\
-$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ \\
- {\bf $201613023$ } & {\bf  $1$ } & {\bf  $0.08$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0016$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.15$ } & {\bf  $0.0016$} \\
-$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ \\
- {\bf $201629650$ } & {\bf  $1$ } & {\bf  $0.43$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.005$ } & {\bf  $0.0012$ } & {\bf  $0.17$ } & {\bf  $0.0062$} \\
-$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ \\
- \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}  $0.81$  & \color{red}  $0.0016$  & \color{red}  $0.13$  & \color{red}  $0.01$  & \color{red}  $0.94$\\
-$201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.03$ & $0.29$ & $0.06$ & $0.32$ \\
- {\bf $201736247$ } & {\bf  $1$ } & {\bf  $0.42$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0015$ } & {\bf  $0.00092$ } & {\bf  $0.22$ } & {\bf  $0.0024$} \\
-$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ \\
-$201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0099$ & $0.00069$ & $0.17$ & $0.011$ \\
-$201779067$ & $1$ & $1.97$ & $0.034$ & $0.038$ & $0.3$ & $0.03$ & $0.37$ \\
-$201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.014$ & $0.0024$ & $0.17$ & $0.016$ \\
- {\bf $201855371$ } & {\bf  $1$ } & {\bf  $0.62$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0006$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.20$ } & {\bf  $0.00071$} \\
- {\bf $201912552$ } & {\bf  $1$ } & {\bf  $0.47$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00058$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.22$ } & {\bf  $0.00058$} \\
-$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$
+$201208431$ & $1$ & $0.51$ & $< 10^{-4}$ & $0.0058$ & $0.00011$ & $0.22$ & $0.0059$ & Validated \\
+ \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.072$  & \color{red}  $0.93$  & \color{red}  $0.22$  & \color{red}  $1$  & \color{red}  FP\\
+$201295312$ & $1$ & $0.04$ & $< 10^{-4}$ & $0.008$ & $0.00014$ & $0.15$ & $0.0082$ & Validated \\
+$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ & Candidate \\
+$201338508$ & $2$ & $0.33$ & $< 10^{-4}$ & $0.006$ & $< 10^{-4}$ & $0.17$ & $0.006$ & Validated \\
+$201367065$ & $1$ & $0.15$ & $< 10^{-4}$ & $0.01$ & $< 10^{-4}$ & $0.18$ & $0.01$ & Validated \\
+$201367065$ & $2$ & $0.67$ & $< 10^{-4}$ & $0.00063$ & $< 10^{-4}$ & $0.14$ & $0.00063$ & Validated \\
+$201384232$ & $1$ & $0.44$ & $< 10^{-4}$ & $0.00017$ & $0.00023$ & $0.21$ & $0.0004$ & Validated \\
+$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ & Candidate \\
+$201403446$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.0069$ & $0.0013$ & $0.13$ & $0.0083$ & Validated \\
+$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ & Candidate \\
+$201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.22$ & $0.048$ & $0.18$ & $0.27$ & Candidate \\
+$201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.15$ & $0.0028$ & $0.14$ & $0.15$ & Candidate \\
+ \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.13$  & \color{red}  $0.86$  & \color{red}  $0.18$  & \color{red}  $0.99$  & \color{red}  FP\\
+$201505350$ & $2$ & $0.70$ & $< 10^{-4}$ & $0.0025$ & $0.00013$ & $0.07$ & $0.0026$ & Validated \\
+$201546283$ & $1$ & $0.15$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Validated \\
+$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ & Candidate \\
+$201555883$ & $1$ & $0.94$ & $< 10^{-4}$ & $0.0044$ & $0.0004$ & $0.20$ & $0.0048$ & Validated \\
+ \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}  $0.0023$  & \color{red}  $0.14$  & \color{red}  $0.82$  & \color{red}  $0.07$  & \color{red}  $0.96$  & \color{red}  FP\\
+$201569483$ & $1$ & $2.06$ & $0.48$ & $0.00061$ & $0.097$ & $0.01$ & $0.58$ & Candidate \\
+$201577035$ & $1$ & $0.14$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.00015$ & $0.20$ & $0.0002$ & Validated \\
+$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ & Candidate \\
+$201613023$ & $1$ & $0.08$ & $< 10^{-4}$ & $0.0016$ & $< 10^{-4}$ & $0.15$ & $0.0016$ & Validated \\
+$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ & Candidate \\
+$201629650$ & $1$ & $0.43$ & $< 10^{-4}$ & $0.005$ & $0.0012$ & $0.17$ & $0.0062$ & Validated \\
+$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ & Candidate \\
+ \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}  $0.81$  & \color{red}  $0.0016$  & \color{red}  $0.13$  & \color{red}  $0.01$  & \color{red}  $0.94$  & \color{red}  FP\\
+$201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.03$ & $0.29$ & $0.06$ & $0.32$ & Candidate \\
+$201736247$ & $1$ & $0.42$ & $< 10^{-4}$ & $0.0015$ & $0.00092$ & $0.22$ & $0.0024$ & Validated \\
+$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ & Candidate \\
+$201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0099$ & $0.00069$ & $0.17$ & $0.011$ & Candidate \\
+$201779067$ & $1$ & $1.97$ & $0.034$ & $0.038$ & $0.3$ & $0.03$ & $0.37$ & Candidate \\
+$201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.014$ & $0.0024$ & $0.17$ & $0.016$ & Candidate \\
+$201855371$ & $1$ & $0.62$ & $< 10^{-4}$ & $0.0006$ & $< 10^{-4}$ & $0.20$ & $0.00071$ & Validated \\
+$201912552$ & $1$ & $0.47$ & $< 10^{-4}$ & $0.00058$ & $< 10^{-4}$ & $0.22$ & $0.00058$ & Validated \\
+$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$ & Candidate
 

### 2015-03-09 table_fpp.tex
wording

@@
 $201208431$ & $1$ & $0.51$ & $< 10^{-4}$ & $0.0058$ & $0.00011$ & $0.22$ & $0.0059$ & Validated \\
- \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.072$  & \color{red}  $0.93$  & \color{red}  $0.22$  & \color{red}  $1$  & \color{red}  FP\\
+$201257461$ & $1$ & $0.59$ & $< 10^{-4}$ & $0.072$ & $0.93$ & $0.22$ & $1$ & FP \\
 $201295312$ & $1$ & $0.04$ & $< 10^{-4}$ & $0.008$ & $0.00014$ & $0.15$ & $0.0082$ & Validated \\
@@
 $201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.15$ & $0.0028$ & $0.14$ & $0.15$ & Candidate \\
- \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.13$  & \color{red}  $0.86$  & \color{red}  $0.18$  & \color{red}  $0.99$  & \color{red}  FP\\
+$201505350$ & $1$ & $2.69$ & $< 10^{-4}$ & $0.13$ & $0.86$ & $0.18$ & $0.99$ & FP \\
 $201505350$ & $2$ & $0.70$ & $< 10^{-4}$ & $0.0025$ & $0.00013$ & $0.07$ & $0.0026$ & Validated \\
@@
 $201555883$ & $1$ & $0.94$ & $< 10^{-4}$ & $0.0044$ & $0.0004$ & $0.20$ & $0.0048$ & Validated \\
- \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}  $0.0023$  & \color{red}  $0.14$  & \color{red}  $0.82$  & \color{red}  $0.07$  & \color{red}  $0.96$  & \color{red}  FP\\
+$201565013$ & $1$ & $1.69$ & $0.0023$ & $0.14$ & $0.82$ & $0.07$ & $0.96$ & FP \\
 $201569483$ & $1$ & $2.06$ & $0.48$ & $0.00061$ & $0.097$ & $0.01$ & $0.58$ & Candidate \\
@@
 $201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ & Candidate \\
- \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}  $0.81$  & \color{red}  $0.0016$  & \color{red}  $0.13$  & \color{red}  $0.01$  & \color{red}  $0.94$  & \color{red}  FP\\
+$201649426$ & $1$ & $3.10$ & $0.81$ & $0.0016$ & $0.13$ & $0.01$ & $0.94$ & FP \\
 $201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.03$ & $0.29$ & $0.06$ & $0.32$ & Candidate \\

### 2015-03-10 table_fpp.tex
redid FPPs with contrast curves

@@
 \startdata
-$201208431$ & $1$ & $0.51$ & $< 10^{-4}$ & $0.0058$ & $0.00011$ & $0.22$ & $0.0059$ & Validated \\
-$201257461$ & $1$ & $0.59$ & $< 10^{-4}$ & $0.072$ & $0.93$ & $0.22$ & $1$ & FP \\
-$201295312$ & $1$ & $0.04$ & $< 10^{-4}$ & $0.008$ & $0.00014$ & $0.15$ & $0.0082$ & Validated \\
-$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ & Candidate \\
-$201338508$ & $2$ & $0.33$ & $< 10^{-4}$ & $0.006$ & $< 10^{-4}$ & $0.17$ & $0.006$ & Validated \\
-$201367065$ & $1$ & $0.15$ & $< 10^{-4}$ & $0.01$ & $< 10^{-4}$ & $0.18$ & $0.01$ & Validated \\
-$201367065$ & $2$ & $0.67$ & $< 10^{-4}$ & $0.00063$ & $< 10^{-4}$ & $0.14$ & $0.00063$ & Validated \\
-$201384232$ & $1$ & $0.44$ & $< 10^{-4}$ & $0.00017$ & $0.00023$ & $0.21$ & $0.0004$ & Validated \\
-$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ & Candidate \\
-$201403446$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.0069$ & $0.0013$ & $0.13$ & $0.0083$ & Validated \\
-$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ & Candidate \\
-$201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.22$ & $0.048$ & $0.18$ & $0.27$ & Candidate \\
-$201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.15$ & $0.0028$ & $0.14$ & $0.15$ & Candidate \\
-$201505350$ & $1$ & $2.69$ & $< 10^{-4}$ & $0.13$ & $0.86$ & $0.18$ & $0.99$ & FP \\
-$201505350$ & $2$ & $0.70$ & $< 10^{-4}$ & $0.0025$ & $0.00013$ & $0.07$ & $0.0026$ & Validated \\
-$201546283$ & $1$ & $0.15$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Validated \\
-$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ & Candidate \\
-$201555883$ & $1$ & $0.94$ & $< 10^{-4}$ & $0.0044$ & $0.0004$ & $0.20$ & $0.0048$ & Validated \\
-$201565013$ & $1$ & $1.69$ & $0.0023$ & $0.14$ & $0.82$ & $0.07$ & $0.96$ & FP \\
-$201569483$ & $1$ & $2.06$ & $0.48$ & $0.00061$ & $0.097$ & $0.01$ & $0.58$ & Candidate \\
-$201577035$ & $1$ & $0.14$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.00015$ & $0.20$ & $0.0002$ & Validated \\
-$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ & Candidate \\
-$201613023$ & $1$ & $0.08$ & $< 10^{-4}$ & $0.0016$ & $< 10^{-4}$ & $0.15$ & $0.0016$ & Validated \\
-$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ & Candidate \\
-$201629650$ & $1$ & $0.43$ & $< 10^{-4}$ & $0.005$ & $0.0012$ & $0.17$ & $0.0062$ & Validated \\
-$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ & Candidate \\
-$201649426$ & $1$ & $3.10$ & $0.81$ & $0.0016$ & $0.13$ & $0.01$ & $0.94$ & FP \\
-$201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.03$ & $0.29$ & $0.06$ & $0.32$ & Candidate \\
-$201736247$ & $1$ & $0.42$ & $< 10^{-4}$ & $0.0015$ & $0.00092$ & $0.22$ & $0.0024$ & Validated \\
-$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ & Candidate \\
-$201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0099$ & $0.00069$ & $0.17$ & $0.011$ & Candidate \\
-$201779067$ & $1$ & $1.97$ & $0.034$ & $0.038$ & $0.3$ & $0.03$ & $0.37$ & Candidate \\
-$201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.014$ & $0.0024$ & $0.17$ & $0.016$ & Candidate \\
-$201855371$ & $1$ & $0.62$ & $< 10^{-4}$ & $0.0006$ & $< 10^{-4}$ & $0.20$ & $0.00071$ & Validated \\
-$201912552$ & $1$ & $0.47$ & $< 10^{-4}$ & $0.00058$ & $< 10^{-4}$ & $0.22$ & $0.00058$ & Validated \\
-$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$ & Candidate
+$201208431$ & $1$ & $0.51$ & $< 10^{-4}$ & $0.00074$ & $0.0001$ & $0.22$ & $0.00084$ & Planet \\
+ \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.011$  & \color{red}  $0.99$  & \color{red}  $0.22$  & \color{red}  $1$  & \color{red}  FP\\
+$201295312$ & $1$ & $0.04$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.0001$ & $0.15$ & $0.00011$ & Planet \\
+$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.004$ & $0.00059$ & $0.17$ & $0.0046$ & Planet \\
+$201338508$ & $2$ & $0.33$ & $< 10^{-4}$ & $0.00077$ & $< 10^{-4}$ & $0.17$ & $0.00077$ & Planet \\
+$201367065$ & $1$ & $0.15$ & $< 10^{-4}$ & $0.0013$ & $< 10^{-4}$ & $0.18$ & $0.0013$ & Planet \\
+$201367065$ & $2$ & $0.67$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.14$ & $< 10^{-4}$ & Planet \\
+$201384232$ & $1$ & $0.44$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.00021$ & $0.21$ & $0.00023$ & Planet \\
+$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.0026$ & $0.022$ & $0.17$ & $0.025$ & Candidate \\
+$201403446$ & $1$ & $0.18$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.00098$ & $0.13$ & $0.001$ & Planet \\
+$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.0018$ & $0.049$ & $0.22$ & $0.051$ & Candidate \\
+$201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.034$ & $0.055$ & $0.18$ & $0.089$ & Candidate \\
+$201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.021$ & $0.003$ & $0.14$ & $0.025$ & Candidate \\
+ \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.02$  & \color{red}  $0.97$  & \color{red}  $0.18$  & \color{red}  $0.99$  & \color{red}  FP\\
+$201505350$ & $2$ & $0.70$ & $< 10^{-4}$ & $0.0003$ & $0.00012$ & $0.07$ & $0.00042$ & Planet \\
+$201546283$ & $1$ & $0.15$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Planet \\
+$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.0017$ & $0.00065$ & $0.20$ & $0.0024$ & Planet \\
+$201555883$ & $1$ & $0.94$ & $< 10^{-4}$ & $0.00058$ & $0.00037$ & $0.20$ & $0.00095$ & Planet \\
+ \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}  $0.0027$  & \color{red}  $0.027$  & \color{red}  $0.93$  & \color{red}  $0.07$  & \color{red}  $0.96$  & \color{red}  FP\\
+$201569483$ & $1$ & $2.06$ & $0.47$ & $< 10^{-4}$ & $0.092$ & $0.01$ & $0.56$ & Candidate \\
+$201577035$ & $1$ & $0.14$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.0001$ & $0.20$ & $0.00011$ & Planet \\
+$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.0013$ & $0.0021$ & $0.17$ & $0.0034$ & Planet \\
+$201613023$ & $1$ & $0.08$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.15$ & $< 10^{-4}$ & Planet \\
+$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.016$ & $0.0017$ & $0.16$ & $0.018$ & Candidate \\
+$201629650$ & $1$ & $0.43$ & $< 10^{-4}$ & $0.00063$ & $0.0011$ & $0.17$ & $0.0017$ & Planet \\
+$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.0075$ & $0.069$ & $0.09$ & $0.076$ & Candidate \\
+ \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}  $0.82$  & \color{red}  $0.00022$  & \color{red}  $0.12$  & \color{red}  $0.01$  & \color{red}  $0.94$  & \color{red}  FP\\
+$201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.004$ & $0.28$ & $0.06$ & $0.28$ & Candidate \\
+$201736247$ & $1$ & $0.42$ & $< 10^{-4}$ & $0.00019$ & $0.00085$ & $0.22$ & $0.001$ & Planet \\
+$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.0019$ & $0.0015$ & $0.18$ & $0.0034$ & Planet \\
+$201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0013$ & $0.00064$ & $0.17$ & $0.0019$ & Planet \\
+$201779067$ & $1$ & $1.97$ & $0.036$ & $0.005$ & $0.29$ & $0.03$ & $0.33$ & Candidate \\
+$201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.0017$ & $0.0022$ & $0.17$ & $0.0039$ & Planet \\
+$201855371$ & $1$ & $0.62$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $0.00017$ & Planet \\
+$201912552$ & $1$ & $0.47$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
+$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.0068$ & $0.052$ & $0.05$ & $0.059$ & Candidate
 

### 2015-03-10 table_fpp.tex
fpp table changes

--- 2015-03-09 table_fpp.tex
@@
 %\LongTables
-\begin{deluxetable*}{lcllllllc}
+\begin{deluxetable*}{lclccccccc}
 \tablewidth{0pt}
@@
 \colhead{max($\delta_{\rm sec}$)} &
+\colhead{AO?} &
 \colhead{${\rm Pr}_{\rm EB}$} &
@@
 \startdata
-$201208431$ & $1$ & $0.51$ & $< 10^{-4}$ & $0.0058$ & $0.00011$ & $0.22$ & $0.0059$ & Validated \\
-$201257461$ & $1$ & $0.59$ & $< 10^{-4}$ & $0.072$ & $0.93$ & $0.22$ & $1$ & FP \\
-$201295312$ & $1$ & $0.04$ & $< 10^{-4}$ & $0.008$ & $0.00014$ & $0.15$ & $0.0082$ & Validated \\
-$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ & Candidate \\
-$201338508$ & $2$ & $0.33$ & $< 10^{-4}$ & $0.006$ & $< 10^{-4}$ & $0.17$ & $0.006$ & Validated \\
-$201367065$ & $1$ & $0.15$ & $< 10^{-4}$ & $0.01$ & $< 10^{-4}$ & $0.18$ & $0.01$ & Validated \\
-$201367065$ & $2$ & $0.67$ & $< 10^{-4}$ & $0.00063$ & $< 10^{-4}$ & $0.14$ & $0.00063$ & Validated \\
-$201384232$ & $1$ & $0.44$ & $< 10^{-4}$ & $0.00017$ & $0.00023$ & $0.21$ & $0.0004$ & Validated \\
-$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ & Candidate \\
-$201403446$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.0069$ & $0.0013$ & $0.13$ & $0.0083$ & Validated \\
-$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ & Candidate \\
-$201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.22$ & $0.048$ & $0.18$ & $0.27$ & Candidate \\
-$201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.15$ & $0.0028$ & $0.14$ & $0.15$ & Candidate \\
-$201505350$ & $1$ & $2.69$ & $< 10^{-4}$ & $0.13$ & $0.86$ & $0.18$ & $0.99$ & FP \\
-$201505350$ & $2$ & $0.70$ & $< 10^{-4}$ & $0.0025$ & $0.00013$ & $0.07$ & $0.0026$ & Validated \\
-$201546283$ & $1$ & $0.15$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Validated \\
-$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ & Candidate \\
-$201555883$ & $1$ & $0.94$ & $< 10^{-4}$ & $0.0044$ & $0.0004$ & $0.20$ & $0.0048$ & Validated \\
-$201565013$ & $1$ & $1.69$ & $0.0023$ & $0.14$ & $0.82$ & $0.07$ & $0.96$ & FP \\
-$201569483$ & $1$ & $2.06$ & $0.48$ & $0.00061$ & $0.097$ & $0.01$ & $0.58$ & Candidate \\
-$201577035$ & $1$ & $0.14$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.00015$ & $0.20$ & $0.0002$ & Validated \\
-$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ & Candidate \\
-$201613023$ & $1$ & $0.08$ & $< 10^{-4}$ & $0.0016$ & $< 10^{-4}$ & $0.15$ & $0.0016$ & Validated \\
-$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ & Candidate \\
-$201629650$ & $1$ & $0.43$ & $< 10^{-4}$ & $0.005$ & $0.0012$ & $0.17$ & $0.0062$ & Validated \\
-$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ & Candidate \\
-$201649426$ & $1$ & $3.10$ & $0.81$ & $0.0016$ & $0.13$ & $0.01$ & $0.94$ & FP \\
-$201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.03$ & $0.29$ & $0.06$ & $0.32$ & Candidate \\
-$201736247$ & $1$ & $0.42$ & $< 10^{-4}$ & $0.0015$ & $0.00092$ & $0.22$ & $0.0024$ & Validated \\
-$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ & Candidate \\
-$201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0099$ & $0.00069$ & $0.17$ & $0.011$ & Candidate \\
-$201779067$ & $1$ & $1.97$ & $0.034$ & $0.038$ & $0.3$ & $0.03$ & $0.37$ & Candidate \\
-$201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.014$ & $0.0024$ & $0.17$ & $0.016$ & Candidate \\
-$201855371$ & $1$ & $0.62$ & $< 10^{-4}$ & $0.0006$ & $< 10^{-4}$ & $0.20$ & $0.00071$ & Validated \\
-$201912552$ & $1$ & $0.47$ & $< 10^{-4}$ & $0.00058$ & $< 10^{-4}$ & $0.22$ & $0.00058$ & Validated \\
-$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$ & Candidate
+$201208431$ & $1$ & $0.51$ &  - & $< 10^{-4}$ & $7.4\times10^{-4}$ & $1.0\times10^{-4}$ & $0.22$ & $8.4\times10^{-4}$ & Planet \\
+ \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $0.011$  & \color{red}  $0.989$  & \color{red}  $0.22$  & \color{red}  $1.000$  & \color{red}  FP\\
+$201295312$ & $1$ & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $1.0\times10^{-4}$ & $0.15$ & $1.1\times10^{-4}$ & Planet \\
+$201338508$ & $1$ & $0.63$ &  - & $< 10^{-4}$ & $4.0\times10^{-3}$ & $5.9\times10^{-4}$ & $0.17$ & $4.6\times10^{-3}$ & Planet \\
+$201338508$ & $2$ & $0.33$ &  - & $< 10^{-4}$ & $7.7\times10^{-4}$ & $< 10^{-4}$ & $0.17$ & $7.7\times10^{-4}$ & Planet \\
+$201367065$ & $1$ & $0.15$ &  - & $< 10^{-4}$ & $1.3\times10^{-3}$ & $< 10^{-4}$ & $0.18$ & $1.3\times10^{-3}$ & Planet \\
+$201367065$ & $2$ & $0.67$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.14$ & $< 10^{-4}$ & Planet \\
+$201384232$ & $1$ & $0.44$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.1\times10^{-4}$ & $0.21$ & $2.3\times10^{-4}$ & Planet \\
+$201393098$ & $1$ & $0.52$ &  - & $< 10^{-4}$ & $2.6\times10^{-3}$ & $0.022$ & $0.17$ & $0.025$ & Candidate \\
+$201403446$ & $1$ & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $9.8\times10^{-4}$ & $0.13$ & $10.0\times10^{-4}$ & Planet \\
+$201445392$ & $1$ & $0.26$ &  - & $< 10^{-4}$ & $1.8\times10^{-3}$ & $0.049$ & $0.22$ & $0.051$ & Candidate \\
+$201445392$ & $2$ & $0.18$ &  - & $< 10^{-4}$ & $0.034$ & $0.055$ & $0.18$ & $0.089$ & Candidate \\
+$201465501$ & $1$ & $0.68$ &  - & $< 10^{-4}$ & $0.021$ & $3.0\times10^{-3}$ & $0.14$ & $0.025$ & Candidate \\
+ \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $0.020$  & \color{red}  $0.966$  & \color{red}  $0.18$  & \color{red}  $0.986$  & \color{red}  FP\\
+$201505350$ & $2$ & $0.70$ &  - & $< 10^{-4}$ & $3.0\times10^{-4}$ & $1.2\times10^{-4}$ & $0.07$ & $4.2\times10^{-4}$ & Planet \\
+$201546283$ & $1$ & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Planet \\
+$201549860$ & $1$ & $0.18$ &  - & $< 10^{-4}$ & $1.7\times10^{-3}$ & $6.5\times10^{-4}$ & $0.20$ & $2.4\times10^{-3}$ & Planet \\
+$201555883$ & $1$ & $0.94$ &  - & $< 10^{-4}$ & $5.8\times10^{-4}$ & $3.7\times10^{-4}$ & $0.20$ & $9.5\times10^{-4}$ & Planet \\
+ \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}   -  & \color{red}  $2.7\times10^{-3}$  & \color{red}  $0.027$  & \color{red}  $0.926$  & \color{red}  $0.07$  & \color{red}  $0.956$  & \color{red}  FP\\
+$201569483$ & $1$ & $2.06$ &  - & $0.468$ & $< 10^{-4}$ & $0.092$ & $0.01$ & $0.560$ & Candidate \\
+$201577035$ & $1$ & $0.14$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $1.0\times10^{-4}$ & $0.20$ & $1.1\times10^{-4}$ & Planet \\
+$201596316$ & $1$ & $0.45$ &  - & $< 10^{-4}$ & $1.3\times10^{-3}$ & $2.1\times10^{-3}$ & $0.17$ & $3.4\times10^{-3}$ & Planet \\
+$201613023$ & $1$ & $0.08$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.15$ & $< 10^{-4}$ & Planet \\
+$201617985$ & $1$ & $0.27$ &  - & $< 10^{-4}$ & $0.016$ & $1.7\times10^{-3}$ & $0.16$ & $0.018$ & Candidate \\
+$201629650$ & $1$ & $0.43$ &  - & $< 10^{-4}$ & $6.3\times10^{-4}$ & $1.1\times10^{-3}$ & $0.17$ & $1.7\times10^{-3}$ & Planet \\
+$201635569$ & $1$ & $0.79$ &  - & $< 10^{-4}$ & $7.5\times10^{-3}$ & $0.069$ & $0.09$ & $0.076$ & Candidate \\
+ \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.819$  & \color{red}  $2.2\times10^{-4}$  & \color{red}  $0.119$  & \color{red}  $0.01$  & \color{red}  $0.938$  & \color{red}  FP\\
+$201702477$ & $1$ & $0.70$ &  - & $< 10^{-4}$ & $4.0\times10^{-3}$ & $0.277$ & $0.06$ & $0.281$ & Candidate \\
+$201736247$ & $1$ & $0.42$ &  - & $< 10^{-4}$ & $1.9\times10^{-4}$ & $8.5\times10^{-4}$ & $0.22$ & $1.0\times10^{-3}$ & Planet \\
+$201754305$ & $1$ & $0.65$ &  - & $< 10^{-4}$ & $1.9\times10^{-3}$ & $1.5\times10^{-3}$ & $0.18$ & $3.4\times10^{-3}$ & Planet \\
+$201754305$ & $2$ & $0.38$ &  - & $< 10^{-4}$ & $1.2\times10^{-3}$ & $6.4\times10^{-4}$ & $0.17$ & $1.9\times10^{-3}$ & Planet \\
+$201779067$ & $1$ & $1.97$ &  - & $0.036$ & $5.0\times10^{-3}$ & $0.286$ & $0.03$ & $0.327$ & Candidate \\
+$201828749$ & $1$ & $0.39$ &  - & $< 10^{-4}$ & $1.7\times10^{-3}$ & $2.2\times10^{-3}$ & $0.17$ & $3.9\times10^{-3}$ & Planet \\
+$201855371$ & $1$ & $0.62$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $1.7\times10^{-4}$ & Planet \\
+$201912552$ & $1$ & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
+$201929294$ & $1$ & $3.12$ &  - & $< 10^{-4}$ & $6.8\times10^{-3}$ & $0.052$ & $0.05$ & $0.059$ & Candidate
 

### 2015-03-10 fpp/write_fpptable.py

@@ -2,20 +2,26 @@
 
 import re
 import os, os.path, glob
+import numpy as np
 
 from k2fpp.fpp import max_secondary
+from k2fpp.contrast import AO_contrast_curves
 
 def prob_entry(val):
     val = float(val)
     if val > 1e-4:
-        return '${:.2g}$'.format(val)
+        if val < 0.01:
+            lv = -np.floor(np.log10(val))
+            return '${:.1f}\\times10^{{-{:.0f}}}$'.format(val*10**lv,lv)
+        else:
+            return '${:.3f}$'.format(val)
     else:
         return '$< 10^{-4}$'
 
 def format_line(line, fpp):
     fpp = float(fpp)
     newline = line
-    if fpp < 0.01 and False:
+    if fpp < 0.01 and False: #not bothering to bold.
         newline = ''
         for v in line.split('&'):
             m = re.search('\$(.*)\$\s+\\\\',v)
@@ -42,7 +48,7 @@ fout = open('../table_fpp.tex','w')
 fout.write(r"""
 \clearpage
 %\LongTables
-\begin{deluxetable*}{lcllllllc}
+\begin{deluxetable*}{lclccccccc}
 \tablewidth{0pt}
 \tabletypesize{\scriptsize}
 \tablecaption{False Positive Probability Calculation Results}
@@ -51,6 +57,7 @@ fout.write(r"""
 \colhead{EPIC} &
 \colhead{Cand. Num.} &
 \colhead{max($\delta_{\rm sec}$)} &
+\colhead{AO?} &
 \colhead{${\rm Pr}_{\rm EB}$} &
 \colhead{${\rm Pr}_{\rm BEB}$} &
 \colhead{${\rm Pr}_{\rm HEB}$} &
@@ -68,11 +75,18 @@ for f in folders:
     for line in open(resultsfile,'r'):
         line = line.split()
     beb,eb,heb,pl,fpV,fp,FPP = line
+
     m = re.search('(\d+)\.(\d)',f)
     epic_id = int(m.group(1))
     i = int(m.group(2))
     line = '${}$ & ${}$ & '.format(epic_id,i)
     line += '${:.2f}$ & '.format(max_secondary(epic_id,i)*1e3)
+    ccs = AO_contrast_curves(epic_id)
+    if len(ccs)>0:
+        line += ' Y & '
+    else:
+        line += ' - & '
+
     for val in [eb,beb,heb]:
         val = float(val)
         line += '{} & '.format(prob_entry(val))

### 2015-03-10 ms.tex
blah
tdm edits
fpp table changes

@@
 \newcommand{\Nfp}{4}
-\newcommand{\Nvalidated}{21}
-\newcommand{\Nlimbo}{11}
+\newcommand{\Nvalidated}{22}
+\newcommand{\Nlimbo}{10} %adds to 36?  good.
 
@@
 astrophysical false positive.
-This method uses population simulations
+This method uses population simulations of the light curves of
 of false positive scenarios and true transiting planets to quantify
@@
 It then combines this information with observationally motivated prior
-assumtions about the populations of field stars, the properties of
+assumptions about the populations of field stars, the properties of
 multiple star systems, and the occurrence rate of planets as determined
@@
 \texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
-a new implementation of the \citet{Morton12} procedure, to calculate
-false positive probabilities (FPPs) for each of these K2 candidates.
-While we have obtained follow-up observations of a number of these systems,
-we do the preliminary FPP calculations without taking these into account,
-in order to demonstrate the power of \texttt{vespa} analysis
-even in the absence of follow-up observations.
-The constraints we impose on false positive scenarios in these
-``follow-up free'' calculations are the following:
+a new general-purpose implementation of the \citet{Morton12} procedure, 
+to calculate false positive probabilities (FPPs) for each of these 
+K2 candidates.  We impose the following constraints on false positive
+scenarios:
 \begin{itemize}
-\item A chance-aligned eclipsing binary system must reside within
-a 4 arcsecond radius of the target star.
+\item A chance-aligned eclipsing binary system may reside within
+a sky area equivalent to 8 arcsecond radius of the target star.
 \item The maximum allowed depth of a potential secondary eclipse event,
@@
 period of the planet candidate, once the primary transit is masked out.
+\item High-resolution imaging constraints, where available (see below)
 \end{itemize}
@@
 
-We emphasize that t
+We emphasize that the majority of these planets were validated based 
+solely on the transit signal, with no need for follow-up imaging.  This
+demonstrates the utility of \texttt{vespa} analysis, which will be
+crucial to interpreting future \kt\ detected candidates and prioritizing
+follow-up observing efforts.
 
@@
 which we identify as a likely eclipsing binary due to the observed transit
-depth \anytodo{Right? Right?}.
+depth \anytodo{Right? Right?  Can this be more quantitative?  Are these two stars 
+close to one another?  How bright is  the purported parent? Are they 
+On/near the same CCD column?  FPP gives this a pass, so we 
+need to be clear about this.}.
 We conclude the observed transit signal from EPIC 201555883 is likely the result
@@
 \include{table_photometry}
+\turnpage
 
@@
 
-%\include{table_fpp}
+\include{table_fpp}
 

### 2015-03-10 ms.tex
added reference; more tdm edits

@@
 When possible, such astrophsycial false positive scenarios are traditionally
-ruled out by detailed follow-up observations, such as high-resolution
-imaging or radial-velocity measurements.
+ruled out by detailed follow-up observations, often a combination of 
+high-resolution imaging and radial-velocity measurements.
 However, the \kep\ mission, with its thousands of planet candidates
@@
 multiple star systems, and the occurrence rate of planets as determined
-from \kep\ \citet{Fressin13}, in order to determine the probability that
+from \kep\ \citep{Fressin13}, in order to determine the probability that
 the observed signal may be a false positive.
@@
 \begin{itemize}
-\item A chance-aligned eclipsing binary system may reside within
-a sky area equivalent to 8 arcsecond radius of the target star.
+\item A chance-aligned eclipsing binary system may reside anywhere within
+an 8 arcsecond radius from the target star.
 \item The maximum allowed depth of a potential secondary eclipse event,
@@
 demonstrates the utility of \texttt{vespa} analysis, which will be
-crucial to interpreting future \kt\ detected candidates and prioritizing
+crucial to interpreting future \KT\ detected candidates and prioritizing
 follow-up observing efforts.

### 2015-03-10 ms.tex
tdm

@@
 an 8 arcsecond radius from the target star.
-\item The maximum allowed depth of a potential secondary eclipse event,
-determined as the most significantly detected signal at the same
+\item The maximum allowed depth of a potential secondary eclipse event
+is the most significantly detected signal at the same
 period of the planet candidate, once the primary transit is masked out.
-\item High-resolution imaging constraints, where available (see below)
+\item Blended stars must be allowed by the available adaptive optics
+and archival imaging data (discussed in detail below).
 \end{itemize}
 
-Table \ref{Tab:FPP} summarizes the results of these
+Table \ref{Table:FPP} summarizes the results of these
 calculations, presenting the relative probability for each candidate

### 2015-03-10 fpp/write_fpptable.py

@@ -52,7 +52,7 @@ fout.write(r"""
 \tablewidth{0pt}
 \tabletypesize{\scriptsize}
 \tablecaption{False Positive Probability Calculation Results}
-\label{Tab:FPP}
+\label{Table:FPP}
 \tablehead{
 \colhead{EPIC} &
 \colhead{Cand. Num.} &

### 2015-03-10 ms.tex
stellar props stuff

@@
 To convert the observed photometric data into physical properties for each
-star, we employ the use of stellar models.
-We first download the isochrone grids from the 2012 updated photometric
-systems for the relevant bandpasses from the Dartmouth Stellar Evolution
-Database \citep{Dotter08}.
-We then interpolate the isochrones onto a grid uniformly spaced in
-stellar mass (from 0.20 to 2.0 \msun), metallicity (from \feh$=-1.5$ to
-\feh$=+0.5$), age (from 1.0 to 14.0 Gyr), and log distance (from 10 pc to
-1000 pc).
-In our interpolation, we assume \afe$=0.0$ and $Y=0.2741$, the solar value.
-We then compare the expected apparent magnitudes to our observed photometry
-to measure the likelihood of each grid point.
-For each parameter, we then marginalize our likelihood over all other
-parameters in order to estimate the value of the physical properties
-for each star.
-\anytodo{This was done using MCMC right? Did you interpolate the
-\emph{likelihood function} or the \emph{model predictions}?}
+star, we used the publicly available \texttt{isochrones} Python module\footnote{
+\url{http://github.com/timothydmorton/isochrones}}, a general-purpose
+interpolation tool for stellar model grids.  
+This software does trilinear interpolation in mass-age-\feh\ space for any
+given set of model grids, thus being able to predict the value for any
+physical or photometric property provided by the models at any values of
+mass, age, and \feh\ within the boundaries of the grid.
+
+This enables a set of observed properties ($\left\{ x_i, \sigma_i \right\}$), 
+either spectroscopic, photometric, 
+or both, to define a likelihood function that may be sampled in
+an MCMC chain:
+\begin{equation}
+\label{eq:ischochronelhood}
+\ln \mathcal L(\boldsymbol{\theta}) = -\frac{1}{2} \displaystyle \sum_i \frac{\left(x_i - 
+  I_i\left(\boldsymbol{\theta} \right)\right)^2}{\sigma_i^2},
+\end{equation}
+where $I_i(\boldsymbol{\theta})$ is the isochrone model prediction of property 
+$i$ at the given parameters $\boldsymbol{\theta}$.  
+If the observed properties include any apparent magnitudes, then 
+$\boldsymbol{\theta}$ includes distance and $A_V$ extinction in addition 
+to mass, age, and \feh.
+
+In this work, we use grids from the Dartmouth Stellar
+Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
+helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
+module.  
+We then run an MCMC chain using \texttt{emcee} \citep{Foreman-Mackey12}
+for each host star conditioned on the observed 
+photometric properties as presented in \ref{Table:photometry}, with 
+the exception of the W4 band, which we leave out this analysis due to 
+its unreliability.
 
@@
 \citep{Thompson14}.
+
+\anytodo{Is this paragraph necessary anymore?}
 We find that by measuring stellar parameters without any WISE data (that is, using

### 2015-03-10 ms.tex
tdm

@@
 interpolation tool for stellar model grids.  
-This software does trilinear interpolation in mass-age-\feh\ space for any
+This software does trilinear interpolation in mass--age--\feh\ space for any
 given set of model grids, thus being able to predict the value for any

### 2015-03-10 ms.tex
more stellar models

@@
 \citep{Thompson14}.
+
+In order to try to encapsulate the effect of model uncertainties, we also run 
+MCMC chains using \texttt{isochrones} with photometric errors inflated 
+artificially by a factor of three.  We provide full chains using both
+inflated and un-inflated errors, though in the rest of this work we adopt
+the results obtained using inflated uncertainties.
 

### 2015-03-10 ms.tex
stellar models

--- 2015-03-10 ms.tex
@@
 \citep{Thompson14}.
+
+In order to try to encapsulate the effect of model uncertainties, we also run 
+MCMC chains with photometric errors inflated artificially by a factor of three.  
+We provide full chains using both inflated and un-inflated uncertainties, 
+though in the rest of this work we adopt
+the results obtained using the inflated values.
 

### 2015-03-10 ms.tex
tdm

@@
 \section{False Positive Analysis}
+
 As has been well known from the early days of transit searches, it is

### 2015-03-11 ms.tex
references

@@
 
-\newcommand{\caltech}{2}
-\newcommand{\cfa}{3}
-\newcommand{\nyu}{4}
-\newcommand{\princeton}{5}
-\newcommand{\mpia}{6}
-\newcommand{\cds}{7}
+\newcommand{\caltech}{1}
+\newcommand{\cfa}{2}
+\newcommand{\nyu}{3}
+\newcommand{\princeton}{4}
+\newcommand{\mpia}{5}
+\newcommand{\cds}{6}
+\newcommand{\jcpa}{7}
+\newcommand{\texas}{8}
+\newcommand{\hjs}{9}
+
 \author{%
 % The Heavy Lifters
-Benjamin~T.~Montet\altaffilmark{1,\caltech,\cfa},
+Benjamin~T.~Montet\altaffilmark{\caltech,\cfa},
 Daniel~Foreman-Mackey\altaffilmark{\nyu},
@@
 % (ranked by integration time x collecting area)
-Brendan~P.~Bowler,
-David~W.~Latham,
-Allyson~Bieryla,
-Andrew~W.~Mann,
+Brendan~P.~Bowler\altaffilmark{\caltech, \jcpa},
+David~W.~Latham\altaffilmark{\cfa},
+Allyson~Bieryla\altaffilmark{\cfa},
+Andrew~W.~Mann\altaffilmark{\texas, \hjs},
 And Any TRES Team Members We Should Add
@@
 
-\altaffiltext{1}         {btm@astro.caltech.edu}
+\email{btm@astro.caltech.edu}
 \altaffiltext{\caltech}  {Cahill Center for Astronomy and Astrophysics,
@@
                           726 Broadway, 7th Floor, New York, NY, 10003, USA}
+\altaffiltext{\jcpa} {Caltech Joint Center for Planetary Astronomy Fellow}
+\altaffiltext{\texas} {Department of Astronomy, The University of Texas at
+                            Austin, Austin, TX 78712, USA}
+\altaffiltext{\hjs} {Harlan J. Smith Fellow, The University of Texas at Austin}
 
@@
 
-\keywords{\btmtodo{Keywords}}
+\keywords{catalogs --- planetary systems --- planets and satellites: detection
+                   --- stars: fundamental parameters}
 
@@
 by discrepancies between the models and reality.
+Even more dangerously, any region of parameter space not probed by the models would 
+be entirely missed in our stellar modeling.
+
+As stated in \textsection\ref{sec:stellarparams}, we place a distance upper limit of 500 pc 
+for all stars in our sample. 
+Given the location of the \Ci\ field with respect to the galactic plane, we expect a low 
+contamination rate by halo giants. 
+However, there are a few stars that are possibly miscategorized giants.
+EPIC 201257461 is identified in the RAdial Velocity Experiment (RAVE) Fourth Data Release
+as a target with $\logg = 3.18$, consistent with that of a giant star.
+It is therefore perhaps not surprising that this system is flagged as a false positive based on 
+the transit shape.
 
@@
 B.T.M. is supported by the National Science Foundation Graduate Research
-Fellowship under Grant No. DGE‐1144469.
+Fellowship under Grant No. DGE-€1144469.
 J.A.J. is supported by generous grants from the David and Lucile Packard
@@
 (grant IIS-1124794), the National Aeronautics and Space Administration (grant
-NNX12AI50G), and the Moore–Sloan Data Science Environment at NYU.
+NNX12AI50G), and the Moore-Sloan Data Science Environment at NYU.
 
@@
 
-{\it Facilities:} \facility{Kepler}%, \btmtodo{More...}
+{\it Facilities:} \facility{Kepler}, \btmtodo{More...}
 
@@
 \include{table_photometry}
-\turnpage
+%\turnpage
 
@@
 
+\include{table_planets}
+\turnpage
 \include{table_fpp}

### 2015-03-11 ms.tex
cleaning up more text

@@
 \newcommand{\Nfp}{4}
-\newcommand{\Nvalidated}{22}
-\newcommand{\Nlimbo}{10} %adds to 36?  good.
+\newcommand{\Nvalidated}{21}
+\newcommand{\Nlimbo}{11} %adds to 36?  good.
 
@@
 \title{(Working Title) Stellar and Planetary Properties of \KT\ \Ci\
-Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving
-Earth-like Insolation?)}
+Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving
+Earth-like Insolation?}
 
@@
 \newcommand{\cfa}{2}
-\newcommand{\nyu}{3}
-\newcommand{\princeton}{4}
+\newcommand{\nyu}{4}
+\newcommand{\princeton}{3}
 \newcommand{\mpia}{5}
@@
 Benjamin~T.~Montet\altaffilmark{\caltech,\cfa},
+Timothy~D.~Morton\altaffilmark{\princeton},
 Daniel~Foreman-Mackey\altaffilmark{\nyu},
-Timothy~D.~Morton\altaffilmark{\princeton},
 % The Benefactors
@@
 seeing limited survey data, and adaptive optics imaging, we are able to confirm
-\anytodo{Number} of these systems as transiting planets at the \anytodo{Sigma} confidence
-level. We also are able to confirm \anytodo{Number} of these systems as false positives.
+\Nvalidated\ of these systems as transiting planets at the 99\% confidence
+level. We also are able to confirm \Nfp\ of these systems as false positives.
 
@@
 uncertainties from the AAVSO Photometric all-sky survey (APASS) DR6
-\btmtodo{Cite: Who?}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
+\citep{Henden14}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
 We also record the $J$, $H$, and $K$ magnitudes and their uncertainties
@@
 module.  
-We then run an MCMC chain using \texttt{emcee} \citep{Foreman-Mackey12}
+We then run an MCMC chain using \texttt{emcee} \citep{Foreman-Mackey12},
+an implementation of the affine-invariant ensemble sampler of 
+\citet{Goodman10}
 for each host star conditioned on the observed 
@@
 the results obtained using the inflated values.
-
-\anytodo{Is this paragraph necessary anymore?}
-We find that by measuring stellar parameters without any WISE data (that is, using
-only $BVgriJHK$), we largely reproduce the same effective temperatures as when
-the WISE data is included.
-However, at the low-mass end including the WISE data systematically increases the
-measured radius and increases \logg, as shown in \btmtodo{Figure}.
-Suggestively, spectroscopic stellar parameters of EPIC 201912552
-(\textsection\ref{Spexobs}) suggest the derived photometric properties better
-represent the true physical parameters when the WISE data is included.
-
-\btmtodo{Show plot}
 
@@
 reject the hypothesis that the transit is actually a false positive
-induced by a background eclipsing binary. \anytodo{Can we place limits
-on this possibility from the lack of a centroid shift?}
+induced by a background eclipsing binary. 
+However, from the transit shape alone we can place a FPP of this
+system of $1.1 \times 10^{-4}$.
 
@@
 
-\btmtodo{Method}
+For all targets with AO, we can confirm the planetary nature of the signal 
+without this extra step, but we include it for EPIC 201912552 for 
+completeness, considering thee additional follow-up this target may warrant.
+We download data from the POSS I and II surveys, which imaged
+EPIC 201912552 in 1955 and 1989, respectively. 
+This star has a proper motion of $-74 \pm 2$ mas yr$^{-1}$ in RA and 
+$-122 \pm 4$ mas yr$^{-1}$ in declination, so it has moved by $8.35\arcsec$ 
+since the POSS I data were collected.
+As shown in Figure \ref{fig:archival}, we do not detect any targets at the 
+present-day location of EPIC 201912552 in either of the POSS surveys.
 
-\btmtodo{Plots showing POSS observations.}
+\begin{figure*}[htbp]
+\centerline{\includegraphics[width=1.0\textwidth, trim=0 1.5cm 0 1.5cm, clip=true]{f3}}
+\caption{Imaging for EPIC 201912552 from 1955 to 2002. There is no background
+object directly behind the present day location of the target (red circle) that could be missed 
+by the AO observations, while modern SDSS imaging can rule out wide companions
+that may have been missed at wide separations, beyond the AO field of view.}
+\label{fig:archival}
+\end{figure*}
 
-For these targets, we can extend our contrast curves to zero
+For this target, we can extend our contrast curves to zero
 present-day orbital separation and rule out the possibility that
-these transit events are caused by background eclipsing binaries.
+these transit events are caused by a background eclipsing binary.
 By combining present-day seeing-limited photometric survey data,
@@
 to occur, and highly unlikely to cause enough dilution to call the planetary
-nature of these signals into question.
+nature of this signal into question.
 
@@
 transiting planet is actually a false positive.
-
-\subsection{False Positive Rates (and confirmations?)}
-This is Tim.
 
@@
 
-\subsection{EPIC 201465501?}
-Is this a subsection? It's a star with a mass of ~0.2 Msun and a candidate with
-a period of 18 days. I suppose it depends on the FPP.
+\subsection{Two Candidates, One Ephemeris}
 
-\subsection{An Instrumental False Positive}
+EPIC 201569483 was originally listed in \paperit\ as a planet candidate.
+The transit events have a depth of approximately 7\%.
+In this work, we conclude this system is more likely than not a false 
+positive, with an FPP of 0.560. 
+The most likely scenario is that of an eclipsing binary, which would 
+not be surprising given the transit depth.
 
-EPIC 201555883 was originally listed in \paperit\ as a planet candidate.
-After submission of that work, this object of interest was identified as
-having a transit ephemeris consistent with that of EPIC 201569483,
-which we identify as a likely eclipsing binary due to the observed transit
-depth \anytodo{Right? Right?  Can this be more quantitative?  Are these two stars 
-close to one another?  How bright is  the purported parent? Are they 
-On/near the same CCD column?  FPP gives this a pass, so we 
-need to be clear about this.}.
-We conclude the observed transit signal from EPIC 201555883 is likely the result
-of an instrumental artifact.
-
+It was later realized that EPIC 201555883 has a period, time of transit, 
+and transit duration consistent with EPIC 201569483. 
 Such effects are not uncommon in \kep\ data.
@@
 outlining four physical reasons why these anomalies may occur.
-While EPIC 201555883 is likely a false positive, it does not appear that it can neatly be
-explained by any one of the effects described by \citet{Coughlin14} alone.
-This artifact should be carefully studied in the future, as it may help illuminate other
-potential detector artifacts, both in \kep\ and \KT\ data.
+As those authors explain, period-matching candidates can be the result of direct PRF 
+contamination, antipodal reflection across the Schmidt telescope, CCD crosstalk 
+across a \kep\ module, or ``column anomalies'' across one column of the CCD.
+
+EPIC 201555883 is a unique case in that it does not appear to fall under any of these 
+cases. It falls on module 23, while EPIC 201569483 is on module 8, neither 180 degrees
+away from or on the same column as this candidate. 
+Moreover, there is not any evidence of a mechanism that could cause a third star to 
+induce both the appearance of a $7\%$ eclipse on one module and an additional 
+transit event on a different module.
+
+Formally, our false positive validation scheme gives a FPP of $9.5 \times 10^{-4}$, 
+reaching our threshold for planet validation. 
+In this case, given the period matching between the two events, we refrain from 
+declaring this system a planet. 
+However, since we cannot explain how such a false positive would occur as a result
+of an instrumental systematic in the \kep\ telescope, we also refrain from declaring 
+this target a definite false positive. 
+Additional follow-up observations of both targets are clearly warranted to better
+understand a possible systematic that has not previously been observed in 
+either \kep\ or \KT.
 
@@
 We have presented stellar parameters for all planet candidates systems observed by
-\paperit, confirming \btmtodo{Nconfirm} of the 36 candidates as bona fide planets and
-\btmtodo{NFP} as bona fide false positives.
+\paperit, validating \Nvalidated\ of the 36 candidates as bona fide planets and
+\Nfp\ as bona fide false positives.
 
@@
 \acknowledgements
-We thank Eric Agol (UW), Dan Huber (Sydney) [and Other People] for conversations and
-suggestions which improved the quality of this manuscript.
+We thank Eric Agol (UW), Dan Huber (Sydney) and Jeff Coughlin (SETI) for 
+conversations and suggestions which improved the quality of this manuscript.
 
@@
 
-{\it Facilities:} \facility{Kepler}, \btmtodo{More...}
+{\it Facilities:} \facility{Kepler},  \facility{PO:Hale (PHARO)}, \facility{FLWO:1.5m},
+\facility{IRTF:SpeX}
 

### 2015-03-11 ms.tex
more changes, more to do

@@
 
+\anytodo{201828749 has an AO companion, flux ratio 6:1 or so. We call it a planet.
+It's a very flat bottom thing, with fairly short ingress and egress: the transit shape
+is way more planet than EB so I'm comfortable with this designation. We need
+to talk about this though.}
+
 \subsection{Known Background Stars}
@@
 the transit shape.
+EPIC 201929294 has a reduced proper motion consistent with that of a giant star
 

### 2015-03-12 ms.tex
new stellar table

@@
 The full list of stellar parameters adopted in this paper is included in
-Table 2.
+Tables 2 and 3. The former lists parameters derived from photometry with
+un-inflated uncertainties, while the latter includes this inflating intended to
+encapsulate the effect of model uncertainties.
 % For some reason I can't get it to identify the table \ref here.
@@
 by the AO observations, while modern SDSS imaging can rule out wide companions
-that may have been missed at wide separations, beyond the AO field of view.}
+that may have been missed at wide separations, beyond the AO field of view. 
+All subplots are on the same scale.}
 \label{fig:archival}
@@
 
+\include{table_stellarprops_inflated}
+
 \include{table_planets}

### 2015-03-12 ms.tex
Fig 1, Table 6, more discussion text

@@
 
-\title{(Working Title) Stellar and Planetary Properties of \KT\ \Ci\
+\title{Stellar and Planetary Properties of \KT\ \Ci\
 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving
-Earth-like Insolation?}
+Earth-like Insolation}
 
@@
                           Cambridge, MA 02138, USA}
+\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
+                          Princeton, NJ, 08544, USA}
 \altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
@@
                           4 Washington Place, New York, NY, 10003, USA}
-\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
-                          Princeton, NJ, 08544, USA}
 \altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
@@
 order of magnitude larger than those in $W1-W3$, so we neglect $W4$.
-These data are reported in Table 1.
+These data are reported in Table 1, and a color-color diagram showing the
+$r-J, J-K$ colors of our candidates is included as Fig. \ref{fig:photometry}.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.5\textwidth]{f1}}
+\caption{Color-color diagram displaying $r-J, J-K$ photometry for targets 
+observed by \kep\ during the original
+mission (black), with our \KT\ \Ci\ planet candidates overlaid (fuchsia). 
+Also included is the location of the Sun (yellow). 
+Nearly all of our candidates have photometry consistent with later spectral
+types than G2.}
+\label{fig:photometry}
+\end{figure}
 
 \subsection{Stellar Models}
+\label{sec:stellarparams}
 To convert the observed photometric data into physical properties for each
@@
 We include a list of these potential contaminants as Table
-\ref{Table:BGstars}.
+6.
 
-%Table:BGstars
-% Primary    RA Dec Separation DeltaR         MaxDepth
-% 201295312  &  &   &          & 7.10 \pm 0.10 & 0.75
-% 201465501  &  &   &          & 7.90 \pm 0.25 & 0.36
-% 201546283  &  &   &          & 5.87 \pm 0.06 & 2.31
-% 201779067  &  &   &          & 4.21 \pm 0.03 & 10.56
-
-In Table \ref{Table:BGstars}, the ``maximum depth'' column represents
+In Table 6, the ``maximum depth'' column represents
 the maximum observed ``transit'' depth if the transit were actually caused
@@
 
-As stated in \textsection\ref{sec:stellarparams}, we place a distance upper limit of 500 pc 
-for all stars in our sample. 
+As stated in \textsection\ref{sec:stellarparams}, we infer stellar parameters using the 
+Dartmouth models, with a mass upper limit of $3.7 M_\odot$. 
 Given the location of the \Ci\ field with respect to the galactic plane, we expect a low 
@@
 the transit shape.
-EPIC 201929294 has a reduced proper motion consistent with that of a giant star
+EPIC 201929294, with a proper motion of $0.010\arcsec$ yr$^{-1}$ \citep{Zacharias12}  has 
+a reduced proper motion consistent with that of a giant star.
+While suggestive, this observation does not definitively provide information about the
+nature of this target. 
+Likewise, our false positive analysis is neither able to confirm nor exclude the planetary
+nature of the observed transit signal around this target.
 
@@
 \include{table_planets}
-\turnpage
+\begin{turnpage}
 \include{table_fpp}
+\end{turnpage}
+
+\include{table_bg}
 

### 2015-03-12 ms.tex
more discussion

@@
 
+The planets we confirm in this paper, like the planets found in the original \kep\ mission,
+span a wide range of parameter space. 
+They are at distances ranging from $34$ to $500$ pc, have radii ranging from $1.3$ to 
+$5.3 R_\odot$, and orbital periods ranging from 5.0 to 50.3 days.
+Like the original mission, we find significantly more small planets than large planets.
+
+Unlike the original mission, however, we find that nearly all of our confirmed planets
+are around stars less massive than the Sun. 
+This difference is a result of both the \Ci\ field and the target selection process.
+\Ci\ is at a significantly higher galactic latitude than the original \kep\ mission, 
+meaning there is a much lower number density of targets at large distances.
+A magnitude limited survey pointed in this direction would then have much in
+common with a volume limited survey near the galactic plane, as massive stars
+at kiloparsec distances are relatively unlikely likely to exist.
+Therefore, the pool of targets that could be selected for \Ci\ contains a larger
+fraction of subsolar stars.
+
+Low-mass stars, particularly M dwarfs, are also a specific focus of the \KT\ mission.
+One of the primary goals of the Kepler mission was to ``Determine the abundance of 
+terrestrial and larger planets in or near the habitable zone of a wide variety of spectral 
+types of stars'' \citep{Batalha13} However, $\sim70\%$ of Kepler's target stars had 
+masses within 20\% 
+of the Sun's, while 70\% of the stars in the Galaxy have less than 50\% the mass of the 
+Sun \citep{Brown11}.
+\KT\ will fulfill the promise of \kep, with the goal of providing a yield of small planets
+around bright, small stars to facilitate follow-up measurements \citep{Howell14}.
+This is clear from the \KT\ target selection process, with thousands of K and M dwarfs
+being selected in each campaign.
+Based on these plans, we expect that \KT\ will detect hundreds of planets during its 
+lifetime, with the majority being mini-Neptunes and super-Earths around stars
+less massive than the Sun.
+
+\anytodo{Does anyone feel we should include anything else in the discussion?}
+
 \anytodo{We should have a figure of many subplots, of phase-folded

### 2015-03-12 ms.tex
ao figure

@@
 
+Images for all systems AO data was obtained for is shown in Fig. \ref{Fig:AO}.
+
+\begin{figure*}[htbp]
+\centerline{\includegraphics[width=1.0\textwidth]{f2}}
+\caption{AO data for all systems imaged. 
+The main frame for each single system shows the deep, saturated image.
+The inset for each single system shows a shallower, unsaturated image to better
+identify companions at close projected orbital separations.
+For the two systems with imaged companions, EPIC 201546283 and 201828749,
+only unsaturated frames are collected.
+All subplots, including insets, are plotted on the same scale.}
+\label{fig:AO}
+\end{figure*}
+
 \anytodo{201828749 has an AO companion, flux ratio 6:1 or so. We call it a planet.
@@
 \begin{figure*}[htbp]
-\centerline{\includegraphics[width=1.0\textwidth, trim=0 1.5cm 0 1.5cm, clip=true]{f3}}
+\centerline{\includegraphics[width=1.0\textwidth, trim=0 6.30cm 0 6.30cm, clip=true]{f3}}
 \caption{Imaging for EPIC 201912552 from 1955 to 2002. There is no background

### 2015-03-13 ms.tex
abstract tweaks, small discussion change

@@
 orbital period of 33 days.
-\anytodo{Anything we should add?}
+We also present \texttt{vespa}, a new general-purpose implementation
+of the \citet{Morton12} procedure to calculate false positive probabilities
+for \KT\ candidates.
 \end{abstract}
@@
 for each host star conditioned on the observed 
-photometric properties as presented in \ref{Table:photometry}, with 
-the exception of the W4 band, which we leave out this analysis due to 
-its unreliability.
+photometric properties as presented in Table 1.
 
@@
 to calculate false positive probabilities (FPPs) for each of these 
-K2 candidates.  We impose the following constraints on false positive
+\KT\ candidates.  We impose the following constraints on false positive
 scenarios:
@@
 All subplots, including insets, are plotted on the same scale.}
-\label{fig:AO}
+\label{Fig:AO}
 \end{figure*}
@@
 \subsection{Known Background Stars}
-The P3K AO system has a field of view of $3.84 \times 3.84$ arcseconds.
-\btmtodo{Check with Brendan to make sure he used this mode}.
+The PHARO AO system has a field of view of NUMBER arcseconds.
+\btmtodo{Check with Brendan to find this number}.
 Each \KT\ pixel is a square of $3.98 \times 3.98$ arcseconds.
 A background eclipsing binary within a few \KT\ pixels of our target
-stars could mimic a transit signal while evading detection by P3K.
+stars could mimic a transit signal inside our aperture while evading detection 
+by PHARO.
 Such wide eclipsing binaries should appear in seeing-limited ground-based
@@
 \Nfp\ as bona fide false positives. 
+Of these planets, 4 have been previously validated in other works, while 17 are 
+validated here for the first time.
 
@@
 Their tireless efforts were all essential to the tremendous success of the mission and the
-successes of K2, present and future.
+successes of \KT\, present and future.
 

### 2015-03-14 ms.tex
ready to send to coauthors

@@
 
-\title{Stellar and Planetary Properties of \KT\ \Ci\
+\title{Stellar and Planetary Properties of \KT\ Campaign 1
 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving
@@
 The result of this observing strategy is that the targets appear to drift
-at the rate of $\sim 1\arcsec$ s$^{-1}$, with rapid corrections that occur
+at the rate of $\sim 1\arcsec$ hr$^{-1}$, with rapid corrections that occur
 approximately once every six hours.
@@
 photometric properties as presented in Table 1.
+We include a prior on stellar metallicity representative of the observed metallicities
+of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}.
 
@@
 We provide full chains using both inflated and un-inflated uncertainties, 
-though in the rest of this work we adopt
+though in the rest of this work (and in Table 2) we adopt
 the results obtained using the inflated values.
@@
 The full list of stellar parameters adopted in this paper is included in
-Tables 2 and 3. The former lists parameters derived from photometry with
-un-inflated uncertainties, while the latter includes this inflating intended to
-encapsulate the effect of model uncertainties.
+Table 2.
 % For some reason I can't get it to identify the table \ref here.
@@
 the values that are not constrained by the light curve.
-As described in SOME APPENDIX, these samples can be re-weighted and used to
+As described in the Appendix, these samples can be re-weighted and used to
 evaluate the posterior probability of the physical parameters of the planets
@@
 This also means that the effects of different measurements of the stellar
-parameters can be easily tested by applying the method described in THAT SAME
-APPENDIX.
-
+parameters can be easily tested by applying the method described in 
+Appendix A.
 The key assumption of this method is that the likelihood function used in
@@
 
-The results are given in SOME TABLE.
+The results are given in Table 3.
 
@@
 
-Table \ref{Table:FPP} summarizes the results of these
+Table 4 summarizes the results of these
 calculations, presenting the relative probability for each candidate
@@
 stars is significantly lower.
-We include a list of these potential contaminants as Table
-6.
+We include a list of these potential contaminants as Table 5.
 
-In Table 6, the ``maximum depth'' column represents
+In Table 5, the ``maximum depth'' column represents
 the maximum observed ``transit'' depth if the transit were actually caused
@@
 
-\include{table_stellarprops_inflated}
-
 \include{table_planets}

### 2015-03-17 ms.tex

@@
 \newcommand{\anytodo}[1]{\todo{ANYONE}{NavyBlue}{#1}}
+\newcommand{\dfmtodo}[1]{\todo{DFM}{ForestGreen}{#1}}
 
@@
 In this paper, we present stellar and planetary properties for all systems.
-We combine archival imaging, ground-based seeing limited survey data, and
+We combine ground-based seeing limited survey data and
 adaptive optics imaging with a detailed transit analysis scheme to confirm
@@
 
-To derive the physical planet parameters conditioned on the measured stellar
-parameters, we used the posterior probability distribution for quantities
-measured using the light curve---from \paperit---and re-weighted them using
-the results of the photometric and spectroscopic analysis.
-In \paperit, the authors generated MCMC samples from the posterior
-probability distribution over all the physical parameters (including stellar
-mass and radius, and the planet radius) using broad, un-informative priors on
-the values that are not constrained by the light curve.
-As described in the Appendix, these samples can be re-weighted and used to
-evaluate the posterior probability of the physical parameters of the planets
-conditioned on the stellar values.
-This also means that the effects of different measurements of the stellar
-parameters can be easily tested by applying the method described in 
-Appendix A.
-The key assumption of this method is that the likelihood function used in
-\paperit\ is correct.
+\dfmtodo{Re-write this section.}
 That model was an exposure-time integrated, limb darkened light curve
@@
 
-\appendix
-\section{Computing physical planet parameters}
-
-In \paperit, the authors generated $K$ samples from the posterior probability
-distribution of the physical parameters of the systems conditioned on the
-light curves using broad, un-informative priors on most of the parameters.
-
-\begin{eqnarray}
-p(w\,|\,x) &=& \frac{p(w)\,p(x\,|\,w)}{p(x)} \\
-&=& \frac{q(w)\,p(x\,|\,w)}{q(x)}\,\frac{p(w)}{q(w)}\,\frac{q(x)}{p(x)} \\
-&=& q(w\,|\,x)\,\frac{p(w)}{q(w)}\,\frac{q(x)}{p(x)}
-\end{eqnarray}
-
-We have $K$ samples
-\begin{eqnarray}
-w^{(k)} &\sim& p(w\,|\,x)
-\end{eqnarray}
-and the point of these samples is to do integrals of the form
-\begin{eqnarray}
-E[f(w)] &=& \int f(w)\,p(w\,|\,x) \dd w \quad.
-\end{eqnarray}
-Now, if we want to update this with a new measurement $p^\prime(w)$,
-
 \bibliography{exopapers}
 
+% \begin{turnpage}
 \include{table_photometry}
-%\turnpage
-
+% \end{turnpage}
 \include{table_stellarprops}
-
 \include{table_planets}
-\begin{turnpage}
 \include{table_fpp}
-\end{turnpage}
 

### 2015-03-18 ms.tex
planet properties words

@@
 Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
-hosting a \anytodo{Radius} planet with $T_{eq} = 275 \pm 15$ K and an
+hosting a $2.29 \pm 0.24 R_\odot$ planet with $T_{eq} = 273 \pm 15$ K and an
 orbital period of 33 days.
@@
 
-\dfmtodo{Re-write this section.}
-That model was an exposure-time integrated, limb darkened light curve
-\citep{Mandel02,Kipping10b} marginalized over the parameters of the
+In \paperit, we present only parameters directly observable from the \KT\
+light curve itself: the period, time of transit center, and transit depth.
+With stellar properties now in hand, we can convert these observational
+results into fundamental parameters of each planet candidate.
+
+For each candidate, we fit a transit and systematic model simultaneously
+to the data.
+The transit model is an exposure-time integrated, two-parameter limb darkened 
+light curve \citep{Mandel02,Kipping10b}.
+We parameterize... \dfmtodo{What are the parameters in the model?}
+
+This method enable us to marginalize over the parameters of the
 data-driven model of the instrumental systematics described in \paperit.
@@
 
-(Include comment here about how the planet parameters assume no dilution.
-Except for the two that we have AO detected binaries for, probably?
-Brendan should have us flux ratios by the end of the day.
-In those cases, I suppose we need to include planet properties in both cases
-in which the transit is around either the more or less massive star.)
+\dfmtodo{Add more to this section.}
+
+In this analysis, we assume the dilution caused by additional stars contributing
+flux into the aperture is negligible for nearly all systems.
+Given the location of the \Ci\ field at a high galactic latitude, we expect low
+contamination by background giants. 
+Nevertheless, this assumption may not be valid for all systems.
+Any contamination unaccounted for, as may happen if any of these stars are
+actually unresolved binaries, would cause us to underestimate the radii
+of any planets we detect.
+Therefore, high-contrast adaptive optics imaging of any systems should be
+obtained before any of these planets are placed on a planet mass-radius
+diagram.
+
+One system, EPIC 201828749, is known to be a binary through AO imaging
+as discussed in \ref{sec:AO}. \btmtodo{More text...}
 
@@
 \subsection{Adaptive Optics Imaging}
+\label{sec:AO}
 
@@
 Unlike GJ\,1214b, EPIC 201912552b is not highly irradiated.
-Instead, it is at an reduced semimajor axis \ars$ = 82.1 \pm 8.6$.
-Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 275 \pm 15$
-K, meaning its bulk insolation is $135 \pm 30$ percent that of the Earth's.
+Instead, it is at an reduced semimajor axis \ars$ = 83.2 \pm 9.1$.
+Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 273 \pm 15$
+K, meaning its bulk insolation is $131 \pm 30$ percent that of the Earth's.
 Although the planet is likely too large to be rocky \citep{Rogers14},

### 2015-03-18 ms.tex
ao section

@@
 One system, EPIC 201828749, is known to be a binary through AO imaging
-as discussed in \ref{sec:AO}. \btmtodo{More text...}
+as discussed in \textsection\ref{sec:AO}. 
+In this case, we do account for the dilution induced by the companion. 
+From our relative $JHK$ photometry of the two stars, we infer an expected flux
+ratio between the two stars in the \kep\ bandpass, inflating the transit depth by 
+this factor to account for the dilution. 
+We marginalize  \dfmtodo{More text...}
 
@@
 
-This is Brendan.
+We obtained high resolution images of seven stars with the 
+Palomar High Angular Resolution Observer (PHARO) infrared detector 
+\citep{Hayward01} behind the PALM3000 adaptive optics system \citep{Dekany13}
+at the Palomar 5.1-meter Hale telescope on the nights of 2015 Feb 3 and 4 UT.
+Sky conditions were mostly clear with light cirrus and $\approx$1$\farcs$0--1$\farcs$3 seeing
+on both nights.  
+We used the smallest plate scale of 25~mas pix$^{-1}$ which resulted
+in a field of view of 25$\farcs$6$\times$25$\farcs$6 across the 1024$^{2}$ pix$^{2}$ array.
+All observations were obtained with the 32x pupil sampling mode, resulting in Strehl ratios
+of $\approx$20--30\% in $K_S$ for our $V$=11--13~mag targets as measured by the Strehl
+monitor at the telescope in real time.
+We obtained unsaturated dithered frames of each target in $K_S$-band with typical 
+integration times of 2--10~s.
+Except for EPIC~201828749 and EPIC~201546283, which had nearby candidate 
+binary companions, we also 
+acquired deep saturated images (5--10 frames at 60 sec each) 
+to search for fainter companions.
 
-Images for all systems AO data was obtained for is shown in Fig. \ref{Fig:AO}.
+Images were registered and contrast curves were generated following \citet{Bowler15a}.
+For the saturated data, the star's position in each image was found by masking the
+saturated region and fitting a 2D bivariate Gaussian to the PSF wings.  
+Contrast
+curves for the median-combined image are calibrated using the unsaturated frames.  
+The typical sensitivity is 6.5--7.5~mag at 1$''$.
+The images were astrometrically calibrated using dithered observations of the 
+Trapezium cluster centered
+on $\theta$$^1$~Ori~C taken on 2015 Feb 3 UT.  
+Based on the reference astrometry for pairs of stars in the field from
+\citet{McCaughrean94}, we measure a plate scale of 25.2~$\pm$~0.4~mas pix$^{-1}$ 
+and north orientation of --0.2~$\pm$~0.3$^{\circ}$.  
+Since this latter value is consistent with being aligned with 
+the detector columns, we adopt a value of 0.0~$\pm$~0.3$^{\circ}$ for this work.
+Relative photometry of nearby stars is carried out using aperture photometry with 
+an aperture radius of 12~pix (0$\farcs$3).  
+For EPIC~201828749, we also acquired $J$- and $H$-band images.
+Astrometry and photometry is derived separately for each image, and the mean and standard deviation 
+of these measurements is adopted for our final values listed in Table~XX.
+
+Images for all systems AO data was obtained for is shown in Fig. \ref{Fig:AO},
+while contrast curves showing the $5\sigma$ limits for detection
+as a function of orbital separation are given in Fig. \ref{Fig:CC}.
 
@@
 only unsaturated frames are collected.
+The pixel scale is 0.0252$\arcsec$ per pixel, and each subplot is a square 400 pixels
+on a side. 
+Each inset is a square 100 pixels on a side.
 All subplots, including insets, are plotted on the same scale.}
@@
 \end{figure*}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.5\textwidth]{f3}}
+\caption{$5\sigma$ contrast curves for all systems with AO nondetections.
+For all systems, we can exclude the possibility that a companion at a given $\Delta K_S$
+exists. 
+From our known transit depths, we can then rule out significant parameter space in which 
+an eclipsing binary could reside and mimic a transit signal.}
+\label{Fig:CC}
+\end{figure}
 
@@
 \subsection{Known Background Stars}
-The PHARO AO system has a field of view of NUMBER arcseconds.
-\btmtodo{Check with Brendan to find this number}.
+The PHARO AO system has a field of view of 25 arcseconds.
 Each \KT\ pixel is a square of $3.98 \times 3.98$ arcseconds.
@@
 \begin{figure*}[htbp]
-\centerline{\includegraphics[width=1.0\textwidth, trim=0 6.30cm 0 6.30cm, clip=true]{f3}}
+\centerline{\includegraphics[width=1.0\textwidth, trim=0 6.30cm 0 6.30cm, clip=true]{f4}}
 \caption{Imaging for EPIC 201912552 from 1955 to 2002. There is no background

### 2015-03-18 ms.tex
additional figures

@@
 Similar in spirit to other published methods of
-probabilistic validation, such as Blender \citep{} and PASTIS
-\citep{}, it has the advantage of being computationally less demanding
+probabilistic validation, such as Blender \citep{Torres11a} and PASTIS
+\citep{Diaz14a}, it has the advantage of being computationally less demanding
 and fully automated, and thus easily applied in batch to a large
@@
 follow-up observing efforts.
+We show these transit signals as Fig. \ref{fig:transits}.
+
+\begin{figure*}[htbp]
+\centerline{\includegraphics[width=1.0\textwidth]{f2}}
+\caption{\btmtodo{PLACEHOLDER, UPDATE}.
+Phase-folded \KT\ photometry for all planet candidates analyzed in 
+this paper.
+Each is the product of a fiducial noise model, in which the median systematic
+has been removed for illustrative purposes.
+The systems which we validate as transiting planets are labeled in 
+green. 
+The systems which we confirm as false positive events are labeled in red.
+The systems which we leave as candidates are labeled in black.
+}
+\label{fig:transits}
+\end{figure*}
 
@@
 Astrometry and photometry is derived separately for each image, and the mean and standard deviation 
-of these measurements is adopted for our final values listed in Table~XX.
+of these measurements is adopted for our final values listed in Table~6.
+
+We note that we validate 201828749 as a true transiting planet, despite the presence of this binary
+companion. 
+From the transit shape, we can rule out the possibility this system is a background eclipsing
+binary.
+Regardless of which star this object transits, the object is planet-sized.
+Given that small planets are significantly more common than large planets, it is more likely
+that the planet is orbiting the brighter star, and our parameters listed in Table 3 reflect this
+likelihood. If the planet is truly orbiting the fainter star, then it has a larger radius than is 
+listed in this table.
 
@@
 \begin{figure*}[htbp]
-\centerline{\includegraphics[width=1.0\textwidth]{f2}}
+\centerline{\includegraphics[width=1.0\textwidth]{f3}}
 \caption{AO data for all systems imaged.
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=0.5\textwidth]{f3}}
+\centerline{\includegraphics[width=0.5\textwidth]{f4}}
 \caption{$5\sigma$ contrast curves for all systems with AO nondetections.
@@
 \end{figure}
-
-\anytodo{201828749 has an AO companion, flux ratio 6:1 or so. We call it a planet.
-It's a very flat bottom thing, with fairly short ingress and egress: the transit shape
-is way more planet than EB so I'm comfortable with this designation. We need
-to talk about this though.}
 
@@
 \begin{figure*}[htbp]
-\centerline{\includegraphics[width=1.0\textwidth, trim=0 6.30cm 0 6.30cm, clip=true]{f4}}
+\centerline{\includegraphics[width=1.0\textwidth, trim=0 6.30cm 0 6.30cm, clip=true]{f5}}
 \caption{Imaging for EPIC 201912552 from 1955 to 2002. There is no background
@@
 The remaining three are all representative of the multiple-planet systems observed by
-\kep \citep{Lissauer11b, Fabrycky14}.
+\kep\ \citep{Lissauer11b, Fabrycky14}.
 Two of the systems are near a period commensurability and all three consist of
@@
 
-\anytodo{We should have a figure of many subplots, of phase-folded
-transits for all the confirmed planets.
-To ease Dan's mind, we will say that they are the product of
-some fidicual transit model and are only presented here for illustrative
-purposes.}
-
 \acknowledgements

### 2015-03-20 ms.tex

@@
 Andrew~W.~Mann\altaffilmark{\texas, \hjs},
-And Any TRES Team Members We Should Add
 }
@@
 We combine ground-based seeing limited survey data and
-adaptive optics imaging with a detailed transit analysis scheme to confirm
-\Nvalidated\ as planets and identify \Nfp\ as likely false positives.
+adaptive optics imaging with a detailed transit analysis scheme to validate
+\Nvalidated\ candidates as planets and identify \Nfp\ candidates as likely false positives.
 Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
-hosting a $2.29 \pm 0.24 R_\odot$ planet with $T_{eq} = 273 \pm 15$ K and an
+hosting a $2.24 \pm 0.25 R_\odot$ planet with $T_{eq} = 271 \pm 16$ K and an
 orbital period of 33 days.
@@
 discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, Mullaly15}.
-The fidelity of this sample is high, so most of these planet candidates are truly planets
+The fidelity of this sample is high: most of these planet candidates are truly planets
 \citep{Morton11b, Fressin13}.
@@
 thruster firing.
-The result of this observing strategy is that the targets appear to drift
-at the rate of $\sim 1\arcsec$ hr$^{-1}$, with rapid corrections that occur
+As a result, the detector drifts relative to the sky
+at the rate of $\sim 1\arcsec$ hr$^{-1}$, with rapid corrections 
 approximately once every six hours.
@@
 Worse yet, these variations occur on timescales similar to transit signals, potentially
-masking the observational signature of a planet passing between \kep\ and the host star.
+masking the observational signature of a planet passing between \kep\ and its host star.
 
-There has been considerable effort to recover these signals.
+There has been considerable effort to recover these planetary signals.
 \citet{Vanderburg14} extract aperture photometry and de-correlate with image centroid
@@
 A similar technique was employed by \citet{Armstrong15a} to identify potential eclipsing
-binary systems and to identify a transiting system very near a 3:2 period commensurability
+binary systems and to identify a transiting system near a 3:2 period commensurability
 \citep{Armstrong15b}.
@@
 signal, and such a technique is prone to either over-fitting, in which some of the
-astrophysical signal is also removed, or under-fitting, in which some instrumental noise
-remains.
-A better strategy is to simultaneously fit both the signal and the noise, as is commonly
-done in cosmology and, increasingly, in radial velocity searches for planetary systems
+astrophysical signal is also removed, or under-fitting, in which some
+of the instrumental systematics remain.
+A better strategy is to simultaneously fit both the signal and the systematics, as is common
+practice in cosmology and, increasingly, in radial velocity searches for planetary systems
 \citep[e.g.][]{Ferreira00, Boisse11, Haywood14, Grunblatt15}.
@@
 in a search for transiting planets.
-The authors of that paper assume that the dominant trends in the observed stellar light
+They assume that the dominant trends in the observed stellar light
 curves are caused by spacecraft motion and are shared by many stars.
@@
 This method enables fitting without over-fitting, and also permits marginalization over
-uncertainties induced by the noise model.
+uncertainties induced by the systematic model.
 Therefore, any uncertainties in the systematics can be propogated into uncertainties in
@@
 Given these parameters and the transit data, as well as archival imaging, ground-based
-seeing limited survey data, and adaptive optics imaging, we are able to confirm
+seeing-limited survey data, and adaptive optics imaging, we are able to confirm
 \Nvalidated\ of these systems as transiting planets at the 99\% confidence
@@
 spectroscopic data with which to characterize the stellar properties.
+Additionally, there are no measured parallaxes for any of these stars.
 Instead, we rely on photometry.
@@
 We include a prior on stellar metallicity representative of the observed metallicities
-of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}.
+of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}, and 
+only consider stars with masses below $3.7$ $M_\odot$.
 
@@
 MCMC chains with photometric errors inflated artificially by a factor of three.
-We provide full chains using both inflated and un-inflated uncertainties,
+We provide full chains using both inflated and un-inflated 
+uncertainties,\footnote{http://www.astro.princeton.edu/~tdm/k2/}
 though in the rest of this work (and in Table 2) we adopt
@@
 
-A near-infrared spectrum of EPIC 201912552 was obtained using the updated SpeX
+A near-infrared spectrum of EPIC 201912552 was obtained using the upgraded SpeX
 (uSpeX) spectrograph \citep{Rayner03} on the NASA Infrared Telescope Facility
@@
 The spectrum was flat fielded, extracted, wavelength calibrated, and stacked
-using the \textit{SpeXTool} package \citep{Cushing04}.
+using the \textit{Spextool} package \citep{Cushing04}.
 An A0V-type star was observed immediately after
@@
 2.2m telescope on the night of January 30 2015.
-SNIFS provides simultaneous coverage from 3200\AA--9700\,AA\ at a resolution
+SNIFS provides simultaneous coverage from 3200\AA--9700\AA\ at a resolution
 of $\simeq1000$. Final S/N of the spectrum was $>100$ pre resolving element
@@
 
+Each of these scenarios are astrophysical, caused by one object passing
+in front of another, blocking some fraction of the total light. 
+The calculations here do not include the possibility that each signal 
+is caused by an instrumental artifact in the data or some other 
+astrophysical event, such as stellar activity, masquerading as planet
+transits.
+
 Table 4 summarizes the results of these
@@
 have FPP $<$ 1\%; these we consider to be validated planets.
+Of these, 18 are validated for the first time.
 The remaining \Nlimbo\ candidates have FPPs neither high enough to discard
@@
 \centerline{\includegraphics[width=1.0\textwidth]{f2}}
-\caption{\btmtodo{PLACEHOLDER, UPDATE}.
+\caption{\btmtodo{PLACEHOLDER, UPDATE. Needs transit models}.
 Phase-folded \KT\ photometry for all planet candidates analyzed in 
@@
 The systems which we leave as candidates are labeled in black.
+Red curves outline the median transit model for each candidate system.
 }
@@
 \citep{Hayward01} behind the PALM3000 adaptive optics system \citep{Dekany13}
-at the Palomar 5.1-meter Hale telescope on the nights of 2015 Feb 3 and 4 UT.
+at the Palomar 5.1-meter Hale telescope on the nights of 2015 February 3 and 4 UT.
 Sky conditions were mostly clear with light cirrus and $\approx$1$\farcs$0--1$\farcs$3 seeing
@@
 Astrometry and photometry is derived separately for each image, and the mean and standard deviation 
-of these measurements is adopted for our final values listed in Table~6.
+of these measurements is adopted for our final values listed in Table~5.
 
@@
 identify companions at close projected orbital separations.
-For the two systems with imaged companions, EPIC 201546283 and 201828749,
+For the two systems with imaged companions, EPIC 201546283 and 
+EPIC 201828749,
 only unsaturated frames are collected.
-The pixel scale is 0.0252$\arcsec$ per pixel, and each subplot is a square 400 pixels
-on a side. 
-Each inset is a square 100 pixels on a side.
+The pixel scale is $0\farcs0252$ per pixel.
+Each subplot is a square 400 pixels on a side and
+each inset is a square 100 pixels on a side.
 All subplots, including insets, are plotted on the same scale.}
@@
 The PHARO AO system has a field of view of 25 arcseconds.
-Each \KT\ pixel is a square of $3.98 \times 3.98$ arcseconds.
+Each \KT\ pixel is a square, $3\farcs98$ on a side.
 A background eclipsing binary within a few \KT\ pixels of our target
@@
 For each target, we return
-all stars within 12\arcsec with $\Delta r < 8$ relative to each object
+all stars within 12\arcsec\ with $\Delta r < 8$ relative to each object
 of interest.
@@
 stars is significantly lower.
-We include a list of these potential contaminants as Table 5.
+We include all potential contaminants in Table 5.
 
@@
 The probability is small, given the $0\farcs1$ diffraction limit
-of P200 at $2\mu$m, but nonzero.
+of the Hale Telescope at $2$ $\mu$m, but nonzero.
 We can rule out the possibility of such chance alignments with
@@
 For all targets with AO, we can confirm the planetary nature of the signal
-without this extra step, but we include it for EPIC 201912552 for
-completeness, considering thee additional follow-up this target may warrant.
+without this extra step, but we include it for EPIC 201912552, considering 
+the additional follow-up this target may warrant.
 We download data from the POSS I and II surveys, which imaged
 EPIC 201912552 in 1955 and 1989, respectively.
-This star has a proper motion of $-74 \pm 2$ mas yr$^{-1}$ in RA and
-$-122 \pm 4$ mas yr$^{-1}$ in declination, so it has moved by $8.35\arcsec$
+This star has a proper motion of $-74 \pm 2$ mas yr$^{-1}$ in right ascension
+ and $-122 \pm 4$ mas yr$^{-1}$ in declination, so it has moved by $8\farcs35$
 since the POSS I data were collected.
@@
 star and positioned in their orbits so that their projected separation is
-smaller than the diffraction limit of the P200 telescope.
+smaller than the diffraction limit of the Hale Telescope.
 Such an alignment would require the orbital inclination of the binary to be
@@
 While we cannot fully rule out this possibility, such an alignment is unlikely
-to occur, and highly unlikely to cause enough dilution to call the planetary
+to occur and unable to cause enough dilution to call the planetary
 nature of this signal into question.
@@
 
-We observed EPIC 201912552 on (all UT) February 04 2015 and February 24 2015
+We observed EPIC 201912552 on 2015 February 04 and 25 UT
 with the Tillinghast Reflector Echelle
@@
 
-The two observed spectra have RVs that differ by $47.1 \pm 41.9$ m s$^{-1}$.
-A deviation at this magnitude can only be explained by the presence of
-a planetary system and instrumental noise, eliminating the possibility the
-transiting planet is actually a false positive.
+The two observed spectra have RVs that differ by $47 \pm 42$ m s$^{-1}$.
+If the RVs were caused by a stellar companion, the RV shift between these
+observations would be on the order of km s$^{-1}$.
+Therefore, the transiting object must be planetary in nature.
 
@@
 
-Of particular interest is EPIC 201912552.
+The planet orbiting EPIC 201912552 may be an interesting target for 
+atmospheric studies of transiting exoplanets.
 
@@
 to become a prime target for atmospheric characterization studies
-and is ideal as a target for future space-based missions such as JWST.
+and is ideal as a target for future space-based missions such as 
+\textit{JWST}.
 
 Unlike GJ\,1214b, EPIC 201912552b is not highly irradiated.
-Instead, it is at an reduced semimajor axis \ars$ = 83.2 \pm 9.1$.
-Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 273 \pm 15$
-K, meaning its bulk insolation is $131 \pm 30$ percent that of the Earth's.
+Instead, it is at a reduced semimajor axis \ars$ = 84.3 \pm 9.5$.
+Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 271 \pm 16$
+K, meaning its bulk insolation is $128 \pm 28$ percent that of the Earth's.
 Although the planet is likely too large to be rocky \citep{Rogers14},
@@
 The transit events have a depth of approximately 7\%.
-In this work, we conclude this system is more likely than not a false
+In this work, we conclude this system is likely a false
 positive, with an FPP of 0.560.
@@
 across a \kep\ module, or ``column anomalies'' across one column of the CCD.
+Typically, the instrumental false positive event appears considerably shallower than the 
+true astrophysical event.
 
@@
 cases. It falls on module 23, while EPIC 201569483 is on module 8, neither 180 degrees
-away from or on the same column as this candidate.
+away from nor on the same column as this candidate.
 Moreover, there is not any evidence of a mechanism that could cause a third star to
 induce both the appearance of a $7\%$ eclipse on one module and an additional
-transit event on a different module.
+anomalous transit event on a different module.
 
@@
 reaching our threshold for planet validation.
+Since \texttt{vespa} does not account for the possibility of instrumental artifacts
+in the data, this number represents only the \textit{astrophysical} false positive
+probability.
 In this case, given the period matching between the two events, we refrain from
@@
 An additional four targets orbit stars with $K <10$.
-These targets are ideal for ground-based followup, and may be useful targets for Spitzer and
+These targets are ideal for ground-based followup and may be useful targets for Spitzer and
 JWST to probe planetary atmospheres.
@@
 \paperit, validating \Nvalidated\ of the 36 candidates as bona fide planets and
-\Nfp\ as bona fide false positives.
+\Nfp\ as false positives.
 Of these planets, 4 have been previously validated in other works, while 17 are
@@
 span a wide range of parameter space.
-They are at distances ranging from $34$ to $500$ pc, have radii ranging from $1.3$ to
-$5.3 R_\odot$, and orbital periods ranging from 5.0 to 50.3 days.
+They are at distances ranging from $34$ to $700$ pc, have radii ranging from $1.3$ to
+5.3 $R_\oplus$, and orbit with periods ranging from 5.0 to 50.3 days.
 Like the original mission, we find significantly more small planets than large planets.
@@
 meaning there is a much lower number density of targets at large distances.
-A magnitude limited survey pointed in this direction would then have much in
-common with a volume limited survey near the galactic plane, as massive stars
-at kiloparsec distances are relatively unlikely likely to exist.
-Therefore, the pool of targets that could be selected for \Ci\ contains a larger
+As massive stars
+at kiloparsec distances are relatively less likely to exist in \Ci\ than near the
+galactic plane, the pool of targets that could be selected for \Ci\ contains a larger
 fraction of subsolar stars.
@@
 Low-mass stars, particularly M dwarfs, are also a specific focus of the \KT\ mission.
-One of the primary goals of the Kepler mission was to ``Determine the abundance of
+One of the primary goals of the \kep\ mission was to ``determine the abundance of
 terrestrial and larger planets in or near the habitable zone of a wide variety of spectral
@@
 less massive than the Sun.
-
-\anytodo{Does anyone feel we should include anything else in the discussion?}
 

### 2015-03-21 fpp/do_fpp.py
added files

@@ -1,0 +1,26 @@
+#!/usr/bin/env python
+from __future__ import print_function, division
+
+import sys
+
+from k2fpp.fpp import K2_FPPCalculation
+from k2fpp.contrast import all_ccs
+
+import logging
+
+import warnings
+warnings.simplefilter("error")
+warnings.simplefilter("ignore", DeprecationWarning)
+
+epic_id = int(sys.argv[1])
+index = int(sys.argv[2])
+recalc = sys.argv[-1] == '--recalc'
+
+print('calculating FPP for {}, planet {}...'.format(epic_id, index))
+fpp = K2_FPPCalculation(epic_id, i=index, recalc=recalc)
+fpp.set_maxrad(8)
+ccs = all_ccs(epic_id)
+for cc in ccs:
+    fpp.apply_cc(cc)
+fpp.FPPplots()
+

### 2015-03-21 fpp/k2fpp/fpp.py

@@ -1,0 +1,90 @@
+from __future__ import print_function, division
+
+from vespa.fpp import FPPCalculation
+from vespa.populations import PopulationSet
+import os, os.path
+import numpy as np
+import pandas as pd
+import logging
+
+from .transitsignal import K2_TransitSignal
+from .tables import PAPER1_TABLE
+from .starmodels import get_starmodel
+from .photometry import all_mags
+from .utils import fp_fressin
+
+#K2_FPPDIR = os.getenv('K2_FPPDIR',
+#                      os.path.expanduser(os.path.join('~','.k2fpp')))
+K2_FPPDIR = 'fppmodels'
+
+from astropy import constants as const
+RSUN = const.R_sun.cgs.value
+REARTH = const.R_earth.cgs.value
+
+SECONDARY_FILE = os.path.expanduser('~/repositories/k2-characterization'+
+                                    '/fpp/secondary.csv')
+SECONDARY = pd.read_csv(SECONDARY_FILE, 
+                        names=['epic_id','period',
+                               'primary','t0_1',
+                               'secondary','t0_2'])
+SECONDARY.index = SECONDARY['epic_id']
+
+def max_secondary(epic_id, i=1):
+    secdepth = SECONDARY.ix[epic_id, 'secondary']
+    if np.size(secdepth) > 1:
+        secdepth = secdepth.iloc[i-1]
+    return secdepth/1e3
+
+class K2_FPPCalculation(FPPCalculation):
+    def __init__(self, epic_id, i=None,
+                 recalc=False, **kwargs):
+        
+        name = '{}'.format(epic_id)
+        if i is None:
+            name += '.1'
+        else:
+            name += '.{:.0f}'.format(i)
+
+        ra = PAPER1_TABLE.ix[epic_id,'ra']
+        dec = PAPER1_TABLE.ix[epic_id,'dec']
+        rprs = PAPER1_TABLE.ix[epic_id,'rprs']
+        if np.size(ra) > 1:
+            ra = ra.iloc[0]
+            dec = dec.iloc[0]
+            if i is None:
+                raise ValueError('{} has {} candidates.  ' +\
+                                     'Please provide index'.format(epic_id,
+                                                                   len(ra)))
+            rprs = rprs.iloc[i-1]
+        folder = os.path.join(K2_FPPDIR,name)
+        if not os.path.exists(folder):
+            os.makedirs(folder)
+        trsig = K2_TransitSignal(epic_id, i)
[…]

### 2015-03-21 fpp/write_list.py

@@ -1,0 +1,31 @@
+#!/usr/bin/env python
+from __future__ import print_function, division
+
+import pandas as pd
+import numpy as np
+
+from k2fpp.tables import PAPER1_TABLE
+
+import logging
+
+import warnings
+warnings.simplefilter("error")
+warnings.simplefilter("ignore", DeprecationWarning)
+
+
+ids = []
+inds = []
+for epic_id in PAPER1_TABLE.index:
+    name = PAPER1_TABLE.ix[epic_id,'epic_id']
+    if type(name)==pd.Series:
+        for i in range(1,len(name)+1):
+            ids.append(epic_id)
+            inds.append(i)
+    else:
+        ids.append(epic_id)
+        inds.append(1)
+
+for epic_id, i in zip(ids, inds):
+    print('./do_fpp.py {} {}'.format(epic_id,i))
+
+

### 2015-03-21 table_fpp.tex
tdm

--- 2015-03-09 table_fpp.tex
@@
 %\LongTables
-\begin{deluxetable*}{lcllllllc}
+\begin{deluxetable*}{lcccccccc}
 \tablewidth{0pt}
@@
 \tablecaption{False Positive Probability Calculation Results}
-\label{Tab:FPP}
+\label{Table:FPP}
 \tablehead{
-\colhead{EPIC} &
-\colhead{Cand. Num.} &
+\colhead{Candidate} &
 \colhead{max($\delta_{\rm sec}$)} &
+\colhead{AO?} &
 \colhead{${\rm Pr}_{\rm EB}$} &
@@
 \startdata
-$201208431$ & $1$ & $0.51$ & $< 10^{-4}$ & $0.0058$ & $0.00011$ & $0.22$ & $0.0059$ & Validated \\
-$201257461$ & $1$ & $0.59$ & $< 10^{-4}$ & $0.072$ & $0.93$ & $0.22$ & $1$ & FP \\
-$201295312$ & $1$ & $0.04$ & $< 10^{-4}$ & $0.008$ & $0.00014$ & $0.15$ & $0.0082$ & Validated \\
-$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ & Candidate \\
-$201338508$ & $2$ & $0.33$ & $< 10^{-4}$ & $0.006$ & $< 10^{-4}$ & $0.17$ & $0.006$ & Validated \\
-$201367065$ & $1$ & $0.15$ & $< 10^{-4}$ & $0.01$ & $< 10^{-4}$ & $0.18$ & $0.01$ & Validated \\
-$201367065$ & $2$ & $0.67$ & $< 10^{-4}$ & $0.00063$ & $< 10^{-4}$ & $0.14$ & $0.00063$ & Validated \\
-$201384232$ & $1$ & $0.44$ & $< 10^{-4}$ & $0.00017$ & $0.00023$ & $0.21$ & $0.0004$ & Validated \\
-$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ & Candidate \\
-$201403446$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.0069$ & $0.0013$ & $0.13$ & $0.0083$ & Validated \\
-$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ & Candidate \\
-$201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.22$ & $0.048$ & $0.18$ & $0.27$ & Candidate \\
-$201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.15$ & $0.0028$ & $0.14$ & $0.15$ & Candidate \\
-$201505350$ & $1$ & $2.69$ & $< 10^{-4}$ & $0.13$ & $0.86$ & $0.18$ & $0.99$ & FP \\
-$201505350$ & $2$ & $0.70$ & $< 10^{-4}$ & $0.0025$ & $0.00013$ & $0.07$ & $0.0026$ & Validated \\
-$201546283$ & $1$ & $0.15$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Validated \\
-$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ & Candidate \\
-$201555883$ & $1$ & $0.94$ & $< 10^{-4}$ & $0.0044$ & $0.0004$ & $0.20$ & $0.0048$ & Validated \\
-$201565013$ & $1$ & $1.69$ & $0.0023$ & $0.14$ & $0.82$ & $0.07$ & $0.96$ & FP \\
-$201569483$ & $1$ & $2.06$ & $0.48$ & $0.00061$ & $0.097$ & $0.01$ & $0.58$ & Candidate \\
-$201577035$ & $1$ & $0.14$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.00015$ & $0.20$ & $0.0002$ & Validated \\
-$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ & Candidate \\
-$201613023$ & $1$ & $0.08$ & $< 10^{-4}$ & $0.0016$ & $< 10^{-4}$ & $0.15$ & $0.0016$ & Validated \\
-$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ & Candidate \\
-$201629650$ & $1$ & $0.43$ & $< 10^{-4}$ & $0.005$ & $0.0012$ & $0.17$ & $0.0062$ & Validated \\
-$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ & Candidate \\
-$201649426$ & $1$ & $3.10$ & $0.81$ & $0.0016$ & $0.13$ & $0.01$ & $0.94$ & FP \\
-$201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.03$ & $0.29$ & $0.06$ & $0.32$ & Candidate \\
-$201736247$ & $1$ & $0.42$ & $< 10^{-4}$ & $0.0015$ & $0.00092$ & $0.22$ & $0.0024$ & Validated \\
-$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ & Candidate \\
-$201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0099$ & $0.00069$ & $0.17$ & $0.011$ & Candidate \\
-$201779067$ & $1$ & $1.97$ & $0.034$ & $0.038$ & $0.3$ & $0.03$ & $0.37$ & Candidate \\
-$201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.014$ & $0.0024$ & $0.17$ & $0.016$ & Candidate \\
-$201855371$ & $1$ & $0.62$ & $< 10^{-4}$ & $0.0006$ & $< 10^{-4}$ & $0.20$ & $0.00071$ & Validated \\
-$201912552$ & $1$ & $0.47$ & $< 10^{-4}$ & $0.00058$ & $< 10^{-4}$ & $0.22$ & $0.00058$ & Validated \\
-$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$ & Candidate
+$201208431.01$ & $0.51$ &  - & $< 10^{-4}$ & $7.4\times10^{-4}$ & $1.0\times10^{-4}$ & $0.22$ & $8.4\times10^{-4}$ & Planet \\
+ \color{red} $201257461.01$ & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $0.011$  & \color{red}  $0.989$  & \color{red}  $0.22$  & \color{red}  $1.000$  & \color{red}  FP\\
+$201295312.01$ & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $1.0\times10^{-4}$ & $0.15$ & $1.1\times10^{-4}$ & Planet \\
+$201338508.01$ & $0.63$ &  - & $< 10^{-4}$ & $4.0\times10^{-3}$ & $5.9\times10^{-4}$ & $0.17$ & $4.6\times10^{-3}$ & Planet \\
+$201338508.02$ & $0.33$ &  - & $< 10^{-4}$ & $7.7\times10^{-4}$ & $< 10^{-4}$ & $0.17$ & $7.7\times10^{-4}$ & Planet \\
+$201367065.01$ & $0.15$ &  - & $< 10^{-4}$ & $1.3\times10^{-3}$ & $< 10^{-4}$ & $0.18$ & $1.3\times10^{-3}$ & Planet \\
+$201367065.02$ & $0.67$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.14$ & $< 10^{-4}$ & Planet \\
+$201384232.01$ & $0.44$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.1\times10^{-4}$ & $0.21$ & $2.3\times10^{-4}$ & Planet \\
+$201393098.01$ & $0.52$ &  - & $< 10^{-4}$ & $2.6\times10^{-3}$ & $0.022$ & $0.17$ & $0.025$ & Candidate \\
+$201403446.01$ & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $9.8\times10^{-4}$ & $0.13$ & $10.0\times10^{-4}$ & Planet \\
+$201445392.01$ & $0.26$ &  - & $< 10^{-4}$ & $1.8\times10^{-3}$ & $0.049$ & $0.22$ & $0.051$ & Candidate \\
+$201445392.02$ & $0.18$ &  - & $< 10^{-4}$ & $0.034$ & $0.055$ & $0.18$ & $0.089$ & Candidate \\
+$201465501.01$ & $0.68$ &  - & $< 10^{-4}$ & $0.021$ & $3.0\times10^{-3}$ & $0.14$ & $0.025$ & Candidate \\
+ \color{red} $201505350.01$  & \color{red}  $2.69$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $0.020$  & \color{red}  $0.966$  & \color{red}  $0.18$  & \color{red}  $0.986$  & \color{red}  FP\\
+$201505350.02$ & $0.70$ &  - & $< 10^{-4}$ & $3.0\times10^{-4}$ & $1.2\times10^{-4}$ & $0.07$ & $4.2\times10^{-4}$ & Planet \\
+$201546283.01$ & $0.15$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Planet \\
+$201549860.01$ & $0.18$ &  - & $< 10^{-4}$ & $1.7\times10^{-3}$ & $6.5\times10^{-4}$ & $0.20$ & $2.4\times10^{-3}$ & Planet \\
+$201555883.01$\tablenotemark{1} & $0.94$ &  - & $< 10^{-4}$ & $5.8\times10^{-4}$ & $3.7\times10^{-4}$ & $0.20$ & $9.5\times10^{-4}$ & Candidate \\
+ \color{red} $201565013.01$  & \color{red}  $1.69$  & \color{red}   -  & \color{red}  $2.7\times10^{-3}$  & \color{red}  $0.027$  & \color{red}  $0.926$  & \color{red}  $0.07$  & \color{red}  $0.956$  & \color{red}  FP\\
+$201569483.01$ & $2.06$ &  - & $0.468$ & $< 10^{-4}$ & $0.092$ & $0.01$ & $0.560$ & Candidate \\
+$201577035.01$ & $0.14$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $1.0\times10^{-4}$ & $0.20$ & $1.1\times10^{-4}$ & Planet \\
+$201596316.01$ & $0.45$ &  - & $< 10^{-4}$ & $1.3\times10^{-3}$ & $2.1\times10^{-3}$ & $0.17$ & $3.4\times10^{-3}$ & Planet \\
+$201613023.01$ & $0.08$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.15$ & $< 10^{-4}$ & Planet \\
+$201617985.01$ & $0.27$ &  - & $< 10^{-4}$ & $0.016$ & $1.7\times10^{-3}$ & $0.16$ & $0.018$ & Candidate \\
+$201629650.01$ & $0.43$ &  - & $< 10^{-4}$ & $6.3\times10^{-4}$ & $1.1\times10^{-3}$ & $0.17$ & $1.7\times10^{-3}$ & Planet \\
+$201635569.01$ & $0.79$ &  - & $< 10^{-4}$ & $7.5\times10^{-3}$ & $0.069$ & $0.09$ & $0.076$ & Candidate \\
+ \color{red} $201649426.01$  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.819$  & \color{red}  $2.2\times10^{-4}$  & \color{red}  $0.119$  & \color{red}  $0.01$  & \color{red}  $0.938$  & \color{red}  FP\\
+$201702477.01$ & $0.70$ &  - & $< 10^{-4}$ & $4.0\times10^{-3}$ & $0.277$ & $0.06$ & $0.281$ & Candidate \\
+$201736247.01$ & $0.42$ &  - & $< 10^{-4}$ & $1.9\times10^{-4}$ & $8.5\times10^{-4}$ & $0.22$ & $1.0\times10^{-3}$ & Planet \\
+$201754305.01$ & $0.65$ &  - & $< 10^{-4}$ & $1.9\times10^{-3}$ & $1.5\times10^{-3}$ & $0.18$ & $3.4\times10^{-3}$ & Planet \\
+$201754305.02$ & $0.38$ &  - & $< 10^{-4}$ & $1.2\times10^{-3}$ & $6.4\times10^{-4}$ & $0.17$ & $1.9\times10^{-3}$ & Planet \\
+$201779067.01$ & $1.97$ &  - & $0.036$ & $5.0\times10^{-3}$ & $0.286$ & $0.03$ & $0.327$ & Candidate \\
+$201828749.01$ & $0.39$ &  Y & $< 10^{-4}$ & $1.7\times10^{-3}$ & $2.2\times10^{-3}$ & $0.17$ & $3.9\times10^{-3}$ & Planet \\
+$201855371.01$ & $0.62$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $1.7\times10^{-4}$ & Planet \\
+$201912552.01$ & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
+$201929294.02$ & $3.12$ &  - & $< 10^{-4}$ & $6.8\times10^{-3}$ & $0.052$ & $0.05$ & $0.059$ & Candidate
 
 \enddata
-\tablecomments{blurgh.}
+\tablenotetext{1}{Passes FPP criterion for planet, but kept as candidate due to the ephemeris match with EPIC 201569483}
 \end{deluxetable*}

### 2015-03-21 fpp/k2fpp/contrast.py
written ini files

@@ -9,6 +9,7 @@ from scipy.io.idl import readsav
 from starutils.contrastcurve import ContrastCurve
 
 from .photometry import all_mags
+from .tables import MAGS
 
 AODATA_DIR = os.path.expanduser('~/repositories/k2-characterization/aodata/proc')
 
@@ -30,6 +31,23 @@ def AO_contrast_curves(epic_id):
             ok = coverage==1
             ccs.append(ContrastCurve(rs[ok],dmags[ok],band,
                                      name='PHARO'.format(band)))
+
+    #no join curve for this one
+    if epic_id==201828749:
+        for f in files:
+            m = re.search('_epic\d+_(\w+)_sat_unsat_qlconprofiles.sav', f)
+            if m:
+                data = readsav(f)
+                band = m.group(1).upper()
+                if band=='KS':
+                    band = 'K'
+                rs = data['angscalearr']
+                dmags = data['fivesigqlconprof']
+                coverage = data['unsatfraccoverage']
+                ok = coverage==1
+                ccs.append(ContrastCurve(rs[ok],dmags[ok],band,
+                                     name='PHARO'.format(band)))
+            
     return ccs
 
 def SDSS_contrast(epic_id):
@@ -56,3 +74,8 @@ def write_ccs(epic_id, rootfolder=os.path.expanduser('~/repositories/k2-characte
             outfile = '{}/{}_{}.cc'.format(dir, cc.name, cc.band)
             np.savetxt(outfile, np.array([cc.rs,cc.dmags]).T)
     
+def write_all_ccs():
+    for epic_id in MAGS.index:
+        write_ccs(epic_id)
+
+        

### 2015-03-21 fpp/write_ini.py

@@ -1,0 +1,59 @@
+#!/usr/bin/env python
+from __future__ import print_function, division
+
+import numpy as np
+import os, os.path, re, glob
+from configobj import ConfigObj
+
+from k2fpp.tables import PAPER1_TABLE, MAGS
+from k2fpp.photometry import all_mags
+
+cands = np.loadtxt('allcands.list', dtype=str)
+
+FOLDER = os.path.expanduser('~/repositories/k2-characterization/fpp/fppmodels')
+
+def write_ini(epic_id, i=1, maxrad=12):
+    filename ='{}/{}.{}/fpp.ini'.format(FOLDER, epic_id, i)
+    config = ConfigObj()
+    config.filename = filename
+
+    config['name'] = '{}.{}'.format(epic_id, i)
+        
+    ra = PAPER1_TABLE.ix[epic_id,'ra']
+    dec = PAPER1_TABLE.ix[epic_id,'dec']
+    rprs = PAPER1_TABLE.ix[epic_id,'rprs']
+    period = PAPER1_TABLE.ix[epic_id,'period']
+    if np.size(ra) > 1:
+        ra = ra.iloc[0]
+        dec = dec.iloc[0]
+        rprs = rprs.iloc[i-1]    
+        period = period.iloc[i-1]
+
+    config['ra'] = ra
+    config['dec'] = dec
+    config['rprs'] = rprs
+    config['period'] = period
+
+    mags = all_mags(epic_id)
+    config['mags'] = {}
+    for b in ['B','V','J','H','K',
+              'W1','W2','W3']:
+        mag, err = (mags[b], mags['{}err'.format(b)])
+        config['mags'][b] = [mag,err]
+    config['mags']['Kepler'] = mags['Kepler']
+
+    config['constraints'] = {}
+    config['constraints']['maxrad'] = maxrad
+    ccfiles = glob.glob('{}/{}/*.cc'.format(FOLDER,config['name']))
+    config['constraints']['ccfiles'] = [os.path.basename(f)
+                                        for f in ccfiles]
+    config.write()
+        
+if __name__=='__main__':
+
+    for cand in cands:
+        m = re.search('(\d+)\.(\d)',cand)
+        if m:
+            epic_id = int(m.group(1))
+            i = int(m.group(2))
+            write_ini(epic_id, i)

### 2015-03-21 fpp/write_ini.py
writing trsig files now

@@ -7,6 +7,7 @@ from configobj import ConfigObj
 
 from k2fpp.tables import PAPER1_TABLE, MAGS
 from k2fpp.photometry import all_mags
+from k2fpp.transitsignal import K2_TransitSignal
 
 cands = np.loadtxt('allcands.list', dtype=str)
 
@@ -48,7 +49,11 @@ def write_ini(epic_id, i=1, maxrad=12):
     config['constraints']['ccfiles'] = [os.path.basename(f)
                                         for f in ccfiles]
     config.write()
-        
+
+def write_trsig(epic_id, i=1):
+    trsig = K2_TransitSignal(epic_id, i)
+    trsig.save('{}/{}.{}/trsig.pkl'.format(FOLDER, epic_id, i))
+    
 if __name__=='__main__':
 
     for cand in cands:
@@ -57,3 +62,4 @@ if __name__=='__main__':
             epic_id = int(m.group(1))
             i = int(m.group(2))
             write_ini(epic_id, i)
+            write_trsig(epic_id, i)

### 2015-03-21 fpp/k2fpp/fpp.py
write_ini now using get_trsig

@@ -87,4 +87,8 @@ class K2_FPPCalculation(FPPCalculation):
 
         FPPCalculation.__init__(self, trsig, popset, folder=folder)
         self.apply_secthresh(max_secondary(epic_id, i))
-        
+
+
+#function version of the above
+def get_trsig(epic_id, i=None, recalc=False, **kwargs):
+    

### 2015-03-21 fpp/k2fpp/transitsignal.py

@@ -61,3 +61,25 @@ class K2_TransitSignal(TransitSignal_FromSamples):
                                         samples['T_tau'])
         self.name = name
 
+#function version of the above
+def get_trsig(epic_id, i=None):
+    samples = get_samples(epic_id)
+
+    if(type(samples)==list):
+        #integer number must be passed
+        samples = samples[i-1]
+        period = PAPER1_TABLE.ix[epic_id, 'period'].iloc[i-1]
+    else:
+        period = PAPER1_TABLE.ix[epic_id, 'period']
+
+    name = '{}'.format(epic_id)
+    if i is None:
+        name += '.1'
+    else:
+        name += '{:.0f}'.format(i)
+
+    TransitSignal_FromSamples(period, 
+                                samples['T'],
+                                samples['delta'],
+                                samples['T_tau'])
+    self.name = name    

### 2015-03-21 fpp/write_ini.py

@@ -7,7 +7,7 @@ from configobj import ConfigObj
 
 from k2fpp.tables import PAPER1_TABLE, MAGS
 from k2fpp.photometry import all_mags
-from k2fpp.transitsignal import K2_TransitSignal
+from k2fpp.transitsignal import get_trsig
 
 cands = np.loadtxt('allcands.list', dtype=str)
 
@@ -51,7 +51,7 @@ def write_ini(epic_id, i=1, maxrad=12):
     config.write()
 
 def write_trsig(epic_id, i=1):
-    trsig = K2_TransitSignal(epic_id, i)
+    trsig = get_trsig(epic_id, i)
     trsig.save('{}/{}.{}/trsig.pkl'.format(FOLDER, epic_id, i))
     
 if __name__=='__main__':

### 2015-03-21 fpp/k2fpp/transitsignal.py
update get_trsig

@@ -78,8 +78,9 @@ def get_trsig(epic_id, i=None):
     else:
         name += '{:.0f}'.format(i)
 
-    TransitSignal_FromSamples(period, 
+    trsig = TransitSignal_FromSamples(period, 
                                 samples['T'],
                                 samples['delta'],
-                                samples['T_tau'])
-    self.name = name    
+                                samples['T_tau'],
+                                name=name)
+    return trsig

### 2015-03-21 fpp/write_ini.py
only write ccfiles if not zero-length

@@ -46,8 +46,9 @@ def write_ini(epic_id, i=1, maxrad=12):
     config['constraints'] = {}
     config['constraints']['maxrad'] = maxrad
     ccfiles = glob.glob('{}/{}/*.cc'.format(FOLDER,config['name']))
-    config['constraints']['ccfiles'] = [os.path.basename(f)
-                                        for f in ccfiles]
+    if len(ccfiles > 0):
+        config['constraints']['ccfiles'] = [os.path.basename(f)
+                                            for f in ccfiles]
     config.write()
 
 def write_trsig(epic_id, i=1):

### 2015-03-21 fpp/write_ini.py
typo

@@ -46,7 +46,7 @@ def write_ini(epic_id, i=1, maxrad=12):
     config['constraints'] = {}
     config['constraints']['maxrad'] = maxrad
     ccfiles = glob.glob('{}/{}/*.cc'.format(FOLDER,config['name']))
-    if len(ccfiles > 0):
+    if len(ccfiles) > 0:
         config['constraints']['ccfiles'] = [os.path.basename(f)
                                             for f in ccfiles]
     config.write()

### 2015-03-21 fpp/write_ini.py
adding back gri

@@ -37,7 +37,7 @@ def write_ini(epic_id, i=1, maxrad=12):
 
     mags = all_mags(epic_id)
     config['mags'] = {}
-    for b in ['B','V','J','H','K',
+    for b in ['B','V','g','r','i','J','H','K',
               'W1','W2','W3']:
         mag, err = (mags[b], mags['{}err'.format(b)])
         config['mags'][b] = [mag,err]

### 2015-03-21 fpp/write_ini.py
not overwriting write_trsig

@@ -51,9 +51,11 @@ def write_ini(epic_id, i=1, maxrad=12):
                                             for f in ccfiles]
     config.write()
 
-def write_trsig(epic_id, i=1):
-    trsig = get_trsig(epic_id, i)
-    trsig.save('{}/{}.{}/trsig.pkl'.format(FOLDER, epic_id, i))
+def write_trsig(epic_id, i=1, redo=False):
+    trsig_file = '{}/{}.{}/trsig.pkl'.format(FOLDER, epic_id, i)
+    if not os.path.exists(trsig_file) and not redo:
+        trsig = get_trsig(epic_id, i)
+        trsig.save(trsig_file)
     
 if __name__=='__main__':
 

### 2015-03-21 fpp/write_ini.py
inflating photometric errors

@@ -13,7 +13,7 @@ cands = np.loadtxt('allcands.list', dtype=str)
 
 FOLDER = os.path.expanduser('~/repositories/k2-characterization/fpp/fppmodels')
 
-def write_ini(epic_id, i=1, maxrad=12):
+def write_ini(epic_id, i=1, maxrad=12, photerr_inflate=3):
     filename ='{}/{}.{}/fpp.ini'.format(FOLDER, epic_id, i)
     config = ConfigObj()
     config.filename = filename
@@ -40,7 +40,7 @@ def write_ini(epic_id, i=1, maxrad=12):
     for b in ['B','V','g','r','i','J','H','K',
               'W1','W2','W3']:
         mag, err = (mags[b], mags['{}err'.format(b)])
-        config['mags'][b] = [mag,err]
+        config['mags'][b] = [mag,err*photerr_inflate]
     config['mags']['Kepler'] = mags['Kepler']
 
     config['constraints'] = {}

### 2015-03-22 fpp/k2fpp/tables.py
implemented specific apertures

@@ -68,8 +68,14 @@ def mag_table(filename='../table_photometry.txt'):
     df.index = df['name']
     return df
 
+def aperture_table(filename='../apertures.csv'):
+    df = pd.read_csv(filename)
+    df.index = df['epic']
+    return df
+    
 MAGS = mag_table()
 DARTMOUTH_PARS = dartmouth_table()
 PADOVA_PARS = padova_table()
 PAPER1_TABLE = paper1_table()
+APERTURES = aperture_table()
 

### 2015-03-22 fpp/write_ini.py

@@ -5,7 +5,7 @@ import numpy as np
 import os, os.path, re, glob
 from configobj import ConfigObj
 
-from k2fpp.tables import PAPER1_TABLE, MAGS
+from k2fpp.tables import PAPER1_TABLE, MAGS, APERTURES
 from k2fpp.photometry import all_mags
 from k2fpp.transitsignal import get_trsig
 
@@ -13,7 +13,7 @@ cands = np.loadtxt('allcands.list', dtype=str)
 
 FOLDER = os.path.expanduser('~/repositories/k2-characterization/fpp/fppmodels')
 
-def write_ini(epic_id, i=1, maxrad=12, photerr_inflate=3):
+def write_ini(epic_id, i=1, photerr_inflate=3):
     filename ='{}/{}.{}/fpp.ini'.format(FOLDER, epic_id, i)
     config = ConfigObj()
     config.filename = filename
@@ -44,7 +44,7 @@ def write_ini(epic_id, i=1, maxrad=12, photerr_inflate=3):
     config['mags']['Kepler'] = mags['Kepler']
 
     config['constraints'] = {}
-    config['constraints']['maxrad'] = maxrad
+    config['constraints']['maxrad'] = (APERTURES.ix[epic_id, 'radius'] + 1)*4
     ccfiles = glob.glob('{}/{}/*.cc'.format(FOLDER,config['name']))
     if len(ccfiles) > 0:
         config['constraints']['ccfiles'] = [os.path.basename(f)

### 2015-03-23 ms.tex
words for planet properties

@@
 
-In \paperit, we present only parameters directly observable from the \KT\
-light curve itself: the period, time of transit center, and transit depth.
+In \paperit, only parameters directly observable from the \KT\ light curve
+itself were reported: the period, time of transit center, and transit depth.
 With stellar properties now in hand, we can convert these observational
 results into fundamental parameters of each planet candidate.
+For each candidate, we fit the light curve using a physical transit model
+\citep{Mandel02, Kipping10b} simultaneously with the systematics model
+described by \paperit.
+We use \texttt{emcee} to sample from the posterior probability distribution
+for the stellar---limb darkening coefficients, mass, radius, and effective
+temperature---and planetary---radius, period, phase, impact parameter,
+eccentricity, and argument of periapsis---parameters, conditioned on the
+light curve and the measured stellar properties.
+Following \paperit, the likelihood function that we use is marginalized over
+the parameters of the systematics model.
+To incorporate the stellar measurements, we approximate the measurements as a
+three-dimensional Gaussian in mass, radius, and effective temperature.
 
-For each candidate, we fit a transit and systematic model simultaneously
-to the data.
-The transit model is an exposure-time integrated, two-parameter limb darkened 
-light curve \citep{Mandel02,Kipping10b}.
-We parameterize... \dfmtodo{What are the parameters in the model?}
-
-This method enable us to marginalize over the parameters of the
-data-driven model of the instrumental systematics described in \paperit.
-
-The results are given in Table 3.
-
-\dfmtodo{Add more to this section.}
-
-In this analysis, we assume the dilution caused by additional stars contributing
-flux into the aperture is negligible for nearly all systems.
-Given the location of the \Ci\ field at a high galactic latitude, we expect low
-contamination by background giants. 
+In this analysis, we assume the dilution caused by additional stars
+contributing flux into the aperture is negligible for nearly all systems.
+Given the location of the \Ci\ field at a high galactic latitude, we expect
+low contamination by background giants.
 Nevertheless, this assumption may not be valid for all systems.
 Any contamination unaccounted for, as may happen if any of these stars are
-actually unresolved binaries, would cause us to underestimate the radii
-of any planets we detect.
+actually unresolved binaries, would cause us to underestimate the radii of any
+planets we detect.
 Therefore, high-contrast adaptive optics imaging of any systems should be
@@
 
-One system, EPIC 201828749, is known to be a binary through AO imaging
-as discussed in \textsection\ref{sec:AO}. 
-In this case, we do account for the dilution induced by the companion. 
-From our relative $JHK$ photometry of the two stars, we infer an expected flux
-ratio between the two stars in the \kep\ bandpass, inflating the transit depth by 
-this factor to account for the dilution. 
-We marginalize  \dfmtodo{More text...}
+The planet parameters measured by this analysis are listed in Table 3.
+
+%%%
+%%%  I haven't actually done this... perhaps I can do it in response to
+%%%  referee if they ask for it...
+%%%
+% One system, EPIC 201828749, is known to be a binary through AO imaging
+% as discussed in \textsection\ref{sec:AO}.
+% In this case, we do account for the dilution induced by the companion.
+% From our relative $JHK$ photometry of the two stars, we infer an expected flux
+% ratio between the two stars in the \kep\ bandpass, inflating the transit depth
+% by this factor to account for the dilution.
+% We marginalize  \dfmtodo{More text...}
 

### 2015-03-23 ms.tex
footnote urls

@@
 We provide full chains using both inflated and un-inflated
-uncertainties,\footnote{http://www.astro.princeton.edu/~tdm/k2/}
+uncertainties,\footnote{\url{http://www.astro.princeton.edu/~tdm/k2/}}
 though in the rest of this work (and in Table 2) we adopt
@@
 \teff\ was calculated by comparing our optical spectra with the CFIST
-suite\footnote{http://phoenix.ens-lyon.fr/Grids/BT-Settl/CIFIST2011/} of the BT-SETTL
+suite\footnote{\url{http://phoenix.ens-lyon.fr/Grids/BT-Settl/CIFIST2011/}} of the BT-SETTL
 version of the PHOENIX atmosphere models \citep{Allard13}, which gave a temperature

### 2015-03-23 ms.tex
junk

--- 2015-03-20 ms.tex
@@
 \newcommand{\anytodo}[1]{\todo{ANYONE}{NavyBlue}{#1}}
-\newcommand{\dfmtodo}[1]{\todo{DFM}{ForestGreen}{#1}}
 
 \newcommand{\Nfp}{4}
-\newcommand{\Nvalidated}{21}
-\newcommand{\Nlimbo}{11} %adds to 36?  good.
+\newcommand{\Nvalidated}{22} %16 without contrast curves
+\newcommand{\Nlimbo}{10} %adds up to 36
 
@@
 
-\title{Stellar and Planetary Properties of \KT\ Campaign 1
-Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving
-Earth-like Insolation}
+\title{(Working Title) Stellar and Planetary Properties of \KT\ \Ci\
+Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving
+Earth-like Insolation?)}
 
-\newcommand{\caltech}{1}
-\newcommand{\cfa}{2}
+\newcommand{\caltech}{2}
+\newcommand{\cfa}{3}
 \newcommand{\nyu}{4}
-\newcommand{\princeton}{3}
-\newcommand{\mpia}{5}
-\newcommand{\cds}{6}
-\newcommand{\jcpa}{7}
-\newcommand{\texas}{8}
-\newcommand{\hjs}{9}
-
+\newcommand{\princeton}{5}
+\newcommand{\mpia}{6}
+\newcommand{\cds}{7}
 \author{%
 % The Heavy Lifters
-Benjamin~T.~Montet\altaffilmark{\caltech,\cfa},
+Benjamin~T.~Montet\altaffilmark{1,\caltech,\cfa},
+Daniel~Foreman-Mackey\altaffilmark{\nyu},
 Timothy~D.~Morton\altaffilmark{\princeton},
-Daniel~Foreman-Mackey\altaffilmark{\nyu},
 % The Benefactors
@@
 % (ranked by integration time x collecting area)
-Brendan~P.~Bowler\altaffilmark{\caltech, \jcpa},
-David~W.~Latham\altaffilmark{\cfa},
-Allyson~Bieryla\altaffilmark{\cfa},
-Andrew~W.~Mann\altaffilmark{\texas, \hjs},
+Brendan~P.~Bowler,
+David~W.~Latham,
+Allyson~Bieryla,
+Andrew~W.~Mann,
+And Any TRES Team Members We Should Add
 }
 
-\email{btm@astro.caltech.edu}
+\altaffiltext{1}         {btm@astro.caltech.edu}
 \altaffiltext{\caltech}  {Cahill Center for Astronomy and Astrophysics,
@@
                           Cambridge, MA 02138, USA}
-\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
-                          Princeton, NJ, 08544, USA}
 \altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
@@
                           4 Washington Place, New York, NY, 10003, USA}
+\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
+                          Princeton, NJ, 08544, USA}
 \altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
@@
                           726 Broadway, 7th Floor, New York, NY, 10003, USA}
-\altaffiltext{\jcpa} {Caltech Joint Center for Planetary Astronomy Fellow}
-\altaffiltext{\texas} {Department of Astronomy, The University of Texas at
-                            Austin, Austin, TX 78712, USA}
-\altaffiltext{\hjs} {Harlan J. Smith Fellow, The University of Texas at Austin}
 
@@
 In this paper, we present stellar and planetary properties for all systems.
-We combine ground-based seeing limited survey data and
-adaptive optics imaging with a detailed transit analysis scheme to validate
-\Nvalidated\ candidates as planets and identify \Nfp\ candidates as likely false positives.
+We combine archival imaging, ground-based seeing limited survey data, and
+adaptive optics imaging with a detailed transit analysis scheme to confirm
+\Nvalidated\ as planets and identify \Nfp\ as likely false positives.
 Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
-hosting a $2.24 \pm 0.25 R_\odot$ planet with $T_{eq} = 271 \pm 16$ K and an
+hosting a \anytodo{Radius} planet with $T_{eq} = 275 \pm 15$ K and an
 orbital period of 33 days.
-We also present \texttt{vespa}, a new general-purpose implementation
-of the \citet{Morton12} procedure to calculate false positive probabilities
-for \KT\ candidates.
+\anytodo{Anything we should add?}
 \end{abstract}
 
-\keywords{catalogs --- planetary systems --- planets and satellites: detection
-                   --- stars: fundamental parameters}
+\keywords{\btmtodo{Keywords}}
 
@@
 discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, Mullaly15}.
-The fidelity of this sample is high: most of these planet candidates are truly planets
+The fidelity of this sample is high, so most of these planet candidates are truly planets
 \citep{Morton11b, Fressin13}.
@@
 thruster firing.
-As a result, the detector drifts relative to the sky
-at the rate of $\sim 1\arcsec$ hr$^{-1}$, with rapid corrections 
+The result of this observing strategy is that the targets appear to drift
+at the rate of $\sim 1\arcsec$ s$^{-1}$, with rapid corrections that occur
 approximately once every six hours.
@@
 Worse yet, these variations occur on timescales similar to transit signals, potentially
-masking the observational signature of a planet passing between \kep\ and its host star.
+masking the observational signature of a planet passing between \kep\ and the host star.
 
-There has been considerable effort to recover these planetary signals.
+There has been considerable effort to recover these signals.
 \citet{Vanderburg14} extract aperture photometry and de-correlate with image centroid
@@
 A similar technique was employed by \citet{Armstrong15a} to identify potential eclipsing
-binary systems and to identify a transiting system near a 3:2 period commensurability
+binary systems and to identify a transiting system very near a 3:2 period commensurability
 \citep{Armstrong15b}.
@@
 signal, and such a technique is prone to either over-fitting, in which some of the
-astrophysical signal is also removed, or under-fitting, in which some
-of the instrumental systematics remain.
-A better strategy is to simultaneously fit both the signal and the systematics, as is common
-practice in cosmology and, increasingly, in radial velocity searches for planetary systems
+astrophysical signal is also removed, or under-fitting, in which some instrumental noise
+remains.
+A better strategy is to simultaneously fit both the signal and the noise, as is commonly
+done in cosmology and, increasingly, in radial velocity searches for planetary systems
 \citep[e.g.][]{Ferreira00, Boisse11, Haywood14, Grunblatt15}.
@@
 in a search for transiting planets.
-They assume that the dominant trends in the observed stellar light
+The authors of that paper assume that the dominant trends in the observed stellar light
 curves are caused by spacecraft motion and are shared by many stars.
@@
 This method enables fitting without over-fitting, and also permits marginalization over
-uncertainties induced by the systematic model.
+uncertainties induced by the noise model.
 Therefore, any uncertainties in the systematics can be propogated into uncertainties in
@@
 Given these parameters and the transit data, as well as archival imaging, ground-based
-seeing-limited survey data, and adaptive optics imaging, we are able to confirm
-\Nvalidated\ of these systems as transiting planets at the 99\% confidence
-level. We also are able to confirm \Nfp\ of these systems as false positives.
+seeing limited survey data, and adaptive optics imaging, we are able to confirm
+\anytodo{Number} of these systems as transiting planets at the \anytodo{Sigma} confidence
+level. We also are able to confirm \anytodo{Number} of these systems as false positives.
 
@@
 spectroscopic data with which to characterize the stellar properties.
-Additionally, there are no measured parallaxes for any of these stars.
 Instead, we rely on photometry.
@@
 uncertainties from the AAVSO Photometric all-sky survey (APASS) DR6
-\citep{Henden14}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
+\btmtodo{Cite: Who?}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
 We also record the $J$, $H$, and $K$ magnitudes and their uncertainties
@@
 order of magnitude larger than those in $W1-W3$, so we neglect $W4$.
-These data are reported in Table 1, and a color-color diagram showing the
-$r-J, J-K$ colors of our candidates is included as Fig. \ref{fig:photometry}.
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.5\textwidth]{f1}}
-\caption{Color-color diagram displaying $r-J, J-K$ photometry for targets
-observed by \kep\ during the original
-mission (black), with our \KT\ \Ci\ planet candidates overlaid (fuchsia).
-Also included is the location of the Sun (yellow).
-Nearly all of our candidates have photometry consistent with later spectral
-types than G2.}
-\label{fig:photometry}
-\end{figure}
+These data are reported in Table 1.
 
 \subsection{Stellar Models}
-\label{sec:stellarparams}
 To convert the observed photometric data into physical properties for each
-star, we used the publicly available \texttt{isochrones} Python module\footnote{
-\url{http://github.com/timothydmorton/isochrones}}, a general-purpose
-interpolation tool for stellar model grids.
-This software does trilinear interpolation in mass--age--\feh\ space for any
-given set of model grids, thus being able to predict the value for any
-physical or photometric property provided by the models at any values of
-mass, age, and \feh\ within the boundaries of the grid.
-
-This enables a set of observed properties ($\left\{ x_i, \sigma_i \right\}$),
-either spectroscopic, photometric,
-or both, to define a likelihood function that may be sampled in
-an MCMC chain:
-\begin{equation}
-\label{eq:ischochronelhood}
-\ln \mathcal L(\boldsymbol{\theta}) = -\frac{1}{2} \displaystyle \sum_i \frac{\left(x_i -
-  I_i\left(\boldsymbol{\theta} \right)\right)^2}{\sigma_i^2},
-\end{equation}
-where $I_i(\boldsymbol{\theta})$ is the isochrone model prediction of property
-$i$ at the given parameters $\boldsymbol{\theta}$.
-If the observed properties include any apparent magnitudes, then
-$\boldsymbol{\theta}$ includes distance and $A_V$ extinction in addition
-to mass, age, and \feh.
-
-In this work, we use grids from the Dartmouth Stellar
-Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
-helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
-module.
-We then run an MCMC chain using \texttt{emcee} \citep{Foreman-Mackey12},
-an implementation of the affine-invariant ensemble sampler of
-\citet{Goodman10}
-for each host star conditioned on the observed
-photometric properties as presented in Table 1.
-We include a prior on stellar metallicity representative of the observed metallicities
-of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}, and 
-only consider stars with masses below $3.7$ $M_\odot$.
+star, we employ the use of stellar models.
+We first download the isochrone grids from the 2012 updated photometric
+systems for the relevant bandpasses from the Dartmouth Stellar Evolution
+Database \citep{Dotter08}.
+We then interpolate the isochrones onto a grid uniformly spaced in
+stellar mass (from 0.20 to 2.0 \msun), metallicity (from \feh$=-1.5$ to
+\feh$=+0.5$), age (from 1.0 to 14.0 Gyr), and log distance (from 10 pc to
+1000 pc).
+In our interpolation, we assume \afe$=0.0$ and $Y=0.2741$, the solar value.
+We then compare the expected apparent magnitudes to our observed photometry
+to measure the likelihood of each grid point.
+For each parameter, we then marginalize our likelihood over all other
+parameters in order to estimate the value of the physical properties
+for each star.
+\anytodo{This was done using MCMC right? Did you interpolate the
+\emph{likelihood function} or the \emph{model predictions}?}
 
@@
 \citep{Thompson14}.
+We find that by measuring stellar parameters without any WISE data (that is, using
+only $BVgriJHK$), we largely reproduce the same effective temperatures as when
+the WISE data is included.
+However, at the low-mass end including the WISE data systematically increases the
+measured radius and increases \logg, as shown in \btmtodo{Figure}.
+Suggestively, spectroscopic stellar parameters of EPIC 201912552
+(\textsection\ref{Spexobs}) suggest the derived photometric properties better
+represent the true physical parameters when the WISE data is included.
 
-In order to try to encapsulate the effect of model uncertainties, we also run
-MCMC chains with photometric errors inflated artificially by a factor of three.
-We provide full chains using both inflated and un-inflated 
-uncertainties,\footnote{http://www.astro.princeton.edu/~tdm/k2/}
-though in the rest of this work (and in Table 2) we adopt
-the results obtained using the inflated values.
+\btmtodo{Show plot}
 
@@
 
-A near-infrared spectrum of EPIC 201912552 was obtained using the upgraded SpeX
+A near-infrared spectrum of EPIC 201912552 was obtained using the updated SpeX
 (uSpeX) spectrograph \citep{Rayner03} on the NASA Infrared Telescope Facility
@@
 The spectrum was flat fielded, extracted, wavelength calibrated, and stacked
-using the \textit{Spextool} package \citep{Cushing04}.
+using the \textit{SpeXTool} package \citep{Cushing04}.
 An A0V-type star was observed immediately after
@@
 2.2m telescope on the night of January 30 2015.
-SNIFS provides simultaneous coverage from 3200\AA--9700\AA\ at a resolution
+SNIFS provides simultaneous coverage from 3200\AA--9700\,AA\ at a resolution
 of $\simeq1000$. Final S/N of the spectrum was $>100$ pre resolving element
@@
 
-In \paperit, we present only parameters directly observable from the \KT\
-light curve itself: the period, time of transit center, and transit depth.
-With stellar properties now in hand, we can convert these observational
-results into fundamental parameters of each planet candidate.
+To derive the physical planet parameters conditioned on the measured stellar
+parameters, we used the posterior probability distribution for quantities
+measured using the light curve---from \paperit---and re-weighted them using
+the results of the photometric and spectroscopic analysis.
+In \paperit, the authors generated MCMC samples from the posterior
+probability distribution over all the physical parameters (including stellar
+mass and radius, and the planet radius) using broad, un-informative priors on
+the values that are not constrained by the light curve.
+As described in SOME APPENDIX, these samples can be re-weighted and used to
+evaluate the posterior probability of the physical parameters of the planets
+conditioned on the stellar values.
+This also means that the effects of different measurements of the stellar
+parameters can be easily tested by applying the method described in THAT SAME
+APPENDIX.
 
-For each candidate, we fit a transit and systematic model simultaneously
-to the data.
-The transit model is an exposure-time integrated, two-parameter limb darkened 
-light curve \citep{Mandel02,Kipping10b}.
-We parameterize... \dfmtodo{What are the parameters in the model?}
-
-This method enable us to marginalize over the parameters of the
+The key assumption of this method is that the likelihood function used in
+\paperit\ is correct.
+That model was an exposure-time integrated, limb darkened light curve
+\citep{Mandel02,Kipping10b} marginalized over the parameters of the
 data-driven model of the instrumental systematics described in \paperit.
 
-The results are given in Table 3.
+The results are given in SOME TABLE.
 
-\dfmtodo{Add more to this section.}
-
-In this analysis, we assume the dilution caused by additional stars contributing
-flux into the aperture is negligible for nearly all systems.
-Given the location of the \Ci\ field at a high galactic latitude, we expect low
-contamination by background giants. 
-Nevertheless, this assumption may not be valid for all systems.
-Any contamination unaccounted for, as may happen if any of these stars are
-actually unresolved binaries, would cause us to underestimate the radii
-of any planets we detect.
-Therefore, high-contrast adaptive optics imaging of any systems should be
-obtained before any of these planets are placed on a planet mass-radius
-diagram.
-
-One system, EPIC 201828749, is known to be a binary through AO imaging
-as discussed in \textsection\ref{sec:AO}. 
-In this case, we do account for the dilution induced by the companion. 
-From our relative $JHK$ photometry of the two stars, we infer an expected flux
-ratio between the two stars in the \kep\ bandpass, inflating the transit depth by 
-this factor to account for the dilution. 
-We marginalize  \dfmtodo{More text...}
+(Include comment here about how the planet parameters assume no dilution.
+Except for the two that we have AO detected binaries for, probably?
+Brendan should have us flux ratios by the end of the day.
+In those cases, I suppose we need to include planet properties in both cases
+in which the transit is around either the more or less massive star.)
 
 \section{False Positive Analysis}
-
 As has been well known from the early days of transit searches, it is
@@
 When possible, such astrophsycial false positive scenarios are traditionally
-ruled out by detailed follow-up observations, often a combination of
-high-resolution imaging and radial-velocity measurements.
+ruled out by detailed follow-up observations, such as high-resolution
+imaging or radial-velocity measurements.
 However, the \kep\ mission, with its thousands of planet candidates
@@
 astrophysical false positive.
-This method uses population simulations of the light curves of
+This method uses population simulations
 of false positive scenarios and true transiting planets to quantify
@@
 It then combines this information with observationally motivated prior
-assumptions about the populations of field stars, the properties of
+assumtions about the populations of field stars, the properties of
 multiple star systems, and the occurrence rate of planets as determined
-from \kep\ \citep{Fressin13}, in order to determine the probability that
+from \kep\ \citet{Fressin13}, in order to determine the probability that
 the observed signal may be a false positive.
 Similar in spirit to other published methods of
-probabilistic validation, such as Blender \citep{Torres11a} and PASTIS
-\citep{Diaz14a}, it has the advantage of being computationally less demanding
+probabilistic validation, such as Blender \citep{} and PASTIS
+\citep{}, it has the advantage of being computationally less demanding
 and fully automated, and thus easily applied in batch to a large
@@
 \texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
-a new general-purpose implementation of the \citet{Morton12} procedure,
-to calculate false positive probabilities (FPPs) for each of these
-\KT\ candidates.  We impose the following constraints on false positive
-scenarios:
+a new implementation of the \citet{Morton12} procedure, to calculate
+false positive probabilities (FPPs) for each of these K2 candidates.
+While we have obtained follow-up observations of a number of these systems,
+we do the preliminary FPP calculations without taking these into account,
+in order to demonstrate the power of \texttt{vespa} analysis
+even in the absence of follow-up observations.
+The constraints we impose on false positive scenarios in these
+``follow-up free'' calculations are the following:
 \begin{itemize}
-\item A chance-aligned eclipsing binary system may reside anywhere within
-an 8 arcsecond radius from the target star.
-\item The maximum allowed depth of a potential secondary eclipse event
-is the most significantly detected signal at the same
+\item A chance-aligned eclipsing binary system must reside within
+a 4 arcsecond radius of the target star.
+\item The maximum allowed depth of a potential secondary eclipse event,
+determined as the most significantly detected signal at the same
 period of the planet candidate, once the primary transit is masked out.
-\item Blended stars must be allowed by the available adaptive optics
-and archival imaging data (discussed in detail below).
 \end{itemize}
 
-Each of these scenarios are astrophysical, caused by one object passing
-in front of another, blocking some fraction of the total light. 
-The calculations here do not include the possibility that each signal 
-is caused by an instrumental artifact in the data or some other 
-astrophysical event, such as stellar activity, masquerading as planet
-transits.
-
-Table 4 summarizes the results of these
+Table \ref{Tab:FPP} summarizes the results of these
 calculations, presenting the relative probability for each candidate
@@
 have FPP $<$ 1\%; these we consider to be validated planets.
-Of these, 18 are validated for the first time.
 The remaining \Nlimbo\ candidates have FPPs neither high enough to discard
@@
 
-We emphasize that the majority of these planets were validated based
-solely on the transit signal, with no need for follow-up imaging.  This
-demonstrates the utility of \texttt{vespa} analysis, which will be
-crucial to interpreting future \KT\ detected candidates and prioritizing
-follow-up observing efforts.
-We show these transit signals as Fig. \ref{fig:transits}.
-
-\begin{figure*}[htbp]
-\centerline{\includegraphics[width=1.0\textwidth]{f2}}
-\caption{\btmtodo{PLACEHOLDER, UPDATE. Needs transit models}.
-Phase-folded \KT\ photometry for all planet candidates analyzed in 
-this paper.
-Each is the product of a fiducial noise model, in which the median systematic
-has been removed for illustrative purposes.
-The systems which we validate as transiting planets are labeled in 
-green. 
-The systems which we confirm as false positive events are labeled in red.
-The systems which we leave as candidates are labeled in black.
-Red curves outline the median transit model for each candidate system.
-}
-\label{fig:transits}
-\end{figure*}
+We emphasize that t
 
 \subsection{Adaptive Optics Imaging}
-\label{sec:AO}
 
-We obtained high resolution images of seven stars with the 
-Palomar High Angular Resolution Observer (PHARO) infrared detector 
-\citep{Hayward01} behind the PALM3000 adaptive optics system \citep{Dekany13}
-at the Palomar 5.1-meter Hale telescope on the nights of 2015 February 3 and 4 UT.
-Sky conditions were mostly clear with light cirrus and $\approx$1$\farcs$0--1$\farcs$3 seeing
-on both nights.  
-We used the smallest plate scale of 25~mas pix$^{-1}$ which resulted
-in a field of view of 25$\farcs$6$\times$25$\farcs$6 across the 1024$^{2}$ pix$^{2}$ array.
-All observations were obtained with the 32x pupil sampling mode, resulting in Strehl ratios
-of $\approx$20--30\% in $K_S$ for our $V$=11--13~mag targets as measured by the Strehl
-monitor at the telescope in real time.
-We obtained unsaturated dithered frames of each target in $K_S$-band with typical 
-integration times of 2--10~s.
-Except for EPIC~201828749 and EPIC~201546283, which had nearby candidate 
-binary companions, we also 
-acquired deep saturated images (5--10 frames at 60 sec each) 
-to search for fainter companions.
-
-Images were registered and contrast curves were generated following \citet{Bowler15a}.
-For the saturated data, the star's position in each image was found by masking the
-saturated region and fitting a 2D bivariate Gaussian to the PSF wings.  
-Contrast
-curves for the median-combined image are calibrated using the unsaturated frames.  
-The typical sensitivity is 6.5--7.5~mag at 1$''$.
-The images were astrometrically calibrated using dithered observations of the 
-Trapezium cluster centered
-on $\theta$$^1$~Ori~C taken on 2015 Feb 3 UT.  
-Based on the reference astrometry for pairs of stars in the field from
-\citet{McCaughrean94}, we measure a plate scale of 25.2~$\pm$~0.4~mas pix$^{-1}$ 
-and north orientation of --0.2~$\pm$~0.3$^{\circ}$.  
-Since this latter value is consistent with being aligned with 
-the detector columns, we adopt a value of 0.0~$\pm$~0.3$^{\circ}$ for this work.
-Relative photometry of nearby stars is carried out using aperture photometry with 
-an aperture radius of 12~pix (0$\farcs$3).  
-For EPIC~201828749, we also acquired $J$- and $H$-band images.
-Astrometry and photometry is derived separately for each image, and the mean and standard deviation 
-of these measurements is adopted for our final values listed in Table~5.
-
-We note that we validate 201828749 as a true transiting planet, despite the presence of this binary
-companion. 
-From the transit shape, we can rule out the possibility this system is a background eclipsing
-binary.
-Regardless of which star this object transits, the object is planet-sized.
-Given that small planets are significantly more common than large planets, it is more likely
-that the planet is orbiting the brighter star, and our parameters listed in Table 3 reflect this
-likelihood. If the planet is truly orbiting the fainter star, then it has a larger radius than is 
-listed in this table.
-
-Images for all systems AO data was obtained for is shown in Fig. \ref{Fig:AO},
-while contrast curves showing the $5\sigma$ limits for detection
-as a function of orbital separation are given in Fig. \ref{Fig:CC}.
-
-\begin{figure*}[htbp]
-\centerline{\includegraphics[width=1.0\textwidth]{f3}}
-\caption{AO data for all systems imaged.
-The main frame for each single system shows the deep, saturated image.
-The inset for each single system shows a shallower, unsaturated image to better
-identify companions at close projected orbital separations.
-For the two systems with imaged companions, EPIC 201546283 and 
-EPIC 201828749,
-only unsaturated frames are collected.
-The pixel scale is $0\farcs0252$ per pixel.
-Each subplot is a square 400 pixels on a side and
-each inset is a square 100 pixels on a side.
-All subplots, including insets, are plotted on the same scale.}
-\label{Fig:AO}
-\end{figure*}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.5\textwidth]{f4}}
-\caption{$5\sigma$ contrast curves for all systems with AO nondetections.
-For all systems, we can exclude the possibility that a companion at a given $\Delta K_S$
-exists. 
-From our known transit depths, we can then rule out significant parameter space in which 
-an eclipsing binary could reside and mimic a transit signal.}
-\label{Fig:CC}
-\end{figure}
+This is Brendan.
 
 \subsection{Known Background Stars}
-The PHARO AO system has a field of view of 25 arcseconds.
-Each \KT\ pixel is a square, $3\farcs98$ on a side.
+The P3K AO system has a field of view of $3.84 \times 3.84$ arcseconds.
+\btmtodo{Check with Brendan to make sure he used this mode (doesn't seem 
+like he did)}.
+Each \KT\ pixel is a square of $3.98 \times 3.98$ arcseconds.
 A background eclipsing binary within a few \KT\ pixels of our target
-stars could mimic a transit signal inside our aperture while evading detection
-by PHARO.
+stars could mimic a transit signal while evading detection by P3K.
 Such wide eclipsing binaries should appear in seeing-limited ground-based
@@
 For each target, we return
-all stars within 12\arcsec\ with $\Delta r < 8$ relative to each object
+all stars within 12\arcsec with $\Delta r < 8$ relative to each object
 of interest.
@@
 stars is significantly lower.
-We include all potential contaminants in Table 5.
+We include a list of these potential contaminants as Table
+\ref{Table:BGstars}.
 
-In Table 5, the ``maximum depth'' column represents
+%Table:BGstars
+% Primary    RA Dec Separation DeltaR         MaxDepth
+% 201295312  &  &   &          & 7.10 \pm 0.10 & 0.75
+% 201465501  &  &   &          & 7.90 \pm 0.25 & 0.36
+% 201546283  &  &   &          & 5.87 \pm 0.06 & 2.31
+% 201779067  &  &   &          & 4.21 \pm 0.03 & 10.56
+
+In Table \ref{Table:BGstars}, the ``maximum depth'' column represents
 the maximum observed ``transit'' depth if the transit were actually caused
@@
 reject the hypothesis that the transit is actually a false positive
-induced by a background eclipsing binary.
-However, from the transit shape alone we can place a FPP of this
-system of $1.1 \times 10^{-4}$.
+induced by a background eclipsing binary. \anytodo{Can we place limits
+on this possibility from the lack of a centroid shift?}
 
@@
 The probability is small, given the $0\farcs1$ diffraction limit
-of the Hale Telescope at $2$ $\mu$m, but nonzero.
+of P200 at $2\mu$m, but nonzero.
 We can rule out the possibility of such chance alignments with
@@
 
-For all targets with AO, we can confirm the planetary nature of the signal
-without this extra step, but we include it for EPIC 201912552, considering 
-the additional follow-up this target may warrant.
-We download data from the POSS I and II surveys, which imaged
-EPIC 201912552 in 1955 and 1989, respectively.
-This star has a proper motion of $-74 \pm 2$ mas yr$^{-1}$ in right ascension
- and $-122 \pm 4$ mas yr$^{-1}$ in declination, so it has moved by $8\farcs35$
-since the POSS I data were collected.
-As shown in Figure \ref{fig:archival}, we do not detect any targets at the
-present-day location of EPIC 201912552 in either of the POSS surveys.
+\btmtodo{Method}
 
-\begin{figure*}[htbp]
-\centerline{\includegraphics[width=1.0\textwidth, trim=0 6.30cm 0 6.30cm, clip=true]{f5}}
-\caption{Imaging for EPIC 201912552 from 1955 to 2002. There is no background
-object directly behind the present day location of the target (red circle) that could be missed
-by the AO observations, while modern SDSS imaging can rule out wide companions
-that may have been missed at wide separations, beyond the AO field of view.
-All subplots are on the same scale.}
-\label{fig:archival}
-\end{figure*}
+\btmtodo{Plots showing POSS observations.}
 
-For this target, we can extend our contrast curves to zero
+For these targets, we can extend our contrast curves to zero
 present-day orbital separation and rule out the possibility that
-these transit events are caused by a background eclipsing binary.
+these transit events are caused by background eclipsing binaries.
 By combining present-day seeing-limited photometric survey data,
@@
 star and positioned in their orbits so that their projected separation is
-smaller than the diffraction limit of the Hale Telescope.
+smaller than the diffraction limit of the P200 telescope.
 Such an alignment would require the orbital inclination of the binary to be
@@
 While we cannot fully rule out this possibility, such an alignment is unlikely
-to occur and unable to cause enough dilution to call the planetary
-nature of this signal into question.
+to occur, and highly unlikely to cause enough dilution to call the planetary
+nature of these signals into question.
 
@@
 
-We observed EPIC 201912552 on 2015 February 04 and 25 UT
+We observed EPIC 201912552 on (all UT) February 04 2015 and February 24 2015
 with the Tillinghast Reflector Echelle
@@
 
-The two observed spectra have RVs that differ by $47 \pm 42$ m s$^{-1}$.
-If the RVs were caused by a stellar companion, the RV shift between these
-observations would be on the order of km s$^{-1}$.
-Therefore, the transiting object must be planetary in nature.
+The two observed spectra have RVs that differ by $47.1 \pm 41.9$ m s$^{-1}$.
+A deviation at this magnitude can only be explained by the presence of
+a planetary system and instrumental noise, eliminating the possibility the
+transiting planet is actually a false positive.
+
+\subsection{False Positive Rates (and confirmations?)}
+This is Tim.
 
@@
 
-The planet orbiting EPIC 201912552 may be an interesting target for 
-atmospheric studies of transiting exoplanets.
+Of particular interest is EPIC 201912552.
 
@@
 to become a prime target for atmospheric characterization studies
-and is ideal as a target for future space-based missions such as 
-\textit{JWST}.
+and is ideal as a target for future space-based missions such as JWST.
 
 Unlike GJ\,1214b, EPIC 201912552b is not highly irradiated.
-Instead, it is at a reduced semimajor axis \ars$ = 84.3 \pm 9.5$.
-Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 271 \pm 16$
-K, meaning its bulk insolation is $128 \pm 28$ percent that of the Earth's.
+Instead, it is at an reduced semimajor axis \ars$ = 82.1 \pm 8.6$.
+Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 275 \pm 15$
+K, meaning its bulk insolation is $135 \pm 30$ percent that of the Earth's.
 Although the planet is likely too large to be rocky \citep{Rogers14},
@@
 
-\subsection{Two Candidates, One Ephemeris}
+\subsection{EPIC 201465501?}
+Is this a subsection? It's a star with a mass of ~0.2 Msun and a candidate with
+a period of 18 days. I suppose it depends on the FPP.
 
-EPIC 201569483 was originally listed in \paperit\ as a planet candidate.
-The transit events have a depth of approximately 7\%.
-In this work, we conclude this system is likely a false
-positive, with an FPP of 0.560.
-The most likely scenario is that of an eclipsing binary, which would
-not be surprising given the transit depth.
+\subsection{An Instrumental False Positive}
 
-It was later realized that EPIC 201555883 has a period, time of transit,
-and transit duration consistent with EPIC 201569483.
+EPIC 201555883 was originally listed in \paperit\ as a planet candidate.
+After submission of that work, this object of interest was identified as
+having a transit ephemeris consistent with that of EPIC 201569483,
+which we identify as a likely eclipsing binary due to the observed transit
+depth \anytodo{Right? Right?  Can this be more quantitative?  Are these two stars 
+close to one another?  How bright is  the purported parent? Are they 
+On/near the same CCD column?  FPP gives this a pass, so we 
+need to be clear about this.}.
+We conclude the observed transit signal from EPIC 201555883 is likely the result
+of an instrumental artifact.
+
 Such effects are not uncommon in \kep\ data.
@@
 outlining four physical reasons why these anomalies may occur.
-As those authors explain, period-matching candidates can be the result of direct PRF
-contamination, antipodal reflection across the Schmidt telescope, CCD crosstalk
-across a \kep\ module, or ``column anomalies'' across one column of the CCD.
-Typically, the instrumental false positive event appears considerably shallower than the 
-true astrophysical event.
-
-EPIC 201555883 is a unique case in that it does not appear to fall under any of these
-cases. It falls on module 23, while EPIC 201569483 is on module 8, neither 180 degrees
-away from nor on the same column as this candidate.
-Moreover, there is not any evidence of a mechanism that could cause a third star to
-induce both the appearance of a $7\%$ eclipse on one module and an additional
-anomalous transit event on a different module.
-
-Formally, our false positive validation scheme gives a FPP of $9.5 \times 10^{-4}$,
-reaching our threshold for planet validation.
-Since \texttt{vespa} does not account for the possibility of instrumental artifacts
-in the data, this number represents only the \textit{astrophysical} false positive
-probability.
-In this case, given the period matching between the two events, we refrain from
-declaring this system a planet.
-However, since we cannot explain how such a false positive would occur as a result
-of an instrumental systematic in the \kep\ telescope, we also refrain from declaring
-this target a definite false positive.
-Additional follow-up observations of both targets are clearly warranted to better
-understand a possible systematic that has not previously been observed in
-either \kep\ or \KT.
+While EPIC 201555883 is likely a false positive, it does not appear that it can neatly be
+explained by any one of the effects described by \citet{Coughlin14} alone.
+This artifact should be carefully studied in the future, as it may help illuminate other
+potential detector artifacts, both in \kep\ and \KT\ data.
 
@@
 The remaining three are all representative of the multiple-planet systems observed by
-\kep\ \citep{Lissauer11b, Fabrycky14}.
+\kep \citep{Lissauer11b, Fabrycky14}.
 Two of the systems are near a period commensurability and all three consist of
@@
 An additional four targets orbit stars with $K <10$.
-These targets are ideal for ground-based followup and may be useful targets for Spitzer and
+These targets are ideal for ground-based followup, and may be useful targets for Spitzer and
 JWST to probe planetary atmospheres.
@@
 We have presented stellar parameters for all planet candidates systems observed by
-\paperit, validating \Nvalidated\ of the 36 candidates as bona fide planets and
-\Nfp\ as false positives.
-Of these planets, 4 have been previously validated in other works, while 17 are
-validated here for the first time.
+\paperit, confirming \btmtodo{Nconfirm} of the 36 candidates as bona fide planets and
+\btmtodo{NFP} as bona fide false positives.
 
@@
 by discrepancies between the models and reality.
-Even more dangerously, any region of parameter space not probed by the models would
-be entirely missed in our stellar modeling.
 
-As stated in \textsection\ref{sec:stellarparams}, we infer stellar parameters using the
-Dartmouth models, with a mass upper limit of $3.7 M_\odot$.
-Given the location of the \Ci\ field with respect to the galactic plane, we expect a low
-contamination rate by halo giants.
-However, there are a few stars that are possibly miscategorized giants.
-EPIC 201257461 is identified in the RAdial Velocity Experiment (RAVE) Fourth Data Release
-as a target with $\logg = 3.18$, consistent with that of a giant star.
-It is therefore perhaps not surprising that this system is flagged as a false positive based on
-the transit shape.
-EPIC 201929294, with a proper motion of $0.010\arcsec$ yr$^{-1}$ \citep{Zacharias12}  has
-a reduced proper motion consistent with that of a giant star.
-While suggestive, this observation does not definitively provide information about the
-nature of this target.
-Likewise, our false positive analysis is neither able to confirm nor exclude the planetary
-nature of the observed transit signal around this target.
-
-The planets we confirm in this paper, like the planets found in the original \kep\ mission,
-span a wide range of parameter space.
-They are at distances ranging from $34$ to $700$ pc, have radii ranging from $1.3$ to
-5.3 $R_\oplus$, and orbit with periods ranging from 5.0 to 50.3 days.
-Like the original mission, we find significantly more small planets than large planets.
-
-Unlike the original mission, however, we find that nearly all of our confirmed planets
-are around stars less massive than the Sun.
-This difference is a result of both the \Ci\ field and the target selection process.
-\Ci\ is at a significantly higher galactic latitude than the original \kep\ mission,
-meaning there is a much lower number density of targets at large distances.
-As massive stars
-at kiloparsec distances are relatively less likely to exist in \Ci\ than near the
-galactic plane, the pool of targets that could be selected for \Ci\ contains a larger
-fraction of subsolar stars.
-
-Low-mass stars, particularly M dwarfs, are also a specific focus of the \KT\ mission.
-One of the primary goals of the \kep\ mission was to ``determine the abundance of
-terrestrial and larger planets in or near the habitable zone of a wide variety of spectral
-types of stars'' \citep{Batalha13} However, $\sim70\%$ of Kepler's target stars had
-masses within 20\%
-of the Sun's, while 70\% of the stars in the Galaxy have less than 50\% the mass of the
-Sun \citep{Brown11}.
-\KT\ will fulfill the promise of \kep, with the goal of providing a yield of small planets
-around bright, small stars to facilitate follow-up measurements \citep{Howell14}.
-This is clear from the \KT\ target selection process, with thousands of K and M dwarfs
-being selected in each campaign.
-Based on these plans, we expect that \KT\ will detect hundreds of planets during its
-lifetime, with the majority being mini-Neptunes and super-Earths around stars
-less massive than the Sun.
+\anytodo{We should have a figure of many subplots, of phase-folded
+transits for all the confirmed planets.
+To ease Dan's mind, we will say that they are the product of
+some fidicual transit model and are only presented here for illustrative
+purposes.}
 
 \acknowledgements
-We thank Eric Agol (UW), Dan Huber (Sydney) and Jeff Coughlin (SETI) for
-conversations and suggestions which improved the quality of this manuscript.
+We thank Eric Agol (UW), Dan Huber (Sydney) [and Other People] for conversations and
+suggestions which improved the quality of this manuscript.
 
@@
 Their tireless efforts were all essential to the tremendous success of the mission and the
-successes of \KT\, present and future.
+successes of K2, present and future.
 
@@
 B.T.M. is supported by the National Science Foundation Graduate Research
-Fellowship under Grant No. DGE-€1144469.
+Fellowship under Grant No. DGE‐1144469.
 J.A.J. is supported by generous grants from the David and Lucile Packard
@@
 (grant IIS-1124794), the National Aeronautics and Space Administration (grant
-NNX12AI50G), and the Moore-Sloan Data Science Environment at NYU.
+NNX12AI50G), and the Moore–Sloan Data Science Environment at NYU.
 
@@
 
-{\it Facilities:} \facility{Kepler},  \facility{PO:Hale (PHARO)}, \facility{FLWO:1.5m},
-\facility{IRTF:SpeX}
+{\it Facilities:} \facility{Kepler}%, \btmtodo{More...}
+
+\appendix
+\section{Computing physical planet parameters}
+
+In \paperit, the authors generated $K$ samples from the posterior probability
+distribution of the physical parameters of the systems conditioned on the
+light curves using broad, un-informative priors on most of the parameters.
+
+\begin{eqnarray}
+p(w\,|\,x) &=& \frac{p(w)\,p(x\,|\,w)}{p(x)} \\
+&=& \frac{q(w)\,p(x\,|\,w)}{q(x)}\,\frac{p(w)}{q(w)}\,\frac{q(x)}{p(x)} \\
+&=& q(w\,|\,x)\,\frac{p(w)}{q(w)}\,\frac{q(x)}{p(x)}
+\end{eqnarray}
+
+We have $K$ samples
+\begin{eqnarray}
+w^{(k)} &\sim& p(w\,|\,x)
+\end{eqnarray}
+and the point of these samples is to do integrals of the form
+\begin{eqnarray}
+E[f(w)] &=& \int f(w)\,p(w\,|\,x) \dd w \quad.
+\end{eqnarray}
+Now, if we want to update this with a new measurement $p^\prime(w)$,
 
@@
 
-% \begin{turnpage}
 \include{table_photometry}
-% \end{turnpage}
+
 \include{table_stellarprops}
-\include{table_planets}
+
 \include{table_fpp}
 
-\include{table_bg}
-
 \end{document}

### 2015-03-23 ms.tex
a few words for the systematic FP

--- 2015-03-23 ms.tex
@@
 Such effects are not uncommon in \kep\ data.
-\citet{Batalha13} found $\sim 25$ planet candidates to be false positives based on matching
-ephemerides between candidates.
-In that paper, the authors limited their search to candidates within $20\arcsec$ of other
-objects of interest.
-\citet{Coughlin14} expanded on this method, identifying 685 KOIs as false positives and
-outlining four physical reasons why these anomalies may occur.
-As those authors explain, period-matching candidates can be the result of direct PRF
-contamination, antipodal reflection across the Schmidt telescope, CCD crosstalk
-across a \kep\ module, or ``column anomalies'' across one column of the CCD.
-Typically, the instrumental false positive event appears considerably shallower than the
-true astrophysical event.
+\citet{Batalha13} found $\sim 25$ planet candidates to be false positives
+based on matching ephemerides between candidates.
+In that paper, the authors limited their search to candidates within
+$20\arcsec$ of other objects of interest.
+\citet{Coughlin14} expanded on this method, identifying 685 KOIs as false
+positives and outlining four physical reasons why these anomalies may occur.
+As those authors explain, period-matching candidates can be the result of
+direct PRF contamination, antipodal reflection across the Schmidt telescope,
+CCD crosstalk across a \kep\ module, or ``column anomalies'' across one column
+of the CCD.
+Typically, the instrumental false positive event appears considerably
+shallower than the true astrophysical event.
 
-EPIC 201555883 is a unique case in that it does not appear to fall under any of these
-cases. It falls on module 23, while EPIC 201569483 is on module 8, neither 180 degrees
-away from nor on the same column as this candidate.
-Moreover, there is not any evidence of a mechanism that could cause a third star to
-induce both the appearance of a $7\%$ eclipse on one module and an additional
-anomalous transit event on a different module.
+EPIC 201555883 is a unique case in that it does not appear to fall under any
+of these cases. It falls on module 23, while EPIC 201569483 is on module 8,
+neither 180 degrees away from nor on the same column as this candidate.
+Moreover, there is not any evidence of a mechanism that could cause a third
+star to induce both the appearance of a $7\%$ eclipse on one module and an
+additional anomalous transit event on a different module.
+Instead, this candidate could be a false positive caused by a different
+systematic mechanism.
+\paperit\ modeled the systematic effects in the \KT\ light curves using a
+linear combination of ``eigen light curves'' generated empirically by running
+a principle component analysis on the light curves of every star.
+This means that the training set includes the light curves for variable stars,
+eclipsing binaries, and even transiting planets.
 
-Formally, our false positive validation scheme gives a FPP of $9.5 \times 10^{-4}$,
-reaching our threshold for planet validation.
-Since \texttt{vespa} does not account for the possibility of instrumental artifacts
-in the data, this number represents only the \textit{astrophysical} false positive
-probability.
-In this case, given the period matching between the two events, we refrain from
-declaring this system a planet.
-However, since we cannot explain how such a false positive would occur as a result
-of an instrumental systematic in the \kep\ telescope, we also refrain from declaring
-this target a definite false positive.
-Additional follow-up observations of both targets are clearly warranted to better
-understand a possible systematic that has not previously been observed in
-either \kep\ or \KT.
+Formally, our false positive validation scheme gives a FPP of $9.5 \times
+10^{-4}$, reaching our threshold for planet validation.
+Since \texttt{vespa} does not account for the possibility of instrumental
+artifacts in the data, this number represents only the \textit{astrophysical}
+false positive probability.
+In this case, given the period matching between the two events, we refrain
+from declaring this system a planet.
+However, since we cannot explain how such a false positive would occur as a
+result of an instrumental systematic in the \kep\ telescope, we also refrain
+from declaring this target a definite false positive.
+Additional follow-up observations of both targets are clearly warranted to
+better understand a possible systematic that has not previously been observed
+in either \kep\ or \KT.
 

### 2015-03-25 table_fpp.tex
re-ran fpp calculation

--- 2015-03-10 table_fpp.tex
@@
 \tablecaption{False Positive Probability Calculation Results}
-\label{Tab:FPP}
+\label{Table:FPP}
 \tablehead{
@@
 \startdata
-$201208431$ & $1$ & $0.51$ & $< 10^{-4}$ & $0.00074$ & $0.0001$ & $0.22$ & $0.00084$ & Planet \\
- \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.011$  & \color{red}  $0.99$  & \color{red}  $0.22$  & \color{red}  $1$  & \color{red}  FP\\
-$201295312$ & $1$ & $0.04$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.0001$ & $0.15$ & $0.00011$ & Planet \\
-$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.004$ & $0.00059$ & $0.17$ & $0.0046$ & Planet \\
-$201338508$ & $2$ & $0.33$ & $< 10^{-4}$ & $0.00077$ & $< 10^{-4}$ & $0.17$ & $0.00077$ & Planet \\
-$201367065$ & $1$ & $0.15$ & $< 10^{-4}$ & $0.0013$ & $< 10^{-4}$ & $0.18$ & $0.0013$ & Planet \\
-$201367065$ & $2$ & $0.67$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.14$ & $< 10^{-4}$ & Planet \\
-$201384232$ & $1$ & $0.44$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.00021$ & $0.21$ & $0.00023$ & Planet \\
-$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.0026$ & $0.022$ & $0.17$ & $0.025$ & Candidate \\
-$201403446$ & $1$ & $0.18$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.00098$ & $0.13$ & $0.001$ & Planet \\
-$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.0018$ & $0.049$ & $0.22$ & $0.051$ & Candidate \\
-$201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.034$ & $0.055$ & $0.18$ & $0.089$ & Candidate \\
-$201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.021$ & $0.003$ & $0.14$ & $0.025$ & Candidate \\
- \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.02$  & \color{red}  $0.97$  & \color{red}  $0.18$  & \color{red}  $0.99$  & \color{red}  FP\\
-$201505350$ & $2$ & $0.70$ & $< 10^{-4}$ & $0.0003$ & $0.00012$ & $0.07$ & $0.00042$ & Planet \\
-$201546283$ & $1$ & $0.15$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Planet \\
-$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.0017$ & $0.00065$ & $0.20$ & $0.0024$ & Planet \\
-$201555883$ & $1$ & $0.94$ & $< 10^{-4}$ & $0.00058$ & $0.00037$ & $0.20$ & $0.00095$ & Planet \\
- \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}  $0.0027$  & \color{red}  $0.027$  & \color{red}  $0.93$  & \color{red}  $0.07$  & \color{red}  $0.96$  & \color{red}  FP\\
-$201569483$ & $1$ & $2.06$ & $0.47$ & $< 10^{-4}$ & $0.092$ & $0.01$ & $0.56$ & Candidate \\
-$201577035$ & $1$ & $0.14$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.0001$ & $0.20$ & $0.00011$ & Planet \\
-$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.0013$ & $0.0021$ & $0.17$ & $0.0034$ & Planet \\
-$201613023$ & $1$ & $0.08$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.15$ & $< 10^{-4}$ & Planet \\
-$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.016$ & $0.0017$ & $0.16$ & $0.018$ & Candidate \\
-$201629650$ & $1$ & $0.43$ & $< 10^{-4}$ & $0.00063$ & $0.0011$ & $0.17$ & $0.0017$ & Planet \\
-$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.0075$ & $0.069$ & $0.09$ & $0.076$ & Candidate \\
- \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}  $0.82$  & \color{red}  $0.00022$  & \color{red}  $0.12$  & \color{red}  $0.01$  & \color{red}  $0.94$  & \color{red}  FP\\
-$201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.004$ & $0.28$ & $0.06$ & $0.28$ & Candidate \\
-$201736247$ & $1$ & $0.42$ & $< 10^{-4}$ & $0.00019$ & $0.00085$ & $0.22$ & $0.001$ & Planet \\
-$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.0019$ & $0.0015$ & $0.18$ & $0.0034$ & Planet \\
-$201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0013$ & $0.00064$ & $0.17$ & $0.0019$ & Planet \\
-$201779067$ & $1$ & $1.97$ & $0.036$ & $0.005$ & $0.29$ & $0.03$ & $0.33$ & Candidate \\
-$201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.0017$ & $0.0022$ & $0.17$ & $0.0039$ & Planet \\
-$201855371$ & $1$ & $0.62$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $0.00017$ & Planet \\
-$201912552$ & $1$ & $0.47$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
-$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.0068$ & $0.052$ & $0.05$ & $0.059$ & Candidate
+$201208431$ & $1$ & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.0\times10^{-4}$ & $0.21$ & $2.2\times10^{-4}$ & Planet \\
+ \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $0.946$  & \color{red}  $0.054$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.22$  & \color{red}  $1.000$  & \color{red}  FP\\
+$201295312$ & $1$ & $0.04$ &  Y & $0.018$ & $6.2\times10^{-4}$ & $< 10^{-4}$ & $0.18$ & $0.019$ & Candidate \\
+$201338508$ & $1$ & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.3\times10^{-3}$ & $0.19$ & $1.4\times10^{-3}$ & Planet \\
+$201338508$ & $2$ & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.19$ & $1.6\times10^{-4}$ & Planet \\
+$201367065$ & $1$ & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.19$ & $< 10^{-4}$ & Planet \\
+$201367065$ & $2$ & $0.67$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.14$ & $< 10^{-4}$ & Planet \\
+$201384232$ & $1$ & $0.44$ &  - & $7.7\times10^{-3}$ & $1.5\times10^{-4}$ & $< 10^{-4}$ & $0.20$ & $7.9\times10^{-3}$ & Planet \\
+$201393098$ & $1$ & $0.52$ &  - & $0.051$ & $0.011$ & $< 10^{-4}$ & $0.22$ & $0.062$ & Candidate \\
+$201403446$ & $1$ & $0.18$ &  Y & $2.3\times10^{-4}$ & $5.6\times10^{-4}$ & $< 10^{-4}$ & $0.17$ & $8.0\times10^{-4}$ & Planet \\
+$201445392$ & $1$ & $0.26$ &  - & $0.065$ & $7.4\times10^{-3}$ & $1.9\times10^{-3}$ & $0.20$ & $0.074$ & Candidate \\
+$201445392$ & $2$ & $0.18$ &  - & $0.075$ & $8.6\times10^{-3}$ & $0.037$ & $0.22$ & $0.120$ & Candidate \\
+$201465501$ & $1$ & $0.68$ &  - & $< 10^{-4}$ & $0.013$ & $8.0\times10^{-4}$ & $0.14$ & $0.014$ & Candidate \\
+$201505350$ & $1$ & $2.69$ &  - & $0.642$ & $0.195$ & $1.5\times10^{-3}$ & $0.10$ & $0.839$ & Candidate \\
+$201505350$ & $2$ & $0.70$ &  - & $0.012$ & $1.8\times10^{-3}$ & $< 10^{-4}$ & $0.05$ & $0.014$ & Candidate \\
+$201546283$ & $1$ & $0.15$ &  - & $6.6\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.08$ & $7.5\times10^{-4}$ & Planet \\
+$201549860$ & $1$ & $0.18$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $9.1\times10^{-4}$ & $0.22$ & $9.3\times10^{-4}$ & Planet \\
+$201555883$ & $1$ & $0.94$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $5.0\times10^{-4}$ & $0.15$ & $6.0\times10^{-4}$ & Planet \\
+ \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}   -  & \color{red}  $0.843$  & \color{red}  $0.122$  & \color{red}  $0.013$  & \color{red}  $0.05$  & \color{red}  $0.977$  & \color{red}  FP\\
+ \color{red} $201569483$  & \color{red}  $1$  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.966$  & \color{red}  $0.023$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.989$  & \color{red}  FP\\
+$201577035$ & $1$ & $0.14$ &  Y & $2.9\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.12$ & $3.0\times10^{-3}$ & Planet \\
+$201596316$ & $1$ & $0.45$ &  - & $7.6\times10^{-3}$ & $8.2\times10^{-4}$ & $1.3\times10^{-4}$ & $0.20$ & $8.6\times10^{-3}$ & Planet \\
+$201613023$ & $1$ & $0.08$ &  Y & $3.3\times10^{-3}$ & $1.2\times10^{-4}$ & $< 10^{-4}$ & $0.22$ & $3.4\times10^{-3}$ & Planet \\
+$201617985$ & $1$ & $0.27$ &  - & $< 10^{-4}$ & $1.2\times10^{-4}$ & $8.8\times10^{-3}$ & $0.18$ & $9.0\times10^{-3}$ & Planet \\
+$201629650$ & $1$ & $0.43$ &  - & $0.010$ & $9.5\times10^{-4}$ & $< 10^{-4}$ & $0.21$ & $0.011$ & Candidate \\
+$201635569$ & $1$ & $0.79$ &  - & $3.9\times10^{-4}$ & $0.018$ & $0.037$ & $0.08$ & $0.055$ & Candidate \\
+ \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.971$  & \color{red}  $0.018$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.989$  & \color{red}  FP\\
+$201702477$ & $1$ & $0.70$ &  - & $0.445$ & $0.051$ & $5.6\times10^{-4}$ & $0.05$ & $0.497$ & Candidate \\
+$201736247$ & $1$ & $0.42$ &  - & $5.5\times10^{-3}$ & $3.8\times10^{-4}$ & $< 10^{-4}$ & $0.21$ & $5.9\times10^{-3}$ & Planet \\
+$201754305$ & $1$ & $0.65$ &  - & $7.3\times10^{-3}$ & $2.7\times10^{-4}$ & $2.5\times10^{-4}$ & $0.20$ & $7.9\times10^{-3}$ & Planet \\
+$201754305$ & $2$ & $0.38$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.6\times10^{-4}$ & $0.20$ & $3.3\times10^{-4}$ & Planet \\
+ \color{red} $201779067$  & \color{red}  $1$  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.971$  & \color{red}  $0.017$  & \color{red}  $2.5\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.988$  & \color{red}  FP\\
+$201828749$ & $1$ & $0.39$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $3.5\times10^{-4}$ & $0.17$ & $3.5\times10^{-4}$ & Planet \\
+$201855371$ & $1$ & $0.62$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet \\
+$201912552$ & $1$ & $0.47$ &  Y & $0.023$ & $2.4\times10^{-4}$ & $< 10^{-4}$ & $0.21$ & $0.023$ & Candidate \\
+$201929294$ & $1$ & $3.12$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.0\times10^{-3}$ & $0.06$ & $4.0\times10^{-3}$ & Planet
 

### 2015-03-25 fpp/k2fpp/contrast.py

@@ -54,7 +54,7 @@ def SDSS_contrast(epic_id):
     """fwhm 1.4", lim. mag r=22.2
     """
     mags = all_mags(epic_id)
-    rs = [2.8,4,8,12] #blah blah
+    rs = [2.8,4,8,12,25] #blah blah
     dmag = 22.2-mags['r']
     dmags = [dmag]*len(rs)
     return ContrastCurve(rs,dmags,'r',name='SDSS')

### 2015-03-25 ms.tex
new bg table
comments from jj

@@
 \begin{abstract}
-Recently, \paperit{} presented a list of 36 planet candidates orbiting
-31 stars in \KT\ \Ci.
-In this paper, we present stellar and planetary properties for all systems.
+The extended \kep\ mission, \KT, is now providing photometry of new fields every 
+three months in a search for transiting planets.
+In a recent study, Foreman-Mackey and collaborators presented a list of 36 planet 
+candidates orbiting 31 stars in \KT\ \Ci.
+In this contribution, we present stellar and planetary properties for all systems.
 We combine ground-based seeing limited survey data and
@@
 of the \citet{Morton12} procedure to calculate false positive probabilities
+and statistically validate transiting exoplanets
 for \KT\ candidates.
@@
 The fidelity of this sample is high: most of these planet candidates are truly planets
-\citep{Morton11b, Fressin13}.
-The demise of two reaction wheels on the spacecraft led to a repurposing
+\citep{Morton11b, Fressin13, Desert15}.
+The mechanical failure of two reaction wheels on the spacecraft led to a repurposing
 of the spacecraft into the \KT\ mission, in which the telescope points at
@@
 As a result, the detector drifts relative to the sky
-at the rate of $\sim 1\arcsec$ hr$^{-1}$, with rapid corrections
+at the rate of $\sim 1\arcsec$ hr$^{-1}$, with rapid corrections due to thruster fires
 approximately once every six hours.
@@
 \citet{Vanderburg14} extract aperture photometry and de-correlate with image centroid
-position, ``correcting'' the data to ``remove'' the effects of the spacecraft motion.
+position to calibrate the photometry as a function of position.
 These data were used to confirm the first planet discovered in \KT\ \citep{Vanderburg15}.
@@
 \citep{Armstrong15b}.
-\citet{Aigrain15} and \citet{Crossfield15} use a Gaussian Process model for the measured
+\citet{Aigrain15} use a Gaussian Process model for the measured
 flux, with pointing measurements as the inputs, and then ``de-trend'' the data with that model.
-The latter of these detected the first multi-planet system in \KT\ data.
+\citet{Crossfield15} apply a very similar method, which was used to detect the first 
+multi-planet system in \KT\ data.
 
@@
 The authors intentionally make no effort to separate astrophysical false positives from
-true transiting planets.
+true transiting planets, similar to the \kep\ ``objects of interest.''
 
@@
 \Nvalidated\ of these systems as transiting planets at the 99\% confidence
-level. We also are able to confirm \Nfp\ of these systems as false positives.
+level. 
+Additionally, we identify four systems as false positives.
 
@@
 and in the remaining two cases, the photometric uncertainity in $W4$ is at least an
-order of magnitude larger than those in $W1-W3$, so we neglect $W4$.
+order of magnitude larger than those in $W1-W3$, so we do not use $W4$ 
+for any system.
 These data are reported in Table 1, and a color-color diagram showing the
@@
 observed by \kep\ during the original
-mission (black), with our \KT\ \Ci\ planet candidates overlaid (fuchsia).
-Also included is the location of the Sun (yellow).
-Nearly all of our candidates have photometry consistent with later spectral
-types than G2.}
+mission (black), with our \KT\ \Ci\ planet candidates overlaid (red).
+Also included is the location of the Sun (yellow) and host stars of previously
+confirmed \KT\ planets (blue).
+90\% of our candidates have photometry consistent with later spectral
+types than the Sun.}
 \label{fig:photometry}
@@
 \url{http://github.com/timothydmorton/isochrones}}, a general-purpose
-interpolation tool for stellar model grids.
+interpolation tool for the fitting of stellar models to photometric or spectroscopic
+parameters.
 This software does trilinear interpolation in mass--age--\feh\ space for any
@@
 \label{eq:ischochronelhood}
-\ln \mathcal L(\boldsymbol{\theta}) = -\frac{1}{2} \displaystyle \sum_i \frac{\left(x_i -
+\ln \mathcal L(\boldsymbol{\theta}) \propto -\frac{1}{2} \displaystyle \sum_i \frac{\left(x_i -
   I_i\left(\boldsymbol{\theta} \right)\right)^2}{\sigma_i^2},
@@
 If the observed properties include any apparent magnitudes, then
-$\boldsymbol{\theta}$ includes distance and $A_V$ extinction in addition
+$\boldsymbol{\theta}$ includes distance and extinction in addition
 to mass, age, and \feh.
@@
 There is some evidence that the Dartmouth models may under-predict
-radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
+radii of M dwarfs by $\sim 15\%$ when compared to other methods \citep{Newton15,
 Montet15}.
@@
 
-In order to try to encapsulate the effect of model uncertainties, we also run
+In order to account for the effects of model uncertainties, we also run
 MCMC chains with photometric errors inflated artificially by a factor of three.
@@
 planet if (a) it is a highly grazing eclipse, or (b) the binary system
-comprises only a small fraction of the total light in the photometric
-aperture, resulting in a diluted eclipse depth.
+shares a photometric aperture with a significantly brighter star, 
+resulting in a diluted eclipse depth.
 When possible, such astrophsycial false positive scenarios are traditionally
@@
 toward probabilistic interpretation of transit signals, rather than
-comprehensive follow-up of each individual candidate.
+comprehensive follow-up of each individual candidate \citep{Morton11b}.
 
@@
 astrophysical false positive.
-This method uses population simulations of the light curves of
-of false positive scenarios and true transiting planets to quantify
-the typical shape of each, comparing to the observed transit shape.
+This method uses Galactic population simulations to determine the 
+distributions of possible false positive scenarios, comparing the
+typical light curve shape of each to the data.
 It then combines this information with observationally motivated prior
@@
 Similar in spirit to other published methods of
-probabilistic validation, such as Blender \citep{Torres11a} and PASTIS
+probabilistic validation, such as BLENDER \citep{Torres11a} and PASTIS
 \citep{Diaz14a}, it has the advantage of being computationally less demanding
@@
 
-We find that \Nfp\ of the presented candidates FPP $>$90\%;
+We find that four of the presented candidates have FPP $>$90\%;
 these we consider to be likely false positives.
 On the other hand, we find that \Nvalidated\ candidates
-have FPP $<$ 1\%; these we consider to be validated planets.
+have FPP $<$ 1\%; we consider these to be statistically validated planets.
 Of these, 18 are validated for the first time.
@@
 demonstrates the utility of \texttt{vespa} analysis, which will be
-crucial to interpreting future \KT\ detected candidates and prioritizing
-follow-up observing efforts.
+crucial to interpreting future candidates detected by \KT, TESS, and PLATO
+and prioritizing follow-up observing efforts.
 We show these transit signals as Fig. \ref{fig:transits}.
@@
 The systems which we validate as transiting planets are labeled in
-green.
+blue.
 The systems which we confirm as false positive events are labeled in red.
@@
 \centerline{\includegraphics[width=1.0\textwidth]{f3}}
-\caption{AO data for all systems imaged.
+\caption{Adaptive optics images for the seven stars observed with high-contrast imaging.
 The main frame for each single system shows the deep, saturated image.
@@
 Unlike the original \kep\ field, the field for \KT\ \Ci\ is
-well out of the galactic plane, so the rate of giant, distanct background
+well out of the galactic plane, so the rate of giant, distant background
 stars is significantly lower.
@@
 
-We have presented stellar parameters for all planet candidates systems observed by
-\paperit, validating \Nvalidated\ of the 36 candidates as bona fide planets and
-\Nfp\ as false positives.
+We have presented stellar parameters for all planet candidates systems identified by
+\paperit.
+We statistically validate \Nvalidated\ of the 36 candidates as bona fide planets, and we
+identify four as false positives.
 Of these planets, 4 have been previously validated in other works, while 17 are
 validated here for the first time.
+The 11 systems not validated as planets or false positives remain as planet candidates.
 
@@
 by discrepancies between the models and reality.
-Even more dangerously, any region of parameter space not probed by the models would
-be entirely missed in our stellar modeling.
 
@@
 5.3 $R_\oplus$, and orbit with periods ranging from 5.0 to 50.3 days.
-Like the original mission, we find significantly more small planets than large planets.
+Like the original mission, we find significantly more small planets than large planets, as
+expected from the radius distributions measured from \kep\ 
+\citep{Howard12, Fressin13, Morton14}.
 
@@
 \include{table_stellarprops}
+
+\begin{turnpage}
 \include{table_planets}
+\end{turnpage}
 \include{table_fpp}

### 2015-03-26 ms.tex
tdm edits

@@
 \newcommand{\Nfp}{4}
-\newcommand{\Nvalidated}{21}
-\newcommand{\Nlimbo}{11} %adds to 36?  good.
+\newcommand{\Nvalidated}{22} %16 without contrast curves
+\newcommand{\Nlimbo}{10} %adds up to 36
 
@@
 In this contribution, we present stellar and planetary properties for all systems.
-We combine ground-based seeing limited survey data and
-adaptive optics imaging with a detailed transit analysis scheme to validate
+We combine ground-based seeing-limited survey data and
+adaptive optics imaging with an automated transit analysis scheme to validate
 \Nvalidated\ candidates as planets and identify \Nfp\ candidates as likely false positives.
@@
 of the \citet{Morton12} procedure to calculate false positive probabilities
-and statistically validate transiting exoplanets
-for \KT\ candidates.
+and statistically validate transiting exoplanets.
 \end{abstract}
@@
 We include a prior on stellar metallicity representative of the observed metallicities
-of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}, and
-only consider stars with masses below $3.7$ $M_\odot$.
+of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}, and a Salpeter-slope
+prior on mass (up to the maximum mass available in the model grids of $3.7$ $M_\odot$).
 
@@
 \item A chance-aligned eclipsing binary system may reside anywhere within
-an 8 arcsecond radius from the target star.
+the photometric aperture of the target star.
 \item The maximum allowed depth of a potential secondary eclipse event
@@
 
-Each of these scenarios are astrophysical, caused by one object passing
-in front of another, blocking some fraction of the total light.
-The calculations here do not include the possibility that each signal
-is caused by an instrumental artifact in the data or some other
-astrophysical event, such as stellar activity, masquerading as planet
-transits.
+Each of these scenarios is an astrophysical eclipse, caused by one
+object passing in front of another, blocking some fraction of the
+total light.  
+The calculations here do not include the possibility
+that each signal is caused by an instrumental artifact in the data or
+some other astrophysical event, such as stellar activity, masquerading
+as planet transits.
 

### 2015-03-26 table_fpp.tex
new FPP calculations

--- 2015-03-10 table_fpp.tex
@@
 \startdata
-$201208431$ & $1$ & $0.51$ &  - & $< 10^{-4}$ & $7.4\times10^{-4}$ & $1.0\times10^{-4}$ & $0.22$ & $8.4\times10^{-4}$ & Planet \\
- \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $0.011$  & \color{red}  $0.989$  & \color{red}  $0.22$  & \color{red}  $1.000$  & \color{red}  FP\\
-$201295312$ & $1$ & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $1.0\times10^{-4}$ & $0.15$ & $1.1\times10^{-4}$ & Planet \\
-$201338508$ & $1$ & $0.63$ &  - & $< 10^{-4}$ & $4.0\times10^{-3}$ & $5.9\times10^{-4}$ & $0.17$ & $4.6\times10^{-3}$ & Planet \\
-$201338508$ & $2$ & $0.33$ &  - & $< 10^{-4}$ & $7.7\times10^{-4}$ & $< 10^{-4}$ & $0.17$ & $7.7\times10^{-4}$ & Planet \\
-$201367065$ & $1$ & $0.15$ &  - & $< 10^{-4}$ & $1.3\times10^{-3}$ & $< 10^{-4}$ & $0.18$ & $1.3\times10^{-3}$ & Planet \\
-$201367065$ & $2$ & $0.67$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.14$ & $< 10^{-4}$ & Planet \\
-$201384232$ & $1$ & $0.44$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.1\times10^{-4}$ & $0.21$ & $2.3\times10^{-4}$ & Planet \\
-$201393098$ & $1$ & $0.52$ &  - & $< 10^{-4}$ & $2.6\times10^{-3}$ & $0.022$ & $0.17$ & $0.025$ & Candidate \\
-$201403446$ & $1$ & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $9.8\times10^{-4}$ & $0.13$ & $10.0\times10^{-4}$ & Planet \\
-$201445392$ & $1$ & $0.26$ &  - & $< 10^{-4}$ & $1.8\times10^{-3}$ & $0.049$ & $0.22$ & $0.051$ & Candidate \\
-$201445392$ & $2$ & $0.18$ &  - & $< 10^{-4}$ & $0.034$ & $0.055$ & $0.18$ & $0.089$ & Candidate \\
-$201465501$ & $1$ & $0.68$ &  - & $< 10^{-4}$ & $0.021$ & $3.0\times10^{-3}$ & $0.14$ & $0.025$ & Candidate \\
- \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $0.020$  & \color{red}  $0.966$  & \color{red}  $0.18$  & \color{red}  $0.986$  & \color{red}  FP\\
-$201505350$ & $2$ & $0.70$ &  - & $< 10^{-4}$ & $3.0\times10^{-4}$ & $1.2\times10^{-4}$ & $0.07$ & $4.2\times10^{-4}$ & Planet \\
-$201546283$ & $1$ & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Planet \\
-$201549860$ & $1$ & $0.18$ &  - & $< 10^{-4}$ & $1.7\times10^{-3}$ & $6.5\times10^{-4}$ & $0.20$ & $2.4\times10^{-3}$ & Planet \\
-$201555883$ & $1$ & $0.94$ &  - & $< 10^{-4}$ & $5.8\times10^{-4}$ & $3.7\times10^{-4}$ & $0.20$ & $9.5\times10^{-4}$ & Planet \\
- \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}   -  & \color{red}  $2.7\times10^{-3}$  & \color{red}  $0.027$  & \color{red}  $0.926$  & \color{red}  $0.07$  & \color{red}  $0.956$  & \color{red}  FP\\
-$201569483$ & $1$ & $2.06$ &  - & $0.468$ & $< 10^{-4}$ & $0.092$ & $0.01$ & $0.560$ & Candidate \\
-$201577035$ & $1$ & $0.14$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $1.0\times10^{-4}$ & $0.20$ & $1.1\times10^{-4}$ & Planet \\
-$201596316$ & $1$ & $0.45$ &  - & $< 10^{-4}$ & $1.3\times10^{-3}$ & $2.1\times10^{-3}$ & $0.17$ & $3.4\times10^{-3}$ & Planet \\
-$201613023$ & $1$ & $0.08$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.15$ & $< 10^{-4}$ & Planet \\
-$201617985$ & $1$ & $0.27$ &  - & $< 10^{-4}$ & $0.016$ & $1.7\times10^{-3}$ & $0.16$ & $0.018$ & Candidate \\
-$201629650$ & $1$ & $0.43$ &  - & $< 10^{-4}$ & $6.3\times10^{-4}$ & $1.1\times10^{-3}$ & $0.17$ & $1.7\times10^{-3}$ & Planet \\
-$201635569$ & $1$ & $0.79$ &  - & $< 10^{-4}$ & $7.5\times10^{-3}$ & $0.069$ & $0.09$ & $0.076$ & Candidate \\
- \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.819$  & \color{red}  $2.2\times10^{-4}$  & \color{red}  $0.119$  & \color{red}  $0.01$  & \color{red}  $0.938$  & \color{red}  FP\\
-$201702477$ & $1$ & $0.70$ &  - & $< 10^{-4}$ & $4.0\times10^{-3}$ & $0.277$ & $0.06$ & $0.281$ & Candidate \\
-$201736247$ & $1$ & $0.42$ &  - & $< 10^{-4}$ & $1.9\times10^{-4}$ & $8.5\times10^{-4}$ & $0.22$ & $1.0\times10^{-3}$ & Planet \\
-$201754305$ & $1$ & $0.65$ &  - & $< 10^{-4}$ & $1.9\times10^{-3}$ & $1.5\times10^{-3}$ & $0.18$ & $3.4\times10^{-3}$ & Planet \\
-$201754305$ & $2$ & $0.38$ &  - & $< 10^{-4}$ & $1.2\times10^{-3}$ & $6.4\times10^{-4}$ & $0.17$ & $1.9\times10^{-3}$ & Planet \\
-$201779067$ & $1$ & $1.97$ &  - & $0.036$ & $5.0\times10^{-3}$ & $0.286$ & $0.03$ & $0.327$ & Candidate \\
-$201828749$ & $1$ & $0.39$ &  - & $< 10^{-4}$ & $1.7\times10^{-3}$ & $2.2\times10^{-3}$ & $0.17$ & $3.9\times10^{-3}$ & Planet \\
-$201855371$ & $1$ & $0.62$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $1.7\times10^{-4}$ & Planet \\
-$201912552$ & $1$ & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
-$201929294$ & $1$ & $3.12$ &  - & $< 10^{-4}$ & $6.8\times10^{-3}$ & $0.052$ & $0.05$ & $0.059$ & Candidate
+$201208431$ & $1$ & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $7.0\times10^{-4}$ & $0.21$ & $7.0\times10^{-4}$ & Planet \\
+ \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $8.8\times10^{-3}$  & \color{red}  $0.940$  & \color{red}  $0.051$  & \color{red}  $0.17$  & \color{red}  $1.000$  & \color{red}  FP\\
+$201295312$ & $1$ & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet \\
+$201338508$ & $1$ & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $3.2\times10^{-3}$ & Planet \\
+$201338508$ & $2$ & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.8\times10^{-4}$ & $0.22$ & $1.8\times10^{-4}$ & Planet \\
+$201367065$ & $1$ & $0.15$ &  - & $0.717$ & $< 10^{-4}$ & $0.044$ & $0.07$ & $0.761$ & Candidate \\
+$201367065$ & $2$ & $0.67$ &  - & $3.2\times10^{-3}$ & $< 10^{-4}$ & $4.2\times10^{-3}$ & $0.17$ & $7.4\times10^{-3}$ & Planet \\
+$201384232$ & $1$ & $0.44$ &  - & $1.2\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $1.4\times10^{-4}$ & Planet \\
+$201393098$ & $1$ & $0.52$ &  - & $1.6\times10^{-3}$ & $< 10^{-4}$ & $5.5\times10^{-4}$ & $0.19$ & $2.2\times10^{-3}$ & Planet \\
+$201403446$ & $1$ & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
+$201445392$ & $1$ & $0.26$ &  - & $1.3\times10^{-3}$ & $< 10^{-4}$ & $0.012$ & $0.19$ & $0.013$ & Candidate \\
+$201445392$ & $2$ & $0.18$ &  - & $0.023$ & $< 10^{-4}$ & $0.254$ & $0.21$ & $0.277$ & Candidate \\
+$201465501$ & $1$ & $0.68$ &  - & $0.491$ & $0.022$ & $9.1\times10^{-3}$ & $0.20$ & $0.522$ & Candidate \\
+$201505350$ & $1$ & $2.69$ &  - & $0.583$ & $< 10^{-4}$ & $0.024$ & $0.07$ & $0.607$ & Candidate \\
+$201505350$ & $2$ & $0.70$ &  - & $0.034$ & $< 10^{-4}$ & $2.3\times10^{-4}$ & $0.07$ & $0.034$ & Candidate \\
+$201546283$ & $1$ & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $1.1\times10^{-4}$ & Planet \\
+$201549860$ & $1$ & $0.18$ &  - & $7.5\times10^{-3}$ & $0.014$ & $0.011$ & $0.22$ & $0.032$ & Candidate \\
+$201555883$ & $1$ & $0.94$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.6\times10^{-3}$ & $0.10$ & $3.6\times10^{-3}$ & Planet \\
+$201565013$ & $1$ & $1.69$ &  - & $0.460$ & $0.391$ & $0.035$ & $0.06$ & $0.887$ & Candidate \\
+ \color{red} $201569483$  & \color{red}  $1$  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.437$  & \color{red}  $0.562$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.999$  & \color{red}  FP\\
+$201577035$ & $1$ & $0.14$ &  Y & $3.0\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.07$ & $3.6\times10^{-4}$ & Planet \\
+$201596316$ & $1$ & $0.45$ &  - & $0.017$ & $< 10^{-4}$ & $3.4\times10^{-4}$ & $0.20$ & $0.017$ & Candidate \\
+$201613023$ & $1$ & $0.08$ &  Y & $9.8\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $9.8\times10^{-4}$ & Planet \\
+$201617985$ & $1$ & $0.27$ &  - & $0.166$ & $< 10^{-4}$ & $0.053$ & $0.19$ & $0.219$ & Candidate \\
+$201629650$ & $1$ & $0.43$ &  - & $1.5\times10^{-3}$ & $< 10^{-4}$ & $2.6\times10^{-4}$ & $0.18$ & $1.8\times10^{-3}$ & Planet \\
+$201635569$ & $1$ & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.043$ & $0.06$ & $0.043$ & Candidate \\
+ \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.856$  & \color{red}  $0.142$  & \color{red}  $1.6\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP\\
+$201702477$ & $1$ & $0.70$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.0\times10^{-3}$ & $0.06$ & $4.0\times10^{-3}$ & Planet \\
+$201736247$ & $1$ & $0.42$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.6\times10^{-4}$ & $0.18$ & $4.9\times10^{-4}$ & Planet \\
+$201754305$ & $1$ & $0.65$ &  - & $2.5\times10^{-3}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $5.7\times10^{-3}$ & Planet \\
+$201754305$ & $2$ & $0.38$ &  - & $1.9\times10^{-3}$ & $< 10^{-4}$ & $1.7\times10^{-3}$ & $0.22$ & $3.6\times10^{-3}$ & Planet \\
+ \color{red} $201779067$  & \color{red}  $1$  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.935$  & \color{red}  $0.063$  & \color{red}  $3.2\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP\\
+$201828749$ & $1$ & $0.39$ &  Y & $2.6\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $2.6\times10^{-3}$ & Planet \\
+$201855371$ & $1$ & $0.62$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
+$201912552$ & $1$ & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet \\
+$201929294$ & $1$ & $3.12$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.8\times10^{-4}$ & $0.07$ & $2.9\times10^{-4}$ & Planet
 

### 2015-03-26 fpp/write_fpptable.py

@@ -79,19 +79,19 @@ for f in folders:
     m = re.search('(\d+)\.(\d)',f)
     epic_id = int(m.group(1))
     i = int(m.group(2))
-    line = '${}$ & ${}$ & '.format(epic_id,i)
-    line += '${:.2f}$ & '.format(max_secondary(epic_id,i)*1e3)
+    line = '${}$ & ${}$ & '.format(epic_id,i)  # EPIC, Cand. Num.
+    line += '${:.2f}$ & '.format(max_secondary(epic_id,i)*1e3) #max(delta_sec)
     ccs = AO_contrast_curves(epic_id)
     if len(ccs)>0:
         line += ' Y & '
-    else:
+    else:                #AO?
         line += ' - & '
 
     for val in [eb,beb,heb]:
         val = float(val)
-        line += '{} & '.format(prob_entry(val))
-    line += '${:.2f}$ & '.format(float(fp))
-    line += '{} & '.format(prob_entry(FPP))
+        line += '{} & '.format(prob_entry(val))  #pEB, pBEB, pHEB
+    line += '${:.2f}$ & '.format(float(fp)) #fp_specific
+    line += '{} & '.format(prob_entry(FPP)) #FPP
     FPP = float(FPP)
     if FPP < 0.01:
         disp = 'Planet'
@@ -99,7 +99,7 @@ for f in folders:
         disp = 'FP'
     else:
         disp = 'Candidate'
-    line += '{} '.format(disp)
+    line += '{} '.format(disp)  #Disposition
     if f != folders[-1]:
         line += '\\\\'
     line += '\n'

### 2015-03-26 table_fpp.tex
FPP table format

@@
 %\LongTables
-\begin{deluxetable*}{lclccccccc}
+\begin{deluxetable*}{ccccccccc}
 \tablewidth{0pt}
@@
 \tablehead{
-\colhead{EPIC} &
-\colhead{Cand. Num.} &
+\colhead{Candidate} &
 \colhead{max($\delta_{\rm sec}$)} &
@@
 \startdata
-$201208431$ & $1$ & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $7.0\times10^{-4}$ & $0.21$ & $7.0\times10^{-4}$ & Planet \\
- \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $8.8\times10^{-3}$  & \color{red}  $0.940$  & \color{red}  $0.051$  & \color{red}  $0.17$  & \color{red}  $1.000$  & \color{red}  FP\\
-$201295312$ & $1$ & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet \\
-$201338508$ & $1$ & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $3.2\times10^{-3}$ & Planet \\
-$201338508$ & $2$ & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.8\times10^{-4}$ & $0.22$ & $1.8\times10^{-4}$ & Planet \\
-$201367065$ & $1$ & $0.15$ &  - & $0.717$ & $< 10^{-4}$ & $0.044$ & $0.07$ & $0.761$ & Candidate \\
-$201367065$ & $2$ & $0.67$ &  - & $3.2\times10^{-3}$ & $< 10^{-4}$ & $4.2\times10^{-3}$ & $0.17$ & $7.4\times10^{-3}$ & Planet \\
-$201384232$ & $1$ & $0.44$ &  - & $1.2\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $1.4\times10^{-4}$ & Planet \\
-$201393098$ & $1$ & $0.52$ &  - & $1.6\times10^{-3}$ & $< 10^{-4}$ & $5.5\times10^{-4}$ & $0.19$ & $2.2\times10^{-3}$ & Planet \\
-$201403446$ & $1$ & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
-$201445392$ & $1$ & $0.26$ &  - & $1.3\times10^{-3}$ & $< 10^{-4}$ & $0.012$ & $0.19$ & $0.013$ & Candidate \\
-$201445392$ & $2$ & $0.18$ &  - & $0.023$ & $< 10^{-4}$ & $0.254$ & $0.21$ & $0.277$ & Candidate \\
-$201465501$ & $1$ & $0.68$ &  - & $0.491$ & $0.022$ & $9.1\times10^{-3}$ & $0.20$ & $0.522$ & Candidate \\
-$201505350$ & $1$ & $2.69$ &  - & $0.583$ & $< 10^{-4}$ & $0.024$ & $0.07$ & $0.607$ & Candidate \\
-$201505350$ & $2$ & $0.70$ &  - & $0.034$ & $< 10^{-4}$ & $2.3\times10^{-4}$ & $0.07$ & $0.034$ & Candidate \\
-$201546283$ & $1$ & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $1.1\times10^{-4}$ & Planet \\
-$201549860$ & $1$ & $0.18$ &  - & $7.5\times10^{-3}$ & $0.014$ & $0.011$ & $0.22$ & $0.032$ & Candidate \\
-$201555883$ & $1$ & $0.94$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.6\times10^{-3}$ & $0.10$ & $3.6\times10^{-3}$ & Planet \\
-$201565013$ & $1$ & $1.69$ &  - & $0.460$ & $0.391$ & $0.035$ & $0.06$ & $0.887$ & Candidate \\
- \color{red} $201569483$  & \color{red}  $1$  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.437$  & \color{red}  $0.562$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.999$  & \color{red}  FP\\
-$201577035$ & $1$ & $0.14$ &  Y & $3.0\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.07$ & $3.6\times10^{-4}$ & Planet \\
-$201596316$ & $1$ & $0.45$ &  - & $0.017$ & $< 10^{-4}$ & $3.4\times10^{-4}$ & $0.20$ & $0.017$ & Candidate \\
-$201613023$ & $1$ & $0.08$ &  Y & $9.8\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $9.8\times10^{-4}$ & Planet \\
-$201617985$ & $1$ & $0.27$ &  - & $0.166$ & $< 10^{-4}$ & $0.053$ & $0.19$ & $0.219$ & Candidate \\
-$201629650$ & $1$ & $0.43$ &  - & $1.5\times10^{-3}$ & $< 10^{-4}$ & $2.6\times10^{-4}$ & $0.18$ & $1.8\times10^{-3}$ & Planet \\
-$201635569$ & $1$ & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.043$ & $0.06$ & $0.043$ & Candidate \\
- \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.856$  & \color{red}  $0.142$  & \color{red}  $1.6\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP\\
-$201702477$ & $1$ & $0.70$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.0\times10^{-3}$ & $0.06$ & $4.0\times10^{-3}$ & Planet \\
-$201736247$ & $1$ & $0.42$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.6\times10^{-4}$ & $0.18$ & $4.9\times10^{-4}$ & Planet \\
-$201754305$ & $1$ & $0.65$ &  - & $2.5\times10^{-3}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $5.7\times10^{-3}$ & Planet \\
-$201754305$ & $2$ & $0.38$ &  - & $1.9\times10^{-3}$ & $< 10^{-4}$ & $1.7\times10^{-3}$ & $0.22$ & $3.6\times10^{-3}$ & Planet \\
- \color{red} $201779067$  & \color{red}  $1$  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.935$  & \color{red}  $0.063$  & \color{red}  $3.2\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP\\
-$201828749$ & $1$ & $0.39$ &  Y & $2.6\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $2.6\times10^{-3}$ & Planet \\
-$201855371$ & $1$ & $0.62$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
-$201912552$ & $1$ & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet \\
-$201929294$ & $1$ & $3.12$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.8\times10^{-4}$ & $0.07$ & $2.9\times10^{-4}$ & Planet
+201208431.01 & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $7.0\times10^{-4}$ & $0.21$ & $7.0\times10^{-4}$ & Planet \\
+ \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $8.8\times10^{-3}$  & \color{red}  $0.940$  & \color{red}  $0.051$  & \color{red}  $0.17$  & \color{red}  $1.000$  & \color{red}  FP\\
+201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet \\
+201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $3.2\times10^{-3}$ & Planet \\
+201338508.02 & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.8\times10^{-4}$ & $0.22$ & $1.8\times10^{-4}$ & Planet \\
+201367065.01 & $0.15$ &  - & $0.717$ & $< 10^{-4}$ & $0.044$ & $0.07$ & $0.761$ & Candidate \\
+201367065.02 & $0.67$ &  - & $3.2\times10^{-3}$ & $< 10^{-4}$ & $4.2\times10^{-3}$ & $0.17$ & $7.4\times10^{-3}$ & Planet \\
+201384232.01 & $0.44$ &  - & $1.2\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $1.4\times10^{-4}$ & Planet \\
+201393098.01 & $0.52$ &  - & $1.6\times10^{-3}$ & $< 10^{-4}$ & $5.5\times10^{-4}$ & $0.19$ & $2.2\times10^{-3}$ & Planet \\
+201403446.01 & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
+201445392.01 & $0.26$ &  - & $1.3\times10^{-3}$ & $< 10^{-4}$ & $0.012$ & $0.19$ & $0.013$ & Candidate \\
+201445392.02 & $0.18$ &  - & $0.023$ & $< 10^{-4}$ & $0.254$ & $0.21$ & $0.277$ & Candidate \\
+201465501.01 & $0.68$ &  - & $0.491$ & $0.022$ & $9.1\times10^{-3}$ & $0.20$ & $0.522$ & Candidate \\
+201505350.01 & $2.69$ &  - & $0.583$ & $< 10^{-4}$ & $0.024$ & $0.07$ & $0.607$ & Candidate \\
+201505350.02 & $0.70$ &  - & $0.034$ & $< 10^{-4}$ & $2.3\times10^{-4}$ & $0.07$ & $0.034$ & Candidate \\
+201546283.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $1.1\times10^{-4}$ & Planet \\
+201549860.01 & $0.18$ &  - & $7.5\times10^{-3}$ & $0.014$ & $0.011$ & $0.22$ & $0.032$ & Candidate \\
+201555883.01 & $0.94$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.6\times10^{-3}$ & $0.10$ & $3.6\times10^{-3}$ & Planet \\
+201565013.01 & $1.69$ &  - & $0.460$ & $0.391$ & $0.035$ & $0.06$ & $0.887$ & Candidate \\
+ \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.437$  & \color{red}  $0.562$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.999$  & \color{red}  FP\\
+201577035.01 & $0.14$ &  Y & $3.0\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.07$ & $3.6\times10^{-4}$ & Planet \\
+201596316.01 & $0.45$ &  - & $0.017$ & $< 10^{-4}$ & $3.4\times10^{-4}$ & $0.20$ & $0.017$ & Candidate \\
+201613023.01 & $0.08$ &  Y & $9.8\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $9.8\times10^{-4}$ & Planet \\
+201617985.01 & $0.27$ &  - & $0.166$ & $< 10^{-4}$ & $0.053$ & $0.19$ & $0.219$ & Candidate \\
+201629650.01 & $0.43$ &  - & $1.5\times10^{-3}$ & $< 10^{-4}$ & $2.6\times10^{-4}$ & $0.18$ & $1.8\times10^{-3}$ & Planet \\
+201635569.01 & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.043$ & $0.06$ & $0.043$ & Candidate \\
+ \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.856$  & \color{red}  $0.142$  & \color{red}  $1.6\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP\\
+201702477.01 & $0.70$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.0\times10^{-3}$ & $0.06$ & $4.0\times10^{-3}$ & Planet \\
+201736247.01 & $0.42$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.6\times10^{-4}$ & $0.18$ & $4.9\times10^{-4}$ & Planet \\
+201754305.01 & $0.65$ &  - & $2.5\times10^{-3}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $5.7\times10^{-3}$ & Planet \\
+201754305.02 & $0.38$ &  - & $1.9\times10^{-3}$ & $< 10^{-4}$ & $1.7\times10^{-3}$ & $0.22$ & $3.6\times10^{-3}$ & Planet \\
+ \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.935$  & \color{red}  $0.063$  & \color{red}  $3.2\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP\\
+201828749.01 & $0.39$ &  Y & $2.6\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $2.6\times10^{-3}$ & Planet \\
+201855371.01 & $0.62$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
+201912552.01 & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet \\
+201929294.01 & $3.12$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.8\times10^{-4}$ & $0.07$ & $2.9\times10^{-4}$ & Planet
 

### 2015-03-26 fpp/write_fpptable.py

@@ -7,6 +7,13 @@ import numpy as np
 from k2fpp.fpp import max_secondary
 from k2fpp.contrast import AO_contrast_curves
 
+notes = {'a': 'Maximum depth [ppt] of potential secondary eclipse signal.',
+         'b': 'Whether adaptive optics imaging has been obtained.',
+         'c': 'Integrated planet occurrence rate assumed between 0.7$\times$'+\
+              'and 1.3$\times$ the candidate\'s radius',
+         'd': 'Declared a false positive because of epoch match' +\
+              'to XXXXXXXX'}
+
 def prob_entry(val):
     val = float(val)
     if val > 1e-4:
@@ -48,14 +55,13 @@ fout = open('../table_fpp.tex','w')
 fout.write(r"""
 \clearpage
 %\LongTables
-\begin{deluxetable*}{lclccccccc}
+\begin{deluxetable*}{ccccccccc}
 \tablewidth{0pt}
 \tabletypesize{\scriptsize}
 \tablecaption{False Positive Probability Calculation Results}
 \label{Table:FPP}
 \tablehead{
-\colhead{EPIC} &
-\colhead{Cand. Num.} &
+\colhead{Candidate} &
 \colhead{max($\delta_{\rm sec}$)} &
 \colhead{AO?} &
 \colhead{${\rm Pr}_{\rm EB}$} &
@@ -79,7 +85,7 @@ for f in folders:
     m = re.search('(\d+)\.(\d)',f)
     epic_id = int(m.group(1))
     i = int(m.group(2))
-    line = '${}$ & ${}$ & '.format(epic_id,i)  # EPIC, Cand. Num.
+    line = '{}.{:02.0f} & '.format(epic_id, i)  # EPIC, Cand. Num.
     line += '${:.2f}$ & '.format(max_secondary(epic_id,i)*1e3) #max(delta_sec)
     ccs = AO_contrast_curves(epic_id)
     if len(ccs)>0:

### 2015-03-26 table_fpp.tex
FP table updates

@@
 \colhead{Candidate} &
-\colhead{max($\delta_{\rm sec}$)} &
-\colhead{AO?} &
+\colhead{max($\delta_{\rm sec}$) [ppt]\tablenotemark{1}} &
+\colhead{AO?\tablenotemark{2}} &
 \colhead{${\rm Pr}_{\rm EB}$} &
@@
 \colhead{${\rm Pr}_{\rm HEB}$} &
-\colhead{$f_{p}$} &
+\colhead{$f_{p}$\tablenotemark{3}} &
 \colhead{FPP} &
@@
 201549860.01 & $0.18$ &  - & $7.5\times10^{-3}$ & $0.014$ & $0.011$ & $0.22$ & $0.032$ & Candidate \\
-201555883.01 & $0.94$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.6\times10^{-3}$ & $0.10$ & $3.6\times10^{-3}$ & Planet \\
+ \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  FP\tablenotemark{a}\\
 201565013.01 & $1.69$ &  - & $0.460$ & $0.391$ & $0.035$ & $0.06$ & $0.887$ & Candidate \\
@@
 \tablecomments{blurgh.}
+\tablenotetext{1}{Maximum depth of potential secondary eclipse signal.}
+\tablenotetext{2}{Whether adaptive optics observation is presented in this paper.}
+\tablenotetext{3}{Integrated planet occurrence rate assumed between 0.7$\times$ and 1.3$\times$ the candidate radius}
+\tablenotetext{a}{Declared a false positive because of epoch match to 201569483.01 (see \S\ref{sec:ephemmatch}).}
 \end{deluxetable*}

### 2015-03-26 fpp/write_fpptable.py

@@ -7,12 +7,17 @@ import numpy as np
 from k2fpp.fpp import max_secondary
 from k2fpp.contrast import AO_contrast_curves
 
-notes = {'a': 'Maximum depth [ppt] of potential secondary eclipse signal.',
-         'b': 'Whether adaptive optics imaging has been obtained.',
-         'c': 'Integrated planet occurrence rate assumed between 0.7$\times$'+\
+FP_OVERRIDE = ['201555883.01']
+
+notes = {'1': 'Maximum depth [ppt] of potential secondary eclipse signal.',
+         '2': 'Whether adaptive optics imaging has been obtained.',
+         '3': 'Integrated planet occurrence rate assumed between 0.7$\times$'+\
               'and 1.3$\times$ the candidate\'s radius',
-         'd': 'Declared a false positive because of epoch match' +\
+         '4': 'Declared a false positive because of epoch match' +\
               'to XXXXXXXX'}
+
+def note(key):
+    return '\tablenotemark{{}}'.format(key)
 
 def prob_entry(val):
     val = float(val)
@@ -25,7 +30,7 @@ def prob_entry(val):
     else:
         return '$< 10^{-4}$'
 
-def format_line(line, fpp):
+def format_line(line, fpp, force_fp=False):
     fpp = float(fpp)
     newline = line
     if fpp < 0.01 and False: #not bothering to bold.
@@ -38,7 +43,7 @@ def format_line(line, fpp):
                 m = re.search('\$(.*)\$',v)
                 if m:
                     newline += r' $\mathbf{ ' + m.group(1) + '}$ &'
-    if fpp > 0.9:
+    if fpp > 0.9 or force_fp:
         newline = ''
         for v in line.split('&'):
             m = re.search('(.*)\s+\\\\',v)
@@ -62,12 +67,12 @@ fout.write(r"""
 \label{Table:FPP}
 \tablehead{
 \colhead{Candidate} &
-\colhead{max($\delta_{\rm sec}$)} &
-\colhead{AO?} &
+\colhead{max($\delta_{\rm sec}$) [ppt]\tablenotemark{1}} &
+\colhead{AO?\tablenotemark{2}} &
 \colhead{${\rm Pr}_{\rm EB}$} &
 \colhead{${\rm Pr}_{\rm BEB}$} &
 \colhead{${\rm Pr}_{\rm HEB}$} &
-\colhead{$f_{p}$} &
[…]

### 2015-03-26 table_fpp.tex
fpp table

@@
 \enddata
-\tablecomments{blurgh.}
+\tablecomments{Results of the \texttt{vespa} astrophysical 
+false positive probability calculations for all candidates.  
+Likely false positives (FPP $> 0.9$) are marked in red.  
+Candidates are declared to be validated if FPP $< 0.01$.  
+EB, BEB, and HEB refer to the three considered astrophysical 
+false positive scenarios, and the relative probability of 
+each is listed in the appropriate column.}
 \tablenotetext{1}{Maximum depth of potential secondary eclipse signal.}

### 2015-03-26 fpp/write_fpptable.py

@@ -129,7 +129,13 @@ for f in folders:
 
 fout.write(r"""
 \enddata
-\tablecomments{blurgh.}
+\tablecomments{Results of the \texttt{vespa} astrophysical 
+false positive probability calculations for all candidates.  
+Likely false positives (FPP $> 0.9$) are marked in red.  
+Candidates are declared to be validated if FPP $< 0.01$.  
+EB, BEB, and HEB refer to the three considered astrophysical 
+false positive scenarios, and the relative probability of 
+each is listed in the appropriate column.}
 \tablenotetext{1}{Maximum depth of potential secondary eclipse signal.}
 \tablenotetext{2}{Whether adaptive optics observation is presented in this paper.}
 \tablenotetext{3}{Integrated planet occurrence rate assumed between 0.7$\times$ and 1.3$\times$ the candidate radius}

### 2015-03-26 fpp/write_fpptable.py
numbers changed

@@ -131,8 +131,9 @@ fout.write(r"""
 \enddata
 \tablecomments{Results of the \texttt{vespa} astrophysical 
 false positive probability calculations for all candidates.  
-Likely false positives (FPP $> 0.9$) are marked in red.  
-Candidates are declared to be validated if FPP $< 0.01$.  
+Likely false positives (FPP $> 0.9$, or otherwise designated)
+ are marked in red.  
+Candidates are declared to be validated planets if FPP $< 0.01$.  
 EB, BEB, and HEB refer to the three considered astrophysical 
 false positive scenarios, and the relative probability of 
 each is listed in the appropriate column.}

### 2015-03-26 table_fpp.tex
numbers changed

@@
  \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $8.8\times10^{-3}$  & \color{red}  $0.940$  & \color{red}  $0.051$  & \color{red}  $0.17$  & \color{red}  $1.000$  & \color{red}  FP\\
-201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet \\
+201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet\tablenotemark{c} \\
 201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $3.2\times10^{-3}$ & Planet \\
@@
 201505350.02 & $0.70$ &  - & $0.034$ & $< 10^{-4}$ & $2.3\times10^{-4}$ & $0.07$ & $0.034$ & Candidate \\
-201546283.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $1.1\times10^{-4}$ & Planet \\
+201546283.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $1.1\times10^{-4}$ & Candidate\tablenotemark{a} \\
 201549860.01 & $0.18$ &  - & $7.5\times10^{-3}$ & $0.014$ & $0.011$ & $0.22$ & $0.032$ & Candidate \\
- \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  FP\tablenotemark{a}\\
+ \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  FP\tablenotemark{b}\\
 201565013.01 & $1.69$ &  - & $0.460$ & $0.391$ & $0.035$ & $0.06$ & $0.887$ & Candidate \\
@@
  \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.935$  & \color{red}  $0.063$  & \color{red}  $3.2\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP\\
-201828749.01 & $0.39$ &  Y & $2.6\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $2.6\times10^{-3}$ & Planet \\
+201828749.01 & $0.39$ &  Y & $2.6\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $2.6\times10^{-3}$ & Candidate\tablenotemark{a} \\
 201855371.01 & $0.62$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
@@
 false positive probability calculations for all candidates.  
-Likely false positives (FPP $> 0.9$) are marked in red.  
-Candidates are declared to be validated if FPP $< 0.01$.  
+Likely false positives (FPP $> 0.9$, or otherwise designated)
+ are marked in red.  
+Candidates are declared to be validated planets if FPP $< 0.01$.  
 EB, BEB, and HEB refer to the three considered astrophysical 
@@
 \tablenotetext{3}{Integrated planet occurrence rate assumed between 0.7$\times$ and 1.3$\times$ the candidate radius}
-\tablenotetext{a}{Declared a false positive because of epoch match to 201569483.01 (see \S\ref{sec:ephemmatch}).}
+\tablenotetext{a}{Despite low FPP, returned to candidate status 
+out of abundance of caution due
+to secondary star detection in or near photometric aperture.  Most of these we do anticipate to be validated once the specific false positive scenarios are considered.}
+\tablenotetext{b}{Declared a false positive because of epoch match to 201569483.01 (see \S\ref{sec:ephemmatch}).}
+\tablenotetext{c}{Identified as planet by \citet{Crossfield15}.}
 \end{deluxetable*}

### 2015-03-26 table_fpp.tex
fpp table edits.  latex formatting error, sorry..

@@
 \colhead{Candidate} &
-\colhead{max($\delta_{\rm sec}$) [ppt]\tablenotemark{1}} &
+\colhead{$\delta_{\rm sec, max}$ [ppt]\tablenotemark{1}} &
 \colhead{AO?\tablenotemark{2}} &
@@
  \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $8.8\times10^{-3}$  & \color{red}  $0.940$  & \color{red}  $0.051$  & \color{red}  $0.17$  & \color{red}  $1.000$  & \color{red}  FP\\
-201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet\tablenotemark{c} \\
+201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet \\
 201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $3.2\times10^{-3}$ & Planet \\
 201338508.02 & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.8\times10^{-4}$ & $0.22$ & $1.8\times10^{-4}$ & Planet \\
-201367065.01 & $0.15$ &  - & $0.717$ & $< 10^{-4}$ & $0.044$ & $0.07$ & $0.761$ & Candidate \\
-201367065.02 & $0.67$ &  - & $3.2\times10^{-3}$ & $< 10^{-4}$ & $4.2\times10^{-3}$ & $0.17$ & $7.4\times10^{-3}$ & Planet \\
+201367065.01 & $0.15$ &  - & $0.717$ & $< 10^{-4}$ & $0.044$ & $0.07$ & $0.761$ & Planet\tablenotemark{c} \\
+201367065.02 & $0.67$ &  - & $3.2\times10^{-3}$ & $< 10^{-4}$ & $4.2\times10^{-3}$ & $0.17$ & $7.4\times10^{-3}$ & Planet\tablenotemark{c} \\
 201384232.01 & $0.44$ &  - & $1.2\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $1.4\times10^{-4}$ & Planet \\
@@
 201465501.01 & $0.68$ &  - & $0.491$ & $0.022$ & $9.1\times10^{-3}$ & $0.20$ & $0.522$ & Candidate \\
-201505350.01 & $2.69$ &  - & $0.583$ & $< 10^{-4}$ & $0.024$ & $0.07$ & $0.607$ & Candidate \\
-201505350.02 & $0.70$ &  - & $0.034$ & $< 10^{-4}$ & $2.3\times10^{-4}$ & $0.07$ & $0.034$ & Candidate \\
+201505350.01 & $2.69$ &  - & $0.583$ & $< 10^{-4}$ & $0.024$ & $0.07$ & $0.607$ & Planet\tablenotemark{d} \\
+201505350.02 & $0.70$ &  - & $0.034$ & $< 10^{-4}$ & $2.3\times10^{-4}$ & $0.07$ & $0.034$ & Planet\tablenotemark{d} \\
 201546283.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $1.1\times10^{-4}$ & Candidate\tablenotemark{a} \\
@@
 201912552.01 & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet \\
-201929294.01 & $3.12$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.8\times10^{-4}$ & $0.07$ & $2.9\times10^{-4}$ & Planet
-
+ \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $2.8\times10^{-4}$  & \color{red}  $0.07$  & \color{red}  $2.9\times10^{-4}$  & \color{red}  FP\tablenotemark{b}
+ &
 \enddata
@@
 false positive scenarios, and the relative probability of 
-each is listed in the appropriate column.}
+each is listed in the appropriate column.  Planets previously 
+identified in the literature are marked as planets even if FPP is not 
+below 1\% threshold.}
 \tablenotetext{1}{Maximum depth of potential secondary eclipse signal.}
@@
 to secondary star detection in or near photometric aperture.  Most of these we do anticipate to be validated once the specific false positive scenarios are considered.}
-\tablenotetext{b}{Declared a false positive because of epoch match to 201569483.01 (see \S\ref{sec:ephemmatch}).}
-\tablenotetext{c}{Identified as planet by \citet{Crossfield15}.}
+\tablenotetext{b}{Declared a false positive due to noise modeling systematics (see \S\ref{sec:systematics}).}
+\tablenotetext{c}{Identified as planets by \citet{Crossfield15}.}
+\tablenotetext{d}{Identified as planets by \citet{Armstrong15b}.}
 \end{deluxetable*}

### 2015-03-26 fpp/write_fpptable.py

@@ -7,7 +7,7 @@ import numpy as np
 from k2fpp.fpp import max_secondary
 from k2fpp.contrast import AO_contrast_curves
 
-FP_OVERRIDE = ['201555883.01']
+FP_OVERRIDE = ['201555883.01', '201929294.01']
 CAND_OVERRIDE = [#'201403446.01',
                  '201546283.01',
                  #'201577035.01',
@@ -66,7 +66,7 @@ fout.write(r"""
 \label{Table:FPP}
 \tablehead{
 \colhead{Candidate} &
-\colhead{max($\delta_{\rm sec}$) [ppt]\tablenotemark{1}} &
+\colhead{$\delta_{\rm sec, max}$ [ppt]\tablenotemark{1}} &
 \colhead{AO?\tablenotemark{2}} &
 \colhead{${\rm Pr}_{\rm EB}$} &
 \colhead{${\rm Pr}_{\rm BEB}$} &
@@ -107,21 +107,23 @@ for f in folders:
     FPP = float(FPP)
     if cand_name in FP_OVERRIDE:
         disp = 'FP'
-        if cand_name=='201555883.01':
+        if cand_name in ['201555883.01', '201929294.01']:
             disp = r'FP\tablenotemark{b}'
     else:
         if FPP < 0.01:
             if cand_name in CAND_OVERRIDE:
                 disp = r'Candidate\tablenotemark{a}'
             else:
-                if cand_name=='201295312.01':
-                    disp = r'Planet\tablenotemark{c}'
-                else:
-                    disp = 'Planet'
+                disp = 'Planet'
         elif FPP > 0.9:
             disp = 'FP'
         else:
-            disp = 'Candidate'
+            disp = 'Candidate' 
+
+        if epic_id==201505350:
+            disp = r'Planet\tablenotemark{d}'
+        if epic_id==201367065:
+            disp = r'Planet\tablenotemark{c}'
     line += '{} '.format(disp)  #Disposition
     if f != folders[-1]:
         line += '\\\\'
@@ -141,15 +143,18 @@ Likely false positives (FPP $> 0.9$, or otherwise designated)
 Candidates are declared to be validated planets if FPP $< 0.01$.  
 EB, BEB, and HEB refer to the three considered astrophysical 
 false positive scenarios, and the relative probability of 
-each is listed in the appropriate column.}
+each is listed in the appropriate column.  Planets previously 
+identified in the literature are marked as planets even if FPP is not 
+below 1\% threshold.}
[…]

### 2015-03-26 table_fpp.tex
manually fixed FPP table
fixed fpptable script

@@
 201208431.01 & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $7.0\times10^{-4}$ & $0.21$ & $7.0\times10^{-4}$ & Planet  \\
- \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $8.8\times10^{-3}$  & \color{red}  $0.940$  & \color{red}  $0.051$  & \color{red}  $0.17$  & \color{red}  $1.000$  & \color{red}  FP\\
+ \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $8.8\times10^{-3}$  & \color{red}  $0.940$  & \color{red}  $0.051$  & \color{red}  $0.17$  & \color{red}  $1.000$  & \color{red}  FP \\
 201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet  \\
@@
 201549860.01 & $0.18$ &  - & $7.5\times10^{-3}$ & $0.014$ & $0.011$ & $0.22$ & $0.032$ & Candidate  \\
- \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  FP\tablenotemark{b}\\
+ \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  FP\tablenotemark{b} \\
 201565013.01 & $1.69$ &  - & $0.460$ & $0.391$ & $0.035$ & $0.06$ & $0.887$ & Candidate  \\
- \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.437$  & \color{red}  $0.562$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.999$  & \color{red}  FP\\
+ \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.437$  & \color{red}  $0.562$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.999$  & \color{red}  FP \\
 201577035.01 & $0.14$ &  Y & $3.0\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.07$ & $3.6\times10^{-4}$ & Planet  \\
@@
 201635569.01 & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.043$ & $0.06$ & $0.043$ & Candidate  \\
- \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.856$  & \color{red}  $0.142$  & \color{red}  $1.6\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP\\
+ \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.856$  & \color{red}  $0.142$  & \color{red}  $1.6\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP \\
 201702477.01 & $0.70$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.0\times10^{-3}$ & $0.06$ & $4.0\times10^{-3}$ & Planet  \\
@@
 201754305.02 & $0.38$ &  - & $1.9\times10^{-3}$ & $< 10^{-4}$ & $1.7\times10^{-3}$ & $0.22$ & $3.6\times10^{-3}$ & Planet  \\
- \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.935$  & \color{red}  $0.063$  & \color{red}  $3.2\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP\\
+ \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.935$  & \color{red}  $0.063$  & \color{red}  $3.2\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP \\
 201828749.01 & $0.39$ &  Y & $2.6\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $2.6\times10^{-3}$ & Candidate\tablenotemark{a}  \\
@@
  \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $2.8\times10^{-4}$  & \color{red}  $0.07$  & \color{red}  $2.9\times10^{-4}$  & \color{red}  FP\tablenotemark{b}
- &
+
 \enddata

### 2015-03-26 fpp/write_fpptable.py

@@ -49,7 +49,11 @@ def format_line(line, fpp, force_fp=False):
             if m:
                 newline += r' \color{red} ' + m.group(1) + '\\\\\n'
             else:
-                newline += r' \color{red} ' + v + ' &'
+                #hack to fix last line.
+                if re.search('201929294',newline) and re.search('FP',v):
+                    newline += r' \color{red} ' + v 
+                else:
+                    newline += r' \color{red} ' + v + ' &'
         
     return newline
         
@@ -106,24 +110,24 @@ for f in folders:
     line += '{} & '.format(prob_entry(FPP)) #FPP
     FPP = float(FPP)
     if cand_name in FP_OVERRIDE:
-        disp = 'FP'
+        disp = 'FP '
         if cand_name in ['201555883.01', '201929294.01']:
-            disp = r'FP\tablenotemark{b}'
+            disp = r'FP\tablenotemark{b} '
     else:
         if FPP < 0.01:
             if cand_name in CAND_OVERRIDE:
-                disp = r'Candidate\tablenotemark{a}'
+                disp = r'Candidate\tablenotemark{a} '
             else:
-                disp = 'Planet'
+                disp = 'Planet '
         elif FPP > 0.9:
-            disp = 'FP'
+            disp = 'FP '
         else:
-            disp = 'Candidate' 
+            disp = 'Candidate ' 
 
         if epic_id==201505350:
-            disp = r'Planet\tablenotemark{d}'
+            disp = r'Planet\tablenotemark{d} '
         if epic_id==201367065:
-            disp = r'Planet\tablenotemark{c}'
+            disp = r'Planet\tablenotemark{c} '
     line += '{} '.format(disp)  #Disposition
     if f != folders[-1]:
         line += '\\\\'

### 2015-03-26 table_fpp.tex
fpp table edits

@@
 out of abundance of caution due
-to secondary star detection in or near photometric aperture.  Most of these we do anticipate to be validated once the specific false positive scenarios are considered.}
+to secondary star detection in or near photometric aperture.}
 \tablenotetext{b}{Declared a false positive due to noise modeling systematics (see \S\ref{sec:systematics}).}

### 2015-03-26 fpp/write_fpptable.py

@@ -155,7 +155,7 @@ below 1\% threshold.}
 \tablenotetext{3}{Integrated planet occurrence rate assumed between 0.7$\times$ and 1.3$\times$ the candidate radius}
 \tablenotetext{a}{Despite low FPP, returned to candidate status 
 out of abundance of caution due
-to secondary star detection in or near photometric aperture.  Most of these we do anticipate to be validated once the specific false positive scenarios are considered.}
+to secondary star detection in or near photometric aperture.}
 \tablenotetext{b}{Declared a false positive due to noise modeling systematics (see \S\ref{sec:systematics}).}
 \tablenotetext{c}{Identified as planets by \citet{Crossfield15}.}
 \tablenotetext{d}{Identified as planets by \citet{Armstrong15b}.}

### 2015-03-26 ms.tex
FP table updates
numbers changed

@@
 
-\newcommand{\Nfp}{4}
-\newcommand{\Nvalidated}{22} %16 without contrast curves
-\newcommand{\Nlimbo}{10} %adds up to 36
+\newcommand{\Nfp}{5}
+\newcommand{\Nvalidated}{13} 
+\newcommand{\Nrecandidate}{7}
+\newcommand{\Nlimbo}{11} %adds up to 36
 
@@
 Such an effect may be the result of the Dartmouth model reliance on BT-Settl
-atmospheres, which have been shown to predict near-IR colors that are too blue
+atmospheres, which are based on incomplete molecular line lists and
+have been shown to predict near-IR colors that are too blue
 \citep{Thompson14}.
@@
 MCMC chains with photometric errors inflated artificially by a factor of three.
+The observed photometric parameters are then consistent with spectroscopically-derived
+parameters for stars with published spectra, and consistent with typical uncertainties
+from photometric data \citep[e.g.][]{Huber14}.
 We provide full chains using both inflated and un-inflated
@@
 
-\subsection{SpeX Spectroscopy}
+\subsection{SNIFS and SpeX Spectroscopy}
 \label{Spexobs}
@@
 possible for an eclipsing binary star to masquerade as a transiting
-planet if (a) it is a highly grazing eclipse, or (b) the binary system
+planet. 
+There are many scenarios which can cause an astrophysical false positive.
+The most common scenarios are if (a) it is a highly grazing eclipse, or (b) the binary system
 shares a photometric aperture with a significantly brighter star, 
@@
 Regardless of which star this object transits, the object is planet-sized.
-Given that small planets are significantly more common than large planets, it is more likely
-that the planet is orbiting the brighter star, and our parameters listed in Table 3 reflect this
-likelihood. If the planet is truly orbiting the fainter star, then it has a larger radius than is
-listed in this table.
+In Table 3, we assume the planet is orbiting the larger star. 
+If the planet is truly orbiting the fainter star, then its radius must be larger than is listed to 
+account for the observed transit depth.
 
@@
 observations would be on the order of km s$^{-1}$.
-Therefore, the transiting object must be planetary in nature.
+Therefore, we can rule out any stellar-mass companions that would be able
+to create this transit signal.
 
@@
 \subsection{Two Candidates, One Ephemeris}
+\label{sec:ephemmatch}
 

### 2015-03-26 ms.tex

@@
 uncertainties induced by the systematic model.
-Therefore, any uncertainties in the systematics can be propogated into uncertainties in
+Therefore, any uncertainties in the systematics can be propagated into uncertainties in
 detected planet parameters, instead of assuming the systematics are understood perfectly.
@@
 is not detected: there is no enforced upper limit on the allowed planet radius.
-The authors intentionally make no effort to separate astrophysical false positives from
-true transiting planets, similar to the \kep\ ``objects of interest.''
+The authors intentionally make no effort to separate true transiting planets from 
+astrophysical events that mimic the appearance of transits, such as an eclipsing 
+binary with a high mass ratio, similar to the \kep\ team's list of ``objects of interest.''
 

### 2015-03-26 ms.tex
tdm archival edit

@@
 of the Hale Telescope at $2$ $\mu$m, but nonzero.  
-We can rule out the possibility of such chance alignments with
-archival imaging data.
-
-For all targets with AO, we can confirm the planetary nature of the signal
-without this extra step, but we include it for EPIC 201912552, considering
+While the \texttt{vespa} calculations quantify this probability for
+this to occur, we can also rule out the possibility of such
+chance alignments, down to a certain contrast, with archival imaging data.
+
+We include this extra analysis step for EPIC 201912552, considering
 the additional follow-up this target may warrant.
@@
 nearly $90^\circ$ and the phase $\varpi + \theta \approx \pi/2$ or $3\pi/2$.
-While we cannot fully rule out this possibility, such an alignment is unlikely
-to occur and unable to cause enough dilution to call the planetary
-nature of this signal into question.
+While we cannot fully rule out this possibility, the \texttt{vespa}
+calculations confirm that its probability is negligibly small.
 

### 2015-03-26 ms.tex
background star text

@@
 
-To investigate the possibility that such wide companions exist,
-we query the ninth data release of the Sloan Digital Sky Survey
-\citep[SDSS DR9,][]{Ahn12}.
-For each target, we return
-all stars within 12\arcsec\ with $\Delta r < 8$ relative to each object
-of interest.
-Of the 31 stars in our sample, four have such a companion.
-Unlike the original \kep\ field, the field for \KT\ \Ci\ is
-well out of the galactic plane, so the rate of giant, distant background
-stars is significantly lower.
-We include all potential contaminants in Table 5.
-
-In Table 5, the ``maximum depth'' column represents
-the maximum observed ``transit'' depth if the transit were actually caused
-by a total eclipse of the hypothetical background binary system, inducing
-a 50\% flux decrement in the background star's apparent brightness.
-
-For EPIC 201465501 and 201779067, the observed transit depth is
-larger than each of these values, so we reject the possibility that
-these events could be the eclipses of the background binaries detected
-here.
-
-For EPIC 201546283, the observed transit depth is nearly identical to
-the maximum false positive depth.
-The photometry for this potential contaminant is consistent with that
-of an M3V star; for this object to cause the observed eclipse it must
-be a total eclipse of two M3V stars.
-However, in that case, the observed event would be exactly V-shaped,
-with second and third contact occurring simultaneously.
-Since the transit is not V-shaped, it must be the result of
-a relatively small body passing in front of a relatively large body.
-Therefore, it cannot be caused by this observed background dwarf star.
-
-For EPIC 201295312, the transit depth is significantly shallower than
-the maximum false positive depth, so we cannot immediately
-reject the hypothesis that the transit is actually a false positive
-induced by a background eclipsing binary.
-However, from the transit shape alone we can place a FPP of this
-system of $1.1 \times 10^{-4}$.
+To investigate the possibility that such wide companions exist, we
+query the ninth data release of the Sloan Digital Sky Survey
+\citep[SDSS DR9,][]{Ahn12} for all stars within 25\arcsec\ with
+$\Delta r < 8$ relative to each object of interest.  
+Each such companion star has a ``maximum depth'' that it could cause
+as a diluted ``transit'' signal, corresponding to a total eclipse 
+of the hypothetical 
+background binary system, inducing a 50\% flux decrement in the 
+background star's apparent brightness.
+Table 5 lists the 11 such stars (plus one detected in AO imaging),
+whose maximum depth is at least as deep 
+as the observed transit depth, thus making them possible contaminants.
+
+The photometric apertures used to detect these candidates range in radius from
+$10\farcs0$ to $19\farcs9$.  In order to be a plausible contaminant,
+any companion star must
+be either within this aperture or just outside but bright
+enough for signficant flux to leak in.  
+Evaluating each of the systems listed in Table 5, we judge that we cannot yet
+rule out contamination as a potential source of the transit signal for four 
+candidates: 201295312.01, 201403446.01, 201546283.01, 201828749.01.  Despite receiving
+low FPP scores from \texttt{vespa}, we list these systems as candidates in
+Table 4, rather than planets.  Further updates to the \texttt{vespa} code 
+will allow consideration of ``specific'' false positive scenarios; that is, 
+scenarios that correspond to actually detected stars such as these, rather than 
+hypothetical background or bound companions.
+
+The candidates with identified companions that we judge to not be plausible 
+sources of potential contamination are the following:
+\begin{itemize}
+
+\item 201546283.01--- For this system, the ``maximum depth// is nearly 
+identical to the observed transit depth, which would require a perfectly
+V-shaped eclipse to explain.  As this is not the case (see Figure 2), 
+this signal cannot
+be caused by contamination from this star.
+
+\item 201629650.01--- The companion to this star is $17\farcs3$ from
+the EPIC target.  As this is outside the aperture 
+(radius $15\farcs9$) and the background star is not particularly bright, 
+we rule out contamination for this system.
+
+\item 201702477.01--- The companion to this star is $12\farcs15$ from the
+EPIC target, and the aperture size is $10\farcs0$.  In addition,
+the maximum depth in this system is almost identical to the transit depth.
+For these two reasons we rule out contamination in this case.
+
+\end{itemize}
 
 SDSS is 95\% complete at $r=22.2$ and the telescope has a point
-spread function of $1\farcs4$. In all cases except the four above, we
-treat the SDSS data as providing a contrast curve at wide separations
+spread function of $1\farcs4$. 
+For the purposes of the \texttt{vespa} calculation, we thus
+treat nondetection in SDSS data as providing a contrast curve at 
+wide separations
 down to a limiting magnitude of $r=22.2$.

### 2015-03-26 ms.tex
bg table notes

--- 2015-03-26 ms.tex
@@
 transit parameters to calculate false positive probabilities.
-In \textsection5, we discuss potentially interesting systems.
+In \textsection5, we discuss potentially interesting systems, including a mini-Neptune
+orbiting an M dwarf which receives a similar insolation to the Earth.
 In \textsection6, we summarize and discuss our results.
@@
 
-As has been well known from the early days of transit searches, it is
-possible for an eclipsing binary star to masquerade as a transiting
-planet. 
-There are many scenarios which can cause an astrophysical false positive.
+There are many scenarios which can cause an astrophysical false positive,
+where an eclipsing binary star masquerades as a transiting planet.
 The most common scenarios are if (a) it is a highly grazing eclipse, or (b) the binary system
@@
 resulting in a diluted eclipse depth.
-When possible, such astrophsycial false positive scenarios are traditionally
+When possible, such astrophyscial false positive scenarios are traditionally
 ruled out by detailed follow-up observations, often a combination of
@@
 \citep[SDSS DR9,][]{Ahn12}.
-For each target, we return
-all stars within 12\arcsec\ with $\Delta r < 8$ relative to each object
-of interest.
-Of the 31 stars in our sample, four have such a companion.
+For each target, from the depth of the observed transit we determine how
+bright a background object must be to cause the event if the background
+object were an equal mass totally-eclipsing binary.
+We then search for all stars within 25\arcsec\ that are within this brightness
+limit relative to the candidate host star.
+All apertures we use in our \KT\ analysis are smaller than 20\arcsec\ so this
+search should encompass the region where possible background 
+contaminants could reside.
+Of the 31 stars in our sample, eleven have such a companion.
+
 Unlike the original \kep\ field, the field for \KT\ \Ci\ is
@@
 We include all potential contaminants in Table 5.
+We validate or eliminate each of these as a possibility based on the transit shape.
+For example, the events near EPIC 201546283 could only be caused by a 
+background binary if the background object was a completely-eclipsing system
+(so that the eclipse depth was $50\%$). 
+In this case, the transit would be perfectly V-shaped.
+Since it is not, we can rule out the possibility this background object causes
+the transit event.
 
@@
 
-SDSS is 95\% complete at $r=22.2$ and the telescope has a point
+SDSS is 95\% complete at $r=22.2$ mag and the telescope has a point
 spread function of $1\farcs4$. In all cases except the four above, we
 treat the SDSS data as providing a contrast curve at wide separations
-down to a limiting magnitude of $r=22.2$.
+down to a limiting magnitude of $r=22.2$ mag.
 
@@
 
-Unlike GJ\,1214b, EPIC 201912552b is not highly irradiated.
+The planet is slightly smaller than GJ\,1214b, but unlike that planet,
+EPIC 201912552b is not highly irradiated.
 Instead, it is at a reduced semimajor axis \ars$ = 84.3 \pm 9.5$.

### 2015-03-26 ms.tex
more section 4 edits

--- 2015-03-26 ms.tex
@@
 \texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
-a new general-purpose implementation of the \citet{Morton12} procedure,
+a new publicly available, general-purpose implementation 
+of the \citet{Morton12} procedure,
 to calculate false positive probabilities (FPPs) for each of these
@@
 \begin{itemize}
-\item A chance-aligned eclipsing binary system may reside anywhere within
-the photometric aperture of the target star.
+\item A chance-aligned eclipsing binary system may reside anywhere inside
+or within one pixel of the photometric aperture of the target star.
 \item The maximum allowed depth of a potential secondary eclipse event
@@
 these we consider to be likely false positives.
-On the other hand, we find that \Nvalidated\ candidates
-have FPP $<$ 1\%; we consider these to be statistically validated planets.
-Of these, 18 are validated for the first time.
-The remaining \Nlimbo\ candidates have FPPs neither high enough to discard
-nor low enough to securely validate.
-
-We emphasize that the majority of these planets were validated based
-solely on the transit signal, with no need for follow-up imaging.  This
-demonstrates the utility of \texttt{vespa} analysis, which will be
+On the other hand, we find that 21 candidates
+have FPP $<$ 1\%.  
+Two of these we find to be caused by systematics
+in the transit search noise model (details in \S\ref{sec:systematics}), and
+so we identify those as false positives.  
+Four more of these 21 might plausibly be caused by 
+contamination by detected stellar companions within the photometric apertures 
+(see \S\ref{sec:background}), so we keep these as candidates.
+
+This leaves 15 candidates that we statistically validate as planets, plus three
+additional planets that \texttt{vespa} does not validate but have been previously
+identified in the literature \citep{Crossfield15, Armstrong15b}.  
+So in total, of the 36 candidates, 18 are secure planets, 
+14 of which we here validate for the first time.
+
+We emphasize that the majority of these validations rely
+solely on the transit photometry and SDSS data, with no need for follow-up imaging.  This
+demonstrates the utility of the \texttt{vespa} tool, which will be
 crucial to interpreting future candidates detected by \KT, TESS, and PLATO
 and prioritizing follow-up observing efforts.
-We show these transit signals as Fig. \ref{fig:transits}.
+We show the transit signals in Fig. \ref{fig:transits}.
 
@@
 
-We note that we validate 201828749 as a true transiting planet, despite the presence of this binary
-companion.
-From the transit shape, we can rule out the possibility this system is a background eclipsing
-binary.
-Regardless of which star this object transits, the object is planet-sized.
-In Table 3, we assume the planet is orbiting the larger star. 
-If the planet is truly orbiting the fainter star, then its radius must be larger than is listed to 
-account for the observed transit depth.
+%We note that we validate 201828749 as a true transiting planet, despite the presence of this binary
+%companion.
+%From the transit shape, we can rule out the possibility this system is a background eclipsing
+%binary.
+%Regardless of which star this object transits, the object is planet-sized.
+%In Table 3, we assume the planet is orbiting the larger star. 
+%If the planet is truly orbiting the fainter star, then its radius must be larger than is listed to 
+%account for the observed transit depth.
 
@@
 \subsection{Known Background Stars}
+\label{sec:background}
 The PHARO AO system has a field of view of 25 arcseconds.

### 2015-03-26 ms.tex
typo

@@
 
-\item 201546283.01--- For this system, the ``maximum depth// is nearly 
+\item 201546283.01--- For this system, the ``maximum depth'' is nearly 
 identical to the observed transit depth, which would require a perfectly

### 2015-03-26 ms.tex

@@
 \newcommand{\Nfp}{5}
-\newcommand{\Nvalidated}{13} 
-\newcommand{\Nrecandidate}{7}
-\newcommand{\Nlimbo}{11} %adds up to 36
+\newcommand{\Nvalidated}{18} 
+\newcommand{\Nlimbo}{13} %adds up to 36
 
@@
 adaptive optics imaging with an automated transit analysis scheme to validate
-\Nvalidated\ candidates as planets and identify \Nfp\ candidates as likely false positives.
+\Nvalidated\ candidates as planets
+and identify \Nfp\ candidates as likely false positives.
 Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
@@
 orbital period of 33 days.
-We also present \texttt{vespa}, a new general-purpose implementation
+We also present two new open-source software packages that enabled this analysis:  
+\texttt{isochrones}, a flexible tool for fitting theoretical stellar 
+models to observational data to determine stellar properties; and 
+\texttt{vespa}, a new general-purpose implementation
 of the \citet{Morton12} procedure to calculate false positive probabilities
@@
 To convert the observed photometric data into physical properties for each
-star, we used the publicly available \texttt{isochrones} Python module\footnote{
+star, we used the new publicly available \texttt{isochrones} Python module\footnote{
 \url{http://github.com/timothydmorton/isochrones}}, a general-purpose

### 2015-03-26 ms.tex
added isochrones to abstract

@@
 To convert the observed photometric data into physical properties for each
-star, we used the new publicly available \texttt{isochrones} Python module\footnote{
+star, we used the publicly available \texttt{isochrones} Python module\footnote{
 \url{http://github.com/timothydmorton/isochrones}}, a general-purpose

### 2015-03-26 ms.tex

--- 2015-03-26 ms.tex
@@
 
-To investigate the possibility that such wide companions exist, we
-query the ninth data release of the Sloan Digital Sky Survey
-\citep[SDSS DR9,][]{Ahn12} for all stars within 25\arcsec\ with
-$\Delta r < 8$ relative to each object of interest.  
-Each such companion star has a ``maximum depth'' that it could cause
-as a diluted ``transit'' signal, corresponding to a total eclipse 
-of the hypothetical 
-background binary system, inducing a 50\% flux decrement in the 
-background star's apparent brightness.
-Table 5 lists the 11 such stars (plus one detected in AO imaging),
-whose maximum depth is at least as deep 
-as the observed transit depth, thus making them possible contaminants.
+To investigate the possibility that such wide companions exist,
+we query the ninth data release of the Sloan Digital Sky Survey
+\citep[SDSS DR9,][]{Ahn12}.
+For each target, from the depth of the observed transit we determine how
+bright a background object must be to cause the event if the background
+object were an equal mass totally-eclipsing binary.
+We then search for all stars within 25\arcsec\ that are within this brightness
+limit relative to the candidate host star.
+All apertures we use in our \KT\ analysis are smaller than 20\arcsec\ so this
+search should encompass the region where possible background 
+contaminants could reside.
+Of the 31 stars in our sample, eleven have such a companion, plus one
+detected in AO imaging.
+
+Unlike the original \kep\ field, the field for \KT\ \Ci\ is
+well out of the galactic plane, so the rate of giant, distant background
+stars is significantly lower.
+We include all potential contaminants in Table 5.
+We validate or eliminate each of these as a possibility based on the transit shape.
+For example, the events near EPIC 201546283 could only be caused by a 
+background binary if the background object was a completely-eclipsing system
+(so that the eclipse depth was $50\%$). 
+In this case, the transit would be perfectly V-shaped.
+Since it is not, we can rule out the possibility this background object causes
+the transit event.
+
+In Table 5, the ``maximum depth'' column represents
+the maximum observed ``transit'' depth if the transit were actually caused
+by a total eclipse of the hypothetical background binary system, inducing
+a 50\% flux decrement in the background star's apparent brightness.
 
@@
 
-SDSS is 95\% complete at $r=22.2$ and the telescope has a point
+SDSS is 95\% complete at $r=22.2$ mag and the telescope has a point
 spread function of $1\farcs4$. 
@@
 wide separations
-down to a limiting magnitude of $r=22.2$.
+down to a limiting magnitude of $r=22.2$ mag.
 

### 2015-03-26 ms.tex

@@
 We statistically validate \Nvalidated\ of the 36 candidates as bona fide planets, and we
-identify four as false positives.
-Of these planets, 4 have been previously validated in other works, while 17 are
+identify \Nfp\ as false positives.
+Of these planets, 4 have been previously validated in other works, while 14 are
 validated here for the first time.
-The 11 systems not validated as planets or false positives remain as planet candidates.
+The systems not validated as planets or false positives remain as planet candidates.
+
+Enabling much of this analysis are two new open-source Python packages: 
+\texttt{isochrones}\footnote{\url{http://github.com/timothydmorton/isochrones}}, 
+which we use to infer posteriors on physical stellar properties based
+on fitting theoretical stellar models to observed data; and \texttt{vespa}\footnote{
+\url{http://github.com/timothydmorton/vespa}}, a
+new implementation of the \citet{Morton12} transit false positive analysis scheme.  
+Both of these packages will continue to be useful in future analysis of transit candidates
+where comprehensive follow-up observations may be unavailable.
 

### 2015-03-26 ms.tex
tdm

@@
 transit parameters to calculate false positive probabilities.
-In \textsection5, we discuss potentially interesting systems, including a mini-Neptune
-orbiting an M dwarf which receives a similar insolation to the Earth.
+In \textsection5, we discuss potentially interesting systems.
 In \textsection6, we summarize and discuss our results.
@@
 
-There are many scenarios which can cause an astrophysical false positive,
-where an eclipsing binary star masquerades as a transiting planet.
+As has been well known from the early days of transit searches, it is
+possible for an eclipsing binary star to masquerade as a transiting
+planet. 
+There are many scenarios which can cause an astrophysical false positive.
 The most common scenarios are if (a) it is a highly grazing eclipse, or (b) the binary system
@@
 resulting in a diluted eclipse depth.
-When possible, such astrophyscial false positive scenarios are traditionally
+When possible, such astrophsycial false positive scenarios are traditionally
 ruled out by detailed follow-up observations, often a combination of
@@
 
-To investigate the possibility that such wide companions exist,
-we query the ninth data release of the Sloan Digital Sky Survey
-\citep[SDSS DR9,][]{Ahn12}.
-For each target, from the depth of the observed transit we determine how
-bright a background object must be to cause the event if the background
-object were an equal mass totally-eclipsing binary.
-We then search for all stars within 25\arcsec\ that are within this brightness
-limit relative to the candidate host star.
-All apertures we use in our \KT\ analysis are smaller than 20\arcsec\ so this
-search should encompass the region where possible background 
-contaminants could reside.
-Of the 31 stars in our sample, eleven have such a companion, plus one
-detected in AO imaging.
-
-Unlike the original \kep\ field, the field for \KT\ \Ci\ is
-well out of the galactic plane, so the rate of giant, distant background
-stars is significantly lower.
-We include all potential contaminants in Table 5.
-We validate or eliminate each of these as a possibility based on the transit shape.
-For example, the events near EPIC 201546283 could only be caused by a 
-background binary if the background object was a completely-eclipsing system
-(so that the eclipse depth was $50\%$). 
-In this case, the transit would be perfectly V-shaped.
-Since it is not, we can rule out the possibility this background object causes
-the transit event.
-
-In Table 5, the ``maximum depth'' column represents
-the maximum observed ``transit'' depth if the transit were actually caused
-by a total eclipse of the hypothetical background binary system, inducing
-a 50\% flux decrement in the background star's apparent brightness.
+To investigate the possibility that such wide companions exist, we
+query the ninth data release of the Sloan Digital Sky Survey
+\citep[SDSS DR9,][]{Ahn12} for all stars within 25\arcsec\ with
+$\Delta r < 8$ relative to each object of interest.  
+Each such companion star has a ``maximum depth'' that it could cause
+as a diluted ``transit'' signal, corresponding to a total eclipse 
+of the hypothetical 
+background binary system, inducing a 50\% flux decrement in the 
+background star's apparent brightness.
+Table 5 lists the 11 such stars (plus one detected in AO imaging),
+whose maximum depth is at least as deep 
+as the observed transit depth, thus making them possible contaminants.
 
@@
 
-SDSS is 95\% complete at $r=22.2$ mag and the telescope has a point
+SDSS is 95\% complete at $r=22.2$ and the telescope has a point
 spread function of $1\farcs4$. 
@@
 wide separations
-down to a limiting magnitude of $r=22.2$ mag.
+down to a limiting magnitude of $r=22.2$.
 
@@
 
-The planet is slightly smaller than GJ\,1214b, but unlike that planet,
-EPIC 201912552b is not highly irradiated.
+Unlike GJ\,1214b, EPIC 201912552b is not highly irradiated.
 Instead, it is at a reduced semimajor axis \ars$ = 84.3 \pm 9.5$.

### 2015-03-26 ms.tex
some systematic words

--- 2015-03-26 ms.tex
@@
 to calculate false positive probabilities (FPPs) for each of these
-\KT\ candidates.  We impose the following constraints on false positive
-scenarios:
+\KT\ candidates.  
+The following constraints on false positive
+scenarios are imposed:
 \begin{itemize}
@@
 
-We find that four of the presented candidates have FPP $>$90\%;
-these we consider to be likely false positives.
-On the other hand, we find that 21 candidates
+Four of the presented candidates have FPP $>$90\%;
+these are considered to be likely false positives.
+On the other hand, 21 candidates
 have FPP $<$ 1\%.  
-Two of these we find to be caused by systematics
+Two of these are found to be caused by systematics
 in the transit search noise model (details in \S\ref{sec:systematics}), and
@@
 
-\subsection{Two Candidates, One Ephemeris}
-\label{sec:ephemmatch}
-
-EPIC 201569483 was originally listed in \paperit\ as a planet candidate.
-The transit events have a depth of approximately 7\%.
-In this work, we conclude this system is likely a false
-positive, with an FPP of 0.560.
-The most likely scenario is that of an eclipsing binary, which would
-not be surprising given the transit depth.
-
-It was later realized that EPIC 201555883 has a period, time of transit,
-and transit duration consistent with EPIC 201569483.
+\subsection{Non-Astrophysical False Positives}
+\label{sec:systematics}
+
+The method of \paperit assumes that all variability in the light curves are
+caused by either the motion of \KT, in which case the variability is shared
+by all stars, or transits of planets, in which case the variability is intrinsic 
+to only one star.
+This assumption breaks down for extremely spotted stars where the 
+astrophysical variability is larger than the instrumental
+magnitude.
+In that regime, the starspot modulations can be incorrectly fit by the 
+systematic model, causing spurious transits to appear.
+This appears to be the case with EPIC 201929294, which has 
+coherent starspots that appear to have the same rotation period as the
+transit period reported previously.
+Because the starspots are so periodic and coherent, these spurious 
+transits were falsely identified as a planet candidate; we consider that 
+system a false positive in this work.
+
+The planet candidate possibly orbiting EPIC 201555883 has a period, 
+time of transit, and transit duration consistent with EPIC 201569483.
 Such effects are not uncommon in \kep\ data.
-\citet{Batalha13} found $\sim 25$ planet candidates to be false positives
-based on matching ephemerides between candidates.
-In that paper, the authors limited their search to candidates within
-$20\arcsec$ of other objects of interest.
-\citet{Coughlin14} expanded on this method, identifying 685 KOIs as false
-positives and outlining four physical reasons why these anomalies may occur.
-As those authors explain, period-matching candidates can be the result of
-direct PRF contamination, antipodal reflection across the Schmidt telescope,
-CCD crosstalk across a \kep\ module, or ``column anomalies'' across one column
-of the CCD.
-Typically, the instrumental false positive event appears considerably
-shallower than the true astrophysical event.
-
+\citet{Coughlin14} identify 685 KOIs as false
+positives and outline four physical reasons why these anomalies may occur.
 EPIC 201555883 is a unique case in that it does not appear to fall under any
@@
 eclipsing binaries, and even transiting planets.
-
-Formally, our false positive validation scheme gives a FPP of $9.5 \times
-10^{-4}$, reaching our threshold for planet validation.
-Since \texttt{vespa} does not account for the possibility of instrumental
-artifacts in the data, this number represents only the \textit{astrophysical}
-false positive probability.
-In this case, given the period matching between the two events, we refrain
-from declaring this system a planet.
-However, since we cannot explain how such a false positive would occur as a
-result of an instrumental systematic in the \kep\ telescope, we also refrain
-from declaring this target a definite false positive.
-Additional follow-up observations of both targets are clearly warranted to
-better understand a possible systematic that has not previously been observed
-in either \kep\ or \KT.
+In this specific case, the s
 
@@
 mini-Neptune sized planets.
-Like in the \kep\ field, the false positive rate we measure for the multiple planet sample
-here ($0/10$) is lower than for the single systems \citep{Lissauer12, Rowe14}.
 

### 2015-03-26 ms.tex
some systematic words

@@
 
-The method of \paperit assumes that all variability in the light curves are
+The method of \paperit\ assumes that all variability in the light curves are
 caused by either the motion of \KT, in which case the variability is shared
@@
 systematic mechanism.
+
 \paperit\ modeled the systematic effects in the \KT\ light curves using a
@@
 eclipsing binaries, and even transiting planets.
-In this specific case, the s
+Again, this star has significant variability caused by starspots. 
+In this case, the fitting procedure tries to account for stellar variability using
+the eigen light curves.
+This overfit gives undue weight to eigen light curves that include the transits
+of EPIC 201569483, causing this spurious transit to occur.
+Again, we consider this system to be a false positive.
+
+The problem of over-fitting stellar variability using eigen light curves can be
+solved by adding a stellar activity model to our fitting procedure.
+In this case, the spacecraft motion could be fit simultaneously with a model
+of starspot modulation, astroseismic oscillations, and planet transits.
+Such a model is currently under development (Angus et al. \textit{in prep}).
 

### 2015-03-26 ms.tex
intro stuff

@@
 
-\newcommand{\Nfp}{5}
+\newcommand{\Nfp}{6}
 \newcommand{\Nvalidated}{18} 
-\newcommand{\Nlimbo}{13} %adds up to 36
+\newcommand{\Nlimbo}{12} %adds up to 36
 
@@
 
-There has been considerable effort to recover these planetary signals.
-\citet{Vanderburg14} extract aperture photometry and de-correlate with image centroid
-position to calibrate the photometry as a function of position.
-These data were used to confirm the first planet discovered in \KT\ \citep{Vanderburg15}.
-A similar technique was employed by \citet{Armstrong15a} to identify potential eclipsing
-binary systems and to identify a transiting system near a 3:2 period commensurability
-\citep{Armstrong15b}.
-\citet{Aigrain15} use a Gaussian Process model for the measured
-flux, with pointing measurements as the inputs, and then ``de-trend'' the data with that model.
-\citet{Crossfield15} apply a very similar method, which was used to detect the first 
-multi-planet system in \KT\ data.
-
+There has been considerable effort to recover these planetary signals, and to date six
+planets have been confirmed in the \KT\ data 
+\citep{Vanderburg15, Crossfield15, Armstrong15b}.
 What is common to all of these methods are that removal of systematics is considered a
@@
 In this paper, we present stellar and planetary parameters for each system.
-Given these parameters and the transit data, as well as archival imaging, ground-based
+We also analyze the false positive probability of each system using \texttt{vespa},
+a new publicly available, general-purpose implementation 
+of the \citet{Morton12} procedure
+to calculate false positive probabilities (FPPs) for transiting planets.
+Through this analysis, as well as archival imaging, ground-based
 seeing-limited survey data, and adaptive optics imaging, we are able to confirm
@@
 level. 
-Additionally, we identify four systems as false positives.
+Additionally, we identify six systems as false positives.
 
@@
 these are considered to be likely false positives.
-On the other hand, 21 candidates
+On the other hand, 20 candidates
 have FPP $<$ 1\%.  

### 2015-03-26 ms.tex
a few small changes and fixing numbers

--- 2015-03-26 ms.tex
@@
 
-\newcommand{\Nfp}{5}
+\newcommand{\Nfp}{6}
 \newcommand{\Nvalidated}{18}
-\newcommand{\Nlimbo}{13} %adds up to 36
+\newcommand{\Nlimbo}{12} %adds up to 36
 
@@
 \newcommand{\nyu}{4}
+\newcommand{\cds}{5}
 \newcommand{\princeton}{3}
-\newcommand{\mpia}{5}
-\newcommand{\cds}{6}
+\newcommand{\mpia}{6}
 \newcommand{\jcpa}{7}
@@
 Timothy~D.~Morton\altaffilmark{\princeton},
-Daniel~Foreman-Mackey\altaffilmark{\nyu},
+Daniel~Foreman-Mackey\altaffilmark{\nyu,\cds},
 % The Benefactors
@@
                           4 Washington Place, New York, NY, 10003, USA}
-\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
-                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
 \altaffiltext{\cds}      {Center for Data Science,
@@
                           726 Broadway, 7th Floor, New York, NY, 10003, USA}
+\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
+                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
 \altaffiltext{\jcpa} {Caltech Joint Center for Planetary Astronomy Fellow}
@@
 level.
-Additionally, we identify four systems as false positives.
+Additionally, we identify six systems as false positives.
 
@@
 the parameters of the systematics model.
-To incorporate the stellar measurements, we approximate the measurements as a
-three-dimensional Gaussian in mass, radius, and effective temperature.
+To incorporate the stellar measurements, we approximate the constraints using
+a three-dimensional Gaussian in mass, radius, and effective temperature.
 

### 2015-03-26 ms.tex
touching up abstract

--- 2015-03-26 ms.tex
@@
 models to observational data to determine stellar properties; and 
-\texttt{vespa}, a new general-purpose implementation
-of the \citet{Morton12} procedure to calculate false positive probabilities
+\texttt{vespa}, a new general-purpose procedure to calculate false positive probabilities
 and statistically validate transiting exoplanets.

### 2015-03-26 ms.tex

@@
 models to observational data to determine stellar properties; and
-\texttt{vespa}, a new general-purpose implementation
-of the \citet{Morton12} procedure to calculate false positive probabilities
+\texttt{vespa}, a new general-purpose procedure to calculate false positive probabilities
 and statistically validate transiting exoplanets.

### 2015-03-26 ms.tex
number fix

--- 2015-03-26 ms.tex
@@
 these are considered to be likely false positives.
-On the other hand, 20 candidates
+On the other hand, 21 candidates
 have FPP $<$ 1\%.  
@@
 We emphasize that the majority of these validations rely
-solely on the transit photometry and SDSS data, with no need for follow-up imaging.  This
+solely on the transit photometry and SDSS data, with follow-up imaging only obtained for
+seven of the 31 targets.  This
 demonstrates the utility of the \texttt{vespa} tool, which will be

### 2015-03-26 ms.tex

--- 2015-03-26 ms.tex
@@
 these are considered to be likely false positives.
-On the other hand, 20 candidates
+On the other hand, 21 candidates
 have FPP $<$ 1\%.

### 2015-03-26 ms.tex
typo in photometry table label

--- 2015-03-26 ms.tex
@@
 \citep{Howell14}.
-Of our sample, two systems orbit stars with $K < 9$: EPIC 201367065 \citep{Crossfield15} and
+Of our sample, two systems orbit stars with $K < 9$ mag: EPIC 201367065 \citep{Crossfield15} and
 EPIC 201912552.
-An additional four targets orbit stars with $K <10$.
+An additional planet candidate may orbit EPIC 201828749, a star with $K = 9.93 \pm 0.03$ mag.
 These targets are ideal for ground-based followup and may be useful targets for Spitzer and

### 2015-03-26 ms.tex
typo
removing stray todo

@@
 There has been considerable effort to recover these planetary signals, and to date six
-planets have been confirmed in the \KT\ data
+planets have been confirmed orbiting three stars in the \KT\ data
 \citep{Vanderburg15, Crossfield15, Armstrong15b}.
@@
 \centerline{\includegraphics[width=1.0\textwidth]{f2}}
-\caption{\btmtodo{PLACEHOLDER, UPDATE. Needs transit models}.
-Phase-folded \KT\ photometry for all planet candidates analyzed in
+\caption{Phase-folded \KT\ photometry for all planet candidates analyzed in
 this paper.
@@
 rule out contamination as a potential source of the transit signal for four
-candidates: 201295312.01, 201403446.01, 201546283.01, 201828749.01.  Despite receiving
+candidates: 201295312.01, 201403446.01, 201546283.01, and 201828749.01.  
+Despite receiving
 low FPP scores from \texttt{vespa}, we list these systems as candidates in
@@
 \acknowledgements
-We thank Eric Agol (UW), Dan Huber (Sydney) and Jeff Coughlin (SETI) for
+We thank Roberto Sanchis-Ojeda (Berkeley), Dan Huber (Sydney) and 
+Jeff Coughlin (SETI) for
 conversations and suggestions which improved the quality of this manuscript.

### 2015-03-26 ms.tex
consistent figure references

--- 2015-03-26 ms.tex
@@
 These data are reported in Table 1, and a color-color diagram showing the
-$r-J, J-K$ colors of our candidates is included as Fig. \ref{fig:photometry}.
+$r-J, J-K$ colors of our candidates is included as Fig.~\ref{fig:photometry}.
 
@@
 and prioritizing follow-up observing efforts.
-We show the transit signals in Fig. \ref{fig:transits}.
+We show the transit signals in Figure~\ref{fig:transits}.
 
@@
 \centerline{\includegraphics[width=1.0\textwidth]{f2}}
-\caption{\btmtodo{PLACEHOLDER, UPDATE. Needs transit models}.
+\caption{%
 Phase-folded \KT\ photometry for all planet candidates analyzed in
@@
 
-Images for all systems AO data was obtained for is shown in Fig. \ref{Fig:AO},
+Images for all systems AO data was obtained for is shown in Figure~\ref{Fig:AO},
 while contrast curves showing the $5\sigma$ limits for detection
-as a function of orbital separation are given in Fig. \ref{Fig:CC}.
+as a function of orbital separation are given in Figure~\ref{Fig:CC}.
 
@@
 identical to the observed transit depth, which would require a perfectly
-V-shaped eclipse to explain.  As this is not the case (see Figure 2),
+V-shaped eclipse to explain.  As this is not the case (see Figure~2),
 this signal cannot
@@
 since the POSS I data were collected.
-As shown in Figure \ref{fig:archival}, we do not detect any targets at the
+As shown in Figure~\ref{fig:archival}, we do not detect any targets at the
 present-day location of EPIC 201912552 in either of the POSS surveys.
@@
 \subsection{Multiple Planet Systems}
-Five of the systems identified by \paperit\ are candidates to be multiply-transiting
-systems.
+Five of the systems reported by \paperit\ have more than one transiting
+candidate.
 One of these is EPIC 201367065, a three-planet system originally announced by

### 2015-03-26 ms.tex

@@
 \centerline{\includegraphics[width=1.0\textwidth]{f2}}
-\caption{%
-Phase-folded \KT\ photometry for all planet candidates analyzed in
+\caption{Phase-folded \KT\ photometry for all planet candidates analyzed in
 this paper.
@@
 rule out contamination as a potential source of the transit signal for four
-candidates: 201295312.01, 201403446.01, 201546283.01, 201828749.01.  Despite receiving
+candidates: 201295312.01, 201403446.01, 201546283.01, and 201828749.01.
+Despite receiving
 low FPP scores from \texttt{vespa}, we list these systems as candidates in
@@
 \acknowledgements
-We thank Eric Agol (UW), Dan Huber (Sydney) and Jeff Coughlin (SETI) for
+We thank Roberto Sanchis-Ojeda (Berkeley), Dan Huber (Sydney) and
+Jeff Coughlin (SETI) for
 conversations and suggestions which improved the quality of this manuscript.

### 2015-03-26 ms.tex
comma in abstract

--- 2015-03-26 ms.tex
@@
 \texttt{isochrones}, a flexible tool for fitting theoretical stellar
-models to observational data to determine stellar properties; and
+models to observational data to determine stellar properties, and
 \texttt{vespa}, a new general-purpose procedure to calculate false positive probabilities

### 2015-03-29 ms.tex
blah

@@
 
-\newcommand{\Nfp}{6}
-\newcommand{\Nvalidated}{18}
-\newcommand{\Nlimbo}{12} %adds up to 36
+\newcommand{\Nfp}{4}
+\newcommand{\Nvalidated}{21}
+\newcommand{\Nlimbo}{11} %adds to 36?  good.
 
@@
 \newcommand{\nyu}{4}
-\newcommand{\cds}{5}
 \newcommand{\princeton}{3}
-\newcommand{\mpia}{6}
+\newcommand{\mpia}{5}
+\newcommand{\cds}{6}
 \newcommand{\jcpa}{7}
@@
 Timothy~D.~Morton\altaffilmark{\princeton},
-Daniel~Foreman-Mackey\altaffilmark{\nyu,\cds},
+Daniel~Foreman-Mackey\altaffilmark{\nyu},
 % The Benefactors
@@
                           4 Washington Place, New York, NY, 10003, USA}
+\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
+                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
 \altaffiltext{\cds}      {Center for Data Science,
@@
                           726 Broadway, 7th Floor, New York, NY, 10003, USA}
-\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
-                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
 \altaffiltext{\jcpa} {Caltech Joint Center for Planetary Astronomy Fellow}
@@
 \begin{abstract}
-The extended \kep\ mission, \KT, is now providing photometry of new fields every
-three months in a search for transiting planets.
-In a recent study, Foreman-Mackey and collaborators presented a list of 36 planet
-candidates orbiting 31 stars in \KT\ \Ci.
-In this contribution, we present stellar and planetary properties for all systems.
-We combine ground-based seeing-limited survey data and
-adaptive optics imaging with an automated transit analysis scheme to validate
-\Nvalidated\ candidates as planets
-and identify \Nfp\ candidates as likely false positives.
+Recently, \paperit{} identified 36 planet candidates orbiting
+31 stars in \KT\ \Ci.
+In this paper, we present stellar and planetary properties for each
+candidate. 
+We combine ground-based seeing limited survey data and
+adaptive optics imaging with a detailed transit analysis scheme to validate
+\Nvalidated\ candidates as planets and identify \Nfp\ candidates as likely false positives.
 Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
@@
 orbital period of 33 days.
-We also present two new open-source software packages that enabled this analysis:
-\texttt{isochrones}, a flexible tool for fitting theoretical stellar
-models to observational data to determine stellar properties, and
-\texttt{vespa}, a new general-purpose procedure to calculate false positive probabilities
-and statistically validate transiting exoplanets.
+We also present \texttt{vespa}, a new general-purpose implementation
+of the \citet{Morton12} procedure to calculate false positive probabilities
+for \KT\ candidates.
 \end{abstract}
@@
 The fidelity of this sample is high: most of these planet candidates are truly planets
-\citep{Morton11b, Fressin13, Desert15}.
-The mechanical failure of two reaction wheels on the spacecraft led to a repurposing
+\citep{Morton11b, Fressin13}.
+The demise of two reaction wheels on the spacecraft led to a repurposing
 of the spacecraft into the \KT\ mission, in which the telescope points at
@@
 As a result, the detector drifts relative to the sky
-at the rate of $\sim 1\arcsec$ hr$^{-1}$, with rapid corrections due to thruster fires
+at the rate of $\sim 1\arcsec$ hr$^{-1}$, with rapid corrections
 approximately once every six hours.
@@
 
-There has been considerable effort to recover these planetary signals, and to date six
-planets have been confirmed orbiting three stars in the \KT\ data
-\citep{Vanderburg15, Crossfield15, Armstrong15b}.
+There has been considerable effort to recover these planetary signals.
+\citet{Vanderburg14} extract aperture photometry and de-correlate with image centroid
+position, ``correcting'' the data to ``remove'' the effects of the spacecraft motion.
+These data were used to confirm the first planet discovered in \KT\ \citep{Vanderburg15}.
+A similar technique was employed by \citet{Armstrong15a} to identify potential eclipsing
+binary systems and to identify a transiting system near a 3:2 period commensurability
+\citep{Armstrong15b}.
+\citet{Aigrain15} and \citet{Crossfield15} use a Gaussian Process model for the measured
+flux, with pointing measurements as the inputs, and then ``de-trend'' the data with that model.
+The latter of these detected the first multi-planet system in \KT\ data.
+
 What is common to all of these methods are that removal of systematics is considered a
@@
 uncertainties induced by the systematic model.
-Therefore, any uncertainties in the systematics can be propagated into uncertainties in
+Therefore, any uncertainties in the systematics can be propogated into uncertainties in
 detected planet parameters, instead of assuming the systematics are understood perfectly.
@@
 is not detected: there is no enforced upper limit on the allowed planet radius.
-The authors intentionally make no effort to separate true transiting planets from
-astrophysical events that mimic the appearance of transits, such as an eclipsing
-binary with a high mass ratio, similar to the \kep\ team's list of ``objects of interest.''
+The authors intentionally make no effort to separate astrophysical false positives from
+true transiting planets.
 
 In this paper, we present stellar and planetary parameters for each system.
-We also analyze the false positive probability of each system using \texttt{vespa},
-a new publicly available, general-purpose implementation
-of the \citet{Morton12} procedure
-to calculate false positive probabilities (FPPs) for transiting planets.
-Through this analysis, as well as archival imaging, ground-based
+Given these parameters and the transit data, as well as archival imaging, ground-based
 seeing-limited survey data, and adaptive optics imaging, we are able to confirm
 \Nvalidated\ of these systems as transiting planets at the 99\% confidence
-level.
-Additionally, we identify six systems as false positives.
+level. We also are able to confirm \Nfp\ of these systems as false positives.
 
@@
 and in the remaining two cases, the photometric uncertainity in $W4$ is at least an
-order of magnitude larger than those in $W1-W3$, so we do not use $W4$
-for any system.
+order of magnitude larger than those in $W1-W3$, so we neglect $W4$.
 These data are reported in Table 1, and a color-color diagram showing the
@@
 observed by \kep\ during the original
-mission (black), with our \KT\ \Ci\ planet candidates overlaid (red).
-Also included is the location of the Sun (yellow) and host stars of previously
-confirmed \KT\ planets (blue).
-90\% of our candidates have photometry consistent with later spectral
-types than the Sun.}
+mission (black), with our \KT\ \Ci\ planet candidates overlaid (fuchsia).
+Also included is the location of the Sun (yellow).
+Nearly all of our candidates have photometry consistent with later spectral
+types than G2.}
 \label{fig:photometry}
@@
 To convert the observed photometric data into physical properties for each
-star, we used the new publicly available \texttt{isochrones} Python module\footnote{
+star, we used the publicly available \texttt{isochrones} Python module\footnote{
 \url{http://github.com/timothydmorton/isochrones}}, a general-purpose
-interpolation tool for the fitting of stellar models to photometric or spectroscopic
-parameters.
+interpolation tool for stellar model grids.
 This software does trilinear interpolation in mass--age--\feh\ space for any
@@
 \label{eq:ischochronelhood}
-\ln \mathcal L(\boldsymbol{\theta}) \propto -\frac{1}{2} \displaystyle \sum_i \frac{\left(x_i -
+\ln \mathcal L(\boldsymbol{\theta}) = -\frac{1}{2} \displaystyle \sum_i \frac{\left(x_i -
   I_i\left(\boldsymbol{\theta} \right)\right)^2}{\sigma_i^2},
@@
 If the observed properties include any apparent magnitudes, then
-$\boldsymbol{\theta}$ includes distance and extinction in addition
+$\boldsymbol{\theta}$ includes distance and $A_V$ extinction in addition
 to mass, age, and \feh.
@@
 We include a prior on stellar metallicity representative of the observed metallicities
-of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}, and a Salpeter-slope
-prior on mass (up to the maximum mass available in the model grids of $3.7$ $M_\odot$).
+of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}, and
+only consider stars with masses below $3.7$ $M_\odot$.
 
@@
 There is some evidence that the Dartmouth models may under-predict
-radii of M dwarfs by $\sim 15\%$ when compared to other methods \citep{Newton15,
+radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
 Montet15}.
 Such an effect may be the result of the Dartmouth model reliance on BT-Settl
-atmospheres, which are based on incomplete molecular line lists and
-have been shown to predict near-IR colors that are too blue
+atmospheres, which have been shown to predict near-IR colors that are too blue
 \citep{Thompson14}.
 
-In order to account for the effects of model uncertainties, we also run
+In order to try to encapsulate the effect of model uncertainties, we also run
 MCMC chains with photometric errors inflated artificially by a factor of three.
-The observed photometric parameters are then consistent with spectroscopically-derived
-parameters for stars with published spectra, and consistent with typical uncertainties
-from photometric data \citep[e.g.][]{Huber14}.
 We provide full chains using both inflated and un-inflated
@@
 
-\subsection{SNIFS and SpeX Spectroscopy}
+\subsection{SpeX Spectroscopy}
 \label{Spexobs}
@@
 the parameters of the systematics model.
-To incorporate the stellar measurements, we approximate the constraints using
-a three-dimensional Gaussian in mass, radius, and effective temperature.
+To incorporate the stellar measurements, we approximate the measurements as a
+three-dimensional Gaussian in mass, radius, and effective temperature.
 
@@
 
-There are many scenarios which can cause an astrophysical false positive,
-where an eclipsing binary star masquerades as a transiting planet.
-The most common scenarios are if (a) it is a highly grazing eclipse, or (b) the binary system
-shares a photometric aperture with a significantly brighter star,
-resulting in a diluted eclipse depth.
-When possible, such astrophyscial false positive scenarios are traditionally
+As has been well known from the early days of transit searches, it is
+possible for an eclipsing binary star to masquerade as a transiting
+planet if (a) it is a highly grazing eclipse, or (b) the binary system
+comprises only a small fraction of the total light in the photometric
+aperture, resulting in a diluted eclipse depth.
+When possible, such astrophsycial false positive scenarios are traditionally
 ruled out by detailed follow-up observations, often a combination of
@@
 toward probabilistic interpretation of transit signals, rather than
-comprehensive follow-up of each individual candidate \citep{Morton11b}.
+comprehensive follow-up of each individual candidate.
 
@@
 astrophysical false positive.
-This method uses Galactic population simulations to determine the
-distributions of possible false positive scenarios, comparing the
-typical light curve shape of each to the data.
+This method uses population simulations of the light curves of
+of false positive scenarios and true transiting planets to quantify
+the typical shape of each, comparing to the observed transit shape.
 It then combines this information with observationally motivated prior
@@
 Similar in spirit to other published methods of
-probabilistic validation, such as BLENDER \citep{Torres11a} and PASTIS
+probabilistic validation, such as Blender \citep{Torres11a} and PASTIS
 \citep{Diaz14a}, it has the advantage of being computationally less demanding
@@
 \texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
-a new publicly available, general-purpose implementation
-of the \citet{Morton12} procedure,
+a new general-purpose implementation of the \citet{Morton12} procedure,
 to calculate false positive probabilities (FPPs) for each of these
-\KT\ candidates.
-The following constraints on false positive
-scenarios are imposed:
+\KT\ candidates.  We impose the following constraints on false positive
+scenarios:
 \begin{itemize}
-\item A chance-aligned eclipsing binary system may reside anywhere inside
-or within one pixel of the photometric aperture of the target star.
+\item A chance-aligned eclipsing binary system may reside anywhere within
+an 8 arcsecond radius from the target star.
 \item The maximum allowed depth of a potential secondary eclipse event
@@
 
-Each of these scenarios is an astrophysical eclipse, caused by one
-object passing in front of another, blocking some fraction of the
-total light.
-The calculations here do not include the possibility
-that each signal is caused by an instrumental artifact in the data or
-some other astrophysical event, such as stellar activity, masquerading
-as planet transits.
+Each of these scenarios are astrophysical, caused by one object passing
+in front of another, blocking some fraction of the total light.
+The calculations here do not include the possibility that each signal
+is caused by an instrumental artifact in the data or some other
+astrophysical event, such as stellar activity, masquerading as planet
+transits.
 
@@
 
-Four of the presented candidates have FPP $>$90\%;
-these are considered to be likely false positives.
-On the other hand, 21 candidates
-have FPP $<$ 1\%.
-Two of these are found to be caused by systematics
-in the transit search noise model (details in \S\ref{sec:systematics}), and
-so we identify those as false positives.
-Four more of these 21 might plausibly be caused by
-contamination by detected stellar companions within the photometric apertures
-(see \S\ref{sec:background}), so we keep these as candidates.
-
-This leaves 15 candidates that we statistically validate as planets, plus three
-additional planets that \texttt{vespa} does not validate but have been previously
-identified in the literature \citep{Crossfield15, Armstrong15b}.
-So in total, of the 36 candidates, 18 are secure planets,
-14 of which we here validate for the first time.
-
-We emphasize that the majority of these validations rely
-solely on the transit photometry and SDSS data, with follow-up imaging only obtained for
-seven of the 31 targets.  This
-demonstrates the utility of the \texttt{vespa} tool, which will be
-crucial to interpreting future candidates detected by \KT, TESS, and PLATO
-and prioritizing follow-up observing efforts.
-We show the transit signals in Fig. \ref{fig:transits}.
+We find that \Nfp\ of the presented candidates FPP $>$90\%;
+these we consider to be likely false positives.
+On the other hand, we find that \Nvalidated\ candidates
+have FPP $<$ 1\%; these we consider to be validated planets.
+Of these, 18 are validated for the first time.
+The remaining \Nlimbo\ candidates have FPPs neither high enough to discard
+nor low enough to securely validate.
+
+We emphasize that the majority of these planets were validated based
+solely on the transit signal, with no need for follow-up imaging.  This
+demonstrates the utility of \texttt{vespa} analysis, which will be
+crucial to interpreting future \KT\ detected candidates and prioritizing
+follow-up observing efforts.
+We show these transit signals as Fig. \ref{fig:transits}.
 
@@
 \centerline{\includegraphics[width=1.0\textwidth]{f2}}
-\caption{Phase-folded \KT\ photometry for all planet candidates analyzed in
+\caption{\btmtodo{PLACEHOLDER, UPDATE. Needs transit models}.
+Phase-folded \KT\ photometry for all planet candidates analyzed in
 this paper.
@@
 
-%We note that we validate 201828749 as a true transiting planet, despite the presence of this binary
-%companion.
-%From the transit shape, we can rule out the possibility this system is a background eclipsing
-%binary.
-%Regardless of which star this object transits, the object is planet-sized.
-%In Table 3, we assume the planet is orbiting the larger star.
-%If the planet is truly orbiting the fainter star, then its radius must be larger than is listed to
-%account for the observed transit depth.
+We note that we validate 201828749 as a true transiting planet, despite the presence of this binary
+companion.
+From the transit shape, we can rule out the possibility this system is a background eclipsing
+binary.
+Regardless of which star this object transits, the object is planet-sized.
+Given that small planets are significantly more common than large planets, it is more likely
+that the planet is orbiting the brighter star, and our parameters listed in Table 3 reflect this
+likelihood. If the planet is truly orbiting the fainter star, then it has a larger radius than is
+listed in this table.
 
@@
 \centerline{\includegraphics[width=1.0\textwidth]{f3}}
-\caption{Adaptive optics images for the seven stars observed with high-contrast imaging.
+\caption{AO data for all systems imaged.
 The main frame for each single system shows the deep, saturated image.
@@
 \subsection{Known Background Stars}
-\label{sec:background}
 The PHARO AO system has a field of view of 25 arcseconds.
@@
 \citep[SDSS DR9,][]{Ahn12}.
-For each target, from the depth of the observed transit we determine how
-bright a background object must be to cause the event if the background
-object were an equal mass totally-eclipsing binary.
-We then search for all stars within 25\arcsec\ that are within this brightness
-limit relative to the candidate host star.
-All apertures we use in our \KT\ analysis are smaller than 20\arcsec\ so this
-search should encompass the region where possible background
-contaminants could reside.
-Of the 31 stars in our sample, eleven have such a companion, plus one
-detected in AO imaging.
-
+For each target, we return
+all stars within 12\arcsec\ with $\Delta r < 8$ relative to each object
+of interest.
+Of the 31 stars in our sample, four have such a companion.
 Unlike the original \kep\ field, the field for \KT\ \Ci\ is
-well out of the galactic plane, so the rate of giant, distant background
+well out of the galactic plane, so the rate of giant, distanct background
 stars is significantly lower.
 We include all potential contaminants in Table 5.
-We validate or eliminate each of these as a possibility based on the transit shape.
-For example, the events near EPIC 201546283 could only be caused by a
-background binary if the background object was a completely-eclipsing system
-(so that the eclipse depth was $50\%$).
-In this case, the transit would be perfectly V-shaped.
-Since it is not, we can rule out the possibility this background object causes
-the transit event.
 
@@
 
-The photometric apertures used to detect these candidates range in radius from
-$10\farcs0$ to $19\farcs9$.  In order to be a plausible contaminant,
-any companion star must
-be either within this aperture or just outside but bright
-enough for signficant flux to leak in.
-Evaluating each of the systems listed in Table 5, we judge that we cannot yet
-rule out contamination as a potential source of the transit signal for four
-candidates: 201295312.01, 201403446.01, 201546283.01, and 201828749.01.  
-Despite receiving
-low FPP scores from \texttt{vespa}, we list these systems as candidates in
-Table 4, rather than planets.  Further updates to the \texttt{vespa} code
-will allow consideration of ``specific'' false positive scenarios; that is,
-scenarios that correspond to actually detected stars such as these, rather than
-hypothetical background or bound companions.
-
-The candidates with identified companions that we judge to not be plausible
-sources of potential contamination are the following:
-\begin{itemize}
-
-\item 201546283.01--- For this system, the ``maximum depth'' is nearly
-identical to the observed transit depth, which would require a perfectly
-V-shaped eclipse to explain.  As this is not the case (see Figure 2),
-this signal cannot
-be caused by contamination from this star.
-
-\item 201629650.01--- The companion to this star is $17\farcs3$ from
-the EPIC target.  As this is outside the aperture
-(radius $15\farcs9$) and the background star is not particularly bright,
-we rule out contamination for this system.
-
-\item 201702477.01--- The companion to this star is $12\farcs15$ from the
-EPIC target, and the aperture size is $10\farcs0$.  In addition,
-the maximum depth in this system is almost identical to the transit depth.
-For these two reasons we rule out contamination in this case.
-
-\end{itemize}
-
-SDSS is 95\% complete at $r=22.2$ mag and the telescope has a point
-spread function of $1\farcs4$.
-For the purposes of the \texttt{vespa} calculation, we thus
-treat nondetection in SDSS data as providing a contrast curve at
-wide separations
-down to a limiting magnitude of $r=22.2$ mag.
+For EPIC 201465501 and 201779067, the observed transit depth is
+larger than each of these values, so we reject the possibility that
+these events could be the eclipses of the background binaries detected
+here.
+
+For EPIC 201546283, the observed transit depth is nearly identical to
+the maximum false positive depth.
+The photometry for this potential contaminant is consistent with that
+of an M3V star; for this object to cause the observed eclipse it must
+be a total eclipse of two M3V stars.
+However, in that case, the observed event would be exactly V-shaped,
+with second and third contact occurring simultaneously.
+Since the transit is not V-shaped, it must be the result of
+a relatively small body passing in front of a relatively large body.
+Therefore, it cannot be caused by this observed background dwarf star.
+
+For EPIC 201295312, the transit depth is significantly shallower than
+the maximum false positive depth, so we cannot immediately
+reject the hypothesis that the transit is actually a false positive
+induced by a background eclipsing binary.
+However, from the transit shape alone we can place a FPP of this
+system of $1.1 \times 10^{-4}$.
+
+SDSS is 95\% complete at $r=22.2$ and the telescope has a point
+spread function of $1\farcs4$. In all cases except the four above, we
+treat the SDSS data as providing a contrast curve at wide separations
+down to a limiting magnitude of $r=22.2$.
 
@@
 of the Hale Telescope at $2$ $\mu$m, but nonzero.
-While the \texttt{vespa} calculations quantify this probability for
-this to occur, we can also rule out the possibility of such
-chance alignments, down to a certain contrast, with archival imaging data.
-
-We include this extra analysis step for EPIC 201912552, considering
+We can rule out the possibility of such chance alignments with
+archival imaging data.
+
+For all targets with AO, we can confirm the planetary nature of the signal
+without this extra step, but we include it for EPIC 201912552, considering
 the additional follow-up this target may warrant.
@@
 nearly $90^\circ$ and the phase $\varpi + \theta \approx \pi/2$ or $3\pi/2$.
-While we cannot fully rule out this possibility, the \texttt{vespa}
-calculations confirm that its probability is negligibly small.
+While we cannot fully rule out this possibility, such an alignment is unlikely
+to occur and unable to cause enough dilution to call the planetary
+nature of this signal into question.
 
@@
 observations would be on the order of km s$^{-1}$.
-Therefore, we can rule out any stellar-mass companions that would be able
-to create this transit signal.
+Therefore, the transiting object must be planetary in nature.
 
@@
 
-\subsection{Non-Astrophysical False Positives}
-\label{sec:systematics}
-
-The method of \paperit\ assumes that all variability in the light curves are
-caused by either the motion of \KT, in which case the variability is shared
-by all stars, or transits of planets, in which case the variability is intrinsic
-to only one star.
-This assumption breaks down for extremely spotted stars where the
-astrophysical variability is larger than the instrumental
-magnitude.
-In that regime, the starspot modulations can be incorrectly fit by the
-systematic model, causing spurious transits to appear.
-This appears to be the case with EPIC 201929294, which has
-coherent starspots that appear to have the same rotation period as the
-transit period reported previously.
-Because the starspots are so periodic and coherent, these spurious
-transits were falsely identified as a planet candidate; we consider that
-system a false positive in this work.
-
-The planet candidate possibly orbiting EPIC 201555883 has a period,
-time of transit, and transit duration consistent with EPIC 201569483.
+\subsection{Two Candidates, One Ephemeris}
+
+EPIC 201569483 was originally listed in \paperit\ as a planet candidate.
+The transit events have a depth of approximately 7\%.
+In this work, we conclude this system is likely a false
+positive, with an FPP of 0.560.
+The most likely scenario is that of an eclipsing binary, which would
+not be surprising given the transit depth.
+
+It was later realized that EPIC 201555883 has a period, time of transit,
+and transit duration consistent with EPIC 201569483.
 Such effects are not uncommon in \kep\ data.
-\citet{Coughlin14} identify 685 KOIs as false
-positives and outline four physical reasons why these anomalies may occur.
+\citet{Batalha13} found $\sim 25$ planet candidates to be false positives
+based on matching ephemerides between candidates.
+In that paper, the authors limited their search to candidates within
+$20\arcsec$ of other objects of interest.
+\citet{Coughlin14} expanded on this method, identifying 685 KOIs as false
+positives and outlining four physical reasons why these anomalies may occur.
+As those authors explain, period-matching candidates can be the result of
+direct PRF contamination, antipodal reflection across the Schmidt telescope,
+CCD crosstalk across a \kep\ module, or ``column anomalies'' across one column
+of the CCD.
+Typically, the instrumental false positive event appears considerably
+shallower than the true astrophysical event.
+
 EPIC 201555883 is a unique case in that it does not appear to fall under any
@@
 systematic mechanism.
-
 \paperit\ modeled the systematic effects in the \KT\ light curves using a
@@
 eclipsing binaries, and even transiting planets.
-Again, this star has significant variability caused by starspots.
-In this case, the fitting procedure tries to account for stellar variability using
-the eigen light curves.
-This overfit gives undue weight to eigen light curves that include the transits
-of EPIC 201569483, causing this spurious transit to occur.
-Again, we consider this system to be a false positive.
-
-The problem of over-fitting stellar variability using eigen light curves can be
-solved by adding a stellar activity model to our fitting procedure.
-In this case, the spacecraft motion could be fit simultaneously with a model
-of starspot modulation, astroseismic oscillations, and planet transits.
-Such a model is currently under development (Angus et al. \textit{in prep}).
+
+Formally, our false positive validation scheme gives a FPP of $9.5 \times
+10^{-4}$, reaching our threshold for planet validation.
+Since \texttt{vespa} does not account for the possibility of instrumental
+artifacts in the data, this number represents only the \textit{astrophysical}
+false positive probability.
+In this case, given the period matching between the two events, we refrain
+from declaring this system a planet.
+However, since we cannot explain how such a false positive would occur as a
+result of an instrumental systematic in the \kep\ telescope, we also refrain
+from declaring this target a definite false positive.
+Additional follow-up observations of both targets are clearly warranted to
+better understand a possible systematic that has not previously been observed
+in either \kep\ or \KT.
 
 \subsection{Multiple Planet Systems}
-Five of the systems reported by \paperit\ have more than one transiting
-candidate.
+Five of the systems identified by \paperit\ are candidates to be multiply-transiting
+systems.
 One of these is EPIC 201367065, a three-planet system originally announced by
@@
 mini-Neptune sized planets.
+Like in the \kep\ field, the false positive rate we measure for the multiple planet sample
+here ($0/10$) is lower than for the single systems \citep{Lissauer12, Rowe14}.
 
@@
 \citep{Howell14}.
-Of our sample, two systems orbit stars with $K < 9$ mag: EPIC 201367065 \citep{Crossfield15} and
+Of our sample, two systems orbit stars with $K < 9$: EPIC 201367065 \citep{Crossfield15} and
 EPIC 201912552.
-An additional planet candidate may orbit EPIC 201828749, a star with $K = 9.93 \pm 0.03$ mag.
+An additional four targets orbit stars with $K <10$.
 These targets are ideal for ground-based followup and may be useful targets for Spitzer and
@@
 
-We have presented stellar parameters for all planet candidates systems identified by
-\paperit.
-We statistically validate \Nvalidated\ of the 36 candidates as bona fide planets, and we
-identify \Nfp\ as false positives.
-Of these planets, 4 have been previously validated in other works, while 14 are
+We have presented stellar parameters for all planet candidates systems observed by
+\paperit, validating \Nvalidated\ of the 36 candidates as bona fide planets and
+\Nfp\ as false positives.
+Of these planets, 4 have been previously validated in other works, while 17 are
 validated here for the first time.
-The systems not validated as planets or false positives remain as planet candidates.
-
-Enabling much of this analysis are two new open-source Python packages:
-\texttt{isochrones}\footnote{\url{http://github.com/timothydmorton/isochrones}},
-which we use to infer posteriors on physical stellar properties based
-on fitting theoretical stellar models to observed data; and \texttt{vespa}\footnote{
-\url{http://github.com/timothydmorton/vespa}}, a
-new implementation of the \citet{Morton12} transit false positive analysis scheme.
-Both of these packages will continue to be useful in future analysis of transit candidates
-where comprehensive follow-up observations may be unavailable.
 
@@
 by discrepancies between the models and reality.
+Even more dangerously, any region of parameter space not probed by the models would
+be entirely missed in our stellar modeling.
 
@@
 5.3 $R_\oplus$, and orbit with periods ranging from 5.0 to 50.3 days.
-Like the original mission, we find significantly more small planets than large planets, as
-expected from the radius distributions measured from \kep\
-\citep{Howard12, Fressin13, Morton14}.
+Like the original mission, we find significantly more small planets than large planets.
 
@@
 \acknowledgements
-We thank Roberto Sanchis-Ojeda (Berkeley), Dan Huber (Sydney) and 
-Jeff Coughlin (SETI) for
+We thank Eric Agol (UW), Dan Huber (Sydney) and Jeff Coughlin (SETI) for
 conversations and suggestions which improved the quality of this manuscript.

### 2015-03-29 table_fpp.tex

@@
  \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $8.8\times10^{-3}$  & \color{red}  $0.940$  & \color{red}  $0.051$  & \color{red}  $0.17$  & \color{red}  $1.000$  & \color{red}  FP \\
-201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet  \\
+201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
 201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $3.2\times10^{-3}$ & Planet  \\
@@
 201393098.01 & $0.52$ &  - & $1.6\times10^{-3}$ & $< 10^{-4}$ & $5.5\times10^{-4}$ & $0.19$ & $2.2\times10^{-3}$ & Planet  \\
-201403446.01 & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet  \\
+201403446.01 & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
 201445392.01 & $0.26$ &  - & $1.3\times10^{-3}$ & $< 10^{-4}$ & $0.012$ & $0.19$ & $0.013$ & Candidate  \\
@@
 out of abundance of caution due
-to secondary star detection in or near photometric aperture.}
+to secondary star detection within or near photometric aperture.}
 \tablenotetext{b}{Declared a false positive due to noise modeling systematics (see \S\ref{sec:systematics}).}

### 2015-04-15 fpp/fppmodels/201208431.1/SDSS_r.cc
added contrast curves and transit signal pickles

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 7.909000000000000696e+00
+4.000000000000000000e+00 7.909000000000000696e+00
+8.000000000000000000e+00 7.909000000000000696e+00
+1.200000000000000000e+01 7.909000000000000696e+00
+2.500000000000000000e+01 7.909000000000000696e+00

### 2015-04-15 fpp/fppmodels/201257461.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 1.071199999999999974e+01
+4.000000000000000000e+00 1.071199999999999974e+01
+8.000000000000000000e+00 1.071199999999999974e+01
+1.200000000000000000e+01 1.071199999999999974e+01
+2.500000000000000000e+01 1.071199999999999974e+01

### 2015-04-15 fpp/fppmodels/201295312.1/PHARO_K.cc

@@ -1,0 +1,110 @@
+0.000000000000000000e+00 0.000000000000000000e+00
+1.260000020265579224e-01 2.321982383728027344e+00
+2.520000040531158447e-01 3.949667692184448242e+00
+3.779999911785125732e-01 4.501347541809082031e+00
+5.040000081062316895e-01 5.125093936920166016e+00
+6.299999952316284180e-01 5.680143356323242188e+00
+7.559999823570251465e-01 6.180764675140380859e+00
+8.820000290870666504e-01 6.624961376190185547e+00
+1.008000016212463379e+00 7.021989345550537109e+00
+1.133999943733215332e+00 7.395713806152343750e+00
+1.259999990463256836e+00 7.702268123626708984e+00
+1.386000037193298340e+00 7.861840248107910156e+00
+1.511999964714050293e+00 7.888793945312500000e+00
+1.638000011444091797e+00 7.889432907104492188e+00
+1.764000058174133301e+00 7.964354515075683594e+00
+1.889999985694885254e+00 8.005315780639648438e+00
+2.016000032424926758e+00 8.025029182434082031e+00
+2.141999959945678711e+00 8.040803909301757812e+00
+2.267999887466430664e+00 8.103586196899414062e+00
+2.394000053405761719e+00 8.078061103820800781e+00
+2.519999980926513672e+00 8.117260932922363281e+00
+2.645999908447265625e+00 8.113903045654296875e+00
+2.772000074386596680e+00 8.129734992980957031e+00
+2.898000001907348633e+00 8.130412101745605469e+00
+3.023999929428100586e+00 8.137349128723144531e+00
+3.150000095367431641e+00 8.134164810180664062e+00
+3.276000022888183594e+00 8.184373855590820312e+00
+3.401999950408935547e+00 8.135849952697753906e+00
+3.528000116348266602e+00 8.145282745361328125e+00
+3.654000043869018555e+00 8.128430366516113281e+00
+3.779999971389770508e+00 8.131613731384277344e+00
+3.905999898910522461e+00 8.127635955810546875e+00
+4.032000064849853516e+00 8.123669624328613281e+00
+4.157999992370605469e+00 8.114888191223144531e+00
+4.283999919891357422e+00 8.122368812561035156e+00
+4.409999847412109375e+00 8.111609458923339844e+00
+4.535999774932861328e+00 8.142473220825195312e+00
+4.662000179290771484e+00 8.105109214782714844e+00
[…]

### 2015-04-15 fpp/fppmodels/201295312.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 1.011599999999999788e+01
+4.000000000000000000e+00 1.011599999999999788e+01
+8.000000000000000000e+00 1.011599999999999788e+01
+1.200000000000000000e+01 1.011599999999999788e+01
+2.500000000000000000e+01 1.011599999999999788e+01

### 2015-04-15 fpp/fppmodels/201338508.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 7.865999999999997883e+00
+4.000000000000000000e+00 7.865999999999997883e+00
+8.000000000000000000e+00 7.865999999999997883e+00
+1.200000000000000000e+01 7.865999999999997883e+00
+2.500000000000000000e+01 7.865999999999997883e+00

### 2015-04-15 fpp/fppmodels/201367065.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 1.061799999999999855e+01
+4.000000000000000000e+00 1.061799999999999855e+01
+8.000000000000000000e+00 1.061799999999999855e+01
+1.200000000000000000e+01 1.061799999999999855e+01
+2.500000000000000000e+01 1.061799999999999855e+01

### 2015-04-15 fpp/fppmodels/201384232.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 9.717999999999998195e+00
+4.000000000000000000e+00 9.717999999999998195e+00
+8.000000000000000000e+00 9.717999999999998195e+00
+1.200000000000000000e+01 9.717999999999998195e+00
+2.500000000000000000e+01 9.717999999999998195e+00

### 2015-04-15 fpp/fppmodels/201393098.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 9.175999999999998380e+00
+4.000000000000000000e+00 9.175999999999998380e+00
+8.000000000000000000e+00 9.175999999999998380e+00
+1.200000000000000000e+01 9.175999999999998380e+00
+2.500000000000000000e+01 9.175999999999998380e+00

### 2015-04-15 fpp/fppmodels/201403446.1/PHARO_K.cc

@@ -1,0 +1,117 @@
+0.000000000000000000e+00 0.000000000000000000e+00
+1.260000020265579224e-01 1.968023300170898438e+00
+2.520000040531158447e-01 3.350775718688964844e+00
+3.779999911785125732e-01 4.202054023742675781e+00
+5.040000081062316895e-01 4.726270198822021484e+00
+6.299999952316284180e-01 5.452174186706542969e+00
+7.559999823570251465e-01 5.903185367584228516e+00
+8.820000290870666504e-01 6.342168331146240234e+00
+1.008000016212463379e+00 6.672229766845703125e+00
+1.133999943733215332e+00 6.960692405700683594e+00
+1.259999990463256836e+00 7.059750556945800781e+00
+1.386000037193298340e+00 7.089296340942382812e+00
+1.511999964714050293e+00 7.138607978820800781e+00
+1.638000011444091797e+00 7.181904315948486328e+00
+1.764000058174133301e+00 7.171307563781738281e+00
+1.889999985694885254e+00 7.212569236755371094e+00
+2.016000032424926758e+00 7.251519680023193359e+00
+2.141999959945678711e+00 7.292107105255126953e+00
+2.267999887466430664e+00 7.362780094146728516e+00
+2.394000053405761719e+00 7.342188835144042969e+00
+2.519999980926513672e+00 7.344263076782226562e+00
+2.645999908447265625e+00 7.326437950134277344e+00
+2.772000074386596680e+00 7.352418422698974609e+00
+2.898000001907348633e+00 7.360096454620361328e+00
+3.023999929428100586e+00 7.369802474975585938e+00
+3.150000095367431641e+00 7.371363162994384766e+00
+3.276000022888183594e+00 7.372470378875732422e+00
+3.401999950408935547e+00 7.412150382995605469e+00
+3.528000116348266602e+00 7.364014625549316406e+00
+3.654000043869018555e+00 7.408039569854736328e+00
+3.779999971389770508e+00 7.391996383666992188e+00
+3.905999898910522461e+00 7.386587142944335938e+00
+4.032000064849853516e+00 7.380376338958740234e+00
+4.157999992370605469e+00 7.392494201660156250e+00
+4.283999919891357422e+00 7.410959243774414062e+00
+4.409999847412109375e+00 7.408179759979248047e+00
+4.535999774932861328e+00 7.400223255157470703e+00
+4.662000179290771484e+00 7.441384315490722656e+00
[…]

### 2015-04-15 fpp/fppmodels/201403446.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 1.025599999999999845e+01
+4.000000000000000000e+00 1.025599999999999845e+01
+8.000000000000000000e+00 1.025599999999999845e+01
+1.200000000000000000e+01 1.025599999999999845e+01
+2.500000000000000000e+01 1.025599999999999845e+01

### 2015-04-15 fpp/fppmodels/201445392.2/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 7.911999999999999034e+00
+4.000000000000000000e+00 7.911999999999999034e+00
+8.000000000000000000e+00 7.911999999999999034e+00
+1.200000000000000000e+01 7.911999999999999034e+00
+2.500000000000000000e+01 7.911999999999999034e+00

### 2015-04-15 fpp/fppmodels/201465501.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 7.019999999999999574e+00
+4.000000000000000000e+00 7.019999999999999574e+00
+8.000000000000000000e+00 7.019999999999999574e+00
+1.200000000000000000e+01 7.019999999999999574e+00
+2.500000000000000000e+01 7.019999999999999574e+00

### 2015-04-15 fpp/fppmodels/201505350.2/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 9.435999999999998167e+00
+4.000000000000000000e+00 9.435999999999998167e+00
+8.000000000000000000e+00 9.435999999999998167e+00
+1.200000000000000000e+01 9.435999999999998167e+00
+2.500000000000000000e+01 9.435999999999998167e+00

### 2015-04-15 fpp/fppmodels/201546283.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 9.832999999999998408e+00
+4.000000000000000000e+00 9.832999999999998408e+00
+8.000000000000000000e+00 9.832999999999998408e+00
+1.200000000000000000e+01 9.832999999999998408e+00
+2.500000000000000000e+01 9.832999999999998408e+00

### 2015-04-15 fpp/fppmodels/201549860.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 8.346999999999999531e+00
+4.000000000000000000e+00 8.346999999999999531e+00
+8.000000000000000000e+00 8.346999999999999531e+00
+1.200000000000000000e+01 8.346999999999999531e+00
+2.500000000000000000e+01 8.346999999999999531e+00

### 2015-04-15 fpp/fppmodels/201555883.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 7.106999999999999318e+00
+4.000000000000000000e+00 7.106999999999999318e+00
+8.000000000000000000e+00 7.106999999999999318e+00
+1.200000000000000000e+01 7.106999999999999318e+00
+2.500000000000000000e+01 7.106999999999999318e+00

### 2015-04-15 fpp/fppmodels/201565013.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 5.294999999999998153e+00
+4.000000000000000000e+00 5.294999999999998153e+00
+8.000000000000000000e+00 5.294999999999998153e+00
+1.200000000000000000e+01 5.294999999999998153e+00
+2.500000000000000000e+01 5.294999999999998153e+00

### 2015-04-15 fpp/fppmodels/201569483.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 1.043900000000000006e+01
+4.000000000000000000e+00 1.043900000000000006e+01
+8.000000000000000000e+00 1.043900000000000006e+01
+1.200000000000000000e+01 1.043900000000000006e+01
+2.500000000000000000e+01 1.043900000000000006e+01

### 2015-04-15 fpp/fppmodels/201577035.1/PHARO_K.cc

@@ -1,0 +1,124 @@
+0.000000000000000000e+00 0.000000000000000000e+00
+1.260000020265579224e-01 1.970945239067077637e+00
+2.520000040531158447e-01 4.066184043884277344e+00
+3.779999911785125732e-01 5.026388645172119141e+00
+5.040000081062316895e-01 5.760081291198730469e+00
+6.299999952316284180e-01 6.380682945251464844e+00
+7.559999823570251465e-01 6.911050796508789062e+00
+8.820000290870666504e-01 7.145116806030273438e+00
+1.008000016212463379e+00 7.307192802429199219e+00
+1.133999943733215332e+00 7.417432308197021484e+00
+1.259999990463256836e+00 7.432271480560302734e+00
+1.386000037193298340e+00 7.376707077026367188e+00
+1.511999964714050293e+00 7.387394428253173828e+00
+1.638000011444091797e+00 7.383607864379882812e+00
+1.764000058174133301e+00 7.402801990509033203e+00
+1.889999985694885254e+00 7.388534069061279297e+00
+2.016000032424926758e+00 7.340245723724365234e+00
+2.141999959945678711e+00 7.330066204071044922e+00
+2.267999887466430664e+00 7.335883140563964844e+00
+2.394000053405761719e+00 7.333842277526855469e+00
+2.519999980926513672e+00 7.306323528289794922e+00
+2.645999908447265625e+00 7.288790702819824219e+00
+2.772000074386596680e+00 7.259059906005859375e+00
+2.898000001907348633e+00 7.263413429260253906e+00
+3.023999929428100586e+00 7.210943698883056641e+00
+3.150000095367431641e+00 7.190580844879150391e+00
+3.276000022888183594e+00 7.145082950592041016e+00
+3.401999950408935547e+00 7.154023170471191406e+00
+3.528000116348266602e+00 7.141024589538574219e+00
+3.654000043869018555e+00 7.121883392333984375e+00
+3.779999971389770508e+00 7.105968952178955078e+00
+3.905999898910522461e+00 7.104439735412597656e+00
+4.032000064849853516e+00 7.140135288238525391e+00
+4.157999992370605469e+00 7.151841163635253906e+00
+4.283999919891357422e+00 7.188442230224609375e+00
+4.409999847412109375e+00 7.213941574096679688e+00
+4.535999774932861328e+00 7.187086105346679688e+00
+4.662000179290771484e+00 7.206699848175048828e+00
[…]

### 2015-04-15 fpp/fppmodels/201577035.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 9.989000000000000767e+00
+4.000000000000000000e+00 9.989000000000000767e+00
+8.000000000000000000e+00 9.989000000000000767e+00
+1.200000000000000000e+01 9.989000000000000767e+00
+2.500000000000000000e+01 9.989000000000000767e+00

### 2015-04-15 fpp/fppmodels/201596316.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 9.062999999999998835e+00
+4.000000000000000000e+00 9.062999999999998835e+00
+8.000000000000000000e+00 9.062999999999998835e+00
+1.200000000000000000e+01 9.062999999999998835e+00
+2.500000000000000000e+01 9.062999999999998835e+00

### 2015-04-15 fpp/fppmodels/201613023.1/PHARO_K.cc

@@ -1,0 +1,123 @@
+0.000000000000000000e+00 0.000000000000000000e+00
+1.260000020265579224e-01 2.145832777023315430e+00
+2.520000040531158447e-01 4.470203399658203125e+00
+3.779999911785125732e-01 5.256906032562255859e+00
+5.040000081062316895e-01 6.041627883911132812e+00
+6.299999952316284180e-01 6.698771953582763672e+00
+7.559999823570251465e-01 7.210814476013183594e+00
+8.820000290870666504e-01 7.502188682556152344e+00
+1.008000016212463379e+00 7.597804546356201172e+00
+1.133999943733215332e+00 7.850426673889160156e+00
+1.259999990463256836e+00 7.840910911560058594e+00
+1.386000037193298340e+00 7.863941192626953125e+00
+1.511999964714050293e+00 7.844230175018310547e+00
+1.638000011444091797e+00 7.863983154296875000e+00
+1.764000058174133301e+00 7.866557598114013672e+00
+1.889999985694885254e+00 7.867768764495849609e+00
+2.016000032424926758e+00 7.857573986053466797e+00
+2.141999959945678711e+00 7.841361522674560547e+00
+2.267999887466430664e+00 7.838548660278320312e+00
+2.394000053405761719e+00 7.844571590423583984e+00
+2.519999980926513672e+00 7.830342292785644531e+00
+2.645999908447265625e+00 7.786993503570556641e+00
+2.772000074386596680e+00 7.801712512969970703e+00
+2.898000001907348633e+00 7.774348258972167969e+00
+3.023999929428100586e+00 7.783467769622802734e+00
+3.150000095367431641e+00 7.847187519073486328e+00
+3.276000022888183594e+00 7.822246551513671875e+00
+3.401999950408935547e+00 7.857028007507324219e+00
+3.528000116348266602e+00 7.902640819549560547e+00
+3.654000043869018555e+00 7.916877269744873047e+00
+3.779999971389770508e+00 7.923280715942382812e+00
+3.905999898910522461e+00 7.862857341766357422e+00
+4.032000064849853516e+00 7.846765041351318359e+00
+4.157999992370605469e+00 7.855919361114501953e+00
+4.283999919891357422e+00 7.850915431976318359e+00
+4.409999847412109375e+00 7.847173213958740234e+00
+4.535999774932861328e+00 7.871097564697265625e+00
+4.662000179290771484e+00 7.829699516296386719e+00
[…]

### 2015-04-15 fpp/fppmodels/201613023.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 1.015099999999999802e+01
+4.000000000000000000e+00 1.015099999999999802e+01
+8.000000000000000000e+00 1.015099999999999802e+01
+1.200000000000000000e+01 1.015099999999999802e+01
+2.500000000000000000e+01 1.015099999999999802e+01

### 2015-04-15 fpp/fppmodels/201617985.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 7.939000000000000057e+00
+4.000000000000000000e+00 7.939000000000000057e+00
+8.000000000000000000e+00 7.939000000000000057e+00
+1.200000000000000000e+01 7.939000000000000057e+00
+2.500000000000000000e+01 7.939000000000000057e+00

### 2015-04-15 fpp/fppmodels/201629650.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 9.472999999999998977e+00
+4.000000000000000000e+00 9.472999999999998977e+00
+8.000000000000000000e+00 9.472999999999998977e+00
+1.200000000000000000e+01 9.472999999999998977e+00
+2.500000000000000000e+01 9.472999999999998977e+00

### 2015-04-15 fpp/fppmodels/201635569.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 6.576999999999999957e+00
+4.000000000000000000e+00 6.576999999999999957e+00
+8.000000000000000000e+00 6.576999999999999957e+00
+1.200000000000000000e+01 6.576999999999999957e+00
+2.500000000000000000e+01 6.576999999999999957e+00

### 2015-04-15 fpp/fppmodels/201649426.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 9.019000000000000128e+00
+4.000000000000000000e+00 9.019000000000000128e+00
+8.000000000000000000e+00 9.019000000000000128e+00
+1.200000000000000000e+01 9.019000000000000128e+00
+2.500000000000000000e+01 9.019000000000000128e+00

### 2015-04-15 fpp/fppmodels/201702477.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 7.800999999999998380e+00
+4.000000000000000000e+00 7.800999999999998380e+00
+8.000000000000000000e+00 7.800999999999998380e+00
+1.200000000000000000e+01 7.800999999999998380e+00
+2.500000000000000000e+01 7.800999999999998380e+00

### 2015-04-15 fpp/fppmodels/201736247.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 7.850999999999999091e+00
+4.000000000000000000e+00 7.850999999999999091e+00
+8.000000000000000000e+00 7.850999999999999091e+00
+1.200000000000000000e+01 7.850999999999999091e+00
+2.500000000000000000e+01 7.850999999999999091e+00

### 2015-04-15 fpp/fppmodels/201754305.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 7.920999999999997598e+00
+4.000000000000000000e+00 7.920999999999997598e+00
+8.000000000000000000e+00 7.920999999999997598e+00
+1.200000000000000000e+01 7.920999999999997598e+00
+2.500000000000000000e+01 7.920999999999997598e+00

### 2015-04-15 fpp/fppmodels/201779067.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 1.108099999999999774e+01
+4.000000000000000000e+00 1.108099999999999774e+01
+8.000000000000000000e+00 1.108099999999999774e+01
+1.200000000000000000e+01 1.108099999999999774e+01
+2.500000000000000000e+01 1.108099999999999774e+01

### 2015-04-15 fpp/fppmodels/201828749.1/PHARO_H.cc

@@ -1,0 +1,124 @@
+0.000000000000000000e+00 0.000000000000000000e+00
+1.260000020265579224e-01 2.767617940902709961e+00
+2.520000040531158447e-01 4.397443294525146484e+00
+3.779999911785125732e-01 5.169413566589355469e+00
+5.040000081062316895e-01 6.120359420776367188e+00
+6.299999952316284180e-01 6.655040740966796875e+00
+7.559999823570251465e-01 7.180109977722167969e+00
+8.820000290870666504e-01 7.576342582702636719e+00
+1.008000016212463379e+00 7.754891872406005859e+00
+1.133999943733215332e+00 7.896411895751953125e+00
+1.259999990463256836e+00 7.987064361572265625e+00
+1.386000037193298340e+00 7.985310554504394531e+00
+1.511999964714050293e+00 7.928812980651855469e+00
+1.638000011444091797e+00 7.766601085662841797e+00
+1.764000058174133301e+00 7.432515144348144531e+00
+1.889999985694885254e+00 7.279661655426025391e+00
+2.016000032424926758e+00 7.617740154266357422e+00
+2.141999959945678711e+00 7.185525894165039062e+00
+2.267999887466430664e+00 5.412793636322021484e+00
+2.394000053405761719e+00 4.017073631286621094e+00
+2.519999980926513672e+00 4.886163711547851562e+00
+2.645999908447265625e+00 8.012904167175292969e+00
+2.772000074386596680e+00 7.959465026855468750e+00
+2.898000001907348633e+00 7.842472076416015625e+00
+3.023999929428100586e+00 7.881680011749267578e+00
+3.150000095367431641e+00 7.866135597229003906e+00
+3.276000022888183594e+00 8.193073272705078125e+00
+3.401999950408935547e+00 8.257162094116210938e+00
+3.528000116348266602e+00 8.337459564208984375e+00
+3.654000043869018555e+00 8.402884483337402344e+00
+3.779999971389770508e+00 8.442729949951171875e+00
+3.905999898910522461e+00 8.449555397033691406e+00
+4.032000064849853516e+00 8.520739555358886719e+00
+4.157999992370605469e+00 8.519742965698242188e+00
+4.283999919891357422e+00 8.524603843688964844e+00
+4.409999847412109375e+00 8.526880264282226562e+00
+4.535999774932861328e+00 8.512276649475097656e+00
+4.662000179290771484e+00 8.547024726867675781e+00
[…]

### 2015-04-15 fpp/fppmodels/201828749.1/PHARO_J.cc

@@ -1,0 +1,123 @@
+0.000000000000000000e+00 0.000000000000000000e+00
+1.260000020265579224e-01 2.593586444854736328e+00
+2.520000040531158447e-01 4.039646148681640625e+00
+3.779999911785125732e-01 4.987716197967529297e+00
+5.040000081062316895e-01 5.694131374359130859e+00
+6.299999952316284180e-01 6.240717411041259766e+00
+7.559999823570251465e-01 6.720194339752197266e+00
+8.820000290870666504e-01 7.075508117675781250e+00
+1.008000016212463379e+00 7.331658363342285156e+00
+1.133999943733215332e+00 7.367664337158203125e+00
+1.259999990463256836e+00 7.387115478515625000e+00
+1.386000037193298340e+00 7.413280010223388672e+00
+1.511999964714050293e+00 7.474557399749755859e+00
+1.638000011444091797e+00 7.349449157714843750e+00
+1.764000058174133301e+00 7.136044502258300781e+00
+1.889999985694885254e+00 7.006459236145019531e+00
+2.016000032424926758e+00 7.263023376464843750e+00
+2.141999959945678711e+00 7.466620445251464844e+00
+2.267999887466430664e+00 5.314695835113525391e+00
+2.394000053405761719e+00 4.046336174011230469e+00
+2.519999980926513672e+00 4.895678520202636719e+00
+2.645999908447265625e+00 6.876293182373046875e+00
+2.772000074386596680e+00 7.206898689270019531e+00
+2.898000001907348633e+00 7.398960590362548828e+00
+3.023999929428100586e+00 7.399692535400390625e+00
+3.150000095367431641e+00 7.600429058074951172e+00
+3.276000022888183594e+00 7.779510498046875000e+00
+3.401999950408935547e+00 7.813261985778808594e+00
+3.528000116348266602e+00 7.898406505584716797e+00
+3.654000043869018555e+00 7.947533607482910156e+00
+3.779999971389770508e+00 7.981868743896484375e+00
+3.905999898910522461e+00 7.999387264251708984e+00
+4.032000064849853516e+00 8.007725715637207031e+00
+4.157999992370605469e+00 8.002371788024902344e+00
+4.283999919891357422e+00 8.016595840454101562e+00
+4.409999847412109375e+00 8.025981903076171875e+00
+4.535999774932861328e+00 8.019169807434082031e+00
+4.662000179290771484e+00 8.017703056335449219e+00
[…]

### 2015-04-15 fpp/fppmodels/201828749.1/PHARO_K.cc

@@ -1,0 +1,124 @@
+0.000000000000000000e+00 0.000000000000000000e+00
+1.260000020265579224e-01 2.157889127731323242e+00
+2.520000040531158447e-01 4.813655376434326172e+00
+3.779999911785125732e-01 5.575337409973144531e+00
+5.040000081062316895e-01 6.059696197509765625e+00
+6.299999952316284180e-01 6.723708629608154297e+00
+7.559999823570251465e-01 6.993198871612548828e+00
+8.820000290870666504e-01 7.336640357971191406e+00
+1.008000016212463379e+00 7.319638252258300781e+00
+1.133999943733215332e+00 7.397557735443115234e+00
+1.259999990463256836e+00 7.497410297393798828e+00
+1.386000037193298340e+00 7.540590286254882812e+00
+1.511999964714050293e+00 7.530881404876708984e+00
+1.638000011444091797e+00 7.466837882995605469e+00
+1.764000058174133301e+00 7.325817108154296875e+00
+1.889999985694885254e+00 7.246541500091552734e+00
+2.016000032424926758e+00 7.284280776977539062e+00
+2.141999959945678711e+00 6.238629341125488281e+00
+2.267999887466430664e+00 5.382064819335937500e+00
+2.394000053405761719e+00 3.775754451751708984e+00
+2.519999980926513672e+00 4.803255558013916016e+00
+2.645999908447265625e+00 7.390709400177001953e+00
+2.772000074386596680e+00 7.298584938049316406e+00
+2.898000001907348633e+00 7.238075256347656250e+00
+3.023999929428100586e+00 7.349623203277587891e+00
+3.150000095367431641e+00 7.461916446685791016e+00
+3.276000022888183594e+00 7.528651237487792969e+00
+3.401999950408935547e+00 7.546798229217529297e+00
+3.528000116348266602e+00 7.578143119812011719e+00
+3.654000043869018555e+00 7.620040416717529297e+00
+3.779999971389770508e+00 7.609613895416259766e+00
+3.905999898910522461e+00 7.593860149383544922e+00
+4.032000064849853516e+00 7.632239341735839844e+00
+4.157999992370605469e+00 7.625663757324218750e+00
+4.283999919891357422e+00 7.638105392456054688e+00
+4.409999847412109375e+00 7.611096382141113281e+00
+4.535999774932861328e+00 7.614918231964111328e+00
+4.662000179290771484e+00 7.643285274505615234e+00
[…]

### 2015-04-15 fpp/fppmodels/201855371.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 9.241999999999999105e+00
+4.000000000000000000e+00 9.241999999999999105e+00
+8.000000000000000000e+00 9.241999999999999105e+00
+1.200000000000000000e+01 9.241999999999999105e+00
+2.500000000000000000e+01 9.241999999999999105e+00

### 2015-04-15 fpp/fppmodels/201912552.1/PHARO_K.cc

@@ -1,0 +1,124 @@
+0.000000000000000000e+00 2.637017518281936646e-02
+1.260000020265579224e-01 1.856213212013244629e+00
+2.520000040531158447e-01 3.719451904296875000e+00
+3.779999911785125732e-01 4.841462612152099609e+00
+5.040000081062316895e-01 5.489117622375488281e+00
+6.299999952316284180e-01 6.334816932678222656e+00
+7.559999823570251465e-01 6.817530155181884766e+00
+8.820000290870666504e-01 7.137898445129394531e+00
+1.008000016212463379e+00 7.566122055053710938e+00
+1.133999943733215332e+00 7.992341041564941406e+00
+1.259999990463256836e+00 8.033980369567871094e+00
+1.386000037193298340e+00 8.306855201721191406e+00
+1.511999964714050293e+00 8.447607040405273438e+00
+1.638000011444091797e+00 8.494070053100585938e+00
+1.764000058174133301e+00 8.608453750610351562e+00
+1.889999985694885254e+00 8.598946571350097656e+00
+2.016000032424926758e+00 8.612076759338378906e+00
+2.141999959945678711e+00 8.678185462951660156e+00
+2.267999887466430664e+00 8.742238998413085938e+00
+2.394000053405761719e+00 8.816954612731933594e+00
+2.519999980926513672e+00 8.890431404113769531e+00
+2.645999908447265625e+00 8.887032508850097656e+00
+2.772000074386596680e+00 8.896469116210937500e+00
+2.898000001907348633e+00 8.920278549194335938e+00
+3.023999929428100586e+00 9.004869461059570312e+00
+3.150000095367431641e+00 8.999698638916015625e+00
+3.276000022888183594e+00 9.072829246520996094e+00
+3.401999950408935547e+00 9.153480529785156250e+00
+3.528000116348266602e+00 9.264610290527343750e+00
+3.654000043869018555e+00 9.273004531860351562e+00
+3.779999971389770508e+00 9.309271812438964844e+00
+3.905999898910522461e+00 9.299513816833496094e+00
+4.032000064849853516e+00 9.366663932800292969e+00
+4.157999992370605469e+00 9.389894485473632812e+00
+4.283999919891357422e+00 9.394446372985839844e+00
+4.409999847412109375e+00 9.400336265563964844e+00
+4.535999774932861328e+00 9.416728973388671875e+00
+4.662000179290771484e+00 9.442428588867187500e+00
[…]

### 2015-04-15 fpp/fppmodels/201912552.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 9.342000000000000526e+00
+4.000000000000000000e+00 9.342000000000000526e+00
+8.000000000000000000e+00 9.342000000000000526e+00
+1.200000000000000000e+01 9.342000000000000526e+00
+2.500000000000000000e+01 9.342000000000000526e+00

### 2015-04-15 fpp/fppmodels/201929294.1/SDSS_r.cc

@@ -1,0 +1,5 @@
+2.799999999999999822e+00 9.230999999999998096e+00
+4.000000000000000000e+00 9.230999999999998096e+00
+8.000000000000000000e+00 9.230999999999998096e+00
+1.200000000000000000e+01 9.230999999999998096e+00
+2.500000000000000000e+01 9.230999999999998096e+00

### 2015-04-16 table_fpp.tex
updated FPP calculations

@@
 \startdata
-201208431.01 & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $7.0\times10^{-4}$ & $0.21$ & $7.0\times10^{-4}$ & Planet  \\
- \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $8.8\times10^{-3}$  & \color{red}  $0.940$  & \color{red}  $0.051$  & \color{red}  $0.17$  & \color{red}  $1.000$  & \color{red}  FP \\
+201208431.01 & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $5.7\times10^{-4}$ & $0.21$ & $5.7\times10^{-4}$ & Planet  \\
+ \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $1.000$  & \color{red}  $0.17$  & \color{red}  $1.000$  & \color{red}  FP \\
 201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
-201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $3.2\times10^{-3}$ & Planet  \\
-201338508.02 & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.8\times10^{-4}$ & $0.22$ & $1.8\times10^{-4}$ & Planet  \\
-201367065.01 & $0.15$ &  - & $0.717$ & $< 10^{-4}$ & $0.044$ & $0.07$ & $0.761$ & Planet\tablenotemark{c}  \\
-201367065.02 & $0.67$ &  - & $3.2\times10^{-3}$ & $< 10^{-4}$ & $4.2\times10^{-3}$ & $0.17$ & $7.4\times10^{-3}$ & Planet\tablenotemark{c}  \\
-201384232.01 & $0.44$ &  - & $1.2\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $1.4\times10^{-4}$ & Planet  \\
-201393098.01 & $0.52$ &  - & $1.6\times10^{-3}$ & $< 10^{-4}$ & $5.5\times10^{-4}$ & $0.19$ & $2.2\times10^{-3}$ & Planet  \\
+201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.0\times10^{-3}$ & $0.21$ & $2.0\times10^{-3}$ & Planet  \\
+201338508.02 & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.0\times10^{-4}$ & $0.22$ & $2.0\times10^{-4}$ & Planet  \\
+201367065.01 & $0.15$ &  - & $1.0\times10^{-4}$ & $< 10^{-4}$ & $0.026$ & $0.07$ & $0.026$ & Planet\tablenotemark{c}  \\
+201367065.02 & $0.67$ &  - & $0.239$ & $< 10^{-4}$ & $4.9\times10^{-3}$ & $0.17$ & $0.244$ & Planet\tablenotemark{c}  \\
+201384232.01 & $0.44$ &  - & $1.0\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $1.0\times10^{-3}$ & Planet  \\
+201393098.01 & $0.52$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $7.0\times10^{-4}$ & $0.19$ & $7.4\times10^{-4}$ & Planet  \\
 201403446.01 & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
-201445392.01 & $0.26$ &  - & $1.3\times10^{-3}$ & $< 10^{-4}$ & $0.012$ & $0.19$ & $0.013$ & Candidate  \\
-201445392.02 & $0.18$ &  - & $0.023$ & $< 10^{-4}$ & $0.254$ & $0.21$ & $0.277$ & Candidate  \\
-201465501.01 & $0.68$ &  - & $0.491$ & $0.022$ & $9.1\times10^{-3}$ & $0.20$ & $0.522$ & Candidate  \\
-201505350.01 & $2.69$ &  - & $0.583$ & $< 10^{-4}$ & $0.024$ & $0.07$ & $0.607$ & Planet\tablenotemark{d}  \\
-201505350.02 & $0.70$ &  - & $0.034$ & $< 10^{-4}$ & $2.3\times10^{-4}$ & $0.07$ & $0.034$ & Planet\tablenotemark{d}  \\
-201546283.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $1.1\times10^{-4}$ & Candidate\tablenotemark{a}  \\
-201549860.01 & $0.18$ &  - & $7.5\times10^{-3}$ & $0.014$ & $0.011$ & $0.22$ & $0.032$ & Candidate  \\
- \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  FP\tablenotemark{b} \\
-201565013.01 & $1.69$ &  - & $0.460$ & $0.391$ & $0.035$ & $0.06$ & $0.887$ & Candidate  \\
- \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.437$  & \color{red}  $0.562$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.999$  & \color{red}  FP \\
-201577035.01 & $0.14$ &  Y & $3.0\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.07$ & $3.6\times10^{-4}$ & Planet  \\
-201596316.01 & $0.45$ &  - & $0.017$ & $< 10^{-4}$ & $3.4\times10^{-4}$ & $0.20$ & $0.017$ & Candidate  \\
-201613023.01 & $0.08$ &  Y & $9.8\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $9.8\times10^{-4}$ & Planet  \\
-201617985.01 & $0.27$ &  - & $0.166$ & $< 10^{-4}$ & $0.053$ & $0.19$ & $0.219$ & Candidate  \\
-201629650.01 & $0.43$ &  - & $1.5\times10^{-3}$ & $< 10^{-4}$ & $2.6\times10^{-4}$ & $0.18$ & $1.8\times10^{-3}$ & Planet  \\
-201635569.01 & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.043$ & $0.06$ & $0.043$ & Candidate  \\
- \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.856$  & \color{red}  $0.142$  & \color{red}  $1.6\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP \\
-201702477.01 & $0.70$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.0\times10^{-3}$ & $0.06$ & $4.0\times10^{-3}$ & Planet  \\
-201736247.01 & $0.42$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.6\times10^{-4}$ & $0.18$ & $4.9\times10^{-4}$ & Planet  \\
-201754305.01 & $0.65$ &  - & $2.5\times10^{-3}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $5.7\times10^{-3}$ & Planet  \\
-201754305.02 & $0.38$ &  - & $1.9\times10^{-3}$ & $< 10^{-4}$ & $1.7\times10^{-3}$ & $0.22$ & $3.6\times10^{-3}$ & Planet  \\
- \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.935$  & \color{red}  $0.063$  & \color{red}  $3.2\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP \\
-201828749.01 & $0.39$ &  Y & $2.6\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $2.6\times10^{-3}$ & Candidate\tablenotemark{a}  \\
+201445392.01 & $0.26$ &  - & $0.023$ & $< 10^{-4}$ & $2.5\times10^{-3}$ & $0.19$ & $0.025$ & Candidate  \\
+201445392.02 & $0.18$ &  - & $0.024$ & $< 10^{-4}$ & $0.042$ & $0.21$ & $0.066$ & Candidate  \\
+201465501.01 & $0.68$ &  - & $0.569$ & $< 10^{-4}$ & $2.7\times10^{-3}$ & $0.20$ & $0.571$ & Candidate  \\
+201505350.01 & $2.69$ &  - & $0.088$ & $< 10^{-4}$ & $0.059$ & $0.07$ & $0.147$ & Planet\tablenotemark{d}  \\
+201505350.02 & $0.70$ &  - & $4.9\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.08$ & $4.9\times10^{-3}$ & Planet\tablenotemark{d}  \\
+201546283.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
+201549860.01 & $0.18$ &  - & $3.8\times10^{-3}$ & $< 10^{-4}$ & $2.1\times10^{-3}$ & $0.22$ & $5.9\times10^{-3}$ & Candidate\tablenotemark{a}  \\
+ \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $1.6\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $1.6\times10^{-3}$  & \color{red}  FP\tablenotemark{b} \\
+201565013.01 & $1.69$ &  - & $0.639$ & $0.250$ & $6.0\times10^{-3}$ & $0.06$ & $0.895$ & Candidate  \\
+ \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.946$  & \color{red}  $0.051$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.997$  & \color{red}  FP \\
+201577035.01 & $0.14$ &  Y & $2.8\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.07$ & $2.8\times10^{-3}$ & Planet  \\
+201596316.01 & $0.45$ &  - & $< 10^{-4}$ & $1.5\times10^{-3}$ & $2.5\times10^{-4}$ & $0.20$ & $1.8\times10^{-3}$ & Planet  \\
+201613023.01 & $0.08$ &  Y & $1.0\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $1.1\times10^{-4}$ & Planet  \\
+201617985.01 & $0.27$ &  - & $7.6\times10^{-4}$ & $< 10^{-4}$ & $0.013$ & $0.19$ & $0.014$ & Candidate  \\
+201629650.01 & $0.43$ &  - & $2.9\times10^{-4}$ & $< 10^{-4}$ & $1.8\times10^{-4}$ & $0.18$ & $4.8\times10^{-4}$ & Planet  \\
+201635569.01 & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.014$ & $0.06$ & $0.014$ & Candidate  \\
+ \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.797$  & \color{red}  $0.201$  & \color{red}  $1.1\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP \\
+201702477.01 & $0.70$ &  - & $< 10^{-4}$ & $2.1\times10^{-4}$ & $2.3\times10^{-3}$ & $0.06$ & $2.6\times10^{-3}$ & Planet  \\
+201736247.01 & $0.42$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.1\times10^{-4}$ & $0.18$ & $2.1\times10^{-4}$ & Planet  \\
+201754305.01 & $0.65$ &  - & $8.4\times10^{-4}$ & $< 10^{-4}$ & $1.7\times10^{-3}$ & $0.21$ & $2.5\times10^{-3}$ & Planet  \\
+201754305.02 & $0.38$ &  - & $5.5\times10^{-3}$ & $< 10^{-4}$ & $1.0\times10^{-3}$ & $0.21$ & $6.5\times10^{-3}$ & Planet  \\
+ \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.886$  & \color{red}  $0.103$  & \color{red}  $6.4\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.990$  & \color{red}  FP \\
+201828749.01 & $0.39$ &  Y & $0.013$ & $< 10^{-4}$ & $2.2\times10^{-4}$ & $0.17$ & $0.014$ & Candidate  \\
 201855371.01 & $0.62$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet  \\
-201912552.01 & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet  \\
- \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $2.8\times10^{-4}$  & \color{red}  $0.07$  & \color{red}  $2.9\times10^{-4}$  & \color{red}  FP\tablenotemark{b}
+201912552.01 & $0.47$ &  Y & $< 10^{-4}$ & $2.4\times10^{-4}$ & $< 10^{-4}$ & $0.21$ & $2.5\times10^{-4}$ & Planet  \\
+ \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}  $0.700$  & \color{red}  $< 10^{-4}$  & \color{red}  $2.0\times10^{-3}$  & \color{red}  $0.07$  & \color{red}  $0.702$  & \color{red}  FP\tablenotemark{b}
 

### 2015-04-16 fpp/write_fpptable.py

@@ -84,7 +84,7 @@ fout.write(r"""
 \startdata
 """)
 
-folders = glob.glob('fppmodels/*')
+folders = glob.glob('fppmodels/20*')
 folders.sort()
 for f in folders:
     resultsfile = f + '/results.txt'

### 2015-05-11 fpp/write_ini.py
re-running with min_logg=2.3

@@ -65,7 +65,7 @@ def write_ini(epic_id, i=1, photerr_inflate=3):
         star_config[b] = [mag,err*photerr_inflate]
     star_config['Kepler'] = mags['Kepler']
     star_config['maxAV'] = 0.2
-    star_config['logg'] = (4, 1.)
+    star_config['min_logg'] = 2.3
 
     config['constraints'] = {}
     config['constraints']['maxrad'] = (APERTURES.ix[epic_id, 'radius'] + 1)*4

### 2015-05-12 table_fpp.tex
something

@@
 \startdata
-201208431.01 & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $5.7\times10^{-4}$ & $0.21$ & $5.7\times10^{-4}$ & Planet  \\
- \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $1.000$  & \color{red}  $0.17$  & \color{red}  $1.000$  & \color{red}  FP \\
-201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
-201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.0\times10^{-3}$ & $0.21$ & $2.0\times10^{-3}$ & Planet  \\
-201338508.02 & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.0\times10^{-4}$ & $0.22$ & $2.0\times10^{-4}$ & Planet  \\
-201367065.01 & $0.15$ &  - & $1.0\times10^{-4}$ & $< 10^{-4}$ & $0.026$ & $0.07$ & $0.026$ & Planet\tablenotemark{c}  \\
-201367065.02 & $0.67$ &  - & $0.239$ & $< 10^{-4}$ & $4.9\times10^{-3}$ & $0.17$ & $0.244$ & Planet\tablenotemark{c}  \\
-201384232.01 & $0.44$ &  - & $1.0\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $1.0\times10^{-3}$ & Planet  \\
-201393098.01 & $0.52$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $7.0\times10^{-4}$ & $0.19$ & $7.4\times10^{-4}$ & Planet  \\
+201208431.01 & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $5.6\times10^{-4}$ & $0.21$ & $5.6\times10^{-4}$ & Planet  \\
+ \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $0.837$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.163$  & \color{red}  $0.20$  & \color{red}  $1.000$  & \color{red}  FP \\
+201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
+201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.5\times10^{-3}$ & $0.21$ & $1.5\times10^{-3}$ & Planet  \\
+201338508.02 & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.8\times10^{-4}$ & $0.21$ & $1.8\times10^{-4}$ & Planet  \\
+201367065.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.3\times10^{-4}$ & $0.22$ & $1.3\times10^{-4}$ & Planet\tablenotemark{c}  \\
+201367065.02 & $0.67$ &  - & $3.4\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $3.8\times10^{-4}$ & Planet\tablenotemark{c}  \\
+201384232.01 & $0.44$ &  - & $2.5\times10^{-3}$ & $3.9\times10^{-4}$ & $< 10^{-4}$ & $0.14$ & $2.9\times10^{-3}$ & Planet  \\
+201393098.01 & $0.52$ &  - & $1.7\times10^{-4}$ & $< 10^{-4}$ & $8.5\times10^{-4}$ & $0.19$ & $1.0\times10^{-3}$ & Planet  \\
 201403446.01 & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
-201445392.01 & $0.26$ &  - & $0.023$ & $< 10^{-4}$ & $2.5\times10^{-3}$ & $0.19$ & $0.025$ & Candidate  \\
-201445392.02 & $0.18$ &  - & $0.024$ & $< 10^{-4}$ & $0.042$ & $0.21$ & $0.066$ & Candidate  \\
-201465501.01 & $0.68$ &  - & $0.569$ & $< 10^{-4}$ & $2.7\times10^{-3}$ & $0.20$ & $0.571$ & Candidate  \\
-201505350.01 & $2.69$ &  - & $0.088$ & $< 10^{-4}$ & $0.059$ & $0.07$ & $0.147$ & Planet\tablenotemark{d}  \\
-201505350.02 & $0.70$ &  - & $4.9\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.08$ & $4.9\times10^{-3}$ & Planet\tablenotemark{d}  \\
+201445392.01 & $0.26$ &  - & $0.022$ & $2.8\times10^{-4}$ & $3.2\times10^{-3}$ & $0.19$ & $0.025$ & Candidate  \\
+201445392.02 & $0.18$ &  - & $2.6\times10^{-3}$ & $< 10^{-4}$ & $0.048$ & $0.21$ & $0.051$ & Candidate  \\
+201465501.01 & $0.68$ &  - & $< 10^{-4}$ & $0.152$ & $6.6\times10^{-3}$ & $0.20$ & $0.159$ & Candidate  \\
+201505350.01 & $2.69$ &  - & $0.810$ & $< 10^{-4}$ & $0.018$ & $0.07$ & $0.828$ & Planet\tablenotemark{d}  \\
+201505350.02 & $0.70$ &  - & $0.026$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $0.026$ & Planet\tablenotemark{d}  \\
 201546283.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
-201549860.01 & $0.18$ &  - & $3.8\times10^{-3}$ & $< 10^{-4}$ & $2.1\times10^{-3}$ & $0.22$ & $5.9\times10^{-3}$ & Candidate\tablenotemark{a}  \\
- \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $1.6\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $1.6\times10^{-3}$  & \color{red}  FP\tablenotemark{b} \\
-201565013.01 & $1.69$ &  - & $0.639$ & $0.250$ & $6.0\times10^{-3}$ & $0.06$ & $0.895$ & Candidate  \\
- \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.946$  & \color{red}  $0.051$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.997$  & \color{red}  FP \\
-201577035.01 & $0.14$ &  Y & $2.8\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.07$ & $2.8\times10^{-3}$ & Planet  \\
-201596316.01 & $0.45$ &  - & $< 10^{-4}$ & $1.5\times10^{-3}$ & $2.5\times10^{-4}$ & $0.20$ & $1.8\times10^{-3}$ & Planet  \\
-201613023.01 & $0.08$ &  Y & $1.0\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $1.1\times10^{-4}$ & Planet  \\
-201617985.01 & $0.27$ &  - & $7.6\times10^{-4}$ & $< 10^{-4}$ & $0.013$ & $0.19$ & $0.014$ & Candidate  \\
-201629650.01 & $0.43$ &  - & $2.9\times10^{-4}$ & $< 10^{-4}$ & $1.8\times10^{-4}$ & $0.18$ & $4.8\times10^{-4}$ & Planet  \\
-201635569.01 & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.014$ & $0.06$ & $0.014$ & Candidate  \\
- \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.797$  & \color{red}  $0.201$  & \color{red}  $1.1\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP \\
-201702477.01 & $0.70$ &  - & $< 10^{-4}$ & $2.1\times10^{-4}$ & $2.3\times10^{-3}$ & $0.06$ & $2.6\times10^{-3}$ & Planet  \\
-201736247.01 & $0.42$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.1\times10^{-4}$ & $0.18$ & $2.1\times10^{-4}$ & Planet  \\
-201754305.01 & $0.65$ &  - & $8.4\times10^{-4}$ & $< 10^{-4}$ & $1.7\times10^{-3}$ & $0.21$ & $2.5\times10^{-3}$ & Planet  \\
-201754305.02 & $0.38$ &  - & $5.5\times10^{-3}$ & $< 10^{-4}$ & $1.0\times10^{-3}$ & $0.21$ & $6.5\times10^{-3}$ & Planet  \\
- \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.886$  & \color{red}  $0.103$  & \color{red}  $6.4\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.990$  & \color{red}  FP \\
-201828749.01 & $0.39$ &  Y & $0.013$ & $< 10^{-4}$ & $2.2\times10^{-4}$ & $0.17$ & $0.014$ & Candidate  \\
-201855371.01 & $0.62$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet  \\
-201912552.01 & $0.47$ &  Y & $< 10^{-4}$ & $2.4\times10^{-4}$ & $< 10^{-4}$ & $0.21$ & $2.5\times10^{-4}$ & Planet  \\
- \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}  $0.700$  & \color{red}  $< 10^{-4}$  & \color{red}  $2.0\times10^{-3}$  & \color{red}  $0.07$  & \color{red}  $0.702$  & \color{red}  FP\tablenotemark{b}
-
+201549860.01 & $0.18$ &  - & $2.1\times10^{-4}$ & $< 10^{-4}$ & $2.2\times10^{-3}$ & $0.22$ & $2.4\times10^{-3}$ & Candidate\tablenotemark{a}  \\
+ \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $1.5\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $1.5\times10^{-3}$  & \color{red}  FP\tablenotemark{b} \\
+201565013.01 & $1.69$ &  - & $0.846$ & $9.3\times10^{-3}$ & $5.6\times10^{-3}$ & $0.07$ & $0.861$ & Candidate  \\
+ \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.610$  & \color{red}  $0.383$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.993$  & \color{red}  FP \\
+201577035.01 & $0.14$ &  Y & $7.0\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.08$ & $7.0\times10^{-3}$ & Planet  \\
+201596316.01 & $0.45$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.8\times10^{-4}$ & $0.20$ & $3.8\times10^{-4}$ & Planet  \\
+201613023.01 & $0.08$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $< 10^{-4}$ & Planet  \\
+201617985.01 & $0.27$ &  - & $1.9\times10^{-3}$ & $< 10^{-4}$ & $0.015$ & $0.20$ & $0.017$ & Candidate  \\
+201629650.01 & $0.43$ &  - & $2.1\times10^{-3}$ & $< 10^{-4}$ & $1.6\times10^{-4}$ & $0.17$ & $2.3\times10^{-3}$ & Planet  \\
+201635569.01 & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $5.3\times10^{-3}$ & $0.05$ & $5.3\times10^{-3}$ & Planet  \\
+ \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.925$  & \color{red}  $0.072$  & \color{red}  $1.3\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.997$  & \color{red}  FP \\
+201702477.01 & $0.70$ &  - & $0.343$ & $0.039$ & $1.3\times10^{-3}$ & $0.07$ & $0.384$ & Candidate  \\
+201736247.01 & $0.42$ &  - & $9.2\times10^{-3}$ & $< 10^{-4}$ & $2.3\times10^{-4}$ & $0.17$ & $9.4\times10^{-3}$ & Planet  \\
+201754305.01 & $0.65$ &  - & $1.1\times10^{-3}$ & $1.2\times10^{-4}$ & $1.5\times10^{-3}$ & $0.21$ & $2.7\times10^{-3}$ & Planet  \\
+201754305.02 & $0.38$ &  - & $2.7\times10^{-3}$ & $< 10^{-4}$ & $7.5\times10^{-4}$ & $0.21$ & $3.5\times10^{-3}$ & Planet  \\
+ \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.966$  & \color{red}  $0.022$  & \color{red}  $4.4\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.989$  & \color{red}  FP \\
+201828749.01 & $0.39$ &  Y & $0.028$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $0.028$ & Candidate  \\
+201855371.01 & $0.62$ &  - & $3.4\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $4.1\times10^{-4}$ & Planet  \\
+201912552.01 & $0.47$ &  Y & $8.4\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $8.4\times10^{-4}$ & Planet  \\
+ \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}  $0.240$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.020$  & \color{red}  $0.07$  & \color{red}  $0.260$  & \color{red}  FP\tablenotemark{b}
 \enddata
@@
 \tablenotetext{a}{Despite low FPP, returned to candidate status 
-out of abundance of caution due
-to secondary star detection within or near photometric aperture.}
+out of abundance of caution due to secondary star detection within or near photometric aperture.}
 \tablenotetext{b}{Declared a false positive due to noise modeling systematics (see \S\ref{sec:systematics}).}

### 2015-05-12 fpp/write_fpptable.py

@@ -140,8 +140,7 @@ for f in folders:
     fout.write(format_line(line,FPP,force_fp=force_fp))
 
 
-fout.write(r"""
-\enddata
+fout.write(r"""\enddata
 \tablecomments{Results of the \texttt{vespa} astrophysical 
 false positive probability calculations for all candidates.  
 Likely false positives (FPP $> 0.9$, or otherwise designated)
@@ -156,8 +155,7 @@ below 1\% threshold.}
 \tablenotetext{2}{Whether adaptive optics observation is presented in this paper.}
 \tablenotetext{3}{Integrated planet occurrence rate assumed between 0.7$\times$ and 1.3$\times$ the candidate radius}
 \tablenotetext{a}{Despite low FPP, returned to candidate status 
-out of abundance of caution due
-to secondary star detection within or near photometric aperture.}
+out of abundance of caution due to secondary star detection within or near photometric aperture.}
 \tablenotetext{b}{Declared a false positive due to noise modeling systematics (see \S\ref{sec:systematics}).}
 \tablenotetext{c}{Identified as planets by \citet{Crossfield15}.}
 \tablenotetext{d}{Identified as planets by \citet{Armstrong15b}.}

### 2015-05-12 fpp/write_ini.py

@@ -33,9 +33,10 @@ def max_secondary(epic_id, i=1):
 
 
 def write_ini(epic_id, i=1, photerr_inflate=3):
-    filename ='{}/{}.{}/fpp.ini'.format(FOLDER, epic_id, i)
-    config = ConfigObj()
-    config.filename = filename
+    filename = '{}/{}.{}/fpp.ini'.format(FOLDER, epic_id, i)
+    star_filename = '{}/{}.{}/star.ini'.format(FOLDER, epic_id, i)
+    config = ConfigObj(filename)
+    star_config = ConfigObj(star_filename)
 
     config['name'] = '{}.{}'.format(epic_id, i)
         
@@ -55,12 +56,11 @@ def write_ini(epic_id, i=1, photerr_inflate=3):
     config['period'] = period
 
     mags = all_mags(epic_id)
-    config['mags'] = {}
     for b in ['B','V','g','r','i','J','H','K',
               'W1','W2','W3']:
         mag, err = (mags[b], mags['{}err'.format(b)])
-        config['mags'][b] = [mag,err*photerr_inflate]
-    config['mags']['Kepler'] = mags['Kepler']
+        star_config[b] = [mag,err*photerr_inflate]
+    star_config['Kepler'] = mags['Kepler']
 
     config['constraints'] = {}
     config['constraints']['maxrad'] = (APERTURES.ix[epic_id, 'radius'] + 1)*4
@@ -70,7 +70,8 @@ def write_ini(epic_id, i=1, photerr_inflate=3):
         config['constraints']['ccfiles'] = [os.path.basename(f)
                                             for f in ccfiles]
     config.write()
-
+    star_config.write()
+    
 def write_trsig(epic_id, i=1, redo=False):
     trsig_file = '{}/{}.{}/trsig.pkl'.format(FOLDER, epic_id, i)
     if not os.path.exists(trsig_file) and not redo:

### 2015-05-14 table_fpp.tex

@@
 \startdata
-201208431.01 & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $5.6\times10^{-4}$ & $0.21$ & $5.6\times10^{-4}$ & Planet  \\
- \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $0.837$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.163$  & \color{red}  $0.20$  & \color{red}  $1.000$  & \color{red}  FP \\
-201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
-201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.5\times10^{-3}$ & $0.21$ & $1.5\times10^{-3}$ & Planet  \\
-201338508.02 & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.8\times10^{-4}$ & $0.21$ & $1.8\times10^{-4}$ & Planet  \\
-201367065.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.3\times10^{-4}$ & $0.22$ & $1.3\times10^{-4}$ & Planet\tablenotemark{c}  \\
-201367065.02 & $0.67$ &  - & $3.4\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $3.8\times10^{-4}$ & Planet\tablenotemark{c}  \\
-201384232.01 & $0.44$ &  - & $2.5\times10^{-3}$ & $3.9\times10^{-4}$ & $< 10^{-4}$ & $0.14$ & $2.9\times10^{-3}$ & Planet  \\
-201393098.01 & $0.52$ &  - & $1.7\times10^{-4}$ & $< 10^{-4}$ & $8.5\times10^{-4}$ & $0.19$ & $1.0\times10^{-3}$ & Planet  \\
-201403446.01 & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
-201445392.01 & $0.26$ &  - & $0.022$ & $2.8\times10^{-4}$ & $3.2\times10^{-3}$ & $0.19$ & $0.025$ & Candidate  \\
-201445392.02 & $0.18$ &  - & $2.6\times10^{-3}$ & $< 10^{-4}$ & $0.048$ & $0.21$ & $0.051$ & Candidate  \\
-201465501.01 & $0.68$ &  - & $< 10^{-4}$ & $0.152$ & $6.6\times10^{-3}$ & $0.20$ & $0.159$ & Candidate  \\
-201505350.01 & $2.69$ &  - & $0.810$ & $< 10^{-4}$ & $0.018$ & $0.07$ & $0.828$ & Planet\tablenotemark{d}  \\
-201505350.02 & $0.70$ &  - & $0.026$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $0.026$ & Planet\tablenotemark{d}  \\
+201208431.01 & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $8.0\times10^{-4}$ & $0.21$ & $8.0\times10^{-4}$ & Planet  \\
+ \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $1.000$  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $1.000$  & \color{red}  FP \\
+201295312.01 & $0.04$ &  Y & $7.5\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $7.5\times10^{-4}$ & Candidate\tablenotemark{a}  \\
+201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.2\times10^{-3}$ & $0.22$ & $2.2\times10^{-3}$ & Planet  \\
+201338508.02 & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.6\times10^{-4}$ & $0.22$ & $1.6\times10^{-4}$ & Planet  \\
+201367065.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.0\times10^{-4}$ & $0.22$ & $2.0\times10^{-4}$ & Planet\tablenotemark{c}  \\
+201367065.02 & $0.67$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Planet\tablenotemark{c}  \\
+201384232.01 & $0.44$ &  - & $2.1\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.19$ & $2.2\times10^{-3}$ & Planet  \\
+201393098.01 & $0.52$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $6.9\times10^{-4}$ & $0.21$ & $6.9\times10^{-4}$ & Planet  \\
+201403446.01 & $0.18$ &  Y & $1.2\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $1.2\times10^{-3}$ & Candidate\tablenotemark{a}  \\
+201445392.01 & $0.26$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.5\times10^{-3}$ & $0.20$ & $2.6\times10^{-3}$ & Planet  \\
+201445392.02 & $0.18$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.032$ & $0.22$ & $0.032$ & Candidate  \\
+201465501.01 & $0.68$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $5.4\times10^{-3}$ & $0.22$ & $5.4\times10^{-3}$ & Planet  \\
+201505350.01 & $2.69$ &  - & $8.5\times10^{-3}$ & $< 10^{-4}$ & $2.5\times10^{-3}$ & $0.09$ & $0.011$ & Planet\tablenotemark{d}  \\
+201505350.02 & $0.70$ &  - & $1.6\times10^{-3}$ & $< 10^{-4}$ & $4.8\times10^{-4}$ & $0.05$ & $2.1\times10^{-3}$ & Planet\tablenotemark{d}  \\
 201546283.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
-201549860.01 & $0.18$ &  - & $2.1\times10^{-4}$ & $< 10^{-4}$ & $2.2\times10^{-3}$ & $0.22$ & $2.4\times10^{-3}$ & Candidate\tablenotemark{a}  \\
+201549860.01 & $0.18$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.0\times10^{-3}$ & $0.21$ & $2.0\times10^{-3}$ & Candidate\tablenotemark{a}  \\
  \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $1.5\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $1.5\times10^{-3}$  & \color{red}  FP\tablenotemark{b} \\
-201565013.01 & $1.69$ &  - & $0.846$ & $9.3\times10^{-3}$ & $5.6\times10^{-3}$ & $0.07$ & $0.861$ & Candidate  \\
- \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.610$  & \color{red}  $0.383$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.993$  & \color{red}  FP \\
-201577035.01 & $0.14$ &  Y & $7.0\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.08$ & $7.0\times10^{-3}$ & Planet  \\
-201596316.01 & $0.45$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.8\times10^{-4}$ & $0.20$ & $3.8\times10^{-4}$ & Planet  \\
-201613023.01 & $0.08$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $< 10^{-4}$ & Planet  \\
-201617985.01 & $0.27$ &  - & $1.9\times10^{-3}$ & $< 10^{-4}$ & $0.015$ & $0.20$ & $0.017$ & Candidate  \\
-201629650.01 & $0.43$ &  - & $2.1\times10^{-3}$ & $< 10^{-4}$ & $1.6\times10^{-4}$ & $0.17$ & $2.3\times10^{-3}$ & Planet  \\
-201635569.01 & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $5.3\times10^{-3}$ & $0.05$ & $5.3\times10^{-3}$ & Planet  \\
- \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.925$  & \color{red}  $0.072$  & \color{red}  $1.3\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.997$  & \color{red}  FP \\
-201702477.01 & $0.70$ &  - & $0.343$ & $0.039$ & $1.3\times10^{-3}$ & $0.07$ & $0.384$ & Candidate  \\
-201736247.01 & $0.42$ &  - & $9.2\times10^{-3}$ & $< 10^{-4}$ & $2.3\times10^{-4}$ & $0.17$ & $9.4\times10^{-3}$ & Planet  \\
-201754305.01 & $0.65$ &  - & $1.1\times10^{-3}$ & $1.2\times10^{-4}$ & $1.5\times10^{-3}$ & $0.21$ & $2.7\times10^{-3}$ & Planet  \\
-201754305.02 & $0.38$ &  - & $2.7\times10^{-3}$ & $< 10^{-4}$ & $7.5\times10^{-4}$ & $0.21$ & $3.5\times10^{-3}$ & Planet  \\
- \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.966$  & \color{red}  $0.022$  & \color{red}  $4.4\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.989$  & \color{red}  FP \\
-201828749.01 & $0.39$ &  Y & $0.028$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $0.028$ & Candidate  \\
-201855371.01 & $0.62$ &  - & $3.4\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $4.1\times10^{-4}$ & Planet  \\
-201912552.01 & $0.47$ &  Y & $8.4\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $8.4\times10^{-4}$ & Planet  \\
- \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}  $0.240$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.020$  & \color{red}  $0.07$  & \color{red}  $0.260$  & \color{red}  FP\tablenotemark{b}
+201565013.01 & $1.69$ &  - & $0.802$ & $0.058$ & $5.9\times10^{-3}$ & $0.07$ & $0.866$ & Candidate  \\
+ \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.668$  & \color{red}  $0.332$  & \color{red}  $2.4\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $1.000$  & \color{red}  FP \\
+201577035.01 & $0.14$ &  Y & $7.5\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.10$ & $7.6\times10^{-4}$ & Planet  \\
+201596316.01 & $0.45$ &  - & $1.0\times10^{-3}$ & $< 10^{-4}$ & $5.9\times10^{-3}$ & $0.07$ & $6.9\times10^{-3}$ & Planet  \\
+201613023.01 & $0.08$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet  \\
+201617985.01 & $0.27$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.013$ & $0.18$ & $0.013$ & Candidate  \\
+201629650.01 & $0.43$ &  - & $1.1\times10^{-3}$ & $< 10^{-4}$ & $3.4\times10^{-4}$ & $0.21$ & $1.4\times10^{-3}$ & Planet  \\
+201635569.01 & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.5\times10^{-3}$ & $0.05$ & $4.5\times10^{-3}$ & Planet  \\
+ \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.924$  & \color{red}  $0.076$  & \color{red}  $1.0\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $1.000$  & \color{red}  FP \\
+201702477.01 & $0.70$ &  - & $0.150$ & $2.4\times10^{-3}$ & $2.4\times10^{-3}$ & $0.06$ & $0.155$ & Candidate  \\
+201736247.01 & $0.42$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.1\times10^{-4}$ & $0.19$ & $2.7\times10^{-4}$ & Planet  \\
+201754305.01 & $0.65$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.4\times10^{-3}$ & $0.22$ & $1.4\times10^{-3}$ & Planet  \\
+201754305.02 & $0.38$ &  - & $1.1\times10^{-4}$ & $< 10^{-4}$ & $7.8\times10^{-4}$ & $0.22$ & $8.9\times10^{-4}$ & Planet  \\
+ \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.980$  & \color{red}  $2.5\times10^{-3}$  & \color{red}  $7.3\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.984$  & \color{red}  FP \\
+201828749.01 & $0.39$ &  Y & $0.242$ & $< 10^{-4}$ & $1.5\times10^{-3}$ & $0.07$ & $0.244$ & Candidate  \\
+ \color{red} 201855371.01  & \color{red}  $0.62$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.925$  & \color{red}  $0.01$  & \color{red}  $0.925$  & \color{red}  FP \\
+201912552.01 & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet  \\
+ \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $1.000$  & \color{red}  $0.00$  & \color{red}  $1.000$  & \color{red}  FP\tablenotemark{b}
 \enddata

### 2015-05-14 fpp/fppmodels/copy_starmodels.py
added file

@@ -1,0 +1,15 @@
+#!/usr/bin/env python
+
+import numpy as np
+import os, os.path, shutil
+
+dest_folder = os.path.expanduser('~/WWW/public/k2/starmodels')
+
+all_cands = np.unique(np.loadtxt('all.list', dtype=int))
+
+for cand in all_cands:
+    folder = '{}.1'.format(cand)
+    h5file = '{}/dartmouth_starmodel_single.h5'.format(folder)
+    triangle = '{}/dartmouth_triangle_single_physical.png'.format(folder)
+
+    

### 2015-06-10 ms.tex
referee report notes

--- 2015-03-26 ms.tex
@@
 \newcommand{\Nlimbo}{12} %adds up to 36
+
+\newcommand{\change}[1]{\textbf{#1}}
 
@@
 Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
-hosting a $2.24 \pm 0.25 R_\odot$ planet with $T_{eq} = 271 \pm 16$ K and an
+hosting a \change{$2.24 \pm 0.25$ $R_\oplus$} planet with $T_{eq} = 271 \pm 16$ K and an
 orbital period of 33 days.
@@
 module.
-We then run an MCMC chain using \texttt{emcee} \citep{Foreman-Mackey12},
-an implementation of the affine-invariant ensemble sampler of
-\citet{Goodman10}
+\change{We then run an MCMC chain using \texttt{MULTINEST} \citep{Feroz09},
+an implementation of a multimodal nested sampling algorithm,}
 for each host star conditioned on the observed
@@
 
-In order to account for the effects of model uncertainties, we also run
-MCMC chains with photometric errors inflated artificially by a factor of three.
-The observed photometric parameters are then consistent with spectroscopically-derived
-parameters for stars with published spectra, and consistent with typical uncertainties
+As our stellar results are model-dependent, we caution users who intend to use these 
+parameters for other works, such as exoplanet population studies. When available, 
+stellar parameters inferred through other techniques such as asteroseismology or 
+spectroscopy should supersede these values. 
+The observed photometric parameters  then consistent with spectroscopically-derived
+parameters for stars with published spectra, and consistent with typical
+model-dependent uncertainties
 from photometric data \citep[e.g.][]{Huber14}.
-We provide full chains using both inflated and un-inflated
-uncertainties,\footnote{\url{http://www.astro.princeton.edu/~tdm/k2/}}
-though in the rest of this work (and in Table 2) we adopt
-the results obtained using the inflated values.
+We provide full samples of our posteriors on the physical parameters for each 
+star\footnote{\url{http://www.astro.princeton.edu/~tdm/k2/}}.
 
@@
 described by \paperit.
-We use \texttt{emcee} to sample from the posterior probability distribution
+We use \texttt{emcee} \citep{Foreman-Mackey12}, an implementation of the
+affine-invariant ensemble sampler of \citep{Goodman10}
+ to sample from the posterior probability distribution
 for the stellar---limb darkening coefficients, mass, radius, and effective
@@
 conversations and suggestions which improved the quality of this manuscript.
+\change{We also thank Keivan Stassun (Vanderbilt) for his insights into 
+extinction and stellar parameters in both \kep\ and \KT.
+We thank the anonymous referee for their insightful comments as well.}
 

### 2015-06-10 ms.tex
referee report notes

@@
 
-As our stellar results are model-dependent, we caution users who intend to use these 
+\change{As our stellar results are model-dependent, we caution users who intend to use these 
 parameters for other works, such as exoplanet population studies. When available, 
@@
 We provide full samples of our posteriors on the physical parameters for each 
-star\footnote{\url{http://www.astro.princeton.edu/~tdm/k2/}}.
+star\footnote{\url{http://www.astro.princeton.edu/~tdm/k2/}}.}
 

### 2015-06-17 ms.tex
referee comments

@@
 
-\newcommand{\Nfp}{6}
-\newcommand{\Nvalidated}{18}
-\newcommand{\Nlimbo}{12} %adds up to 36
+\newcommand{\Nfp}{7}
+\newcommand{\Nvalidated}{20}
+\newcommand{\Nlimbo}{9} %adds up to 36
+\newcommand{\Nvalnew}{16} % 4 previously validated
 
@@
 adaptive optics imaging with an automated transit analysis scheme to validate
-\Nvalidated\ candidates as planets
+\Nvalidated\ candidates as planets, \Nvalnew\ for the first time,
 and identify \Nfp\ candidates as likely false positives.
@@
 We record the $B$, $V$, $g'$, $r'$, and $i'$ magnitudes and their
-uncertainties from the AAVSO Photometric all-sky survey (APASS) DR6
+uncertainties from the AAVSO Photometric All-Sky Survey (APASS) DR6
 \citep{Henden14}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
@@
 module.
-\change{We then run an MCMC chain using \texttt{MULTINEST} \citep{Feroz09},
+\change{We then run an MCMC \btmtodo{still a chain?} using \texttt{MULTINEST} \citep{Feroz09},
 an implementation of a multimodal nested sampling algorithm,}
@@
 of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}, and a Salpeter-slope
-prior on mass (up to the maximum mass available in the model grids of $3.7$ $M_\odot$).
+prior on mass up to the maximum mass available in the model grids of $3.7$ $M_\odot$.
+
+\change{During the sampling process, we fit for galactic
+extinction as one of our physical parameters.
+For each star's position on the sky, we retrieve the calculated extinction at an infinite distance
+along that line of sight from the NED \btmtodo{acronym}, which reports the 
+\citet{Schlafly11} recalibration of the \citet{Schlegel98} extinction map as measured by
+COBE/DIRBE and IRAS/ISSA. 
+The NED database returns the extinction in all relevant bandpasses except those used by
+WISE, assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}.
+We include the WISE bandpasses by applying the relative extinction values between 
+SDSS, 2MASS, and WISE calculated by \citep{Davenport14}.
+In each step of our fitting process, we draw an $A_V$, calculate the expected extinction
+in all bandpasses $A_X$, and then measure the likelihood of our model stellar fit to the 
+observed apparent magnitudes.
+We apply a uniform prior ranging from zero to the obtained maximum extinction value and
+marginalize over extinction in our final determination of stellar parameters. }
 
@@
 star\footnote{\url{http://www.astro.princeton.edu/~tdm/k2/}}.}
+
+\change{\citet{Bastien14} use observations of stellar ``flicker'' to suggest that 
+approximately 50 percent of planet host stars have evolved off the
+main sequence onto the subgiant branch, so that both the host stars and their 
+planets are larger than previously reported. 
+Similarly, in \KT\ \Ci\ we may expect to find evolved stars in a sample of planet
+candidates. 
+Indeed, we find this to be the case.
+Two stars, EPIC 201257461 and 201649426 are definitively evolved stars,
+with derived radii in excess of 8 \rsun. For approximately one third of the others,
+we find the stellar radius posterior distribution to be bimodal, with both main 
+sequence and subgiant models of the stars being consistent with the photometric
+data.
+Future observations to measure the parallaxes of these stars, such as with Gaia,
+will be helpful in differentiating between these two models to determine 
+more precisely the stellar, and thus the planetary, radii.}
 
@@
 or within one pixel of the photometric aperture of the target star. 
+\change{In creating a light curve for each star, we define photometric apertures ranging
+from 10 to 20 arcseconds for each star, as defined in Table 4.
+Given the 6-arcsecond PSF of the \kep\ telescope, we allow for the possibility
+that companions falling just outside of our aperture (within one pixel) may
+contribute to the light curve, possibly causing a false positive event.
+The search for such companions is discussed in 
+\textsection \ref{sec:background}.}
 \item The maximum allowed depth of a potential secondary eclipse event
 is the most significantly detected signal at the same
-period of the planet candidate, once the primary transit is masked out.
+period of the planet candidate, once the primary transit is masked out 
+(discussed in \textsection\ref{sec:sec}).
+\change{\texttt{vespa} does not allow for the possibility of secondary eclipses 
+larger than those observed in the \KT\ light curve for each star.}
 \item Blended stars must be allowed by the available adaptive optics
-and archival imaging data (discussed in detail below).
+and archival imaging data (discussed in detail in \textsection 
+\ref{sec:AO} and \ref{sec:background}).
+\change{\texttt{vespa} only considers stars below the detection threshold for
+the AO imaging, which is a position-dependent value following a calculated
+contrast curve for each star.}
 \end{itemize}
@@
 
-Table 4 summarizes the results of these
+Table 5 summarizes the results of these
 calculations, presenting the relative probability for each candidate
@@
 these are considered to be likely false positives.
-On the other hand, 21 candidates
+On the other hand, 23 candidates
 have FPP $<$ 1\%.
@@
 so we identify those as false positives.
-Four more of these 21 might plausibly be caused by
+Four more of these 23 might plausibly be caused by
 contamination by detected stellar companions within the photometric apertures
@@
 
-This leaves 15 candidates that we statistically validate as planets, plus three
+This leaves 19 candidates that we statistically validate as planets, plus one
 additional planets that \texttt{vespa} does not validate but have been previously
 identified in the literature \citep{Crossfield15, Armstrong15b}.
-So in total, of the 36 candidates, 18 are secure planets,
-14 of which we here validate for the first time.
+So in total, of the 36 candidates, 20 are secure planets,
+16 of which we here validate for the first time.
 
@@
 \end{figure*}
+
+\subsection{Secondary Eclipse Observations}
+\label{sec:sec}
+\change{One of the definitive signatures of a false positive binary star system masquerading
+as a transiting planet is the presence of a secondary eclipse. While a nondetection of a secondary
+does not exclude the possibility of a binary system (the orbit may be eccentric, 
+or the companion too faint for a secondary eclipse to be detectable in the noise),
+such a nondectection reduces the probability of each of the eclipsing binary false
+positive scenarios.}
+
+\change{To attempt to eliminate each eclipsing binary scenario, we first search each \KT\
+light curve to determine which secondary eclipse signals are not allowed by the data.
+We mask the transit signal of the planet in question and search for the most significant
+signal at the same period. 
+Such a scheme does not assume circular orbits: we return the most significant signal
+at any phase, not only at the midpoint between consecutive transits.}
+
+\change{We report these maximum allowable secondary eclipse depths in Table 5.
+These values are used by \texttt{vespa} as limits on the allowable secondary eclipse.
+Any models that cause a larger event, such as a background eclipsing binary 
+consisting of two equal-mass stars in a circular orbit, can be excluded by the data.
+We note that with the exception of EPIC 201505350.01, all systems with a maximum
+eclipse depth of at least one part per thousand have FPPs of 0.866 or larger.
+EPIC 201505350 is a two-planet system with the two planets near a 3:2 period
+commensurability, so in this case the ``secondary'' is actually the transits of the 
+other planet.}
 
@@
 Astrometry and photometry is derived separately for each image, and the mean and standard deviation
-of these measurements is adopted for our final values listed in Table~5.
+of these measurements is adopted for our final values listed in Table~4.
 
@@
 stars is significantly lower.
-We include all potential contaminants in Table 5.
+We include all potential contaminants in Table 4.
 We validate or eliminate each of these as a possibility based on the transit shape.
@@
 
-In Table 5, the ``maximum depth'' column represents
+In Table 4, the ``maximum depth'' column represents
 the maximum observed ``transit'' depth if the transit were actually caused
@@
 enough for signficant flux to leak in.
-Evaluating each of the systems listed in Table 5, we judge that we cannot yet
+Evaluating each of the systems listed in Table 4, we judge that we cannot yet
 rule out contamination as a potential source of the transit signal for four
@@
 low FPP scores from \texttt{vespa}, we list these systems as candidates in
-Table 4, rather than planets.  Further updates to the \texttt{vespa} code
+Table 5, rather than planets.  Further updates to the \texttt{vespa} code
 will allow consideration of ``specific'' false positive scenarios; that is,
@@
 
-\subsection{Non-Astrophysical False Positives}
+\subsection{Other Sources of False Positives}
 \label{sec:systematics}
@@
 \change{We also thank Keivan Stassun (Vanderbilt) for his insights into 
-extinction and stellar parameters in both \kep\ and \KT.
+ stellar parameters for both \kep\ and \KT, which significantly improved
+ this work.
 We thank the anonymous referee for their insightful comments as well.}
@@
 
+\btmtodo{NED?}
+
 B.T.M. is supported by the National Science Foundation Graduate Research
@@
 \end{turnpage}
+
+\include{table_bg}
+
 \include{table_fpp}
 
-\include{table_bg}
-
 \end{document}

### 2015-06-17 ms.tex
last referee comments: archival imaging

@@
 module.
-\change{We then run an MCMC \btmtodo{still a chain?} using \texttt{MULTINEST} \citep{Feroz09},
+\change{We then infer the stellar parameters using \texttt{MULTINEST} \citep{Feroz09},
 an implementation of a multimodal nested sampling algorithm,}
@@
 For each star's position on the sky, we retrieve the calculated extinction at an infinite distance
-along that line of sight from the NED \btmtodo{acronym}, which reports the 
+along that line of sight from the NASA/IPAC Extragalactic Database (NED), which reports the 
 \citet{Schlafly11} recalibration of the \citet{Schlegel98} extinction map as measured by
@@
 The planet parameters measured by this analysis are listed in Table 3.
-
-%%%
-%%%  I haven't actually done this... perhaps I can do it in response to
-%%%  referee if they ask for it...
-%%%
-% One system, EPIC 201828749, is known to be a binary through AO imaging
-% as discussed in \textsection\ref{sec:AO}.
-% In this case, we do account for the dilution induced by the companion.
-% From our relative $JHK$ photometry of the two stars, we infer an expected flux
-% ratio between the two stars in the \kep\ bandpass, inflating the transit depth
-% by this factor to account for the dilution.
-% We marginalize  \dfmtodo{More text...}
 
@@
 
-We include this extra analysis step for EPIC 201912552, considering
-the additional follow-up this target may warrant.
-We download data from the POSS I and II surveys, which imaged
-EPIC 201912552 in 1955 and 1989, respectively.
-This star has a proper motion of $-74 \pm 2$ mas yr$^{-1}$ in right ascension
- and $-122 \pm 4$ mas yr$^{-1}$ in declination, so it has moved by $8\farcs35$
-since the POSS I data were collected.
-As shown in Figure~\ref{fig:archival}, we do not detect any targets at the
-present-day location of EPIC 201912552 in either of the POSS surveys.
+\change{Five of the stars in our sample have proper motions larger than 50 mas
+yr${-1}$, so they have moved across the sky by $\gtrsim 2\farcs5$ since
+they were imaged during the first Palomar Observatory Sky Survey (POSS) in the
+1950s. 
+To rule out background companions, we download data from the POSS I
+and II surveys, which imaged these targets in 1952-1955 and 1989-1998,
+respectively.
+We also download data from the Sloan Digital Sky Survey, which imaged
+these fields between 2000 and 2009.
+As shown in Figure~\ref{fig:archival}, we do not detect any background
+targets at the present-day location of any of these stars in any of these
+images.
+}
 
 \begin{figure*}[htbp]
-\centerline{\includegraphics[width=1.0\textwidth, trim=0 6.30cm 0 6.30cm, clip=true]{f5}}
-\caption{Imaging for EPIC 201912552 from 1955 to 2002. There is no background
-object directly behind the present day location of the target (red circle) that could be missed
-by the AO observations, while modern SDSS imaging can rule out wide companions
-that may have been missed at wide separations, beyond the AO field of view.
+\centerline{\includegraphics[width=0.65\textwidth]{f5}}
+\caption{Archival maging for the five highest proper motion targets in our sample. 
+In all cases, there are no background
+objects directly behind the present day location of the target (red circle) that could be missed
+by the AO observations. Modern SDSS imaging can also rule out wide companions
+that may have been missed at wide separations, beyond the AO field of view, such as the
+companion which can be seen in the images of EPIC 201577035.
+All figures are aligned such that north is up and east to the left.
 All subplots are on the same scale.}
@@
 
-\btmtodo{NED?}
+This research has made use of the NASA/IPAC Extragalactic Database (NED) 
+which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
+under contract with the National Aeronautics and Space Administration.
 

### 2015-06-17 ms.tex
fixing numbers

@@
 \newcommand{\Nfp}{7}
-\newcommand{\Nvalidated}{20}
+\newcommand{\Nvalidated}{19}
 \newcommand{\Nlimbo}{9} %adds up to 36
@@
 \title{Stellar and Planetary Properties of \KT\ Campaign 1
-Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving
+Candidates and Validation of \Nvalnew\ Systems, Including a Planet Receiving
 Earth-like Insolation}
@@
 these are considered to be likely false positives.
-On the other hand, 23 candidates
+On the other hand, 24 candidates
 have FPP $<$ 1\%.
-Two of these are found to be caused by systematics
+Two systems, one of which is a planet candidate by the above definition,
+ are found to be caused by systematics
 in the transit search noise model (details in \S\ref{sec:systematics}), and
 so we identify those as false positives.
-Four more of these 23 might plausibly be caused by
+Four of the transit signals might plausibly be caused by
 contamination by detected stellar companions within the photometric apertures
@@
 This leaves 19 candidates that we statistically validate as planets, plus one
-additional planets that \texttt{vespa} does not validate but have been previously
+additional planet that \texttt{vespa} does not validate but has been previously
 identified in the literature \citep{Crossfield15, Armstrong15b}.
 So in total, of the 36 candidates, 20 are secure planets,
-16 of which we here validate for the first time.
+16 of which we validate here for the first time.
 
@@
 identify \Nfp\ as false positives.
-Of these planets, 4 have been previously validated in other works, while 14 are
+Of these planets, 3 have been previously validated in other works, while \Nvalnew\ are
 validated here for the first time.
@@
 by discrepancies between the models and reality.
-
-As stated in \textsection\ref{sec:stellarparams}, we infer stellar parameters using the
-Dartmouth models, with a mass upper limit of $3.7 M_\odot$.
-Given the location of the \Ci\ field with respect to the galactic plane, we expect a low
-contamination rate by halo giants.
-However, there are a few stars that are possibly miscategorized giants.
-EPIC 201257461 is identified in the RAdial Velocity Experiment (RAVE) Fourth Data Release
-as a target with $\logg = 3.18$, consistent with that of a giant star.
-It is therefore perhaps not surprising that this system is flagged as a false positive based on
-the transit shape.
-EPIC 201929294, with a proper motion of $0.010\arcsec$ yr$^{-1}$ \citep{Zacharias12}  has
-a reduced proper motion consistent with that of a giant star.
-While suggestive, this observation does not definitively provide information about the
-nature of this target.
-Likewise, our false positive analysis is neither able to confirm nor exclude the planetary
-nature of the observed transit signal around this target.
 

### 2015-06-18 ms.tex
small changes from a careful readthrough

@@
 John~Asher~Johnson\altaffilmark{\cfa},
-David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
+David~W.~Hogg\altaffilmark{\nyu,\cds,\mpia},
 % The Observers
 % (ranked by integration time x collecting area)
-Brendan~P.~Bowler\altaffilmark{\caltech, \jcpa},
+Brendan~P.~Bowler\altaffilmark{\caltech,\jcpa},
 David~W.~Latham\altaffilmark{\cfa},
 Allyson~Bieryla\altaffilmark{\cfa},
-Andrew~W.~Mann\altaffilmark{\texas, \hjs},
+Andrew~W.~Mann\altaffilmark{\texas,\hjs},
 }
@@
 orbital period of 33 days.
-We also present two new open-source software packages that enabled this analysis:
+We also present two new open-source software packages which enable this analysis:
 \texttt{isochrones}, a flexible tool for fitting theoretical stellar
@@
 discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, Mullaly15}.
-The fidelity of this sample is high: most of these planet candidates are truly planets
+The fidelity of this sample is high: most of these candidates are truly planets
 \citep{Morton11b, Fressin13, Desert15}.
@@
 approximately once every six hours.
-Over the full duration of each campaign, the targets appear to remain near the
+Over the full duration of each campaign, the targets remain near the
 same location on the detector but both the slow drift and the corrections are
@@
 We include the WISE bandpasses by applying the relative extinction values between 
-SDSS, 2MASS, and WISE calculated by \citep{Davenport14}.
-In each step of our fitting process, we draw an $A_V$, calculate the expected extinction
+SDSS, 2MASS, and WISE calculated by \citet{Davenport14}.
+In each step of our fitting process, we draw a value for $A_V$, calculate the expected extinction
 in all bandpasses $A_X$, and then measure the likelihood of our model stellar fit to the 
@@
 spectroscopy should supersede these values. 
-The observed photometric parameters  then consistent with spectroscopically-derived
+We note the observed photometric parameters are consistent with spectroscopically-derived
 parameters for stars with published spectra, and consistent with typical
@@
 Similarly, in \KT\ \Ci\ we may expect to find evolved stars in a sample of planet
-candidates. 
+candidates, although we may expect the effect to be lessened due to the 
+high galactic latitude of \Ci.
 Indeed, we find this to be the case.
 Two stars, EPIC 201257461 and 201649426 are definitively evolved stars,
-with derived radii in excess of 8 \rsun. For approximately one third of the others,
+with inferred masses less than 2 \msun but radii above 8 \rsun. 
+For approximately one third of the others,
 we find the stellar radius posterior distribution to be bimodal, with both main 
@@
 data.
+This number is consistent with our expectations of the number of subgiant 
+contaminants in the \Ci\ field (K. Stassun, private communication).
 Future observations to measure the parallaxes of these stars, such as with Gaia,
@@
 SNIFS provides simultaneous coverage from 3200\AA--9700\AA\ at a resolution
-of $\simeq1000$. Final S/N of the spectrum was $>100$ pre resolving element
+of $\simeq1000$. Final S/N of the spectrum was $>100$ per resolving element
 in the red ($\sim6000$\AA).
@@
 a radius 0.394$\pm0.038R_\odot$.
-We use these parameters instead of the derived photometric properties for this target.
+We use these parameters instead of the derived photometric properties for this target,
+although we note the two are consistent at the $1\sigma$ level.
 
@@
 We use \texttt{emcee} \citep{Foreman-Mackey12}, an implementation of the
-affine-invariant ensemble sampler of \citep{Goodman10}
+affine-invariant ensemble sampler of \citet{Goodman10}
  to sample from the posterior probability distribution
@@
 the parameters of the systematics model.
-To incorporate the stellar measurements, we approximate the constraints using
-a three-dimensional Gaussian in mass, radius, and effective temperature.
 
@@
 Therefore, high-contrast adaptive optics imaging of any systems should be
-obtained before any of these planets are placed on a planet mass-radius
-diagram.
-
+obtained before these planets are used in population inference studies.
 The planet parameters measured by this analysis are listed in Table 3.
@@
 
-Four of the presented candidates have FPP $>$90\%;
+Six of the presented candidates have FPP $>$90\%;
 these are considered to be likely false positives.
@@
 eclipse depth of at least one part per thousand have FPPs of 0.866 or larger.
-EPIC 201505350 is a two-planet system with the two planets near a 3:2 period
+The exception, EPIC 201505350, is a two-planet system with the two planets near a 3:2 period
 commensurability, so in this case the ``secondary'' is actually the transits of the 
@@
 
-This research has made use of the NASA/IPAC Extragalactic Database (NED) 
+\change{This research has made use of the NASA/IPAC Extragalactic Database (NED) 
 which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
-under contract with the National Aeronautics and Space Administration.
+under contract with the National Aeronautics and Space Administration.}
 

### 2015-06-22 RefereeResponse.txt

We thank the referee for their careful reading of this manuscript and for their insightful comments, which we think have substantially improved the manuscript. We have addressed their comments below, and also note a few other changes we have made to the text. Below is the referee report, with our comments interspersed.

——

For the substance of the analysis, I have two issues:

1. It's not clear what the authors have done to use possible secondary eclipse information. Table 4 reports a maximum secondary eclipse amplitude, but the paper doesn't describe what that means. Is it an estimate of the maximum depth that would be produced by a blended eclipsing binary? Or the maximum allowed by the data to some (unspecified) degree of confidence? It's not clear who has actually looked at the phased photometry for each system at phase 0.5 to see whether there's a secondary eclipse or not. Perhaps eclipse upper limits were derived by Foreman-Mackey et al., but if so they need to be identified more explicitly in this paper. A limit on the secondary eclipse amplitudes from the data should be factored into the FP vs. planet decision in some way that is clearly described. Does vespa use limits on the secondary eclipse? I think a separate sub-section of this paper is needed to describe the secondary eclipse portion of the analysis with maximum clarity.

We have added section 4.1 to explain how we calculate the maximum secondary eclipse depth allowed by the data and how vespa uses these values as upper limits in allowable secondary eclipses in the false positive analysis (so that any event that would create a larger secondary eclipse is disallowed).

2. The authors use archival imaging, and exploit the proper motion of EPIC 201912552, in order to eliminate closely-blended background stars. I suggest doing (or at least attempting) that for all of the new planets that they identify. The SDSS and POSS images exist, they just have to do the work. All of the planets are important, and deserve the most thorough analysis.

We agree with this point as well, in principle. In practice, this technique is not useful for all systems, as some have proper motions that are too small to gain any reasonable information. The typical proper motion of a star in our sample is ~20 mas/yr, meaning the star will move by 1” over 50 years. The POSS1 data have a PSF of ~3", so if the star has not moved by approximately that amount over the past 50 years we do not gain any appreciable power in our ability to reject chance alignment binaries. Therefore, we repeat and include these data for the stars in our sample with proper motions larger than 50 mas/yr, of which there are 5 (4 in addition to the one where we had done this previously). These are included in Fig. 5 and section 4.4.

As concerns the clarity of the paper, there are several (minor) issues:

1. In the last paragraph of Sec. 2.2, the factor of 3 seems arbitrary. It needs some discussion of why they picked that value.

We agree. The factor of three was chosen as an ad-hoc value because our previous sampling (using emcee) was not sampling the true (multimodal) posterior for each star. We have since changed to a scheme using MULTINEST, which is designed for multimodal posteriors, and we find we are able to reproduce the expected results (comparing against other stars for which photometric parameters have been derived) using the photometry directly. Therefore, we remove the factor of three and fit to the photometric data using the published uncertainties directly.

2. The three bulleted constraints on the false-positive scenarios listed in the vespa description are not very clear. For example, "Blended stars must be allowed by the available adaptive optics..." Probably that means that vespa only considers stars below the detection limits of the AO imaging? And the comment about "anywhere inside or within one pixel of the photometric aperture" - does that mean within one pixel radius of the center of the star, or one pixel from the edge of the aperture? And please remind the reader what is the radius of the aperture. These constraints are very important, and they should be re-written to be more clear and specific.

We have expanded each of these bullet points for clarity and to explain exactly how vespa uses each of these constraints.

3. Sec. 5.2 is entitled "Non-astrophysical False Positives" but it begins with the purely astrophysical case of star spots..! Perhaps Sec. 5.2 should be re-titled as "Other sources of false-positives”.

Yes, this is correct! We have changed the subsection title to “Other Sources of False Positives"

4. Some columns of Table 1 are mysterious without hunting in the text. A better caption is needed. For Table 5, the caption should refer to the Section of the text where the Max Depth column is defined.

We have enhanced captions in both of these tables for clarity. We have also added a reference to the section in which the Max Depth column is defined, as requested.

Other changes:
We have revised our stellar parameter calculations, now using MULTINEST instead of emcee. This has caused our stellar parameters to change slightly, which has caused our planet parameters to change slightly.

We have added a discussion of how we calculate and marginalize over galactic extinction into section 2.2.

### 2015-06-22 table_fpp.tex

@@
 below 1\% threshold.}
-\tablenotetext{1}{Maximum depth of potential secondary eclipse signal.}
+\tablenotetext{1}{Maximum depth of potential secondary eclipse signal as described in \textsection \ref{sec:sec}.}
 \tablenotetext{2}{Whether adaptive optics observation is presented in this paper.}
-\tablenotetext{3}{Integrated planet occurrence rate assumed between 0.7$\times$ and 1.3$\times$ the candidate radius}
+\tablenotetext{3}{Integrated planet occurrence rate assumed between 0.7$\times$ and 1.3$\times$ the candidate radius.}
 \tablenotetext{a}{Despite low FPP, returned to candidate status 

### 2015-06-22 ms.tex

@@
 For each candidate, we fit the light curve using a physical transit model
-\citep{Mandel02, Kipping10b} simultaneously with the systematics model
-described by \paperit.
+\citep{Mandel02, Kipping10b} simultaneously with a systematics model similar
+to the one described by \paperit.
 We use \texttt{emcee} \citep{Foreman-Mackey12}, an implementation of the
@@
 light curve and the measured stellar properties.
+
+\change{%
 Following \paperit, the likelihood function that we use is marginalized over
-the parameters of the systematics model.
+the weights of the ``eigen light curves'' in the linear systematics model.
+Unlike \paperit, we include an empirical Gaussian prior on the weights
+determined by robustly computing the distribution of weights across the full
+set of Campaign~1 light curves.
+This prior mitigates the incorrect detection of false signals induced by
+stellar variability---as discussed below in Section~\ref{sec:systematics}---so
+we exclude these candidates (EPIC 201929294 and EPIC 201555883) from the Table
+of results.
+}
 
@@
  this work.
-We thank the anonymous referee for their insightful comments as well.}
+We thank the anonymous referee for their comments and suggestions.}
 

### 2015-06-22 table_fpp.tex
fpp table rewritten

--- 2015-05-14 table_fpp.tex
@@
 \startdata
-201208431.01 & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $8.0\times10^{-4}$ & $0.21$ & $8.0\times10^{-4}$ & Planet  \\
- \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $1.000$  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $1.000$  & \color{red}  FP \\
-201295312.01 & $0.04$ &  Y & $7.5\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $7.5\times10^{-4}$ & Candidate\tablenotemark{a}  \\
-201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.2\times10^{-3}$ & $0.22$ & $2.2\times10^{-3}$ & Planet  \\
-201338508.02 & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.6\times10^{-4}$ & $0.22$ & $1.6\times10^{-4}$ & Planet  \\
-201367065.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.0\times10^{-4}$ & $0.22$ & $2.0\times10^{-4}$ & Planet\tablenotemark{c}  \\
+201208431.01 & $0.51$ &  - & $< 10^{-4}$ & $8.1\times10^{-4}$ & $< 10^{-4}$ & $0.21$ & $8.1\times10^{-4}$ & Planet  \\
+ \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $0.998$  & \color{red}  $1.7\times10^{-3}$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $1.000$  & \color{red}  FP \\
+201295312.01 & $0.04$ &  Y & $1.4\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $1.4\times10^{-4}$ & Candidate\tablenotemark{a}  \\
+201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $2.9\times10^{-3}$ & $< 10^{-4}$ & $0.22$ & $2.9\times10^{-3}$ & Planet  \\
+201338508.02 & $0.33$ &  - & $< 10^{-4}$ & $1.7\times10^{-4}$ & $< 10^{-4}$ & $0.22$ & $1.7\times10^{-4}$ & Planet  \\
+201367065.01 & $0.15$ &  - & $< 10^{-4}$ & $1.1\times10^{-4}$ & $< 10^{-4}$ & $0.22$ & $1.1\times10^{-4}$ & Planet\tablenotemark{c}  \\
 201367065.02 & $0.67$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Planet\tablenotemark{c}  \\
-201384232.01 & $0.44$ &  - & $2.1\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.19$ & $2.2\times10^{-3}$ & Planet  \\
-201393098.01 & $0.52$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $6.9\times10^{-4}$ & $0.21$ & $6.9\times10^{-4}$ & Planet  \\
-201403446.01 & $0.18$ &  Y & $1.2\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $1.2\times10^{-3}$ & Candidate\tablenotemark{a}  \\
-201445392.01 & $0.26$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.5\times10^{-3}$ & $0.20$ & $2.6\times10^{-3}$ & Planet  \\
-201445392.02 & $0.18$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.032$ & $0.22$ & $0.032$ & Candidate  \\
-201465501.01 & $0.68$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $5.4\times10^{-3}$ & $0.22$ & $5.4\times10^{-3}$ & Planet  \\
-201505350.01 & $2.69$ &  - & $8.5\times10^{-3}$ & $< 10^{-4}$ & $2.5\times10^{-3}$ & $0.09$ & $0.011$ & Planet\tablenotemark{d}  \\
-201505350.02 & $0.70$ &  - & $1.6\times10^{-3}$ & $< 10^{-4}$ & $4.8\times10^{-4}$ & $0.05$ & $2.1\times10^{-3}$ & Planet\tablenotemark{d}  \\
-201546283.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
-201549860.01 & $0.18$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.0\times10^{-3}$ & $0.21$ & $2.0\times10^{-3}$ & Candidate\tablenotemark{a}  \\
- \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $1.5\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $1.5\times10^{-3}$  & \color{red}  FP\tablenotemark{b} \\
-201565013.01 & $1.69$ &  - & $0.802$ & $0.058$ & $5.9\times10^{-3}$ & $0.07$ & $0.866$ & Candidate  \\
- \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.668$  & \color{red}  $0.332$  & \color{red}  $2.4\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $1.000$  & \color{red}  FP \\
-201577035.01 & $0.14$ &  Y & $7.5\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.10$ & $7.6\times10^{-4}$ & Planet  \\
-201596316.01 & $0.45$ &  - & $1.0\times10^{-3}$ & $< 10^{-4}$ & $5.9\times10^{-3}$ & $0.07$ & $6.9\times10^{-3}$ & Planet  \\
-201613023.01 & $0.08$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet  \\
-201617985.01 & $0.27$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.013$ & $0.18$ & $0.013$ & Candidate  \\
-201629650.01 & $0.43$ &  - & $1.1\times10^{-3}$ & $< 10^{-4}$ & $3.4\times10^{-4}$ & $0.21$ & $1.4\times10^{-3}$ & Planet  \\
-201635569.01 & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.5\times10^{-3}$ & $0.05$ & $4.5\times10^{-3}$ & Planet  \\
- \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.924$  & \color{red}  $0.076$  & \color{red}  $1.0\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $1.000$  & \color{red}  FP \\
-201702477.01 & $0.70$ &  - & $0.150$ & $2.4\times10^{-3}$ & $2.4\times10^{-3}$ & $0.06$ & $0.155$ & Candidate  \\
-201736247.01 & $0.42$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.1\times10^{-4}$ & $0.19$ & $2.7\times10^{-4}$ & Planet  \\
-201754305.01 & $0.65$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.4\times10^{-3}$ & $0.22$ & $1.4\times10^{-3}$ & Planet  \\
-201754305.02 & $0.38$ &  - & $1.1\times10^{-4}$ & $< 10^{-4}$ & $7.8\times10^{-4}$ & $0.22$ & $8.9\times10^{-4}$ & Planet  \\
- \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.980$  & \color{red}  $2.5\times10^{-3}$  & \color{red}  $7.3\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.984$  & \color{red}  FP \\
-201828749.01 & $0.39$ &  Y & $0.242$ & $< 10^{-4}$ & $1.5\times10^{-3}$ & $0.07$ & $0.244$ & Candidate  \\
- \color{red} 201855371.01  & \color{red}  $0.62$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.925$  & \color{red}  $0.01$  & \color{red}  $0.925$  & \color{red}  FP \\
+201384232.01 & $0.44$ &  - & $8.4\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.07$ & $8.5\times10^{-3}$ & Planet  \\
+201393098.01 & $0.52$ &  - & $< 10^{-4}$ & $1.1\times10^{-3}$ & $< 10^{-4}$ & $0.05$ & $1.1\times10^{-3}$ & Planet  \\
+201403446.01 & $0.18$ &  Y & $4.8\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.19$ & $4.9\times10^{-4}$ & Candidate\tablenotemark{a}  \\
+201445392.01 & $0.26$ &  - & $< 10^{-4}$ & $2.1\times10^{-3}$ & $< 10^{-4}$ & $0.18$ & $2.1\times10^{-3}$ & Planet  \\
+201445392.02 & $0.18$ &  - & $< 10^{-4}$ & $0.019$ & $< 10^{-4}$ & $0.21$ & $0.019$ & Candidate  \\
+201465501.01 & $0.68$ &  - & $< 10^{-4}$ & $5.8\times10^{-3}$ & $< 10^{-4}$ & $0.21$ & $5.8\times10^{-3}$ & Planet  \\
+201505350.01 & $2.69$ &  - & $< 10^{-4}$ & $5.6\times10^{-3}$ & $< 10^{-4}$ & $0.04$ & $5.6\times10^{-3}$ & Planet\tablenotemark{d}  \\
+201505350.02 & $0.70$ &  - & $< 10^{-4}$ & $1.6\times10^{-4}$ & $< 10^{-4}$ & $0.07$ & $1.7\times10^{-4}$ & Planet\tablenotemark{d}  \\
+201546283.01 & $0.15$ &  - & $7.0\times10^{-4}$ & $2.6\times10^{-4}$ & $< 10^{-4}$ & $0.00$ & $9.6\times10^{-4}$ & Candidate\tablenotemark{a}  \\
+201549860.01 & $0.18$ &  - & $< 10^{-4}$ & $0.026$ & $< 10^{-4}$ & $0.04$ & $0.026$ & Candidate  \\
+201565013.01 & $1.69$ &  - & $0.783$ & $7.3\times10^{-3}$ & $0.063$ & $0.07$ & $0.853$ & Candidate  \\
+ \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.822$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.174$  & \color{red}  $0.00$  & \color{red}  $0.996$  & \color{red}  FP \\
+201577035.01 & $0.14$ &  Y & $4.4\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.07$ & $4.4\times10^{-4}$ & Planet  \\
+201596316.01 & $0.45$ &  - & $< 10^{-4}$ & $1.2\times10^{-3}$ & $< 10^{-4}$ & $0.06$ & $1.2\times10^{-3}$ & Planet  \\
+201613023.01 & $0.08$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.18$ & $< 10^{-4}$ & Planet  \\
+201617985.01 & $0.27$ &  - & $< 10^{-4}$ & $0.012$ & $< 10^{-4}$ & $0.18$ & $0.012$ & Candidate  \\
+201629650.01 & $0.43$ &  - & $5.9\times10^{-4}$ & $2.0\times10^{-4}$ & $< 10^{-4}$ & $0.13$ & $7.8\times10^{-4}$ & Planet  \\
+201635569.01 & $0.79$ &  - & $< 10^{-4}$ & $4.9\times10^{-3}$ & $< 10^{-4}$ & $0.05$ & $4.9\times10^{-3}$ & Planet  \\
+ \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.896$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.104$  & \color{red}  $0.00$  & \color{red}  $1.000$  & \color{red}  FP \\
+201702477.01 & $0.70$ &  - & $0.137$ & $1.2\times10^{-3}$ & $6.6\times10^{-3}$ & $0.05$ & $0.145$ & Candidate  \\
+201736247.01 & $0.42$ &  - & $4.8\times10^{-4}$ & $2.1\times10^{-4}$ & $< 10^{-4}$ & $0.19$ & $6.9\times10^{-4}$ & Planet  \\
+201754305.01 & $0.65$ &  - & $1.0\times10^{-4}$ & $1.4\times10^{-3}$ & $< 10^{-4}$ & $0.21$ & $1.5\times10^{-3}$ & Planet  \\
+201754305.02 & $0.38$ &  - & $2.3\times10^{-4}$ & $9.9\times10^{-4}$ & $< 10^{-4}$ & $0.19$ & $1.2\times10^{-3}$ & Planet  \\
+ \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.968$  & \color{red}  $1.3\times10^{-3}$  & \color{red}  $7.2\times10^{-3}$  & \color{red}  $0.00$  & \color{red}  $0.976$  & \color{red}  FP \\
+201828749.01 & $0.39$ &  Y & $0.644$ & $3.8\times10^{-4}$ & $< 10^{-4}$ & $0.01$ & $0.645$ & Candidate  \\
+201855371.01 & $0.62$ &  - & $< 10^{-4}$ & $8.7\times10^{-3}$ & $< 10^{-4}$ & $0.01$ & $8.7\times10^{-3}$ & Planet  \\
 201912552.01 & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet  \\
- \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $1.000$  & \color{red}  $0.00$  & \color{red}  $1.000$  & \color{red}  FP\tablenotemark{b}
 \enddata

### 2015-06-22 fpp/write_fpptable.py

@@ -16,6 +16,8 @@ CAND_OVERRIDE = ['201295312.01',
                  #'201702477.01',
                  '201828749.01',
                  '201549860.01']
+#SKIP = []
+SKIP = ['201929294.01','201555883.01']
 
 def note(key):
     return '\tablenotemark{{}}'.format(key)
@@ -96,6 +98,9 @@ for f in folders:
     epic_id = int(m.group(1))
     i = int(m.group(2))
     cand_name = '{}.{:02.0f}'.format(epic_id, i)
+
+    if cand_name in SKIP:
+        continue
 
     line = '{} & '.format(cand_name)  # EPIC, Cand. Num.
     line += '${:.2f}$ & '.format(max_secondary(epic_id,i)*1e3) #max(delta_sec)

### 2015-06-22 fpp/write_fpptable.py
edited fpp table

@@ -132,9 +132,9 @@ for f in folders:
             disp = 'Candidate ' 
 
         if epic_id==201505350:
-            disp = r'Planet\tablenotemark{d} '
-        if epic_id==201367065:
             disp = r'Planet\tablenotemark{c} '
+        if epic_id==201367065:
+            disp = r'Planet\tablenotemark{b} '
     line += '{} '.format(disp)  #Disposition
     if f != folders[-1]:
         line += '\\\\'
@@ -161,9 +161,8 @@ below 1\% threshold.}
 \tablenotetext{3}{Integrated planet occurrence rate assumed between 0.7$\times$ and 1.3$\times$ the candidate radius}
 \tablenotetext{a}{Despite low FPP, returned to candidate status 
 out of abundance of caution due to secondary star detection within or near photometric aperture.}
-\tablenotetext{b}{Declared a false positive due to noise modeling systematics (see \S\ref{sec:systematics}).}
-\tablenotetext{c}{Identified as planets by \citet{Crossfield15}.}
-\tablenotetext{d}{Identified as planets by \citet{Armstrong15b}.}
+\tablenotetext{b}{Identified as planets by \citet{Crossfield15}.}
+\tablenotetext{c}{Identified as planets by \citet{Armstrong15b}.}
 \end{deluxetable*}
 """)
 

### 2015-06-22 fpp/write_fpptable.py
fpp table note edits

@@ -154,8 +154,7 @@ Candidates are declared to be validated planets if FPP $< 0.01$.
 EB, BEB, and HEB refer to the three considered astrophysical 
 false positive scenarios, and the relative probability of 
 each is listed in the appropriate column.  Planets previously 
-identified in the literature are marked as planets even if FPP is not 
-below 1\% threshold.}
+identified in the literature are marked.}
 \tablenotetext{1}{Maximum depth of potential secondary eclipse signal.}
 \tablenotetext{2}{Whether adaptive optics observation is presented in this paper.}
 \tablenotetext{3}{Integrated planet occurrence rate assumed between 0.7$\times$ and 1.3$\times$ the candidate radius}

### 2015-06-22 ms.tex
fp table edits

@@
 interpolation tool for the fitting of stellar models to photometric or spectroscopic
-parameters.
+parameters \citep{isochrones}.
 This software does trilinear interpolation in mass--age--\feh\ space for any

### 2015-06-22 table_fpp.tex
edited fpp table
fpp table note edits
fp table edits

@@
 201549860.01 & $0.18$ &  - & $< 10^{-4}$ & $0.026$ & $< 10^{-4}$ & $0.04$ & $0.026$ & Candidate  \\
+ \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}   --  & \color{red}   --  & \color{red}   --  & \color{red}   --  & \color{red}  --  & \color{red}  FP\tablenotemark{b} \\
 201565013.01 & $1.69$ &  - & $0.783$ & $7.3\times10^{-3}$ & $0.063$ & $0.07$ & $0.853$ & Candidate  \\
@@
 201912552.01 & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet  \\
+ \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}   --  & \color{red}   --  & \color{red}   --  & \color{red}   --  & \color{red}  --  & \color{red}  FP\tablenotemark{b}
 \enddata
@@
 each is listed in the appropriate column.  Planets previously 
-identified in the literature are marked as planets even if FPP is not 
-below 1\% threshold.}
+identified in the literature are marked.}
 \tablenotetext{1}{Maximum depth of potential secondary eclipse signal.}

### 2015-06-22 fpp/write_fpptable.py

@@ -16,8 +16,8 @@ CAND_OVERRIDE = ['201295312.01',
                  #'201702477.01',
                  '201828749.01',
                  '201549860.01']
-#SKIP = []
-SKIP = ['201929294.01','201555883.01']
+SKIP = []
+#SKIP = ['201929294.01','201555883.01']
 
 def note(key):
     return '\tablenotemark{{}}'.format(key)
@@ -111,11 +111,17 @@ for f in folders:
         line += ' - & '
 
     for val in [eb,beb,heb]:
-        val = float(val)
-        line += '{} & '.format(prob_entry(val))  #pEB, pBEB, pHEB
-    line += '${:.2f}$ & '.format(float(fp)) #fp_specific
-    line += '{} & '.format(prob_entry(FPP)) #FPP
-    FPP = float(FPP)
+        if cand_name in FP_OVERRIDE:
+            line += ' -- & '
+        else:
+            val = float(val)
+            line += '{} & '.format(prob_entry(val))  #pEB, pBEB, pHEB
+    if cand_name in FP_OVERRIDE:
+        line += ' -- & -- & '
+    else:
+        line += '${:.2f}$ & '.format(float(fp)) #fp_specific
+        line += '{} & '.format(prob_entry(FPP)) #FPP
+        FPP = float(FPP)
     if cand_name in FP_OVERRIDE:
         disp = 'FP '
         if cand_name in ['201555883.01', '201929294.01']:
@@ -132,9 +138,9 @@ for f in folders:
             disp = 'Candidate ' 
 
         if epic_id==201505350:
-            disp = r'Planet\tablenotemark{c} '
+            disp = r'Planet\tablenotemark{d} '
         if epic_id==201367065:
-            disp = r'Planet\tablenotemark{b} '
+            disp = r'Planet\tablenotemark{c} '
     line += '{} '.format(disp)  #Disposition
     if f != folders[-1]:
         line += '\\\\'
@@ -160,8 +166,9 @@ identified in the literature are marked.}
 \tablenotetext{3}{Integrated planet occurrence rate assumed between 0.7$\times$ and 1.3$\times$ the candidate radius}
 \tablenotetext{a}{Despite low FPP, returned to candidate status 
 out of abundance of caution due to secondary star detection within or near photometric aperture.}
-\tablenotetext{b}{Identified as planets by \citet{Crossfield15}.}
[…]

### 2015-06-22 ms.tex
tdm edits

@@
 either spectroscopic, photometric,
-or both, to define a likelihood function that may be sampled in
-an MCMC chain:
+or both, to define a likelihood function to be sampled:
 \begin{equation}
@@
 extinction as one of our physical parameters.
-For each star's position on the sky, we retrieve the calculated extinction at an infinite distance
-along that line of sight from the NASA/IPAC Extragalactic Database (NED), which reports the
-\citet{Schlafly11} recalibration of the \citet{Schlegel98} extinction map as measured by
-COBE/DIRBE and IRAS/ISSA.
-The NED database returns the extinction in all relevant bandpasses except those used by
-WISE, assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}.
+%For each star's position on the sky, we retrieve the calculated extinction at an infinite distance
+%along that line of sight from the NASA/IPAC Extragalactic Database (NED), which reports the
+%\citet{Schlafly11} recalibration of the \citet{Schlegel98} extinction map as measured by
+%COBE/DIRBE and IRAS/ISSA.
+%The NED database returns the extinction in all relevant bandpasses except those used by
+%WISE, assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}.
 We include the WISE bandpasses by applying the relative extinction values between
@@
 In each step of our fitting process, we draw a value for $A_V$, calculate the expected extinction
-in all bandpasses $A_X$, and then measure the likelihood of our model stellar fit to the
-observed apparent magnitudes.
-We apply a uniform prior ranging from zero to the obtained maximum extinction value and
-marginalize over extinction in our final determination of stellar parameters. }
+in all bandpasses $A_X$ assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}, 
+and then measure the likelihood of our model stellar fit to the observed apparent magnitudes.
+We apply a uniform prior ranging from zero to a maximum extinction value of 0.2 
+(a conservative upper limit for a field at such high Galactic latitude), and
+marginalize over extinction in our final determination of stellar parameters.}
 

### 2015-06-22 ms.tex
tdm edits

@@
 In this work, we use
-\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
+\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}} \citep{vespa},
 a new publicly available, general-purpose implementation

### 2015-06-22 ms.tex
changed numbers
updated numbers

@@
 
-\newcommand{\Nfp}{7}
-\newcommand{\Nvalidated}{19}
+\newcommand{\Nfp}{6}
+\newcommand{\Nvalidated}{21}
 \newcommand{\Nlimbo}{9} %adds up to 36
-\newcommand{\Nvalnew}{16} % 4 previously validated
+\newcommand{\Nvalnew}{17} % 4 previously validated
 
@@
 We statistically validate \Nvalidated\ of the 36 candidates as bona fide planets, and we
-identify \Nfp\ as false positives.
-Of these planets, 3 have been previously validated in other works, while \Nvalnew\ are
+identify \Nfp\ as false positives, including two systematic false alarms.
+Of the planets, 4 have been previously validated in other works, while \Nvalnew\ are
 validated here for the first time.

### 2015-06-22 ms.tex
tdm edit

@@
 We apply a uniform prior ranging from zero to a maximum extinction value of 0.2 
-(a conservative upper limit for a field at such high Galactic latitude), and
+(a generous upper limit for a field at such high Galactic latitude), and
 marginalize over extinction in our final determination of stellar parameters.}
